### 2021-04-18 old/old_isipta.tex
Initial Overleaf Import

\documentclass[pmlr,twocolumn,a4paper,10pt]{jmlr}
% \documentclass[pmlr,twocolumn,10pt]{jmlr} % useful when printing your own Letter copy; should not impact layout; do not use for submission
% This class automatically loads the following packages:
% amsmath, amssymb, natbib, graphicx, xcolor, url, algorithm2e, hyperref
  \citestyle{plain} % comment to get author-year; see the natbib docs for more options
\usepackage{isipta2021}
% This style file
% * sets the inputencoding to utf8 (which should be used),
% * loads mathtools (fixes for amsmath) and
% * the font packages textcomp, mathptmx, helvet, and courier (so no font packages should be loaded) and neither should font size be changed
%
%% Choose your variant of English; be consistent
\usepackage[american]{babel}
\usepackage{algorithm,algorithmic,bm}
% \usepackage[british]{babel}
%% Suggested packages, as needed:
% \usepackage{siunitx} % for proper typesetting of numbers and units
\usepackage{booktabs} % commands to create good-looking tables
% \usepackage{rotating} % for sideways figures and tables
% \usepackage{longtable} % for long tables
\usepackage{tikz} % nice language for creating drawings and diagrams
%% Self-defined macros
\newcommand{\swap}[3][-]{#3#1#2} % just an example
%% Frontmatter
% Authors: DO NOT EDIT
\jmlrworkshop{ISIPTA 2021}
\title[Short Title]{% [Short title] can be omitted if title is short enough
  Credal Adaptive Testing
  %Title in Title Case;\titlebreak~ % tilde needed to get space in short title
  %Use the Same Style for Your Section Titles
}

\author{% Authors are listed one per line and grouped per affiliation
  \Name{permutation of Claudio/Giorgia/Francesca/Alessandro}\\ % Accented characters require some attention
  \addr IDSIA
  %\AND
  %\Name{Andrés Cano}\Email{acu@decsai.ugr.es}\\
  %  \Name{Serafín Moral}\Email{smc@decsai.ugr.es}\\
  %\addr Computer Science and Artificial Intelligence, University of Granada, Spain
  %\AND
  %\Name{Jasper {De Bock}}\Email{Jasper.DeBock@UGent.be}\\
  %\addr Electronics and Information Systems, Ghent University, Belgium
}

\begin{document}
\maketitle

\begin{abstract}% No length restrictions, but keep things reasonable
An \emph{adaptive} test is a computer-based testing technique which adjusts the sequence of questions on the basis of the estimated ability level of the test taker. We suggest the use of \emph{credal networks}, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers. Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge. The counterpart is a less straightforward identification of the information-theoretic measure controlling the question-selection and the test-stopping criteria. We elaborate on these issues and propose a sound and computationally feasible procedure. Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
\end{abstract}
\begin{keywords}% Keywords provide context for readers, so put in up to about half a dozen
  keyword, mot clé, Williams-coherence, trefwoord, imprecise Markov chain
\end{keywords}

\section{Single Skill Model}
Let us introduce the discussion by means of a simple example modelling the knowledge level of a student in a particular domain. In order to evaluate such level a number of questions can be asked to the student. We describe the knowledge level (or skill) of the student by means of a single variable $S$. We assume $S$ to be a discrete, ordinal, variable, whose $m$ states $\mathcal{S}:=(s^{(0)},\ldots,s^{(m-1)})$ can be intended as increasing knowledge levels in that domain. Regarding the questions, we initially describe them as Boolean variables, whose true state correspond to a correct answer to the question, while no distinctions between the possible wrong answers are considered.\footnote{Dedicated discussion about abstention.} Let $Q$ with $\mathcal{Q}:=(q,\overline{q})$ denote a generic question we ask to the student. A repository of $n$ questions $\bm{Q}$ is assumed to be available. A \emph{testing} algorithm is a procedure deciding which question and how many questions from $\bm{Q}$ should be asked to the student, on the basis of her previous answers. Algorithm X provides an abstract description of xxx.

\begin{algorithm}[htp!]
    \caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple}}
    \begin{algorithmic}[1]
        \FOR {$s\in\bm{S}$}
        \WHILE{ $h > h^*$}
        \STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
        \STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $h \gets H[P(S|\bm{e}]$
        \ENDWHILE
        \ENDFOR
        \STATE {\bf return} $\arg\max P(s|\bm{e})$
    \end{algorithmic}
\end{algorithm}

\newpage

Let $S$ denote an ordinal variable with $m$ states, denoting the knowledge level of a student with respect to a particular knowledge domain. Let $Q$ denote a question to be

\section{Brainstorming}

\subsection{Linear Programs for Credal Mode}

Given the Boolean question $Q$ and the Boolean skill $S$, we use the score:

\begin{equation}
\sigma_Q := \max_{P\in K} \left[ 
\max \{ P(S=0,Q=0) , P(S=1,Q=0) \}  + \max \{ P(S=0,Q=1),P(S=1,Q=1)\}
\right]
\end{equation}

\begin{theorem}
\begin{equation}
\max_{x}  \max \{ f(x) , g(x) \}  
=
 \max \{ \max_{x'} f(x') , \max_{x''} g(x'') \} 
\end{equation}
Let 
$$y^{*}:=\max_x \max\{f(x),g(x)\}$$
$$y^{**}:= \max \{ \max_{x'} f(x') , \max_{x''} g(x'') \}$$
Say for instance that $y^{**}=max_x f(x)$ and let $x^{**}:=\arg\max_x f(x)$. Thus:
$$f(x^{**})\geq \max_{x'} g(x) \geq g(x^{**})$$

Let $x^{*}:= \arg\max_x \max\{f(x),g(x)\}$. 
It cannot be $y^{*}:=g(x^{*})$ as this would imply $g(x^{*}) \geq f(x^{*})$

%Assume ad absurdum $y^{*}\neq y^{**}$.

If $y^{*}:=f(x^{*})$ we should have $y^{*}=y^{**}$.
Vice versa,

or
%$y^{*}:=g(x^{*})$. In the first case 
\end{theorem}

\subsection*{Pseudocode}
Let us first specify the inputs:
\begin{itemize}
\item Let $\bm{S}:=(S_1,\ldots,S_N)$ denote the set of skills in the model. We describe a \emph{student} as a joint observation $\bm{s}$ of the skills.
\item Let $M$ denote the network \emph{skeleton}, i.e., the model over the skills only
\item A question $Q$ is a binary variables with states right and wrong
\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this skill
\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
\item Let $n_q$ be the maximum number of questions we might ask for each skill
\end{itemize}
The algorithm works as follows.
\begin{enumerate}
\item For eachLet $\bm{S}:=(S_1,\ldots,S_N)$ denote the set of skills in the model
\item Let $M$ denote the network \emph{skeleton}, i.e., the model over the skills only
\item A question $Q$ is a binary variables with states right and wrong
\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this skill
\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
\item Let $n_q$ be the maximum number of questions we might ask for each skill
\end{enumerate}

\begin{algorithm}[htp!]
    \caption{Single skill, precise model\\
    a model (BN, skeleton) $M$ over the skills only
    \\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
    the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
    the student answer models $\{\tilde{P}(Q^j|S)\}$\\
    an entropy threshold $h^*$,\\
    a score function for questions $\gamma$
    \label{alg:simple}}
    \begin{algorithmic}[1]
    \FOR {$i\gets\{1,\ldots,n\}$}
    \STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets (M,\mathcal{Q},\emptyset,\emptyset)$
    \WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
    \STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(M',Q,\bm{e})$
    \STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
    \STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
    \STATE{$q^* \gets \mathrm{sampling} \sim \tilde{P}(Q^*|s^i)$}
    \STATE $M' \gets \mathrm{addChild}(M',Q,S,P(Q|S))$
    \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
    \STATE $h \gets H[P_{M'}(S|\bm{e})]$
    \ENDWHILE
    \STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P_{M'}(s|\bm{e})$
    \ENDFOR
    \STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
    \end{algorithmic}
\end{algorithm}
Three possible scores:
\begin{eqnarray}
    \gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
    \gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
    \gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
\end{eqnarray}

\textcolor{red}{Maybe, instead of (3) I would use a known measure of qualitative variation (\url{https://en.wikipedia.org/wiki/Qualitative_variation}) which extend easily to non binary answers, e.g., the variation ratio ($1-\max_q(P(q))$) or the M1 Gibb's index also known as coefficient of unalikeability and somehow related to the variance (it is the variance in the binary case): $M1 = 1-\sum_q P(q)^2$, or even the entropy, which is not so difficult to compute for $P(Q)$. They are all equivalent in the binary case, as they are all monotonic function of $\max_q(P(q))$ only. }

\begin{algorithm}[htp!]
    \caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
    the credal CPTs of the questions in $\mathcal{Q}$, i.e., $\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
    an upper entropy threshold $\overline{h}^*$,\\
    a score function for questions $\sigma$
    \label{alg:simple}}
    \begin{algorithmic}[1]
    \FOR {$i\gets\{1,\ldots,n\}$}
    \STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets (\mathcal{Q},\emptyset,\emptyset)$
    \WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
    \STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
    \STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
    \STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
    \STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
    \STATE $\mathrm{addChild}(Q,S,P(Q|S))$
    \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
    \STATE $h \gets H[P(S|\bm{e})]$
    \ENDWHILE
    \STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
    \ENDFOR
    \STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
    \end{algorithmic}
\end{algorithm}
Three possible scores:
\begin{eqnarray}
    \gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
    \gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
    \gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
\end{eqnarray}

\begin{algorithm}[htp!]
    \caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple}}
    \begin{algorithmic}[1]
        \FOR {$s\in\bm{S}$}
        \WHILE{ $h > h^*$}
        \STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
        \STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $h \gets H[P(S|\bm{e}]$
        \ENDWHILE
        \ENDFOR
        \STATE {\bf return} $\arg\max P(s|\bm{e})$
    \end{algorithmic}
\end{algorithm}

\subsection*{Formulae}
Let us define the functions, all defined for $x\in [0,1]$, apart from $f$ defines for each $x\geq 0$:
\begin{eqnarray}
f(x)&:=& \frac{1}{1+x},\,,\\
h(x)&:=&-x \cdot \log_2 x - (1-x)  \cdot \log_2 (1-x)\,,\\
l(x)&:=&\frac{x}{1-x}\,,\\
m(x)&:=&2 \max\{x,1-x\}\,,\\
i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
\end{eqnarray}

Derivatives:
\begin{eqnarray}
f'(x)&:=& -\frac{1}{(1+x)^2},\,,\\
h'(x)&:=&\log_2 \frac{1-x}{x}\,\\
G(x) &:=& h \circ f(x)\,\\
G'(x) &:=& h[f(x)] f'(x)=-\frac{\log_2\frac{1-f(x)}{f(x)}}{(1+x)^2}\,\\
G'(x) &:=& -\frac{\log_2 x}{(1+x)^2}\,\\
l(x)&:=&\frac{x}{1-x}\,,\\
m(x)&:=&2 \max\{x,1-x\}\,,\\
i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
\end{eqnarray}

A few remarks. Function $f$ is a monotonically decreasing function with values in $[0,1]$. Function $h(x)$ corresponds to the entropy of a mass function over a Boolean variable with a probability equal to $x$. On the extreme points of its domain, we take the limit value, i.e., zero. The function is unimodal and achieve its maximum on  $x=\frac{1}{2}$. Function $l$ is the popular \emph{logit} function, it is monotonically increasing function of $x$ and $l(1-x)=l(x)^-1$. Function $m(x)$ is $x$ for $x\geq \frac{1}{2}$ and $1-x$ otherwise. 
Exactly as $h$, functions $m$ and $\tilde{i}_\epsilon$, for each $\epsilon>0$, have the same (zero) value for $x=0$ and $x=1$, being all unimodal with maximum in $x=\frac{1}{2}$.
Finally, the popular Gumbel's trick implies:
\begin{equation}
\lim_{\epsilon \to 0} i_\epsilon(x)= 
\lim_{\epsilon \to 0} \tilde{i}_\epsilon(x)
= m(x)\,.
\end{equation}
\subsection*{Another Formula}
Consider a PMF $P(X)$. Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$. Let $\mathcal{P}$ denote the set of all PMFs with the same $p^*:=P(x^*)$. The most entropic PMF in $\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq x^*$ where $m:=|\mathcal{X}|$. While the least entropic is the one with a $x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the other masses equal to zero. These two bounds on the entropy are therefore:
\begin{eqnarray}
\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m \frac{1-p^*}{m-1}\,,\\
\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m (1-p^*)\,.
\end{eqnarray}
This:
\begin{equation}
\overline{h}-\underline{h}=(1-p^*) \log_m (m-1)\,,
\end{equation}
The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being zero for binary variables.

\subsection*{Toy Example}
Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The informativeness score we assign two the question is
\begin{equation}
\sigma_Q = H[S|Q]:=H[S|q_0]P(q_0)+H[S|q_1]P(q_1)\,.
\end{equation}
We have
\begin{equation}
P(q_1)=\pi_1 p + \pi_0 (1-p)
\end{equation}
while $P(q_0)=1-P(q_1)$ and also
\begin{equation}
P(s_1|q_1)=\frac{\pi_1 p}{\pi_1 p + \pi_0 (1-p)}=\frac{1}{1+\frac{\pi_0(1-p)}{\pi_1 p}}
\end{equation}
and
\begin{equation}
P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}} 
\end{equation}
while $P(S=0|Q=1)$ by normalization. Accordingly:
\begin{multline}
\sigma_Q(p,\pi_0,\pi_1)=\\
h \circ f[\gamma/l(p)] \cdot t +
h \circ f[\gamma'/l(p)] \cdot (1-t)\,
%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
\end{multline}
where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 p + \pi_0 (1-p)$.

{\color{blue}{In other words:
$\sigma_Q(p,\pi_0,\pi_1):= G(\frac{1-p}{p} \frac{1-\pi_0}{1-\pi_1}) (1-p) + 
G(\frac{1-p}{p} \frac{\pi_0}{\pi_1}) p$}}

An alternative score might be achieved by replacing $h$ with $m$, i.e.,
\begin{equation}
\sigma_Q' := 
m \circ f[\gamma/l(p)] \cdot t +
m \circ f[\gamma'/l(p)] \cdot (1-t)\,
\end{equation}
As $f$ is monotone, we can commute $m$ and $f$ *** explain ***, i.e.,
\begin{equation}
\sigma_Q' := 
f \circ m[\gamma/l(p)] \cdot t +
f \circ m[\gamma'/l(p)] \cdot (1-t)\,
\end{equation}
with, as $\gamma>0$. $f \circ m[\gamma/l(p)] = f[\gamma m(l(p))]$
We can similarly define another score $\sigma_Q''$ based on $\tilde{i}_\epsilon$.
\subsection*{Explicit maximization}
$$H[S|Q]\simeq \sigma_Q' = \sum_q P(s^*(q)|q) P(q)$$
where $s^*(q):=\arg\max_s P(s|q)$. 
$$\sigma_Q'= \sum_q P(s^*(q),q) = \sum_q P(s^*(q) P(q|s^*(q))$$
Note that, if $s^*(q)$ is the same for each $q$, the score just corresponds to $P(s^*)$. In other words, the score is flat is each answer gives the same most likely skill level *** reasonable ***. Let us move to an imprecise setting and intend the $s^*$ state as
$s^*(q):=\arg\max_s \overline{P}(s|q)$. The objective function is a linear combination of $P(s*(q)$ whose coefficient can be optimized independently. Overall, this corresponds to a linear programming task.
$$\max_s \overline{P}(s,q) = \max_s \max_P P(s) P(q|s) = \max_s \overline{P}(s) \overline{P}(q|s)$$

\subsection*{Francesca's comments}

Comment1: This sentence is not clear to me:  "as $\gamma>0$. $f \circ m[\gamma/l(p)] = f[\gamma m(l(p))]$".\\
Comment2: How shall we use the Gumbel's trick

Comment 3: Below I obtain something that looks different to me, but maybe it is equivalent.

\begin{equation}
P(s_1|q_1)=\frac{\pi_1 p}{P(q_1)}
\end{equation}

\begin{multline}
\sigma_Q(p,\pi_0,\pi_1)=\\
m\left(\frac{\pi_1 p}{P(q_1)}\right) \cdot P(q_1)  +
m\left(\frac{(1-\pi_1) p}{1-P(q_1)}\right) \cdot (1-P(q_1))\,
\end{multline}

But, as $P(q_1)\geq 0$, then
\begin{multline}
m\left(\frac{\pi_1 p}{P(q_1)}\right) =\\
2max\left(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \right) =\\
2max\left(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \right) =\\
\frac{2}{P(q_1)}max\left(\pi_1 p,\pi_0(1- p)\right).\\
\end{multline}

Similarly, as $1-P(q_1)\geq 0$, 
\begin{multline}
m\left(\frac{(1-\pi_1) p}{1-P(q_1)}\right) =\\
\frac{2}{1-P(q_1)}max\left((1-\pi_1) p,(1-\pi_0)(1- p)\right),\\
\end{multline}

so that,

\begin{multline}
\sigma_Q(p,\pi_0,\pi_1)= \\
2 max\{\pi_1 p, \pi_0 (1-p)\}+
2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
\end{multline}

Comment 4: The optimisation in the credal setting shouldn't be the following one?

$$\max_P [\max_s P(s,q=0)+\max_s P(s,q=1)]$$

 $\P(s,q=0)$ and $P(s,q=1)$ are both functions of $p, \pi_0,$ and $\pi_1$ so I do not think we can split the optimization

$$\max_P \max_s P(s,q=0)+\max_P\max_s P(s,q=1)$$

However, it could be a reasonable approximation. Then, we can switch the optimization over $P$ and $s$ because they are both max, and obtain: 
$$\max_s \overline{P}(s)\overline{P}(q=0|s)+\max_s  \overline{P}(s)\overline{P}(q=1|s)$$.

If instead we are looking for the minimum over P, we cannot switch the optimization over $P$ and $s$:
$$\min_P \max_s P(s,q) \neq \max_s \min_P P(s,q)$$.

However I think we can split the optimization into 4 quadratic optimizations.
Let's use the following parametrization:
\begin{multline}\label{eq:minimization}
\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
2\min_{p,\pi_0,\pi_1} \left( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \right) \approx \\
2\left(\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \right) 
\end{multline}

Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It can be written as
$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
where 
\begin{multline}
\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
\begin{array}{ll}
\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
~&\underline{x} \leq x\leq \overline{x}\\ 
\end{array}
\end{multline}
and 
\begin{multline}
\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
\begin{array}{ll}
\text{subject to} & \pi_1 p < \pi_0 (1-p)
~&\underline{x} \leq x\leq \overline{x}\\ 
\end{array}
\end{multline}

where the constraint $x = (\pi_0, \pi_1 ,p)$.

In general, let $N_s$ be the number of skill levels and $N_q$ the number of possible answers, then the number of quadratic optimizations to solve should be equal to $N_s\cdot N_q$.

In this two dimensional example, we might not need the approximation above as the minimization in \ref{eq:minimization} can be written as $\min_{i=1:4}(\tilde{P}_1)$, where

\begin{multline}
\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
\begin{array}{ll}
\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
~&\underline{x} \leq x\leq \overline{x}\\ 
\end{array}
\end{multline}
and so on. However, in this case, the number of optimizations to solve should be $N_s^{N_q}$, that is, it grows exponentially with  $N_q$.

\paragraph{*** Alessandro's reformulation ***}
\begin{equation}
\begin{split}
\text{min} \displaystyle \, \pi_1 \cdot p \\
\text{subject to} & \displaystyle \pi_1 p > \pi_0 (1-p)\\
                 &\displaystyle \underline{\pi}_0 \leq \pi_0 \leq \overline{\pi}_0 \\
                 &\displaystyle \underline{\pi}_1 \leq \pi_1 \leq \overline{\pi}_1 \\
                 &\displaystyle \underline{p} \leq p \leq \overline{p} \\
\end{split}
\end{equation}
with the new variable specification:
\begin{eqnarray}
x_1&:=&\pi_1 \cdot p \,,\\
x_2&:=&\pi_0 \cdot p \,,\\
x_3&:=&(1-\pi_1) \cdot p \,,\\
x_4&:=& \pi_0 \cdot (1-p)\,.\\
\end{eqnarray}
the problem becomes:
\begin{equation}
\begin{split}
\text{min} \displaystyle \, x_1 \\
\text{subject to\phantom{xx}} & \displaystyle x_1 > x_4\\
                 &\displaystyle \underline{\pi}_0 \leq x_2+x_3 \leq \overline{\pi}_0 \\
                 &\displaystyle \underline{\pi}_1 \leq x_1+x_4 \leq \overline{\pi}_1 \\
                 &\displaystyle \underline{p} \leq x_1+x_3 \leq \overline{p} \\
\end{split}
\end{equation}

\section{Introduction}\label{sec:intro}
The use of communication and information technologies in education is actually growing. Both online (e.g., MOOCs) and classroom courses are urgently asking for more flexible and sophisticated e-learning and e-testing tools \cite{pollard2001exploring}. AI-based approaches such as intelligent tutoring systems, adapting the interaction with the student on the basis of his/her knowledge and/or psychological profile, represent an important direction to improve the quality of the (e-)learning experience \cite{burns2014intelligent}.

Bayesian networks (BNs) \cite{koller2009} have been used to model the knowledge driving such intelligent systems \cite{almond2015bayesian}. However, collecting large sets of reliable data in educational domains may be difficult and time consuming (e.g., a course with few students, or taught for the first time), and the quantification should be based on expert knowledge only. To elicit a Bayesian network, an expert might face questions like: ``\emph{which is the probability of a student with a particular knowledge level giving the right answer to a question?}''. Giving sharp probabilities for questions of this kind can be problematic for an expert, whose knowledge is mostly qualitative (e.g., ``\emph{a right answer is very unlikely}''). Fuzzy linguistic approaches represent a viable, non-numerical, way to address these issues \cite{badaracco2013fuzzy}. To stick within the probabilistic framework, verbal-numerical probability scales associated with sharp values \cite{renooij1999talking} or intervals \cite{walley1991statistical} have been also proposed.

In this paper we show how to conjugate an interval-valued probabilistic elicitation of expert knowledge with the BN framework. This means to cope with a \emph{credal network} (CN) \cite{novapiatti}, a generalization of BNs based on the imprecise probability theory \cite{walley1991statistical}, where local parameters are defined by set-valued probabilities. This simplifies the elicitation process and offers a more reliable handling of the related uncertainty. Moving from BNs to CNs implies two main issues: (i) numerical inferences will be interval-valued too, thus making debatable both the decision criterion \cite{troffaes} an the information measures \cite{klir1999uncertainty} to adopt; and (ii) inference tasks in CNs typically belongs to higher complexity classes than their Bayesian counterparts \cite{maua14jair}. Both these issues are addressed by defining a computationally feasible procedure based on CNs to be used for practical implementation of intelligent systems solely specified by expert knowledge. To the best of our knowledge this is the first attempt to perform e-testing with models of this kind.

We focus on the application of CNs to \emph{computer adaptive testing} (CAT), i.e., an approach to e-testing that adjusts the sequence and the number of questions to the ability level of the test taker. CATs have the potential to make the test an individualised experience that challenges and does not discourage the test takers, as most of the questions are near their ability levels. Building upon \emph{item response theory} \cite{hambleton1985item}, the common background underpinning CATs, graphical modeling (such as BNs and CNs) offers a powerful language for describing complex multivariate dependencies between skills and rich tasks. Several researchers have exploited the potential of BNs both in adaptive and non-adaptive educational assessment \cite{vomlel2004building,plajner2015}. These authors focus on applications for which data are available to learn the model parameters. We regard this point as a serious limitation, possibly hindering CATs adoption by many teachers and instructors.

We start from a CAT procedure based on BNs that uses \emph{entropy} as the information-theoretic measure driving the question selection and the stopping criteria (Sect.~\ref{sec:bayesianCAT}). Our goal is to improve  this procedure by using CNs to better describe the pervasive uncertainty characterizing the model. A direct extension of the Bayesian framework to CNs would require the computation of bounds for the conditional entropy with respect to the CN specification. This corresponds to a non-linear non-convex optimization task. We therefore propose a number of simplifying assumptions to overcome this problem at the price of accepting sub-optimal question selection schemes (Sect.~\ref{sec:credalCAT}). The approach is tested on a real-world benchmark about German language proficiency assessment (Sect.~\ref{sec:conc}). The results are promising: CAT based on CNs is effective in reducing the number of questions while maintaining a high accuracy in the evaluation and the approximations introduced do not compromise the procedure's effectiveness.

\section{Bayesian CAT}

\paragraph{Skills modeling.} We describe the knowledge level of a student as a collection of categorical variables, say $\bm{X}:=(X_1,\ldots,X_n)$, called \emph{skills}. A joint \emph{probability mass function} (PMF) $P(\bm{X})$ describes the uncertainty about the actual values of the skills. A compact specification of such multivariate model can be achieved by a BN \cite{koller2009}. This corresponds to: (i) a directed acyclic graph whose nodes are in one-to-one correspondence with the variables of $\bm{X}$; and (ii), for each $X_i\in\bm{X}$, 
 a collection of conditional PMFs $P(X_i|\mathrm{\pi}_{X_i})$, one for each value $\pi_{X_i}$ of the joint variable $\mathrm{\Pi}_{X_i}$ denoting the \emph{parents} (i.e., the immediate predecessors) of $X_i$. The \emph{Markov condition} for BNs assumes every variable conditionally independent of its non-descendants non-parents given the parents. Accordingly, the joint PMF associated with a BN is such that $P(\bm{x}):= \prod_{i=1}^n P(x_i|\pi_{X_i})$, for each $\bm{x}$, where the values of $x_i$ and $\pi_{X_i}$ are those consistent with $\bm{x}$.

\paragraph{Questions modeling.} The above joint probabilistic model describes the uncertainty about the skills of a student prior to his/her answers to the questions. To evaluate the student we formulate a number of \emph{questions}, described as a collection of variables $\bm{Y}:=(Y_1,\ldots,Y_m)$. We assume these variables to be Boolean, with the true value corresponding to the correct answer.\footnote{Extension to non Boolean answers is trivial as all answers $Y_i$ are \emph{manifest} variables, and, thus, $Y_i$ can be always regarded as a binary variable with the two values denoting the observed answer $y_i$ and its negation \cite{antonucci2009}.} We call \emph{background} of a question the set of skills ``required'' to answer it. This can be regarded as a conditional independence statement: given the background skills, the answer to the question is independent of the other skills and of the other questions. Following the Markov condition, this can be modeled by representing each question as a leaf node whose parents are the background skills. Such augmented graph requires the quantification, for each $Y_j\in\bm{Y}$, of a conditional PMF $P(Y_j|\mathrm{\pi}_{Y_j})$ for each value $\mathrm{\pi}_{Y_j}$ of the background skills $\mathrm{\Pi}_{Y_j}$. This procedure defines a BN over the skills and the questions, and hence a joint PMF $P(\bm{X},\bm{Y})$.

\paragraph{Non-adaptive testing.} Let $\bm{Y}=\bm{y}$ denote a student's answers to the test. In the above considered framework, the posterior knowledge about the skills is modeled by the joint PMF $P(\bm{X}|\bm{y})$. By running standard BN updating algorithms, the most probable level $\tilde{x}_i$ of skill $X_i$ can be therefore evaluated  as $\tilde{x}_i:= \arg\max_{x_i} P(x_i|\bm{y})$, for each $X_i\in\bm{X}$. This reflects a non-adaptive, probabilistic approach to student evaluation.

\paragraph{Adaptive testing.} To add adaptiveness to the above approach, every question should be chosen on the basis of the previous answers. As the goal is to gather information about the student skills, we evaluate the expected \emph{information gain} (IG, i.e., the change in information entropy) associated with each possible new question, and pick the one maximizing this measure. The entropy of a BN over $\bm{X}$ can be computed as $H(\bm{X}):=\sum_{i=1}^n H(X_i|\mathrm{\Pi_{X_i}})$ \cite{koller2009}, where $H(X_i|\mathrm{\Pi_{X_i}}):=\sum_{\pi_{X_i}} H(X_i|\pi_{X_i}) P(\pi_{X_i})$ is the \emph{conditional entropy} for $X$ given its parents and $H(X_i|\pi_{X_i})$ is the entropy of the conditional PMF $P(X_i|\pi_{X_i})$.\footnote{To have entropy levels between zero and one, we define the entropy of the PMF $P(X)$ as $H(X):=-\sum_x P(x) \log_b P(x)$, with $b$ number of states of $X$.} Let $\bm{Y}=\bm{y}$ denote the answers to the questions already asked and $\bm{Y}'$ the set from which the next question should be picked. If the answer to every question $Y'\in\bm{Y}'$ would be known, and denoted by $y'$, the question $\tilde{Y}' \in \bf{\mathbf{Y}'}$ to choose would be the one leading to the largest IG. Yet, as the decision has to be made before the student's answer, conditional entropy should be considered instead, i.e.,
\begin{equation}
\tilde{Y}' := \arg \max_{Y'\in \bm{Y}'} \left[H(\bm{X}|\bm{y})-H(\bm{X}|Y',\bm{y})\right]\,. 
\label{eq:expent}
\end{equation}

\begin{figure*}[htp!]
\centering
\begin{tikzpicture}[auto,scale=.7]
\node[block,node distance=.cm,fill=black!10] (pick) {\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) {\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
\node[block, right of=pick,node distance=3cm,fill=black!10] (ask) {\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
\node[block, right of=ask,node distance=3cm,fill=black!10] (collect) {\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
\node[decision, below of=collect,node distance=1.4cm] (decide) {\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? }\end{varwidth}};
\node[block, left of=decide, node distance=3cm,fill=black!10] (stop) {\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
\node[block, left of=stop, node distance=3cm,fill=black!10] (assign) {\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
\path[line] (decide) -- node {\tiny YES}(stop);
\path[line] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
\path[line,dashed] (db) -- (pick);
\path[line] (pick) -- (ask);
\path[line] (ask) -- (collect);
\path[line] (collect) -- (decide);
\path[line] (decide) -- (stop);
\path[line] (stop) -- (assign);
\end{tikzpicture}
\caption{CAT procedure}
\label{fig:alg}
%\vspace{-1cm}
\end{figure*}

CATs should also decide when to stop asking questions. Again, entropy can be used as a measure to decide when the current evaluation is sufficiently informative, i.e., we stop the test if the skills entropy given the answers is below some threshold $\tilde{H}$. The overall approach is depicted in Fig.~\ref{fig:alg}.

\section{Credal CAT}

\paragraph{Credal sets and credal networks.} A set of PMFs over $X_i$ is called here \emph{credal set} (CS) and denoted as $K(X_i)$. We always remove the inner points (i.e., those corresponding to convex combinations of the others) of a CS. CNs \cite{cozman2000} are generalized BNs whose local PMFs are replaced by CSs.  The BN defined in the previous section over the skills $\bm{X}$ and the questions $\bm{Y}$ becomes a CN if we replace with CSs the skill-to-skill and skill-to-question conditional PMFs. A joint CS $K(\bm{X},\bm{Y})$ is consequently obtained as the collection of all the joint PMFs induced by BNs whose parameters take their values from the corresponding CSs, i.e., 
\begin{equation}\label{eq:strongext}
K(\bm{X},\bm{Y}):=\left\{ P(\bm{X},\bm{Y}) \left| 
\substack{
P(\bm{x},\bm{y}):=\prod_{i=1}^n P(x_i|\pi_{X_i}) \cdot \prod_{j=1}^m P(y_j|\pi_{Y_j}), \\P(X_i|\pi_{X_i}) \in K(X_i|\pi_{X_i}) ,\, P(Y_j|\pi_{Y_j}) \in K(Y_j|\pi_{Y_j})}
\right.
\right\}\,,
\end{equation}
where the values of $x_i$, $\pi_{X_i}$, $y_j$, $\pi_{Y_j}$ are those consistent with $\bm{x}$ and $\bm{y}$.

\paragraph{Expert knowledge modeling.} For a reliable expert knowledge modeling, we use CSs induced by \emph{probability intervals}. Qualitative judgments about the probability of a state are converted in interval constraints such as $l\leq P(x) \leq u$, with the interval $[l,u]$ capturing the expert knowledge behind the judgment in a more reliable way than a sharp assessment. The CS consistent with these constraints is eventually obtained by standard polyhedral algorithms. Verbal to interval-numeric scales such as that Tab.~\ref{tb:labels} are used. For instance, if for the probability of the true state of the Boolean variable $Y$ the expert judgment is ``very likely'', the corresponding linear constraint is $.2 \leq P(Y=\textrm{true}) \leq .4$.% and we obtain a CS $K(Y)$ with the PMFs $P_1(Y)=[.2,.8]$ and $P_2(Y)=[.4,.6]$ as non-inner points.

\paragraph{Non-adaptive testing.} Given the answers $\bm{y}$ to the questions $\bm{Y}$, we evaluate the student as in the previous section by updating the marginal probabilities of each skill. With CNs, these posterior values are set-valued and their characterization can be provided by lower and upper bounds, say $\underline{P}(X_i|\bm{y})$ and $\overline{P}(X_i|\bm{y})$ for each $X_i\in\bm{X}$. CN updating algorithms can eventually compute these bounds. The task displays higher complexity than in the case of BNs (e.g., exact inference in non-binary singly-connected CNs is NP-hard \cite{maua14jair}), but approximate techniques can be considered when exact inference is unfeasible \cite{antonucci2014e}.

To compare the posterior intervals and decide the actual level of the student we might adopt the (conservative) \emph{interval dominance} criterion \cite{troffaes}, which rejects a level if its upper probability is smaller than the lower probability of some other level. Overlaps between intervals might therefore induce a situation of \emph{indecision} between two or more levels. This is a so-called \emph{credal} classification of the student level \cite{zaffalon2012evaluating}, and it represents the fact that students answers are somehow contradictory or not informative enough to provide a sharp decision. Interval dominance can return unnecessarily imprecise results. \emph{Maximality} is a more refined criterion that rejects the levels which are less probable than another level for all the elements of the CS \cite{walley1991statistical}. Maximality  can be reduced to multiple updating tasks on auxiliary binary leaf nodes defined for each pair of states \cite{antonucci2014e}.

\paragraph{Adaptive testing.}
To achieve CAT with CNs using entropy as measure of informativeness for PMFs, as in the BN approach of Sect. \ref{sec:bayesianCAT}, computation of entropies should be extended to CSs. This topic has been the subject of much discussion \cite{klir1999uncertainty}. A cautious approach \cite{abellan2003maximum} consists in taking the upper entropy $\overline{H}(\bm{X})$, i.e., the entropy of the most entropic PMF in the convex closure $\overline{K}(\bm{X})$ of  $K(\bm{X})$. 
In our framework, we should, then, look for maximum values of conditional entropies, such as $\overline{H}(X_i|Y',\bm{y})$ or $\overline{H}(X_i|\Pi_{X_i})$, as conditional entropies are required to compute both: (i) the joint (unconditional) entropy $H(\bm{X})$ (and its posterior values); and (ii) the conditional entropies  involved in the  question selection in Eq.~\eqref{eq:expent}.
By definition a conditional entropy is a convex combination (whose weights are the elements of a marginal PMF) of convex functions (the entropies). The objective function might, then, be non-convex, as the weights are also optimization variables.\footnote{E.g., if $f(x)$ and $g(x)$ are convex functions of $x$, $h(x,y):= y f(x) + (1-y) g(x)$ is not convex even for $0 \leq y \leq 1$.}

Then, to bypass this non-convex optimization task, we compute (i) by separately considering the entropies of each skill $X_i\in\bm{X}$. This is analogous to the marginal approach commonly considered in multi-label classification to minimize Hamming losses \cite{antonucci2016c}. The issue (ii) is more challenging. We consider the following upper approximation of $\overline{H}(X_i|Y',\bm{y})$:
\begin{equation}
\overline{\overline{H}}(X_i|Y',\bm{y})=
\max_{P(y'|\bm{y})\in
\{\underline{P}(y'|\bm{y}),\overline{P}(y'|\bm{y})\}}
\sum_{y' \in \{\textrm{true},\textrm{false}\}}
\overline{H}(X_i|\bm{y},y') P(y'|\bm{y})\,,
\end{equation}
where the bounds of $P(y'|\bm{y})$ are obtained by standard CN updating algorithms.
The problem thus reduces to the computation of upper entropies as
\begin{equation}\label{eq:entropy}
\overline{H}(X_i|\bm{y}) := \sup_{P(X_i|\bm{y}) \in \overline{K}(X_i|\bm{y})} H(X_i|\bm{y})\,,
\end{equation}
where  $\overline{K}(X_i|\bm{y})$ is the posterior CS after conditioning on the observed answers $\bm{y}$.  If $\overline{K}(X_i|\bm{y})$ has a finite number of non-inner points, this is a linearly-constrained convex optimization whose solution typically corresponds to either the uniform PMF or a non-inner point on the frontier of $\overline{K}(X_i|\bm{y})$. A numerical solution can be easily found by a simple iterative approach in the special case of CS specified by probability intervals \cite{abellan2003maximum}. We have therefore computed the posterior lower and upper bounds of $P(X_i|\bm{y})$, and then maximized the entropy with respect to those bounds. % as in Eq.~\eqref{eq:entropy}. 
The procedure induces an outer approximation of $\overline{K}(X_i|\bm{y})$, and hence the upper approximation  of the maximum entropy $\overline{\overline{H}}(X|\bm{y})\geq\overline{H}(X|\bm{y})$. 
%With a small notation abuse such approximate value is also denoted as $\overline{H}(X|\bm{y})$ and is regarded here as a measure of the informativeness level achieved for skill $X$ after the answers $\bm{y}$. 
Finally, to generalise Eq.~\eqref{eq:strongext} to CNs, we define the information gain provided by a question $Y'$ for its background skill $X_{Y'}$ as $\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y})$ and select the question $\tilde{Y}'$ leading to the maximum information gain, i.e.,
\begin{equation}\label{eq:credalentropy}
\tilde{Y}' := \arg \max_{Y'\in\bm{Y}'} 
\left[
 \overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y}) 
 \right]
 \,.
\end{equation}
For the stopping criterion, as we do not consider the joint entropy over the skills, we separately require each $\overline{\overline{H}}(X_i|\bm{y})$ to be smaller than a threshold $\tilde{H}$. To be consistent with this choice, we remove from the set of questions to be selected, those whose background skills already satisfy this condition.

Note that the use of an outer approximation of the upper entropy affects only the question selection process (eventually making it sub-optimal), whereas it has no effect on the student evaluation given a set of answers.

\section{Application}
Before the academic year begins, the students of the University of Applied Sciences and Arts of Southern Switzerland (SUPSI) are asked to take an online German language placement test with 95 questions. In years 2015 and 2016, the answers of 451 students to all the questions have been collected. This benchmark is used to simulate CATs based on BNs and CNs as described in Sects.~\ref{sec:bayesianCAT} and \ref{sec:credalCAT}.

\paragraph{Model elicitation.}
Four skills are assessed: \textit{W\"ortschatz} ($X_1$, vocabulary), \textit{Kommunikation} ($X_2$, communication), \textit{H\"oren} ($X_3$, listening), and \textit{Lesen} ($X_4$, reading). For each skill the student is assigned to a knowledge level compliant with EU guidelines.\footnote{\url{http://www.coe.int/t/dg4/linguistic/Source/Framework_EN.pdf}.}
Levels A1, A2, B1, and B2 are considered, and skills are therefore modeled as quaternary variables.
Teachers associate each question with a single skill, which is set as the unique background skill of the question. The number of questions associated with $X_1$/$X_2$/$X_3$/$X_4$ is 26/24/30/15. The current evaluation method assigns levels by setting thresholds on the percentage $\gamma$ of correct answers on each skill (A1 if  $\gamma < 35\%$, A2 up to $55\%$, B1 up to $75\%$).\footnote{These data as well as the software used for the simulations are freely available at \url{http://ipg.idsia.ch/software.php?id=138}.}

We first elicit from the teachers the structure of the BN/CN graph over the skills. The result is a chain, which is augmented by leaf nodes modeling the questions, each having its background skill as single parent. Overall, a tree-shaped topology as in Fig.~\ref{fig:fourskills} is obtained. This makes exact inference in the BN fast, while in the CN a variable elimination might be slow (a minute for query in our setup). A faster approximate CN algorithm is therefore used \cite{antonucci2014e}.

\begin{figure}[htp!]
\centering
\begin{tikzpicture}[scale=.8]
\node[nodo] (w)  at (-0.25,0) {$X_1$};
\node[nodo] (k)  at (3,0) {$X_2$};
\node[nodo] (h)  at (6.5,0) {$X_3$};
\node[nodo] (l)  at (9.25,0)  {$X_4$};
\draw[arco] (w) -- (k);
\draw[arco] (k) -- (h);
\draw[arco] (h) -- (l);
\node[Qnodo] (f1)  at (-0.25,-1) {$Y_1$};
\node[Qnodo] (f2)  at (1.5,-1) {$Y_2$};
\node[Qnodo] (f3)  at (3,-1) {$Y_3$};
\node[Qnodo] (f4)  at (4.5,-1) {$Y_4$};
\node[Qnodo] (f5)  at (6.5,-1) {$Y_5$};
\node[Qnodo] (f6)  at (8.5,-1)  {$Y_6$};
\node[Qnodo] (f7)  at (10,-1)  {$Y_7$};
\draw[arco] (w) -- (f1);
\draw[arco] (k) -- (f2);
\draw[arco] (k) -- (f3);
\draw[arco] (k) -- (f4);
\draw[arco] (h) -- (f5);
\draw[arco] (l) -- (f6);
\draw[arco] (l) -- (f7);
\end{tikzpicture}
\caption{A directed graph for CAT\label{fig:fourskills}.}
\end{figure}
\vspace{-5mm}

Teachers report their knowledge about the unconditional states of $X_1$ and the conditional states of $X_i$ given $X_{i-1}$, for $i=2,3,4$, as qualitative judgments (top of Tab.~\ref{tb:CPTs}). 
To simplify the elicitation, the probabilities $P(X_i|X_{i-1})$ are given the same verbal judgment for all $i=2,3,4$. A more detailed model could provide more accurate evaluations but it would be very hard for the domain expert to elicit it in a reliable way. 
Also, questions are divided by the teachers in three groups, corresponding to different difficulty levels. Questions in the same group are quantified in the same way, irrespective of their background skill, giving the judgments reported in the bottom part of Tab.~\ref{tb:CPTs}.

{\small \begin{table*}[htp!] 
\renewcommand{\arraystretch}{1.2}
\centering
{%\footnotesize
\begin{tabular}{@{}lc@{}}
\toprule
$X_1$&$P(X_1)$\\
\midrule
A1&\emph{improbable}\\
A2&\emph{uncertain}\\
B1&\emph{uncertain}\\
B2&\emph{improbable}\\
\bottomrule
\end{tabular}
\quad
\begin{tabular}{@{}lcccc@{}}
\toprule	
$P(X_i|X_{i-1})$&\phantom{.}$X_{i-1}=\mathrm{A1}$\phantom{.}&\phantom{.}$X_{i-1}=\mathrm{A2}$\phantom{.}&\phantom{.}$X_{i-1}=\mathrm{B1}$\phantom{.}&\phantom{.}$X_{i-1}=\mathrm{B2}$\phantom{.}\\
\midrule
$X_i$=A1&\emph{fifty-fifty}&\emph{uncertain}&\emph{improbable}&\emph{impossible}\\
$X_i$=A2&\emph{uncertain}&\emph{fifty-fifty}&\emph{uncertain}&\emph{improbable}\\
$X_i$=B1&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}&\emph{uncertain}\\
$X_i$=B2&\emph{impossible}&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}\\
\bottomrule
\end{tabular}}
\vskip 2mm
\begin{tabular}{@{}lcccc@{}}\toprule
$P(Y=T|X)$\phantom{aa}&\phantom{a}$X=\mathrm{A1}$\phantom{a}&\phantom{a}$X=\mathrm{A2}$\phantom{a}&\phantom{a}$X=\mathrm{B1}$\phantom{a}&\phantom{a}$X=\mathrm{B2}$\phantom{a}\\
\midrule
Easy&\emph{uncertain}&\emph{fifty-fifty}&\emph{expected}&\emph{probable}\\
Medium&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}& \emph{expected}\\
Difficult&\emph{impossible}&\emph{improbable}&\emph{uncertain}& \emph{fifty-fifty}\\
\bottomrule
\end{tabular}
\vskip 2mm
\caption{Expert judgements.}\label{tb:CPTs}
\end{table*}}
%\vspace{-10mm}
For the CN, those judgements are translated in interval constraints for the corresponding events on the basis of the verbal-numerical scale in Tab.~\ref{tb:labels}. Different probability intervals are considered for skills and questions as they refer to events of different type. For instance, when the expert considers ``\emph{impossible}'' for an A1 level student to know the answer to a difficult question, the student is assigned a probability between .175 and .2 of answering correctly, as the questions offer only four choices plus the option of giving no answer. 
Notice that, by doing so, we are not anymore assuming that all questions in the same difficulty group share exactly the same conditional PMFs (as done by the BN model), as PMFs of different questions can vary independently in the given intervals. This seems a more sensible assumption than that of the precise model.
For the BN, the PMFs corresponding to the centers of mass of the CSs defining the CN are used. Numerical inferences in the BN are consequently included in the intervals computed with the CN.

{\small
\begin{table*}[htp!] 
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{@{}lcccccc@{}}
\toprule
Judgement&\emph{impossible}&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}&\emph{expected}&\emph{probable}\\
\midrule
Skills&$1$-$10\%$&$10$-$20\%$&$20$-$40\%$&$30$-$50\%$&-&-\\
Questions&$17.5$-$20\%$&$22.5$-$25\%$&$30$-$35\%$&$60$-$65\%$&$75$-$80\%$& $95$-$97.5\%$\\
\bottomrule
\end{tabular}
\caption{A verbal-numerical scale for probability-intervals elicitation.}\label{tb:labels}
\end{table*}}

\paragraph{Experimental results.} 
%Acronyms BN-NA, CN-NA, BN-AD, CN-AD denote 
BN and CN methods in their non-adaptive (NA) and adaptive (AD) versions are considered. \emph{Accuracy}, i.e., the proportion of students to whom the test assigns the same level of the current evaluation method, describes BN performances. This measure cannot be used for the set-valued outputs of CN methods. In this case the $u_{65}$ measure can provide a comparison with the accuracy \cite{zaffalon2012evaluating}. If $\mathcal{L}$ is the set of levels assigned by the CN on a skill and $L$ its cardinality, a \emph{discounted} accuracy gives $1/L$ if $\mathcal{L}$ includes the true level and zero otherwise. The $u_{65}$ is a concave reinforcement of this score based on risk-adverse arguments. Its underlying assumption is that acknowledging the indecision between more levels has larger utility than randomly choosing one of them (e.g., the teacher could set up further assessments in the undecided cases). Tab.~\ref{tb:nonAdaptiveResults} shows the NA comparison. In Fig.~\ref{fig:plots} (left), the BN-NA accuracy is separately evaluated on the determinate (light bars) and indeterminate (dark bars) instances, i.e. those for which, respectively, a single level or multiple levels are returned by the CN model. On average, CN-NA returns single levels in $37.25\%$ of the cases and, if this is not the case, an average of $2.36$ levels ($3.22$ with interval dominance) are returned.

\begin{table*}[htp!]
	\centering
	\begin{tabular}{@{}lccccc@{}}\toprule
		Algorithm&\phantom{aa}Average\phantom{aa}&\phantom{aaa}$X_1$\phantom{aaa}&\phantom{aaa}$X_2$\phantom{aaa}& \phantom{aaa}$X_3$\phantom{aaa}&\phantom{aaa}$X_4$\phantom{aaa}\\
		\midrule
		BN-NA (acc)&$63.09\%$&$	67.56	\%$&$60.85\%$&${	75.84	\%}$&$48.10\%$\\
		CN-NA ($u_{65}$)& ${65.37\%}$&$67.71\%$&${66.67\%}$&$	70.33\%$&${56.76\%}$\\
		\bottomrule
	\end{tabular}
	\caption{Non-adaptive tests results.}\label{tb:nonAdaptiveResults}
\end{table*}

In the AD case we also track the average number of asked questions. Results are in Fig.~\ref{fig:plots} (right). CN-AD (circles) is tested for different thresholds over the entropy (labels of the markers) against a version of BN-AD based on the joint entropy (triangles). Similar values are obtained by coping with marginal entropies. We also allow the BN-AD method to return multiple levels by maximizing the expected $u_{65}$ utility over any possible set of levels. This variant is called BN-AD' and the corresponding $u_{65}$ measure is reported  (squares).

\begin{figure}[htp!]
\centering
\begin{tikzpicture}
\begin{axis}[width=4cm,height=3.5cm,ybar=0,bar width=7pt,ylabel={\small acc}, xlabel={Skills},xtick=data,ytick={0,25,50,75,100},ymin=0,ymax=100,yticklabels={0,.25,.50,.75,1},symbolic x coords={$X_1$,$X_2$,$X_3$,$X_4$}, y label style={at={(axis description cs:0.3,.5)},anchor=south},xtick align=inside, legend style={at={(1,1)},anchor=south east},legend style={draw=none}]
\addplot[fill=black!10] coordinates {($X_1$,85.42)($X_2$,87.06)($X_3$,89.51)($X_4$,56.34)}; 
\addlegendentry{\tiny{determinate}} 
\addplot[fill=black!70] coordinates {($X_1$,54.51)($X_2$,45.13)($X_3$,67.72)($X_4$,44.26)};
\addlegendentry{\tiny{indeterminate}}
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}
\begin{axis}[width=7.5cm,height=4cm,ylabel={\small acc/$u_{65}$},xlabel={Number of questions},xmin=35, xmax=100,ymin=50, ymax=70, xtick={40,50,60,70,80,90}, ytick={50,55,60,65},legend style={at={(1,0)},anchor=south east},ymajorgrids=true,xmajorgrids=true,  y label style={at={(axis description cs:0.13,.5)},anchor=south},legend style={draw=none}]
\addplot[black,thick,mark=triangle,mark options={fill=black}, visualization depends on=\thisrow{alignment} \as \alignment, nodes near coords, point meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}] 
table [meta index=2 ] {
x y label alignment
40.36	51.51 .7 0
49.84	55.43 .65 -20
58.34	57.49 .6 80
66.50 59.45 .55 80
79.43	62.75 .45 80
89.04	63.14 .3 80
95  63.09     0  160
};
\addlegendentry{\tiny{BN-AD}}
\addplot[magenta,thick,mark=square,mark options={fill=black}, visualization depends on=\thisrow{alignment} \as \alignment, nodes near coords, point meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}] 
table [meta index=2 ] {
x y label alignment
40.36	59.9 .7 -20
49.84	61.00 .65 -40
58.34	60.86 .6 50
66.50 60.34 .55 -30
79.43	64.90 .45 -80
89.04	66.3 .3 -80
95  66.22     0  -160
};
\addlegendentry{\tiny{BN-AD'}}
\addplot[dashed,blue,thick,mark=o,mark options={solid,fill=white},
visualization depends on=\thisrow{alignment} \as \alignment,
nodes near coords, % Place nodes near each coordinate
point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
every node near coord/.style={anchor=\alignment} ] table [meta index=2 ] {
x       y   label  alignment
42.45 58.27  .95   20
56.96 62.37  .925   -80
66.87 63.49   .9   -80
83.75 62.83  .8    -110
95   65.37   0  160
};
\addlegendentry{\tiny{CN-AD}}
\end{axis}
\end{tikzpicture}
\caption{Non-adaptive (left) and adaptive (right) tests performance.}\label{fig:plots}
\end{figure}

As a comment, CNs seem to identify hard-to-evaluate students as those for which multiple levels are provided. In fact, the agreement between the BN and the traditional tests is larger when the CN test is determinate. As a consequence, the CN $u_{65}$ measure is, on average, larger than the BN accuracy. 
A limitation of the CN test is the large fraction of indeterminate evaluations. One can interpret this result as a lack of robustness of the BN model, as even small variations in the model specifications can result in different decisions. Results also show that, both BN-AD and CN-AD approaches reduce the number of questions asked without significantly affecting the accuracy. BN-AD performances are improved by the ``credal'' variant BN-AD'. The results becomes very similar to those of the CN-AD. Yet, the latter method appears to be a more principled and suitable approach for a direct modeling of qualitative expert knowledge.

%does not require any, potentially questionable, imputation of the probabilistic ranges provided by the experts.

%Yet, we regard theof BN-AD, we regard the CN approach as more principled and suitable for a direct modeling of qualitative expert knowledge.

%uch a difference disappear if the credal-like variant BN-AD' is considered.
%However, the CN-AD procedure appears to be more effective, as the $u_{65}$ accuracy measure decreases more slowly than the accuracies of BN-AD procedures.  
%Finally,comparing the two BN-AD approaches, one can see that the use of the local instead of the joint entropy does not compromise the effectiveness of the adaptive approach.

%Different decision criteria for the assignment of the skill level, e.g., maximality or e-admissibility, should be considered.
%As a consequence, although BNs achieve better performance when considering the discounted accuracy, CN tests should be preferred whenever the utility is better described by the U65 or U80 measures, that is, whenever being undecided between more level should be preferred than assigning one of them at random. 
%As the true level of the students is unknown, this measure should be regarded as the agreement between to different evaluation strategies. 
%\begin{mdframed}[hidealllines=true,backgroundcolor=blue!20]
%\paragraph{Experimental results.} 
%Tab.~\ref{tab:nonadaptive} shows in the non-adaptive case the relative agreement between the traditional evaluation method (TEM) and the two BN-based models (IBN and TBN), computed as the proportion of students to which the tests under comparison assign the same level, averaged over 10 runs of cross-validation. On average 15\% of the students are assigned to a different level with respect to the traditional method (although the difference is never more than one level). The reason is that the BN models account for the difficulty of the questions. E.g., a student with only 70\% of correct answers could be assigned the level B2 if he/she has answered correctly a large number of difficult questions which a student of lower level could not have guessed just by chance. 
%\end{mdframed}
%
%\begin{table}[htp!]
%%\renewcommand{\arraystretch}{1.1}
%\centering
%\begin{tabular}{@{}p{2.5cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}@{}}\toprule
%Algorithm&\multicolumn{1}{l}{W\"ort.}&\multicolumn{1}{l}{Komm.}&\multicolumn{1}{l}{H\"oren}&\multicolumn{1}{l}{Lesen}&\multicolumn{1}{l}{Overall}\\ 
%\midrule
%TEM vs IBN&.80 &.87 &.89 &.85 &.85 \\
%TEM vs TBN&.79 &.87 &.88 &.83 &.84 \\
%IBN vs TBN&.98 &.95 &.94 &.92 &.95 \\
%\bottomrule
%\end{tabular}
%\caption{Relative agreement between models}\label{tab:nonadaptive}
%\vspace{-0.cm}
%\end{table}
%\begin{table}[htp!]
%%\renewcommand{\arraystretch}{1.1}
%\centering
%\begin{tabular}{@{}p{2.5cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}@{}}\toprule
%Algorithm&\multicolumn{1}{l}{W\"ort.}&\multicolumn{1}{l}{Komm.}&\multicolumn{1}{l}{H\"oren}&\multicolumn{1}{l}{Lesen}&\multicolumn{1}{l}{Overall}\\ 
%\midrule
%TEM& .28 &	.82 &	.88 &	.79 &	.84 \\
%IBN& .71 &	.89 &	.83 &	.87 &	.90 \\
%TBN& .79 &	.91 &	.87 &	.89 &	.92 \\
%\bottomrule
%\end{tabular}
%\caption{Split-half reliability}
%\label{tab:halfsplit}
%\vspace{-0.8cm}
%\end{table}
%\begin{mdframed}[hidealllines=true,backgroundcolor=blue!20]
%In this view, we believe that our approach provides more reliable evaluations than the traditional one. Tab.~\ref{tab:halfsplit} shows the internal consistency of the three tests evaluated using the split-half methodology: the questions are randomly divided into two subset of equal size; the two half-tests thus obtained are used to generate two independent evaluations of the students; the correlation coefficient between the outputs of the two half-tests adjusted with the Spearman-Brown correction is retained as a measure of the test reliability. Results show that the reliability of both Bayesian approaches (IBN and TBN) is larger than that of the traditional method. TBN has the highest reliability, as it considers the correlation between different skills and thus all answers contribute to the determination of the level of a skill, even those referring to different skills. 
%Concerning the adaptive case, we have considered different thresholds for the entropy. The left plot in Fig.~\ref{fig:agreement} shows the relative agreement of the adaptive tests using IBN and TBN with the non-adaptive TBN, whereas the right plot shows the average number of questions asked to the students. Both models show a strong reduction in the number of questions as the threshold on the entropy increases. For instance, using the TBN model, the number of questions reduces of about 70\% passing from the non-adaptive test to an adaptive test with entropy threshold $\tilde{H}=0.5$. Yet, the test still provides the same evaluations as the non-adaptive one in more than 70\% of the cases. Such an accuracy loss might be problematic. However, even decreasing the entropy threshold to $\tilde{H}=0.19$, we can still save 20 question on average (to a maximum of 65 questions in the best case) at the price of a reduction of only 3\% in the accuracy. This shows that a significant number of questions provides very little information about the student level of knowledge. Our adaptive approach makes it possible to avoid wasting students' time asking uninformative questions. 
%\end{mdframed}
%\begin{figure}[htp!]
%\centering
%\begin{tikzpicture}
%\begin{axis}[title={Agreement},width=6cm, height=4cm,xlabel={Entropy Threshold $\tilde{H}$},xmin=0, xmax=0.5, ymin=0.7, ymax=1, xtick={0,.1,.2,.3,.4,.5}, ytick={.7,.8,.9,1}, legend pos=north east, ymajorgrids=true, xmajorgrids=true]
%\addplot[color=black,mark=square] coordinates { (0.0625,0.99833) (0.125,0.99217) (0.1875,0.9685) (0.25,0.89583) (0.375,0.75183) (0.5,0.74517)};    
%\addlegendentry{TBN}
%\addplot[color=black!60,mark=star] coordinates { (0.0625,0.94733)(0.125,0.946000)(0.1875,0.943333)(0.25,0.8965000)(0.375,0.744000)(0.5,0.724666)};
%\addlegendentry{IBN}
%\end{axis}
%\end{tikzpicture}
%\begin{tikzpicture}
%\begin{axis}[ title={Number of questions},width=6cm, height=4cm, xlabel={Entropy Threshold $\tilde{H}$}, xmin=0, xmax=0.5, ymin=0, ymax=100, xtick={0,.1,.2,.3,.4,.5}, ytick={0,20,40,60,80,100}, legend pos=north east, ymajorgrids=true, xmajorgrids=true]
%\addplot[color=black!60,mark=star] coordinates { (0.0625,89.741) (0.125,87.229) (0.1875,81.309) (0.25,66.745) (0.375,32.5) (0.5,29.001)};    
%\addlegendentry{IBN}
%\addplot[color=black,mark=square] coordinates { (0.0625,88.553) (0.125,83.476) (0.1875,75.071) (0.25,58.484) (0.375,30.722) (0.5,29)};
%\addlegendentry{TBN}
%\end{axis}
%\end{tikzpicture}
%\caption{Agreement between the adaptive methods and the non-adaptive TBN (left) and average number of questions asked by the adaptive methods (right)}\label{fig:agreement}
%\vspace{-.8cm}
%\end{figure}
%As providing precise values for these probabilities can be very hard even for expert teachers, the subjective opinion about the likelihood of an event was described by using the verbal-numerical probability scales in Table \ref{tb:labels}. 
%The question and skill CPTs are given in tables \ref{tb:questionCPTs} and \ref{tb:skillCPTs}.
%make the model specification complete, the CPTs of the skills, i.e., $\{ P(X_i|\mathrm{\Pi_{X_i}})\}_{i=1}^4$, and those of the questions, i.e., $\{ P(Y_j|B_{Y_j})\}_{j=1}^{95}$ should be quantified.
%In previous work \cite{mangili2016a}, these parameters have been learned from the available data. Results have shown that the resulting model can achieve larger internal consistency than the traditional evaluation method in assessing the student level. Given this result, a data-driven approach is used here to provide \emph{ground truth} evaluations for each student. This approach, hereafter referred to as EM-BN, uses expectation maximization (EM) to learn the CPTs of the BN model in  figure \ref{fig:fourskills} and infer the students level in the four skills. 
%The focus of the paper, however, is to provide an approach to adaptive testing entirely based on expert elicitation. Therefore, 
%As we are interested in adaptive testing entirely based on expert elicitation, teachers have been asked to elicit all CPTs in the model. 
%Following \cite{zaffalon2012evaluating}, the $u_{65}$ descriptors slightly increases the discounted accuracy contribution (i.e., $1/L$ is the set of labels includes the correct one and zero otherwise) with a convex xxx. Note that this descriptors is knows. 
%The above-described model has been used to evaluate the skills of the 451 students in the dataset. 
%As a ground truth we take the result based on the percentage of correct answers.
%Then, we have compared the effectiveness of the BN and CN-based adaptive approaches.
%?? traditional method, come nel paper ITS, EM?? \todo{scegliere ground truth}. 
% we adopt the following performance descriptors:
%\begin{itemize}
%\item discounted accuracy (disA), i.e., the average value of $\frac{I_{\mathcal{L}}(l)}{L}$, where $I$ is the indicator function and $l$ the true level. This can be regarded as the most unfavorable way (among the reasonable ones) to evaluate
%credal classifiers;
%\item set accuracy (setAcc), i.e., the average value of $I_{\mathcal{L}(l)}$. This can be regarded as the performance measure most favorable to a credal classifier;
%\item the utility-discounted accuracy U65 and U80 \cite{zaffalon2012evaluating}, i.e., the average value of a concave function $u\left(\frac{I_{\mathcal{L}}(l)}{L}\right)$ of the discounted utility. This measure assumes that being undecided between $k$ levels is better than choosing the correct level with probability $1/k$. This measure accounts for risk aversion, which increases with $u(0.5)$. We have $u(0.5)=0.65$ and $u(0.5)=0.8$ for, respectively the U65 and the U80 measures; \footnote{Notice that with $u(0.5)=0.5$ we obtain the discounted accuracy measure.}
%\item the average number of times the credal test is determinate, that is, it returns a single level (DET);
%\item the accuracy of the Bayesian test when the credal test is determinate (detA) and when it is indeterminate (indA). These indicators can show the capability of the credal test to identify the students which are more difficult to evaluate;
%\item the average cardinality of $\mathcal{L}$ (Csize).
%\end{itemize}

ISIPTA 2021 papers have to be prepared using \LaTeX.
To start writing your paper, copy \texttt{isipta2021-paper\_template.tex} and replace author and content with your own.

The ISIPTA 2021 paper style is based on the \textsf{jmlr} class with
the \texttt{pmlr,twocolumn} class options.\footnotemark
\footnotetext{%
  You can find the \textsf{jmlr} documentation at \url{https://ctan.org/pkg/jmlr}.
  The bundle you can download there also includes a sample file with more usage examples.
  Version 1.21 and before are known not to work correctly and produce wrong margins.
  Version 1.23 and after have been tested to work.
  The necessary files from version 1.27 are included in the author kit.
}
This class already loads some commonly used packages, so please have a look at its documentation in case you want to load extra packages.
Do not load packages that conflict with \textsf{jmlr}—you will get an error message—, as this would complicate creating the proceedings.

We have added a style file, \textsf{isipta2021} that sets up some more style details and loads some packages.
This includes font definitions, so do not load your own or change the font size or other style-related aspects.
Also do not change the line width, margins, line spacing and other vertical whitespace between layout elements (so do not use \verb|\vspace|).

You can load extra packages available in the big TeX distributions (Mik\TeX, \TeX{Live}, Mac\TeX) as long as your text compiles with PDF\LaTeX.
Please avoid using obsolete commands, such as \verb|\rm|, and obsolete packages, such as \textsf{epsfig}.\footnote{See \url{https://ctan.org/pkg/l2tabu}.}
\swap[ ]{in the header of your source file.}{But feel free to include your own macros}

\section{Practical Guidelines}
\subsection{Page Limits}
\emph{Full papers} have a length of four to nine pages.
This excludes the list of references and informational sections such as Acknowledgments.
There is the option to provide supplementary materials, such as videos, pictures, code, data-sets, etc.
However, these do not have to be considered by the reviewers, so do make sure the paper is self-contained without them.

\emph{Short papers} have a length of three pages.
Again, this excludes the list of references and informational sections such as Acknowledgments.
However, no supplementary material is accepted in this case.

Please be aware that these are the limits for the final versions of the papers. It is recommended that first submissions do not use all the allowed space, in order to leave some room to take into account reviewers suggestions.

\subsection{Submission \& Filenames}
Your ISIPTA 2021 paper must be submitted via the ISIPTA 2021 Easychair page: \url{https://easychair.org/conferences/?conf=isipta2021}

For the submission deadlines, please check the conference website: \url{http://www.sipta.org/isipta21}.

All the files you submit should follow the JMLR-required format: the surname of the first author, in lowercase, without spaces and accents, followed by \texttt{21} (for the publication year), and optional letter in case there are multiple submissions with the same first author surname, and then the extension.
So if this were a submission, the source file must be named \texttt{alandvonvereweg21.tex} and the compiled one \texttt{alandvonvereweg21.pdf} or, in case of multiple submissions, \texttt{alandvonvereweg21a.tex} and \texttt{alandvonvereweg21a.pdf}.
Supplementary materials gets a \texttt{-supp} affix to the name, so for this ‘submission’ a relevant dataset would, e.g., have to be named \texttt{alandvonvereweg21a-supp.csv}.

For the initial submission, you will have to submit the pdf of your paper and separately, if present, all the supplementary materials in one zip file.

If your paper has been accepted and you are preparing the version that will be published, download the copyright form from the conference web page.
Print, fill, and sign the form.
The name of the PDF scan should be the ID with the suffix \texttt{Permission} (for example, \texttt{alandvonvereweg21aPermission.pdf}).

For the final submission, you should update the paper pdf and, if supplementary materials changed, the supplementary materials zip file.
Additionally, you should create a zip file \texttt{alandvonvereweg21a.zip} with all the paper source files (\texttt{alandvonvereweg21a.tex}, \texttt{alandvonvereweg21a.bib}, etc.) and the permission pdf \texttt{alandvonvereweg21aPermission.pdf}.
This zip file should then be uploaded on Easychair as well.

\section{Sections}
Section titles must be in title case at all levels.

\subsection{Subsections}
\subsubsection{Subsubsections}
Avoid using subsubsections.
In case you need to structure your subsections more finely than in paragraphs, have a look at the unnumbered inline sectioning styles below.

\paragraph{‘Paragraphs’}
‘Paragraphs’ are produced using \verb|\paragraph|.
They can be used directly below sections or subsections.

You can have more than one paragraph in a \LaTeX\ ‘paragraph’.

\subparagraph{Subparagraphs}
Subparagraphs are produced using \verb|\subparagraph|.

\section{Cross-Referencing}
Always use \verb|\label| and \verb|\ref|—or one of the commands described below—when cross-referencing.
For example, the next section is Section~\ref{sec:math}.

The \textsf{jmlr} class provides some convenient cross-referencing commands: \verb|\sectionref|, \verb|\equationref|, \verb|\tableref|, \verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|, \verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|, \verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|, \verb|\exampleref| and \verb|\appendixref|.
The argument of these commands may either be a single label or a comma-separated list of labels.
Examples: \sectionref{sec:math} or \sectionref{sec:intro,sec:math} or \sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

\section{Math}\label{sec:math}
The \textsf{jmlr} class loads the \textsf{amsmath} package, so you can use any of the commands and environments defined there.\footnotemark
\footnotetext{%
  See the \textsf{amsmath} documentation at \url{https://ctan.org/pkg/amsmath} for further details.
}
Furthermore, the \textsf{isipta2021} style file loads the \textsf{mathtools} package, which extends \textsf{amsmath} with even more useful commands.\footnotetext{%
  See the \textsf{mathtools} documentation at \url{https://ctan.org/pkg/mathtools} for further details.
}

Use the \textsf{amsmath} environments for displayed equations.
So, specifically, use the \texttt{equation} environment instead of \verb|$$...$$| and the \texttt{align} environment instead of \texttt{eqnarray}.\footnote{For reasons why you shouldn't use the obsolete \texttt{eqnarray} environment, see Lars Madsen, \textit{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.}
An \texttt{equation}:
\begin{equation}\label{eq:example}
  0 = 1 - 1
\end{equation}
Two \texttt{align}'ed equations:
\begin{align*} % no numbers with starred version
  1 + 2 &= 3,\\
  1 - 2 &= -1.
\end{align*}
Equations can also be put inline, of course.
For example, \equationref{eq:example}: \(0=1+1\). % $0=1+1$ also works

The \textsf{amsmath} and \textsf{mathtools} packages provide a lot of nice functionality, such as many common math operators, such as \(\sin\), \(\max\), etc. and also commands for defining new ones.

The following theorem-like environments are predefined by the \textsf{jmlr} class: \texttt{theorem}, \texttt{example}, \texttt{lemma}, \texttt{proposition}, \texttt{remark}, \texttt{corollary}, \texttt{definition}, \texttt{conjecture} and \texttt{axiom}.
You can use the \texttt{proof} environment to display the proof if need be, as in \theoremref{thm:example}.
\begin{theorem}[Example]\label{thm:example}
  All elements of the powerset of \(\varnothing\) are equal.
\end{theorem}
\begin{proof}\textbf{of \theoremref{thm:example}.} % You can leave off the reference in the \textbf if the proof comes right after that what is to be proven
  The powerset of \(\varnothing\) contains a unique element, \(\varnothing\).
\end{proof}

\section{Floats}\label{sec:floats}
Floats, such as figures, tables and algorithms, are moving objects and are supposed to float to the nearest convenient location.
Please do not force them to go in a particular place and do not
put the figure or table in the middle of a paragraph.
Floats are supposed to have a little extra space above and below them to make them stand out from the rest of the text.
This extra spacing is put in automatically and shouldn't need modifying.

\subsection{Figures}\label{sec:figures}
Figures should go in the \texttt{figure} environment.
Within this environment, use \verb|\floatconts| (defined by \textsf{jmlr}) to correctly position the caption and center the image.
To see how this works, look at the definition of \figureref{fig:example}.
Sub-figures can be created using \verb|\subfigure|, which is also defined by the \textsf{jmlr} class.
Use \verb|\includegraphics| for external graphics files but omit the file extension.
Supported formats are \textsf{pdf} (preferred for vector drawings and diagrams), \textsf{png} (preferred for screenshots), and \textsf{jpeg} (preferred for photographs).
Do not use \verb|\epsfig| or \verb|\psfig|.
If you want to scale the image, it's better to use a fraction of the line width rather than an explicit length.
For example, see \figureref{fig:page}.

\begin{figure}
 % The first argument is the label,
 % the caption goes in the second argument, and
 % the figure contents go in the third argument.
\floatconts
  {fig:example}
  {\caption{Example Image}}
  {
    \subfigure[A page]{%
      \label{fig:page}
      \includegraphics[width=0.5\linewidth,page=1]{isipta2021-poster-abstract_template}
    }
    \quad
    \subfigure[A coordinate system]{
      \label{fig:coords}%
      {
        \begin{tikzpicture}[xscale=1.5]
          \coordinate (origin);
          \draw[->] (origin) -- +(1cm,0) node[below] {$x$};
          \draw[->] (origin) -- +(0,1cm) node[left] {$y$};
          \fill[gray] (45:1cm) circle[radius=.2cm];
        \end{tikzpicture}
      }
    }
  }
\end{figure}

Don't use \verb|\graphicspath|.
If the images are contained in a subdirectory, specify this when you include the image, for example \verb|\includegraphics{figures/mypic}|.

\subsection{Tables}\label{sec:tables}
Tables should go in the \texttt{table} environment.
Within this environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.
To see how this works, look at the definition of \tableref{tab:example}.
Similarly to subfigures, subtables can be created using \verb|\subtable|, which is also defined by the \textsf{jmlr} class.

\begin{table}[htbp]
 % The first argument is the label,
 % the caption goes in the second argument, and
 % the table contents go in the third argument.
\floatconts{tab:example}%
  {\caption{An example table with nice horizontal lines and without unnecessary vertical lines}}%
  {
    \begin{tabular}{rl}
      \toprule % from booktabs package
      \bfseries Dataset & \bfseries Result\\
      \midrule % from booktabs package
      Data1 & 0.12345\\
      Data2 & 0.67890\\
      Data3 & 0.54321\\
      Data4 & 0.09876\\
      \bottomrule % from booktabs package
    \end{tabular}
  }
\end{table}

\subsection{Algorithms}\label{sec:algorithms}

Enumerated textual algorithms can be displayed using the \texttt{algorithm} environment; see the \textsf{jmlr} class documentation and sample file for a description.\footnotemark[1]
Code can be displayed using the automatically loaded \texttt{algorithm2e} environment defined by the \textsf{algorithm2e} package.\footnote{See the \textsf{algorithm2e} documentation at \url{https://ctan.org/pkg/algorithm2e}.}

\section{Citations and Bibliography}\label{sec:cite}
The references must be managed using Bib\TeX.
The \textsf{jmlr} class automatically loads \textsf{natbib} and the appropriate style file.
So you have to use the commands provided by this package.\footnote{You can find the \textsf{natbib} documentation at \url{https://ctan.org/pkg/natbib}.}
This template file has the citations defined in the accompanying BibTeX file \texttt{isipta2021-template.bib}.
For a parenthetical citation use \verb|\citep|.
For example: “Good introductions to the topic are available \citep{latexcompanion}.”
For a textual citation use \verb|\citet|.
For example: “\citet{einstein} discusses electrodynamics of moving bodies.”
The citation style can be chosen using the \verb|\citestyle| command in the preamble.

The bibliography is displayed using \verb|\bibliography|.

\appendix

\section{Boring Stuff}\label{apd:first}
In case you wish to structure your paper using appendices, you can do so.
However, they also count towards the page limit.

\textbf{But, everything below this line does not count towards the page limit.}
%% For papers, sections below this line do not count towards the page limit

\acks{%
Acknowledgments can go here.
This includes acknowledgments for financial support as well as for support from other people.
}

\section*{Author Contributions}
If you wish, you can mention which of the authors did what.
Otherwise this section can be omitted.

\section*{Competing Interests}
In case any author has some competing interest it has to be mentioned here.
Otherwise this section can be omitted.

\bibliography{isipta2021-template}
% should be alandvonvereweg21.bib if this were a submission

\end{document}

### 2021-04-18 paper.tex
Initial Overleaf Import

--- 2021-04-18 old/old_isipta.tex
@@
-\documentclass[pmlr,twocolumn,a4paper,10pt]{jmlr}
-% \documentclass[pmlr,twocolumn,10pt]{jmlr} % useful when printing your own Letter copy; should not impact layout; do not use for submission
-% This class automatically loads the following packages:
-% amsmath, amssymb, natbib, graphicx, xcolor, url, algorithm2e, hyperref
-  \citestyle{plain} % comment to get author-year; see the natbib docs for more options
-\usepackage{isipta2021}
-% This style file
-% * sets the inputencoding to utf8 (which should be used),
-% * loads mathtools (fixes for amsmath) and
-% * the font packages textcomp, mathptmx, helvet, and courier (so no font packages should be loaded) and neither should font size be changed
-%
-%% Choose your variant of English; be consistent
+\documentclass[runningheads]{llncs}
+\usepackage{graphicx}
+\usepackage{xcolor} 
+\usepackage{amsmath} 
+\usepackage{amstext} 
+\usepackage{amssymb} 
+\usepackage{amsfonts} 
+\usepackage{mathptmx} 
+\usepackage[scaled=.90]{helvet} 
+\usepackage{courier} 
+\usepackage{textcomp} 
+\usepackage{hyperref} 
+\usepackage{array}
+\usepackage{varwidth}
 \usepackage[american]{babel}
+\usepackage{mathtools} % fixes and extends amsmath
+\mathtoolsset{mathic}
+\allowdisplaybreaks
+\usepackage{mathptmx}
+\usepackage{tabu}
+%\usepackage{breqn}
 \usepackage{algorithm,algorithmic,bm}
-% \usepackage[british]{babel}
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+\renewcommand\UrlFont{\color{blue}\rmfamily}
 %% Suggested packages, as needed:
-% \usepackage{siunitx} % for proper typesetting of numbers and units
 \usepackage{booktabs} % commands to create good-looking tables
-% \usepackage{rotating} % for sideways figures and tables
-% \usepackage{longtable} % for long tables
-\usepackage{tikz} % nice language for creating drawings and diagrams
-%% Self-defined macros
-\newcommand{\swap}[3][-]{#3#1#2} % just an example
-%% Frontmatter
-% Authors: DO NOT EDIT
-\jmlrworkshop{ISIPTA 2021}
-\title[Short Title]{% [Short title] can be omitted if title is short enough
-  Credal Adaptive Testing
-  %Title in Title Case;\titlebreak~ % tilde needed to get space in short title
-  %Use the Same Style for Your Section Titles
-}
-
-\author{% Authors are listed one per line and grouped per affiliation
-  \Name{permutation of Claudio/Giorgia/Francesca/Alessandro}\\ % Accented characters require some attention
-  \addr IDSIA
-  %\AND
-  %\Name{Andrés Cano}\Email{acu@decsai.ugr.es}\\
-  %  \Name{Serafín Moral}\Email{smc@decsai.ugr.es}\\
-  %\addr Computer Science and Artificial Intelligence, University of Granada, Spain
-  %\AND
-  %\Name{Jasper {De Bock}}\Email{Jasper.DeBock@UGent.be}\\
-  %\addr Electronics and Information Systems, Ghent University, Belgium
-}
-
+\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
+%drawing custom shapes
+\usetikzlibrary{%
+	arrows,%
+	calc,%
+	fit,%
+	patterns,%
+	plotmarks,%
+	shapes.geometric,%
+	shapes.misc,%
+	shapes.symbols,%
+	shapes.arrows,%
+	shapes.callouts,%
+	% shapes.multipart,%
+	% shapes.gates.logic.US,%
+	% shapes.gates.logic.IEC,%
+	% er,%
+	% automata,%
+	backgrounds,%
+	chains,%
+	topaths,%
+	trees,%
+	petri,%
+	mindmap,%
+	matrix,%
+	% calendar,%
+	folding,%
+	fadings,%
+	through,%
+	positioning,%
+	scopes,%
+	decorations.fractals,%
+	decorations.shapes,%
+	decorations.text,%
+	decorations.pathmorphing,%
+	decorations.pathreplacing,%
+	decorations.footprints,%
+	decorations.markings,%
+	shadows}
+\usetikzlibrary{arrows,automata,circuits}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.13}
+\usepackage{pgfkeys}
+%\usepackage{trace-pgfkeys}
 \begin{document}
+\title{Approximating Information-Theoretic Scores\\for Adaptive Tests}
+%%\thanks{Supported by organization x.}}
+%\titlerunning{Abbreviated paper title}
+\author{permutation of Alessandro Antonucci \and
+Francesca Mangili \and
+Claudio Bonesana\and
+Giorgia Adorni}
+\authorrunning{F. Author et al.}
+\institute{Dalle Molle Institute for Artificial Intelligence USI-SUPSI -- IDSIA \\
+\email{\{alessandro,francesca,claudio.bonesana,giorgia.adorni\}@idsia.ch}}
 \maketitle          
-
-\begin{abstract}% No length restrictions, but keep things reasonable
-An \emph{adaptive} test is a computer-based testing technique which adjusts the sequence of questions on the basis of the estimated ability level of the test taker.
-We suggest the use of \emph{credal networks}, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers.
+\begin{abstract}
+A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skill levels of the test taker.
+Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills.
+Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model.
+This might make inference considerably harded in the underlying model, this being especially the case for the information theoretic quantity generally used for these models.
+We present.
+
+with xxx. Interval valued quantification
+
+We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers.
 Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge.
-The counterpart is a less straightforward identification of the information-theoretic measure controlling the question-selection and the test-stopping criteria.
+The counterpart is a less straightforward identification of the
+information-theoretic measure controlling the question-selection and the test-stopping criteria.
 We elaborate on these issues and propose a sound and computationally feasible procedure.
-Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
+Validation against a Bayesian-network approach
+on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
+%\keywords{credal networks  \and adaptive test \and bayesian network.}
 \end{abstract}
-\begin{keywords}% Keywords provide context for readers, so put in up to about half a dozen
-  keyword, mot clé, Williams-coherence, trefwoord, imprecise Markov chain
-\end{keywords}
-
-\section{Single Skill Model}
+\section{Testing Algorithms}
+The typical goal of a test or exam is to evaluate the knowledge level of a student or examinee $\sigma$ on the basis of her answers to a number of questions or exercises.
+Let $\bm{Q}$ denote a repository of questions available to the instructor.
+The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be fixed.
+We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the student and able to decide when the test should stop.
+A standard TA pseudocode is in Algorithm \ref{alg:ta}, where $\bm{e}$ denotes the array of the answers collected from the student $\sigma$.
+
+\begin{algorithm}[htbp!]
+    \caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
+    \begin{algorithmic}[1]
+    \STATE $\bm{e}=\emptyset$
+        \WHILE{ {\bf not} $\tt{Stopping}(\bm{e})$}
+        \STATE $Q^* \gets \tt{PickQuestion}(\bm{Q},\bm{e})$
+        \STATE $q^* \gets {\tt{Answer}}(Q^*,\sigma)$
+        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
+        \STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
+        \ENDWHILE
+        \STATE {\bf return} $\tt{Evaluate}(\bm{e})$
+    \end{algorithmic}\label{alg:ta}
+\end{algorithm}
+
+The Boolean function ${\tt Stopping}$ decides whether or not the test should end, this choice being possibly based on the previous answers as collected in $\bm{e}$.
+Trivial examples of such stopping rules might be based on the number of questions asked to the student (${\tt Stopping}(\bm{e})=1$ if and only if $|\bm{e}|>n$) or on the number of correct answers provided that a maximum number of questions is not exceeded.
+Function ${\tt PickQuestion}$ is instead in charge of deciding which question should be asked to the student from the repository $\bm{Q}$.
+A TA is called \emph{adaptive} when this function is based on the previous answers $\bm{e}$.
+Trivial non-adaptive strategies might consist in randomly picking an element of $\bm{Q}$ or following a fixed order.
+Function ${\tt Answer}$ is simply collecting (or simulating) the answer of the student $\sigma$ to a particular question $Q$.
+In our assumptions, this answer is not affected by the previous answers to other questions.\footnote{Generalized setups where the quality of the student answer is affected by the previous answers will be discussed at the end of the paper.
+This might include a \emph{fatigue} model negatively affecting the quality of the answers when many questions have been already answered as well as the presence of \emph{revealing} questions that might improve the quality of other answers.}
+
+Finally, the ${\tt Evaluate}$ function decides the overall judgement for the test (e.g., a numerical grade or a pass/fail Boolean) on the basis of all the answers collected after the test termination.
+Trivial examples of such function are the percentage of correct answers or a Boolean that is true when a sufficient percentage of correct answers has been provided.
+Note also that in our assumptions the TA is \emph{exchangeable}, i.e., the stopping rule, the question finder and the evaluation function are invariant with respect to permutations of $\bm{e}$.
+In other words, the would pick the same next question and the same evaluation for two students who provided the same list of answers in two different orders and similarly would decide to stop or not to stop in the same way.
+
+The typical goal of a TA is to achieve a reliable evaluation of the student $\sigma$.
+As each answer is assumed to improve such quality, asking all the questions, no matter their order because of the exchangeability assumption, would be an obvious choice.
+Yet, asking all the questions in the repository might be impractical (e.g., because of time limitations) in some cases or just provide an unnecessary burden to the students.
+The goal of a good TA is therefore to trade off the accuracy of the evaluation and the number of questions.\footnote{In some generalized setups, other elements such as the \emph{serendipity} to avoid boring sequences of questions might be also considered.}
+
+Item response theory is a popular *** Something about IRT here ***.
+Most of these approaches are based an a unidimensional representation of the student knowledge level.
+Proposals to cope with multidimensional IRTs have been considered, but this results critical when coping with dependencies between them.
+For this reason probabilistic modelling can be considered.
+This is the topic of the next section.
+
+\section{Bayesian Adaptive Testing Algorithms}
+In the setup of algorithm.
+
 Let us introduce the discussion by means of a simple example modelling the knowledge level of a student in a particular domain.
@@
 
-\begin{algorithm}[htp!]
-    \caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple}}
-    \begin{algorithmic}[1]
-        \FOR {$s\in\bm{S}$}
-        \WHILE{ $h > h^*$}
-        \STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
-        \STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
-        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-        \STATE $h \gets H[P(S|\bm{e}]$
-        \ENDWHILE
-        \ENDFOR
-        \STATE {\bf return} $\arg\max P(s|\bm{e})$
-    \end{algorithmic}
-\end{algorithm}
-
-\newpage
-
-Let $S$ denote an ordinal variable with $m$ states, denoting the knowledge level of a student with respect to a particular knowledge domain. Let $Q$ denote a question to be
-
+	%
+	%
 	\section{Brainstorming}
@@
 	\begin{equation}
-\sigma_Q := \max_{P\in K} \left[ 
+		\sigma_Q := \max_{P\in K} \bigl[ 
 		\max \{ P(S=0,Q=0) , P(S=1,Q=0) \}  + \max \{ P(S=0,Q=1),P(S=1,Q=1)\}
-\right]
+		\bigr]
 	\end{equation}
@@
 	\begin{itemize}
-\item Let $\bm{S}:=(S_1,\ldots,S_N)$ denote the set of skills in the model. We describe a \emph{student} as a joint observation $\bm{s}$ of the skills.
+		\item Let $\bm{S}:=(S_1,\ldots,S_N)$ denote the set of skills in the model. We 
+		describe a \emph{student} as a joint observation $\bm{s}$ of the skills.
 		\item Let $M$ denote the network \emph{skeleton}, i.e., the model over the skills only
 		\item A question $Q$ is a binary variables with states right and wrong
-\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this skill
-\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
+		\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this 
+		skill
+		\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question 
+		associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
 		\item Let $n_q$ be the maximum number of questions we might ask for each skill
@@
 		\item A question $Q$ is a binary variables with states right and wrong
-\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this skill
-\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
+		\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this 
+		skill
+		\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question 
+		associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
 		\item Let $n_q$ be the maximum number of questions we might ask for each skill
@@
 			a model (BN, skeleton) $M$ over the skills only
-    \\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
+			\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions 
+			$\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
 			the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
@@
 			\FOR {$i\gets\{1,\ldots,n\}$}
-    \STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets (M,\mathcal{Q},\emptyset,\emptyset)$
+			\STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
+			(M,\mathcal{Q},\emptyset,\emptyset)$
 			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
@@
 
-\textcolor{red}{Maybe, instead of (3) I would use a known measure of qualitative variation (\url{https://en.wikipedia.org/wiki/Qualitative_variation}) which extend easily to non binary answers, e.g., the variation ratio ($1-\max_q(P(q))$) or the M1 Gibb's index also known as coefficient of unalikeability and somehow related to the variance (it is the variance in the binary case): $M1 = 1-\sum_q P(q)^2$, or even the entropy, which is not so difficult to compute for $P(Q)$.
-They are all equivalent in the binary case, as they are all monotonic function of $\max_q(P(q))$ only.
-}
+	\textcolor{red}{Maybe, instead of (3) I would use a known measure of qualitative 
+	variation (\url{https://en.wikipedia.org/wiki/Qualitative_variation}) which extend easily to 
+	non binary answers, e.g., the variation ratio ($1-\max_q(P(q))$) or the M1 Gibb's index 
+	also known as coefficient of unalikeability and somehow related to the variance (it is 
+	the variance in the binary case): $M1 = 1-\sum_q P(q)^2$, or even the entropy, which is 
+	not so difficult to compute for $P(Q)$. They are all equivalent in the binary case, as 
+	they are all monotonic function of $\max_q(P(q))$ only. }
 
 	\begin{algorithm}[htp!]
-    \caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
-    the credal CPTs of the questions in $\mathcal{Q}$, i.e., $\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
+		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
+		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
+			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
+			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
 			an upper entropy threshold $\overline{h}^*$,\\
 			a score function for questions $\sigma$
-    \label{alg:simple}}
+			\label{alg:simple2}}
 		\begin{algorithmic}[1]
 			\FOR {$i\gets\{1,\ldots,n\}$}
-    \STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets (\mathcal{Q},\emptyset,\emptyset)$
+			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
+			(\mathcal{Q},\emptyset,\emptyset)$
 			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
@@
 	\begin{algorithm}[htp!]
-    \caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple}}
+		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
 		\begin{algorithmic}[1]
@@
 	\subsection*{Formulae}
-Let us define the functions, all defined for $x\in [0,1]$, apart from $f$ defines for each $x\geq 0$:
+	Let us define the functions, all defined for $x\in [0,1]$, apart from $f$ defines for each 
+	$x\geq 0$:
 	\begin{eqnarray}
@@
 
-A few remarks.
-Function $f$ is a monotonically decreasing function with values in $[0,1]$.
-Function $h(x)$ corresponds to the entropy of a mass function over a Boolean variable with a probability equal to $x$.
-On the extreme points of its domain, we take the limit value, i.e., zero.
-The function is unimodal and achieve its maximum on  $x=\frac{1}{2}$.
-Function $l$ is the popular \emph{logit} function, it is monotonically increasing function of $x$ and $l(1-x)=l(x)^-1$.
-Function $m(x)$ is $x$ for $x\geq \frac{1}{2}$ and $1-x$ otherwise.
-Exactly as $h$, functions $m$ and $\tilde{i}_\epsilon$, for each $\epsilon>0$, have the same (zero) value for $x=0$ and $x=1$, being all unimodal with maximum in $x=\frac{1}{2}$.
+	A few remarks. Function $f$ is a monotonically decreasing function with values in 
+	$[0,1]$. Function $h(x)$ corresponds to the entropy of a mass function over a Boolean 
+	variable with a probability equal to $x$. On the extreme points of its domain, we take 
+	the limit value, i.e., zero. The function is unimodal and achieve its maximum on  
+	$x=\frac{1}{2}$. Function $l$ is the popular \emph{logit} function, it is monotonically 
+	increasing function of $x$ and $l(1-x)=l(x)^-1$. Function $m(x)$ is $x$ for $x\geq 
+	\frac{1}{2}$ and $1-x$ otherwise. 
+	Exactly as $h$, functions $m$ and $\tilde{i}_\epsilon$, for each $\epsilon>0$, have the 
+	same (zero) value for $x=0$ and $x=1$, being all unimodal with maximum in 
+	$x=\frac{1}{2}$.
 	Finally, the popular Gumbel's trick implies:
@@
 	\subsection*{Another Formula}
-Consider a PMF $P(X)$.
-Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$.
-Let $\mathcal{P}$ denote the set of all PMFs with the same $p^*:=P(x^*)$.
-The most entropic PMF in $\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq x^*$ where $m:=|\mathcal{X}|$.
-While the least entropic is the one with a $x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the other masses equal to zero.
-These two bounds on the entropy are therefore:
+	Consider a PMF $P(X)$. Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$. Let $\mathcal{P}$ 
+	denote the set of all PMFs with the same $p^*:=P(x^*)$. The most entropic PMF in 
+	$\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq x^*$ where 
+	$m:=|\mathcal{X}|$. While the least entropic is the one with a 
+	$x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the other masses 
+	equal to zero. These two bounds on the entropy are therefore:
 	\begin{eqnarray}
@@
 	\end{equation}
-The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being zero for binary variables.
+	The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as 
+	soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being 
+	zero for binary variables.
 
 	\subsection*{Toy Example}
-Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean question/answer $Q$.
-Let us shape the model as a BN, $S\to Q$.
-The prior $P(S)$ is specified by a parameter $p:=P(s_1)$.
-The question CPT $P(Q|S)$ might be specified instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$.
-The informativeness score we assign two the question is
+	Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean 
+	question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is 
+	specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified 
+	instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The 
+	informativeness score we assign two the question is
 	\begin{equation}
@@
 	\begin{equation}
-P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}} 
+		P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ 
+		(1-p)(1-\pi_0)}{p (1-\pi_1)}} 
 	\end{equation}
@@
 	\end{multline}
-where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 p + \pi_0 (1-p)$.
+	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
+	p + \pi_0 (1-p)$.
 
@@
 	Note that, if $s^*(q)$ is the same for each $q$, the score just corresponds to $P(s^*)$. 
-In other words, the score is flat is each answer gives the same most likely skill level *** reasonable ***.
-Let us move to an imprecise setting and intend the $s^*$ state as
-$s^*(q):=\arg\max_s \overline{P}(s|q)$.
-The objective function is a linear combination of $P(s*(q)$ whose coefficient can be optimized independently.
-Overall, this corresponds to a linear programming task.
-$$\max_s \overline{P}(s,q) = \max_s \max_P P(s) P(q|s) = \max_s \overline{P}(s) \overline{P}(q|s)$$
+	In other words, the score is flat is each answer gives the same most likely skill level *** 
+	reasonable ***. Let us move to an imprecise setting and intend the $s^*$ state as
+	$s^*(q):=\arg\max_s \overline{P}(s|q)$. The objective function is a linear combination of 
+	$P(s*(q)$ whose coefficient can be optimized independently. Overall, this corresponds 
+	to a linear programming task.
+	$$\max_s \overline{P}(s,q) = \max_s \max_P P(s) P(q|s) = \max_s \overline{P}(s) 
+	\overline{P}(q|s)$$
 
@@
 
-Comment1: This sentence is not clear to me:  "as $\gamma>0$. $f \circ m[\gamma/l(p)] = f[\gamma m(l(p))]$".\\
+	Comment1: This sentence is not clear to me:  "as $\gamma>0$. $f \circ m[\gamma/l(p)] 
+	= f[\gamma m(l(p))]$".\\
 	Comment2: How shall we use the Gumbel's trick
 
-Comment 3: Below I obtain something that looks different to me, but maybe it is equivalent.
+	Comment 3: Below I obtain something that looks different to me, but maybe it is 
+	equivalent.
 
@@
 		\sigma_Q(p,\pi_0,\pi_1)=\\
-m\left(\frac{\pi_1 p}{P(q_1)}\right) \cdot P(q_1)  +
-m\left(\frac{(1-\pi_1) p}{1-P(q_1)}\right) \cdot (1-P(q_1))\,
+		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
+		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
 	\end{multline}
@@
 	\begin{multline}
-m\left(\frac{\pi_1 p}{P(q_1)}\right) =\\
-2max\left(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \right) =\\
-2max\left(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \right) =\\
-\frac{2}{P(q_1)}max\left(\pi_1 p,\pi_0(1- p)\right).\\
+		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
+		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
+		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
+		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
 	\end{multline}
@@
 	\begin{multline}
-m\left(\frac{(1-\pi_1) p}{1-P(q_1)}\right) =\\
-\frac{2}{1-P(q_1)}max\left((1-\pi_1) p,(1-\pi_0)(1- p)\right),\\
+		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
+		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
 	\end{multline}
@@
 
- $\P(s,q=0)$ and $P(s,q=1)$ are both functions of $p, \pi_0,$ and $\pi_1$ so I do not think we can split the optimization
+	$\P(s,q=0)$ and $P(s,q=1)$ are both functions of $p, \pi_0,$ and $\pi_1$ so I do not 
+	think we can split the optimization
 
@@
 
-However, it could be a reasonable approximation. Then, we can switch the optimization over $P$ and $s$ because they are both max, and obtain: 
+	However, it could be a reasonable approximation. Then, we can switch the optimization 
+	over $P$ and $s$ because they are both max, and obtain: 
 	$$\max_s \overline{P}(s)\overline{P}(q=0|s)+\max_s  \overline{P}(s)\overline{P}(q=1|s)$$.
 
-If instead we are looking for the minimum over P, we cannot switch the optimization over $P$ and $s$:
+	If instead we are looking for the minimum over P, we cannot switch the optimization 
+	over $P$ and $s$:
 	$$\min_P \max_s P(s,q) \neq \max_s \min_P P(s,q)$$.
@@
 		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
-2\min_{p,\pi_0,\pi_1} \left( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \right) \approx \\
-2\left(\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \right) 
+		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
+		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
+		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
+		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
 	\end{multline}
 
-Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It can be written as
+	Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It 
+	can be written as
 	$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
 	where
+
 	\begin{multline}
@@
 		\begin{array}{ll}
-\text{subject to} & \pi_1 p < \pi_0 (1-p)
+			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
 			~&\underline{x} \leq x\leq \overline{x}\\ 
@@
 
-In general, let $N_s$ be the number of skill levels and $N_q$ the number of possible answers, then the number of quadratic optimizations to solve should be equal to $N_s\cdot N_q$.
-
-In this two dimensional example, we might not need the approximation above as the minimization in \ref{eq:minimization} can be written as $\min_{i=1:4}(\tilde{P}_1)$, where
+	In general, let $N_s$ be the number of skill levels and $N_q$ the number of possible 
+	answers, then the number of quadratic optimizations to solve should be equal to 
+	$N_s\cdot N_q$.
+
+	In this two dimensional example, we might not need the approximation above as the 
+	minimization in \ref{eq:minimization} can be written as $\min_{i=1:4}(\tilde{P}_1)$, where
 
@@
 	\end{multline}
-and so on. However, in this case, the number of optimizations to solve should be $N_s^{N_q}$, that is, it grows exponentially with  $N_q$.
+	and so on. However, in this case, the number of optimizations to solve should be 
+	$N_s^{N_q}$, that is, it grows exponentially with  $N_q$.
 
@@
 	\section{Introduction}\label{sec:intro}
-The use of communication and information technologies in education is actually growing.
-Both online (e.g., MOOCs) and classroom courses are urgently asking for more flexible and sophisticated e-learning and e-testing tools \cite{pollard2001exploring}.
-AI-based approaches such as intelligent tutoring systems, adapting the interaction with the student on the basis of his/her knowledge and/or psychological profile, represent an important direction to improve the quality of the (e-)learning experience \cite{burns2014intelligent}.
-
-Bayesian networks (BNs) \cite{koller2009} have been used to model the knowledge driving such intelligent systems \cite{almond2015bayesian}.
-However, collecting large sets of reliable data in educational domains may be difficult and time consuming (e.g., a course with few students, or taught for the first time), and the quantification should be based on expert knowledge only.
-To elicit a Bayesian network, an expert might face questions like: ``\emph{which is the probability of a student with a particular knowledge level giving the right answer to a question?}''.
-Giving sharp probabilities for questions of this kind can be problematic for an expert, whose knowledge is mostly qualitative (e.g., ``\emph{a right answer is very unlikely}'').
-Fuzzy linguistic approaches represent a viable, non-numerical, way to address these issues \cite{badaracco2013fuzzy}.
-To stick within the probabilistic framework, verbal-numerical probability scales associated with sharp values \cite{renooij1999talking} or intervals \cite{walley1991statistical} have been also proposed.
-
-In this paper we show how to conjugate an interval-valued probabilistic elicitation of expert knowledge with the BN framework.
-This means to cope with a \emph{credal network} (CN) \cite{novapiatti}, a generalization of BNs based on the imprecise probability theory \cite{walley1991statistical}, where local parameters are defined by set-valued probabilities.
-This simplifies the elicitation process and offers a more reliable handling of the related uncertainty.
-Moving from BNs to CNs implies two main issues: (i) numerical inferences will be interval-valued too, thus making debatable both the decision criterion \cite{troffaes} an the information measures \cite{klir1999uncertainty} to adopt; and (ii) inference tasks in CNs typically belongs to higher complexity classes than their Bayesian counterparts \cite{maua14jair}.
-Both these issues are addressed by defining a computationally feasible procedure based on CNs to be used for practical implementation of intelligent systems solely specified by expert knowledge.
-To the best of our knowledge this is the first attempt to perform e-testing with models of this kind.
-
-We focus on the application of CNs to \emph{computer adaptive testing} (CAT), i.e., an approach to e-testing that adjusts the sequence and the number of questions to the ability level of the test taker.
-CATs have the potential to make the test an individualised experience that challenges and does not discourage the test takers, as most of the questions are near their ability levels.
-Building upon \emph{item response theory} \cite{hambleton1985item}, the common background underpinning CATs, graphical modeling (such as BNs and CNs) offers a powerful language for describing complex multivariate dependencies between skills and rich tasks.
-Several researchers have exploited the potential of BNs both in adaptive and non-adaptive educational assessment \cite{vomlel2004building,plajner2015}.
-These authors focus on applications for which data are available to learn the model parameters.
-We regard this point as a serious limitation, possibly hindering CATs adoption by many teachers and instructors.
-
-We start from a CAT procedure based on BNs that uses \emph{entropy} as the information-theoretic measure driving the question selection and the stopping criteria (Sect.~\ref{sec:bayesianCAT}).
-Our goal is to improve  this procedure by using CNs to better describe the pervasive uncertainty characterizing the model.
-A direct extension of the Bayesian framework to CNs would require the computation of bounds for the conditional entropy with respect to the CN specification.
-This corresponds to a non-linear non-convex optimization task.
-We therefore propose a number of simplifying assumptions to overcome this problem at the price of accepting sub-optimal question selection schemes (Sect.~\ref{sec:credalCAT}).
-The approach is tested on a real-world benchmark about German language proficiency assessment (Sect.~\ref{sec:conc}).
-The results are promising: CAT based on CNs is effective in reducing the number of questions while maintaining a high accuracy in the evaluation and the approximations introduced do not compromise the procedure's effectiveness.
+	The use of communication and information technologies in education is actually 
+	growing. Both online (e.g., MOOCs) and classroom courses are urgently asking for 
+	more flexible and sophisticated e-learning and e-testing tools 
+	\cite{pollard2001exploring}. AI-based approaches such as intelligent tutoring systems, 
+	adapting the interaction with the student on the basis of his/her knowledge and/or 
+	psychological profile, represent an important direction to improve the quality of the 
+	(e-)learning experience \cite{burns2014intelligent}.
+
+	Bayesian networks (BNs) \cite{koller2009} have been used to model the knowledge 
+	driving such intelligent systems \cite{almond2015bayesian}. However, collecting large 
+	sets of reliable data in educational domains may be difficult and time consuming (e.g., a 
+	course with few students, or taught for the first time), and the quantification should be 
+	based on expert knowledge only. To elicit a Bayesian network, an expert might face 
+	questions like: ``\emph{which is the probability of a student with a particular 
+	knowledge level giving the right answer to a question?}''. Giving sharp probabilities for 
+	questions of this kind can be problematic for an expert, whose knowledge is mostly 
+	qualitative (e.g., ``\emph{a right answer is very unlikely}''). Fuzzy linguistic approaches 
+	represent a viable, non-numerical, way to address these issues 
+	\cite{badaracco2013fuzzy}. To stick within the probabilistic framework, 
+	verbal-numerical probability scales associated with sharp values 
+	\cite{renooij1999talking} or intervals \cite{walley1991statistical} have been also 
+	proposed.
+
+	In this paper we show how to conjugate an interval-valued probabilistic elicitation of 
+	expert knowledge with the BN framework. This means to cope with a \emph{credal 
+	network} (CN) \cite{novapiatti}, a generalization of BNs based on the imprecise 
+	probability theory \cite{walley1991statistical}, where local parameters are defined by 
+	set-valued probabilities. This simplifies the elicitation process and offers a more reliable 
+	handling of the related uncertainty. Moving from BNs to CNs implies two main issues: 
+	(i) numerical inferences will be interval-valued too, thus making debatable both the 
+	decision criterion \cite{troffaes} an the information measures \cite{klir1999uncertainty} 
+	to adopt; and (ii) inference tasks in CNs typically belongs to higher complexity classes 
+	than their Bayesian counterparts \cite{maua14jair}. Both these issues are addressed by 
+	defining a computationally feasible procedure based on CNs to be used for practical 
+	implementation of intelligent systems solely specified by expert knowledge. To the best 
+	of our knowledge this is the first attempt to perform e-testing with models of this kind.
+
+	We focus on the application of CNs to \emph{computer adaptive testing} (CAT), i.e., an 
+	approach to e-testing that adjusts the sequence and the number of questions to the 
+	ability level of the test taker. CATs have the potential to make the test an individualised 
+	experience that challenges and does not discourage the test takers, as most of the 
+	questions are near their ability levels. Building upon \emph{item response theory} 
+	\cite{hambleton1985item}, the common background underpinning CATs, graphical 
+	modeling (such as BNs and CNs) offers a powerful language for describing complex 
+	multivariate dependencies between skills and rich tasks. Several researchers have 
+	exploited the potential of BNs both in adaptive and non-adaptive educational 
+	assessment \cite{vomlel2004building,plajner2015}. These authors focus on applications 
+	for which data are available to learn the model parameters. We regard this point as a 
+	serious limitation, possibly hindering CATs adoption by many teachers and instructors.
+
+	We start from a CAT procedure based on BNs that uses \emph{entropy} as the 
+	information-theoretic measure driving the question selection and the stopping criteria 
+	(Sect.~\ref{sec:bayesianCAT}). Our goal is to improve  this procedure by using CNs to 
+	better describe the pervasive uncertainty characterizing the model. A direct extension 
+	of the Bayesian framework to CNs would require the computation of bounds for the 
+	conditional entropy with respect to the CN specification. This corresponds to a 
+	non-linear non-convex optimization task. We therefore propose a number of 
+	simplifying assumptions to overcome this problem at the price of accepting 
+	sub-optimal question selection schemes (Sect.~\ref{sec:credalCAT}). The approach is 
+	tested on a real-world benchmark about German language proficiency assessment 
+	(Sect.~\ref{sec:conc}). The results are promising: CAT based on CNs is effective in 
+	reducing the number of questions while maintaining a high accuracy in the evaluation 
+	and the approximations introduced do not compromise the procedure's effectiveness.
 
@@
 
-\paragraph{Skills modeling.} We describe the knowledge level of a student as a collection of categorical variables, say $\bm{X}:=(X_1,\ldots,X_n)$, called \emph{skills}.
-A joint \emph{probability mass function} (PMF) $P(\bm{X})$ describes the uncertainty about the actual values of the skills.
-A compact specification of such multivariate model can be achieved by a BN \cite{koller2009}.
-This corresponds to: (i) a directed acyclic graph whose nodes are in one-to-one correspondence with the variables of $\bm{X}$; and (ii), for each $X_i\in\bm{X}$,
- a collection of conditional PMFs $P(X_i|\mathrm{\pi}_{X_i})$, one for each value $\pi_{X_i}$ of the joint variable $\mathrm{\Pi}_{X_i}$ denoting the \emph{parents} (i.e., the immediate predecessors) of $X_i$.
-The \emph{Markov condition} for BNs assumes every variable conditionally independent of its non-descendants non-parents given the parents.
-Accordingly, the joint PMF associated with a BN is such that $P(\bm{x}):= \prod_{i=1}^n P(x_i|\pi_{X_i})$, for each $\bm{x}$, where the values of $x_i$ and $\pi_{X_i}$ are those consistent with $\bm{x}$.
-
-\paragraph{Questions modeling.} The above joint probabilistic model describes the uncertainty about the skills of a student prior to his/her answers to the questions.
-To evaluate the student we formulate a number of \emph{questions}, described as a collection of variables $\bm{Y}:=(Y_1,\ldots,Y_m)$.
-We assume these variables to be Boolean, with the true value corresponding to the correct answer.\footnote{Extension to non Boolean answers is trivial as all answers $Y_i$ are \emph{manifest} variables, and, thus, $Y_i$ can be always regarded as a binary variable with the two values denoting the observed answer $y_i$ and its negation \cite{antonucci2009}.} We call \emph{background} of a question the set of skills ``required'' to answer it.
-This can be regarded as a conditional independence statement: given the background skills, the answer to the question is independent of the other skills and of the other questions.
-Following the Markov condition, this can be modeled by representing each question as a leaf node whose parents are the background skills.
-Such augmented graph requires the quantification, for each $Y_j\in\bm{Y}$, of a conditional PMF $P(Y_j|\mathrm{\pi}_{Y_j})$ for each value $\mathrm{\pi}_{Y_j}$ of the background skills $\mathrm{\Pi}_{Y_j}$.
-This procedure defines a BN over the skills and the questions, and hence a joint PMF $P(\bm{X},\bm{Y})$.
-
-\paragraph{Non-adaptive testing.} Let $\bm{Y}=\bm{y}$ denote a student's answers to the test.
-In the above considered framework, the posterior knowledge about the skills is modeled by the joint PMF $P(\bm{X}|\bm{y})$.
-By running standard BN updating algorithms, the most probable level $\tilde{x}_i$ of skill $X_i$ can be therefore evaluated  as $\tilde{x}_i:= \arg\max_{x_i} P(x_i|\bm{y})$, for each $X_i\in\bm{X}$.
-This reflects a non-adaptive, probabilistic approach to student evaluation.
-
-\paragraph{Adaptive testing.} To add adaptiveness to the above approach, every question should be chosen on the basis of the previous answers.
-As the goal is to gather information about the student skills, we evaluate the expected \emph{information gain} (IG, i.e., the change in information entropy) associated with each possible new question, and pick the one maximizing this measure.
-The entropy of a BN over $\bm{X}$ can be computed as $H(\bm{X}):=\sum_{i=1}^n H(X_i|\mathrm{\Pi_{X_i}})$ \cite{koller2009}, where $H(X_i|\mathrm{\Pi_{X_i}}):=\sum_{\pi_{X_i}} H(X_i|\pi_{X_i}) P(\pi_{X_i})$ is the \emph{conditional entropy} for $X$ given its parents and $H(X_i|\pi_{X_i})$ is the entropy of the conditional PMF $P(X_i|\pi_{X_i})$.\footnote{To have entropy levels between zero and one, we define the entropy of the PMF $P(X)$ as $H(X):=-\sum_x P(x) \log_b P(x)$, with $b$ number of states of $X$.} Let $\bm{Y}=\bm{y}$ denote the answers to the questions already asked and $\bm{Y}'$ the set from which the next question should be picked.
-If the answer to every question $Y'\in\bm{Y}'$ would be known, and denoted by $y'$, the question $\tilde{Y}' \in \bf{\mathbf{Y}'}$ to choose would be the one leading to the largest IG.
-Yet, as the decision has to be made before the student's answer, conditional entropy should be considered instead, i.e.,
-\begin{equation}
-\tilde{Y}' := \arg \max_{Y'\in \bm{Y}'} \left[H(\bm{X}|\bm{y})-H(\bm{X}|Y',\bm{y})\right]\,. 
+	\paragraph{Skills modeling.} We describe the knowledge level of a student as a 
+	collection of categorical variables, say $\bm{X}:=(X_1,\ldots,X_n)$, called \emph{skills}. 
+	A joint \emph{probability mass function} (PMF) $P(\bm{X})$ describes the uncertainty 
+	about the actual values of the skills. A compact specification of such multivariate model 
+	can be achieved by a BN \cite{koller2009}. This corresponds to: (i) a directed acyclic 
+	graph whose nodes are in one-to-one correspondence with the variables of $\bm{X}$; 
+	and (ii), for each $X_i\in\bm{X}$, 
+	a collection of conditional PMFs $P(X_i|\mathrm{\pi}_{X_i})$, one for each value 
+	$\pi_{X_i}$ of the joint variable $\mathrm{\Pi}_{X_i}$ denoting the \emph{parents} (i.e., 
+	the immediate predecessors) of $X_i$. The \emph{Markov condition} for BNs assumes 
+	every variable conditionally independent of its non-descendants non-parents given the 
+	parents. Accordingly, the joint PMF associated with a BN is such that $P(\bm{x}):= 
+	\prod_{i=1}^n P(x_i|\pi_{X_i})$, for each $\bm{x}$, where the values of $x_i$ and 
+	$\pi_{X_i}$ are those consistent with $\bm{x}$.
+
+	\paragraph{Questions modeling.} The above joint probabilistic model describes the 
+	uncertainty about the skills of a student prior to his/her answers to the questions. To 
+	evaluate the student we formulate a number of \emph{questions}, described as a 
+	collection of variables $\bm{Y}:=(Y_1,\ldots,Y_m)$. We assume these variables to be 
+	Boolean, with the true value corresponding to the correct answer.\footnote{Extension 
+	to non Boolean answers is trivial as all answers $Y_i$ are \emph{manifest} variables, 
+	and, thus, $Y_i$ can be always regarded as a binary variable with the two values 
+	denoting the observed answer $y_i$ and its negation \cite{antonucci2009}.} We call 
+	\emph{background} of a question the set of skills ``required'' to answer it. This can be 
+	regarded as a conditional independence statement: given the background skills, the 
+	answer to the question is independent of the other skills and of the other questions. 
+	Following the Markov condition, this can be modeled by representing each question as 
+	a leaf node whose parents are the background skills. Such augmented graph requires 
+	the quantification, for each $Y_j\in\bm{Y}$, of a conditional PMF 
+	$P(Y_j|\mathrm{\pi}_{Y_j})$ for each value $\mathrm{\pi}_{Y_j}$ of the background skills 
+	$\mathrm{\Pi}_{Y_j}$. This procedure defines a BN over the skills and the questions, 
+	and hence a joint PMF $P(\bm{X},\bm{Y})$.
+
+	\paragraph{Non-adaptive testing.} Let $\bm{Y}=\bm{y}$ denote a student's answers 
+	to the test. In the above considered framework, the posterior knowledge about the 
+	skills is modeled by the joint PMF $P(\bm{X}|\bm{y})$. By running standard BN updating 
+	algorithms, the most probable level $\tilde{x}_i$ of skill $X_i$ can be therefore 
+	evaluated  as $\tilde{x}_i:= \arg\max_{x_i} P(x_i|\bm{y})$, for each $X_i\in\bm{X}$. This 
+	reflects a non-adaptive, probabilistic approach to student evaluation.
+
+	\paragraph{Adaptive testing.} To add adaptiveness to the above approach, every 
+	question should be chosen on the basis of the previous answers. As the goal is to 
+	gather information about the student skills, we evaluate the expected 
+	\emph{information gain} (IG, i.e., the change in information entropy) associated with 
+	each possible new question, and pick the one maximizing this measure. The entropy of 
+	a BN over $\bm{X}$ can be computed as $H(\bm{X}):=\sum_{i=1}^n 
+	H(X_i|\mathrm{\Pi_{X_i}})$ \cite{koller2009}, where 
+	$H(X_i|\mathrm{\Pi_{X_i}}):=\sum_{\pi_{X_i}} H(X_i|\pi_{X_i}) P(\pi_{X_i})$ is the 
+	\emph{conditional entropy} for $X$ given its parents and $H(X_i|\pi_{X_i})$ is the 
+	entropy of the conditional PMF $P(X_i|\pi_{X_i})$.\footnote{To have entropy levels 
+	between zero and one, we define the entropy of the PMF $P(X)$ as $H(X):=-\sum_x 
+	P(x) \log_b P(x)$, with $b$ number of states of $X$.} Let $\bm{Y}=\bm{y}$ denote the 
+	answers to the questions already asked and $\bm{Y}'$ the set from which the next 
+	question should be picked. If the answer to every question $Y'\in\bm{Y}'$ would be 
+	known, and denoted by $y'$, the question $\tilde{Y}' \in \bf{\mathbf{Y}'}$ to choose 
+	would be the one leading to the largest IG. Yet, as the decision has to be made before 
+	the student's answer, conditional entropy should be considered instead, i.e.,
+	\begin{equation}
+		\tilde{Y}' := \arg \max_{Y'\in \bm{Y}'} 
+		\bigl[H(\bm{X}|\bm{y})-H(\bm{X}|Y',\bm{y})\bigr]\,. 
 		\label{eq:expent}
@@
 		\begin{tikzpicture}[auto,scale=.7]
-\node[block,node distance=.cm,fill=black!10] (pick) {\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
-\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) {\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
-\node[block, right of=pick,node distance=3cm,fill=black!10] (ask) {\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
-\node[block, right of=ask,node distance=3cm,fill=black!10] (collect) {\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
-\node[decision, below of=collect,node distance=1.4cm] (decide) {\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? }\end{varwidth}};
-\node[block, left of=decide, node distance=3cm,fill=black!10] (stop) {\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
-\node[block, left of=stop, node distance=3cm,fill=black!10] (assign) {\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
-\path[line] (decide) -- node {\tiny YES}(stop);
-\path[line] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
-\path[line,dashed] (db) -- (pick);
-\path[line] (pick) -- (ask);
-\path[line] (ask) -- (collect);
-\path[line] (collect) -- (decide);
-\path[line] (decide) -- (stop);
-\path[line] (stop) -- (assign);
+			\node[node distance=.cm,fill=black!10] (pick) 
+			{\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
+			\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) 
+			{\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
+			\node[right of=pick,node distance=3cm,fill=black!10] (ask) 
+			{\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
+			\node[right of=ask,node distance=3cm,fill=black!10] (collect) 
+			{\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
+			\node[below of=collect,node distance=1.4cm] (decide) 
+			{\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? 
+			}\end{varwidth}};
+			\node[ left of=decide, node distance=3cm,fill=black!10] (stop) 
+			{\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
+			\node[left of=stop, node distance=3cm,fill=black!10] (assign) 
+			{\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
+			\draw[] (decide) -- node {\tiny YES}(stop);
+			\draw[] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
+			\draw[dashed] (db) -- (pick);
+			\draw[] (pick) -- (ask);
+			\draw[] (ask) -- (collect);
+			\draw[] (collect) -- (decide);
+			\draw[] (decide) -- (stop);
+			\draw[] (stop) -- (assign);
 		\end{tikzpicture}
@@
 
-CATs should also decide when to stop asking questions.
-Again, entropy can be used as a measure to decide when the current evaluation is sufficiently informative, i.e., we stop the test if the skills entropy given the answers is below some threshold $\tilde{H}$.
-The overall approach is depicted in Fig.~\ref{fig:alg}.
+	CATs should also decide when to stop asking questions. Again, entropy can be used as 
+	a measure to decide when the current evaluation is sufficiently informative, i.e., we stop 
+	the test if the skills entropy given the answers is below some threshold $\tilde{H}$. The 
+	overall approach is depicted in Fig.~\ref{fig:alg}.
 
@@
 
-\paragraph{Credal sets and credal networks.} A set of PMFs over $X_i$ is called here \emph{credal set} (CS) and denoted as $K(X_i)$.
-We always remove the inner points (i.e., those corresponding to convex combinations of the others) of a CS.
-CNs \cite{cozman2000} are generalized BNs whose local PMFs are replaced by CSs.
-The BN defined in the previous section over the skills $\bm{X}$ and the questions $\bm{Y}$ becomes a CN if we replace with CSs the skill-to-skill and skill-to-question conditional PMFs.
-A joint CS $K(\bm{X},\bm{Y})$ is consequently obtained as the collection of all the joint PMFs induced by BNs whose parameters take their values from the corresponding CSs, i.e.,
+	\paragraph{Credal sets and credal networks.} A set of PMFs over $X_i$ is called here 
+	\emph{credal set} (CS) and denoted as $K(X_i)$. We always remove the inner points 
+	(i.e., those corresponding to convex combinations of the others) of a CS. CNs 
+	\cite{cozman2000} are generalized BNs whose local PMFs are replaced by CSs.  The BN 
+	defined in the previous section over the skills $\bm{X}$ and the questions $\bm{Y}$ 
+	becomes a CN if we replace with CSs the skill-to-skill and skill-to-question conditional 
+	PMFs. A joint CS $K(\bm{X},\bm{Y})$ is consequently obtained as the collection of all 
+	the joint PMFs induced by BNs whose parameters take their values from the 
+	corresponding CSs, i.e., 
 	\begin{equation}\label{eq:strongext}
-K(\bm{X},\bm{Y}):=\left\{ P(\bm{X},\bm{Y}) \left| 
+		K(\bm{X},\bm{Y}):=\bigl\{ P(\bm{X},\bm{Y}) \bigl| 
 		\substack{
-P(\bm{x},\bm{y}):=\prod_{i=1}^n P(x_i|\pi_{X_i}) \cdot \prod_{j=1}^m P(y_j|\pi_{Y_j}), \\P(X_i|\pi_{X_i}) \in K(X_i|\pi_{X_i}) ,\, P(Y_j|\pi_{Y_j}) \in K(Y_j|\pi_{Y_j})}
-\right.
-\right\}\,,
-\end{equation}
-where the values of $x_i$, $\pi_{X_i}$, $y_j$, $\pi_{Y_j}$ are those consistent with $\bm{x}$ and $\bm{y}$.
-
-\paragraph{Expert knowledge modeling.} For a reliable expert knowledge modeling, we use CSs induced by \emph{probability intervals}.
-Qualitative judgments about the probability of a state are converted in interval constraints such as $l\leq P(x) \leq u$, with the interval $[l,u]$ capturing the expert knowledge behind the judgment in a more reliable way than a sharp assessment.
-The CS consistent with these constraints is eventually obtained by standard polyhedral algorithms.
-Verbal to interval-numeric scales such as that Tab.~\ref{tb:labels} are used.
-For instance, if for the probability of the true state of the Boolean variable $Y$ the expert judgment is ``very likely'', the corresponding linear constraint is $.2 \leq P(Y=\textrm{true}) \leq .4$.% and we obtain a CS $K(Y)$ with the PMFs $P_1(Y)=[.2,.8]$ and $P_2(Y)=[.4,.6]$ as non-inner points.
-
-\paragraph{Non-adaptive testing.} Given the answers $\bm{y}$ to the questions $\bm{Y}$, we evaluate the student as in the previous section by updating the marginal probabilities of each skill.
-With CNs, these posterior values are set-valued and their characterization can be provided by lower and upper bounds, say $\underline{P}(X_i|\bm{y})$ and $\overline{P}(X_i|\bm{y})$ for each $X_i\in\bm{X}$.
-CN updating algorithms can eventually compute these bounds.
-The task displays higher complexity than in the case of BNs (e.g., exact inference in non-binary singly-connected CNs is NP-hard \cite{maua14jair}), but approximate techniques can be considered when exact inference is unfeasible \cite{antonucci2014e}.
-
-To compare the posterior intervals and decide the actual level of the student we might adopt the (conservative) \emph{interval dominance} criterion \cite{troffaes}, which rejects a level if its upper probability is smaller than the lower probability of some other level.
-Overlaps between intervals might therefore induce a situation of \emph{indecision} between two or more levels.
-This is a so-called \emph{credal} classification of the student level \cite{zaffalon2012evaluating}, and it represents the fact that students answers are somehow contradictory or not informative enough to provide a sharp decision.
-Interval dominance can return unnecessarily imprecise results.
-\emph{Maximality} is a more refined criterion that rejects the levels which are less probable than another level for all the elements of the CS \cite{walley1991statistical}.
-Maximality  can be reduced to multiple updating tasks on auxiliary binary leaf nodes defined for each pair of states \cite{antonucci2014e}.
+			P(\bm{x},\bm{y}):=\prod_{i=1}^n P(x_i|\pi_{X_i}) \cdot \prod_{j=1}^m P(y_j|\pi_{Y_j}), 
+			\\P(X_i|\pi_{X_i}) \in K(X_i|\pi_{X_i}) ,\, P(Y_j|\pi_{Y_j}) \in K(Y_j|\pi_{Y_j})}
+		\bigr.
+		\bigr\}\,,
+	\end{equation}
+	where the values of $x_i$, $\pi_{X_i}$, $y_j$, $\pi_{Y_j}$ are those consistent with 
+	$\bm{x}$ and $\bm{y}$.
+
+	\paragraph{Expert knowledge modeling.} For a reliable expert knowledge modeling, 
+	we use CSs induced by \emph{probability intervals}. Qualitative judgments about the 
+	probability of a state are converted in interval constraints such as $l\leq P(x) \leq u$, 
+	with the interval $[l,u]$ capturing the expert knowledge behind the judgment in a more 
+	reliable way than a sharp assessment. The CS consistent with these constraints is 
+	eventually obtained by standard polyhedral algorithms. Verbal to interval-numeric 
+	scales such as that Tab.~\ref{tb:labels} are used. For instance, if for the probability of 
+	the true state of the Boolean variable $Y$ the expert judgment is ``very likely'', the 
+	corresponding linear constraint is $.2 \leq P(Y=\textrm{true}) \leq .4$.% and we obtain a 
+	%CS $K(Y)$ with the PMFs $P_1(Y)=[.2,.8]$ and $P_2(Y)=[.4,.6]$ as non-inner points.
+
+	\paragraph{Non-adaptive testing.} Given the answers $\bm{y}$ to the questions 
+	$\bm{Y}$, we evaluate the student as in the previous section by updating the marginal 
+	probabilities of each skill. With CNs, these posterior values are set-valued and their 
+	characterization can be provided by lower and upper bounds, say 
+	$\underline{P}(X_i|\bm{y})$ and $\overline{P}(X_i|\bm{y})$ for each $X_i\in\bm{X}$. CN 
+	updating algorithms can eventually compute these bounds. The task displays higher 
+	complexity than in the case of BNs (e.g., exact inference in non-binary 
+	singly-connected CNs is NP-hard \cite{maua14jair}), but approximate techniques can be 
+	considered when exact inference is unfeasible \cite{antonucci2014e}.
+
+	To compare the posterior intervals and decide the actual level of the student we might 
+	adopt the (conservative) \emph{interval dominance} criterion \cite{troffaes}, which 
+	rejects a level if its upper probability is smaller than the lower probability of some other 
+	level. Overlaps between intervals might therefore induce a situation of 
+	\emph{indecision} between two or more levels. This is a so-called \emph{credal} 
+	classification of the student level \cite{zaffalon2012evaluating}, and it represents the 
+	fact that students answers are somehow contradictory or not informative enough to 
+	provide a sharp decision. Interval dominance can return unnecessarily imprecise results. 
+	\emph{Maximality} is a more refined criterion that rejects the levels which are less 
+	probable than another level for all the elements of the CS \cite{walley1991statistical}. 
+	Maximality  can be reduced to multiple updating tasks on auxiliary binary leaf nodes 
+	defined for each pair of states \cite{antonucci2014e}.
 
 	\paragraph{Adaptive testing.}
-To achieve CAT with CNs using entropy as measure of informativeness for PMFs, as in the BN approach of Sect.
-\ref{sec:bayesianCAT}, computation of entropies should be extended to CSs.
-This topic has been the subject of much discussion \cite{klir1999uncertainty}.
-A cautious approach \cite{abellan2003maximum} consists in taking the upper entropy $\overline{H}(\bm{X})$, i.e., the entropy of the most entropic PMF in the convex closure $\overline{K}(\bm{X})$ of  $K(\bm{X})$.
-In our framework, we should, then, look for maximum values of conditional entropies, such as $\overline{H}(X_i|Y',\bm{y})$ or $\overline{H}(X_i|\Pi_{X_i})$, as conditional entropies are required to compute both: (i) the joint (unconditional) entropy $H(\bm{X})$ (and its posterior values); and (ii) the conditional entropies  involved in the  question selection in Eq.~\eqref{eq:expent}.
-By definition a conditional entropy is a convex combination (whose weights are the elements of a marginal PMF) of convex functions (the entropies).
-The objective function might, then, be non-convex, as the weights are also optimization variables.\footnote{E.g., if $f(x)$ and $g(x)$ are convex functions of $x$, $h(x,y):= y f(x) + (1-y) g(x)$ is not convex even for $0 \leq y \leq 1$.}
-
-Then, to bypass this non-convex optimization task, we compute (i) by separately considering the entropies of each skill $X_i\in\bm{X}$.
-This is analogous to the marginal approach commonly considered in multi-label classification to minimize Hamming losses \cite{antonucci2016c}.
-The issue (ii) is more challenging.
-We consider the following upper approximation of $\overline{H}(X_i|Y',\bm{y})$:
+	To achieve CAT with CNs using entropy as measure of informativeness for PMFs, as in 
+	the BN approach of Sect. \ref{sec:bayesianCAT}, computation of entropies should be 
+	extended to CSs. This topic has been the subject of much discussion 
+	\cite{klir1999uncertainty}. A cautious approach \cite{abellan2003maximum} consists in 
+	taking the upper entropy $\overline{H}(\bm{X})$, i.e., the entropy of the most entropic 
+	PMF in the convex closure $\overline{K}(\bm{X})$ of  $K(\bm{X})$. 
+	In our framework, we should, then, look for maximum values of conditional entropies, 
+	such as $\overline{H}(X_i|Y',\bm{y})$ or $\overline{H}(X_i|\Pi_{X_i})$, as conditional 
+	entropies are required to compute both: (i) the joint (unconditional) entropy 
+	$H(\bm{X})$ (and its posterior values); and (ii) the conditional entropies  involved in 
+	the  question selection in Eq.~\eqref{eq:expent}.
+	By definition a conditional entropy is a convex combination (whose weights are the 
+	elements of a marginal PMF) of convex functions (the entropies). The objective 
+	function might, then, be non-convex, as the weights are also optimization 
+	variables.\footnote{E.g., if $f(x)$ and $g(x)$ are convex functions of $x$, $h(x,y):= y 
+	f(x) + (1-y) g(x)$ is not convex even for $0 \leq y \leq 1$.}
+
+	Then, to bypass this non-convex optimization task, we compute (i) by separately 
+	considering the entropies of each skill $X_i\in\bm{X}$. This is analogous to the marginal 
+	approach commonly considered in multi-label classification to minimize Hamming losses 
+	\cite{antonucci2016c}. The issue (ii) is more challenging. We consider the following 
+	upper approximation of $\overline{H}(X_i|Y',\bm{y})$:
 	\begin{equation}
@@
 	\begin{equation}\label{eq:entropy}
-\overline{H}(X_i|\bm{y}) := \sup_{P(X_i|\bm{y}) \in \overline{K}(X_i|\bm{y})} H(X_i|\bm{y})\,,
-\end{equation}
-where  $\overline{K}(X_i|\bm{y})$ is the posterior CS after conditioning on the observed answers $\bm{y}$.
-If $\overline{K}(X_i|\bm{y})$ has a finite number of non-inner points, this is a linearly-constrained convex optimization whose solution typically corresponds to either the uniform PMF or a non-inner point on the frontier of $\overline{K}(X_i|\bm{y})$.
-A numerical solution can be easily found by a simple iterative approach in the special case of CS specified by probability intervals \cite{abellan2003maximum}.
-We have therefore computed the posterior lower and upper bounds of $P(X_i|\bm{y})$, and then maximized the entropy with respect to those bounds.
-% as in Eq.~\eqref{eq:entropy}.
-The procedure induces an outer approximation of $\overline{K}(X_i|\bm{y})$, and hence the upper approximation  of the maximum entropy $\overline{\overline{H}}(X|\bm{y})\geq\overline{H}(X|\bm{y})$. 
-%With a small notation abuse such approximate value is also denoted as $\overline{H}(X|\bm{y})$ and is regarded here as a measure of the informativeness level achieved for skill $X$ after the answers $\bm{y}$.
-Finally, to generalise Eq.~\eqref{eq:strongext} to CNs, we define the information gain provided by a question $Y'$ for its background skill $X_{Y'}$ as $\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y})$ and select the question $\tilde{Y}'$ leading to the maximum information gain, i.e.,
+		\overline{H}(X_i|\bm{y}) := \sup_{P(X_i|\bm{y}) \in \overline{K}(X_i|\bm{y})} 
+		H(X_i|\bm{y})\,,
+	\end{equation}
+	where  $\overline{K}(X_i|\bm{y})$ is the posterior CS after conditioning on the observed 
+	answers $\bm{y}$.  If $\overline{K}(X_i|\bm{y})$ has a finite number of non-inner 
+	points, this is a linearly-constrained convex optimization whose solution typically 
+	corresponds to either the uniform PMF or a non-inner point on the frontier of 
+	$\overline{K}(X_i|\bm{y})$. A numerical solution can be easily found by a simple iterative 
+	approach in the special case of CS specified by probability intervals 
+	\cite{abellan2003maximum}. We have therefore computed the posterior lower and 
+	upper bounds of $P(X_i|\bm{y})$, and then maximized the entropy with respect to 
+	those bounds. % as in Eq.~\eqref{eq:entropy}. 
+	The procedure induces an outer approximation of $\overline{K}(X_i|\bm{y})$, and hence 
+	the upper approximation  of the maximum entropy 
+	$\overline{\overline{H}}(X|\bm{y})\geq\overline{H}(X|\bm{y})$. 
+	%With a small notation abuse such approximate value is also denoted as 
+	%$\overline{H}(X|\bm{y})$ and is regarded here as a measure of the informativeness 
+	%level 
+	%achieved for skill $X$ after the answers $\bm{y}$. 
+	Finally, to generalise Eq.~\eqref{eq:strongext} to CNs, we define the information gain 
+	provided by a question $Y'$ for its background skill $X_{Y'}$ as 
+	$\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y})$ and 
+	select the question $\tilde{Y}'$ leading to the maximum information gain, i.e.,
 	\begin{equation}\label{eq:credalentropy}
 		\tilde{Y}' := \arg \max_{Y'\in\bm{Y}'} 
-\left[
+		\bigl[
 		\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y}) 
- \right]
+		\bigr]
 		\,.
 	\end{equation}
-For the stopping criterion, as we do not consider the joint entropy over the skills, we separately require each $\overline{\overline{H}}(X_i|\bm{y})$ to be smaller than a threshold $\tilde{H}$.
-To be consistent with this choice, we remove from the set of questions to be selected, those whose background skills already satisfy this condition.
-
-Note that the use of an outer approximation of the upper entropy affects only the question selection process (eventually making it sub-optimal), whereas it has no effect on the student evaluation given a set of answers.
+	For the stopping criterion, as we do not consider the joint entropy over the skills, we 
+	separately require each $\overline{\overline{H}}(X_i|\bm{y})$ to be smaller than a 
+	threshold $\tilde{H}$. To be consistent with this choice, we remove from the set of 
+	questions to be selected, those whose background skills already satisfy this condition.
+
+	Note that the use of an outer approximation of the upper entropy affects only the 
+	question selection process (eventually making it sub-optimal), whereas it has no effect 
+	on the student evaluation given a set of answers.
 
 	\section{Application}
-Before the academic year begins, the students of the University of Applied Sciences and Arts of Southern Switzerland (SUPSI) are asked to take an online German language placement test with 95 questions.
-In years 2015 and 2016, the answers of 451 students to all the questions have been collected.
-This benchmark is used to simulate CATs based on BNs and CNs as described in Sects.~\ref{sec:bayesianCAT} and \ref{sec:credalCAT}.
+	Before the academic year begins, the students of the University of Applied Sciences 
+	and Arts of Southern Switzerland (SUPSI) are asked to take an online German language 
+	placement test with 95 questions. In years 2015 and 2016, the answers of 451 students 
+	to all the questions have been collected. This benchmark is used to simulate CATs 
+	based on BNs and CNs as described in Sects.~\ref{sec:bayesianCAT} and 
+	\ref{sec:credalCAT}.
 
 	\paragraph{Model elicitation.}
-Four skills are assessed: \textit{W\"ortschatz} ($X_1$, vocabulary), \textit{Kommunikation} ($X_2$, communication), \textit{H\"oren} ($X_3$, listening), and \textit{Lesen} ($X_4$, reading).
-For each skill the student is assigned to a knowledge level compliant with EU guidelines.\footnote{\url{http://www.coe.int/t/dg4/linguistic/Source/Framework_EN.pdf}.}
-Levels A1, A2, B1, and B2 are considered, and skills are therefore modeled as quaternary variables.
-Teachers associate each question with a single skill, which is set as the unique background skill of the question.
-The number of questions associated with $X_1$/$X_2$/$X_3$/$X_4$ is 26/24/30/15.
-The current evaluation method assigns levels by setting thresholds on the percentage $\gamma$ of correct answers on each skill (A1 if  $\gamma < 35\%$, A2 up to $55\%$, B1 up to $75\%$).\footnote{These data as well as the software used for the simulations are freely available at \url{http://ipg.idsia.ch/software.php?id=138}.}
-
-We first elicit from the teachers the structure of the BN/CN graph over the skills.
-The result is a chain, which is augmented by leaf nodes modeling the questions, each having its background skill as single parent.
-Overall, a tree-shaped topology as in Fig.~\ref{fig:fourskills} is obtained.
-This makes exact inference in the BN fast, while in the CN a variable elimination might be slow (a minute for query in our setup).
-A faster approximate CN algorithm is therefore used \cite{antonucci2014e}.
+	Four skills are assessed: \textit{W\"ortschatz} ($X_1$, vocabulary), 
+	\textit{Kommunikation} ($X_2$, communication), \textit{H\"oren} ($X_3$, listening), and 
+	\textit{Lesen} ($X_4$, reading). For each skill the student is assigned to a knowledge 
+	level compliant with EU 
+	guidelines.\footnote{\url{http://www.coe.int/t/dg4/linguistic/Source/Framework_EN.pdf}.}
+	Levels A1, A2, B1, and B2 are considered, and skills are therefore modeled as 
+	quaternary variables.
+	Teachers associate each question with a single skill, which is set as the unique 
+	background skill of the question. The number of questions associated with 
+	$X_1$/$X_2$/$X_3$/$X_4$ is 26/24/30/15. The current evaluation method assigns 
+	levels by setting thresholds on the percentage $\gamma$ of correct answers on each 
+	skill (A1 if  $\gamma < 35\%$, A2 up to $55\%$, B1 up to $75\%$).\footnote{These data 
+	as well as the software used for the simulations are freely available at 
+	\url{http://ipg.idsia.ch/software.php?id=138}.}
+
+	We first elicit from the teachers the structure of the BN/CN graph over the skills. The 
+	result is a chain, which is augmented by leaf nodes modeling the questions, each 
+	having its background skill as single parent. Overall, a tree-shaped topology as in 
+	Fig.~\ref{fig:fourskills} is obtained. This makes exact inference in the BN fast, while in 
+	the CN a variable elimination might be slow (a minute for query in our setup). A faster 
+	approximate CN algorithm is therefore used \cite{antonucci2014e}.
 
@@
 		\centering
-\begin{tikzpicture}[scale=.8]
-\node[nodo] (w)  at (-0.25,0) {$X_1$};
-\node[nodo] (k)  at (3,0) {$X_2$};
-\node[nodo] (h)  at (6.5,0) {$X_3$};
-\node[nodo] (l)  at (9.25,0)  {$X_4$};
-\draw[arco] (w) -- (k);
-\draw[arco] (k) -- (h);
-\draw[arco] (h) -- (l);
-\node[Qnodo] (f1)  at (-0.25,-1) {$Y_1$};
-\node[Qnodo] (f2)  at (1.5,-1) {$Y_2$};
-\node[Qnodo] (f3)  at (3,-1) {$Y_3$};
-\node[Qnodo] (f4)  at (4.5,-1) {$Y_4$};
-\node[Qnodo] (f5)  at (6.5,-1) {$Y_5$};
-\node[Qnodo] (f6)  at (8.5,-1)  {$Y_6$};
-\node[Qnodo] (f7)  at (10,-1)  {$Y_7$};
-\draw[arco] (w) -- (f1);
-\draw[arco] (k) -- (f2);
-\draw[arco] (k) -- (f3);
-\draw[arco] (k) -- (f4);
-\draw[arco] (h) -- (f5);
-\draw[arco] (l) -- (f6);
-\draw[arco] (l) -- (f7);
+		\begin{tikzpicture}%[scale=.8]
+			\node[]  at (-0.25,0)  (w)  {$X_1$};
+			\node[]  at (3,0) 		 (k)   {$X_2$};
+			\node[]  at (6.5,0) 	(h)   {$X_3$};
+			\node[]  at (9.25,0)   (l)    {$X_4$};
+			\draw[] (w) -- (k);
+			\draw[] (k) -- (h);
+			\draw[] (h) -- (l);
+			\node[]  at (-0.25,-1)(f1) {$Y_1$};
+			\node[]  at (1.5,-1) 	 (f2) {$Y_2$};
+			\node[]  at (3,-1) 	 (f3) {$Y_3$};
+			\node[]  at (4.5,-1) 	(f4) {$Y_4$};
+			\node[]  at (6.5,-1)	(f5) {$Y_5$};
+			\node[]  at (8.5,-1)   (f6) {$Y_6$};
+			\node[]  at (10,-1)  	(f7)  {$Y_7$};
+			\draw[] (w) -- (f1);
+			\draw[] (k) -- (f2);
+			\draw[] (k) -- (f3);
+			\draw[] (k) -- (f4);
+			\draw[] (h) -- (f5);
+			\draw[] (l) -- (f6);
+			\draw[] (l) -- (f7);
 		\end{tikzpicture}
@@
 
-Teachers report their knowledge about the unconditional states of $X_1$ and the conditional states of $X_i$ given $X_{i-1}$, for $i=2,3,4$, as qualitative judgments (top of Tab.~\ref{tb:CPTs}). 
-To simplify the elicitation, the probabilities $P(X_i|X_{i-1})$ are given the same verbal judgment for all $i=2,3,4$.
-A more detailed model could provide more accurate evaluations but it would be very hard for the domain expert to elicit it in a reliable way.
-Also, questions are divided by the teachers in three groups, corresponding to different difficulty levels.
-Questions in the same group are quantified in the same way, irrespective of their background skill, giving the judgments reported in the bottom part of Tab.~\ref{tb:CPTs}.
+	Teachers report their knowledge about the unconditional states of $X_1$ and the 
+	conditional states of $X_i$ given $X_{i-1}$, for $i=2,3,4$, as qualitative judgments (top 
+	of Tab.~\ref{tb:CPTs}). 
+	To simplify the elicitation, the probabilities $P(X_i|X_{i-1})$ are given the same verbal 
+	judgment for all $i=2,3,4$. A more detailed model could provide more accurate 
+	evaluations but it would be very hard for the domain expert to elicit it in a reliable way. 
+	Also, questions are divided by the teachers in three groups, corresponding to different 
+	difficulty levels. Questions in the same group are quantified in the same way, 
+	irrespective of their background skill, giving the judgments reported in the bottom part 
+	of Tab.~\ref{tb:CPTs}.
 
@@
 				Easy&\emph{uncertain}&\emph{fifty-fifty}&\emph{expected}&\emph{probable}\\
-Medium&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}& \emph{expected}\\
-Difficult&\emph{impossible}&\emph{improbable}&\emph{uncertain}& \emph{fifty-fifty}\\
+				Medium&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}& 
+				\emph{expected}\\
+				Difficult&\emph{impossible}&\emph{improbable}&\emph{uncertain}& 
+				\emph{fifty-fifty}\\
 				\bottomrule
@@
 	%\vspace{-10mm}
-For the CN, those judgements are translated in interval constraints for the corresponding events on the basis of the verbal-numerical scale in Tab.~\ref{tb:labels}.
-Different probability intervals are considered for skills and questions as they refer to events of different type.
-For instance, when the expert considers ``\emph{impossible}'' for an A1 level student to know the answer to a difficult question, the student is assigned a probability between .175 and .2 of answering correctly, as the questions offer only four choices plus the option of giving no answer.
-Notice that, by doing so, we are not anymore assuming that all questions in the same difficulty group share exactly the same conditional PMFs (as done by the BN model), as PMFs of different questions can vary independently in the given intervals.
-This seems a more sensible assumption than that of the precise model.
-For the BN, the PMFs corresponding to the centers of mass of the CSs defining the CN are used. Numerical inferences in the BN are consequently included in the intervals computed with the CN.
+	For the CN, those judgements are translated in interval constraints for the 
+	corresponding events on the basis of the verbal-numerical scale in Tab.~\ref{tb:labels}. 
+	Different probability intervals are considered for skills and questions as they refer to 
+	events of different type. For instance, when the expert considers ``\emph{impossible}'' 
+	for an A1 level student to know the answer to a difficult question, the student is 
+	assigned a probability between .175 and .2 of answering correctly, as the questions 
+	offer only four choices plus the option of giving no answer. 
+	Notice that, by doing so, we are not anymore assuming that all questions in the same 
+	difficulty group share exactly the same conditional PMFs (as done by the BN model), as 
+	PMFs of different questions can vary independently in the given intervals. This seems a 
+	more sensible assumption than that of the precise model.
+	For the BN, the PMFs corresponding to the centers of mass of the CSs defining the CN 
+	are used. Numerical inferences in the BN are consequently included in the intervals 
+	computed with the CN.
 
@@
 				Skills&$1$-$10\%$&$10$-$20\%$&$20$-$40\%$&$30$-$50\%$&-&-\\
-Questions&$17.5$-$20\%$&$22.5$-$25\%$&$30$-$35\%$&$60$-$65\%$&$75$-$80\%$& $95$-$97.5\%$\\
+				Questions&$17.5$-$20\%$&$22.5$-$25\%$&$30$-$35\%$&$60$-$65\%$&$75$-$80\%$&
+				 $95$-$97.5\%$\\
 				\bottomrule
 			\end{tabular}
-\caption{A verbal-numerical scale for probability-intervals elicitation.}\label{tb:labels}
+			\caption{A verbal-numerical scale for probability-intervals 
+			elicitation.}\label{tb:labels}
 	\end{table*}}
@@
 	%Acronyms BN-NA, CN-NA, BN-AD, CN-AD denote 
-BN and CN methods in their non-adaptive (NA) and adaptive (AD) versions are considered.
-\emph{Accuracy}, i.e., the proportion of students to whom the test assigns the same level of the current evaluation method, describes BN performances.
-This measure cannot be used for the set-valued outputs of CN methods.
-In this case the $u_{65}$ measure can provide a comparison with the accuracy \cite{zaffalon2012evaluating}.
-If $\mathcal{L}$ is the set of levels assigned by the CN on a skill and $L$ its cardinality, a \emph{discounted} accuracy gives $1/L$ if $\mathcal{L}$ includes the true level and zero otherwise.
-The $u_{65}$ is a concave reinforcement of this score based on risk-adverse arguments.
-Its underlying assumption is that acknowledging the indecision between more levels has larger utility than randomly choosing one of them (e.g., the teacher could set up further assessments in the undecided cases).
-Tab.~\ref{tb:nonAdaptiveResults} shows the NA comparison.
-In Fig.~\ref{fig:plots} (left), the BN-NA accuracy is separately evaluated on the determinate (light bars) and indeterminate (dark bars) instances, i.e.
-those for which, respectively, a single level or multiple levels are returned by the CN model.
-On average, CN-NA returns single levels in $37.25\%$ of the cases and, if this is not the case, an average of $2.36$ levels ($3.22$ with interval dominance) are returned.
+	BN and CN methods in their non-adaptive (NA) and adaptive (AD) versions are 
+	considered. \emph{Accuracy}, i.e., the proportion of students to whom the test assigns 
+	the same level of the current evaluation method, describes BN performances. This 
+	measure cannot be used for the set-valued outputs of CN methods. In this case the 
+	$u_{65}$ measure can provide a comparison with the accuracy 
+	\cite{zaffalon2012evaluating}. If $\mathcal{L}$ is the set of levels assigned by the CN 
+	on a skill and $L$ its cardinality, a \emph{discounted} accuracy gives $1/L$ if 
+	$\mathcal{L}$ includes the true level and zero otherwise. The $u_{65}$ is a concave 
+	reinforcement of this score based on risk-adverse arguments. Its underlying 
+	assumption is that acknowledging the indecision between more levels has larger utility 
+	than randomly choosing one of them (e.g., the teacher could set up further 
+	assessments in the undecided cases). Tab.~\ref{tb:nonAdaptiveResults} shows the NA 
+	comparison. In Fig.~\ref{fig:plots} (left), the BN-NA accuracy is separately evaluated on 
+	the determinate (light bars) and indeterminate (dark bars) instances, i.e. those for 
+	which, respectively, a single level or multiple levels are returned by the CN model. On 
+	average, CN-NA returns single levels in $37.25\%$ of the cases and, if this is not the 
+	case, an average of $2.36$ levels ($3.22$ with interval dominance) are returned.
 
@@
 		\begin{tabular}{@{}lccccc@{}}\toprule
-		Algorithm&\phantom{aa}Average\phantom{aa}&\phantom{aaa}$X_1$\phantom{aaa}&\phantom{aaa}$X_2$\phantom{aaa}& \phantom{aaa}$X_3$\phantom{aaa}&\phantom{aaa}$X_4$\phantom{aaa}\\
+			Algorithm&\phantom{aa}Average\phantom{aa}&\phantom{aaa}$X_1$\phantom{aaa}&\phantom{aaa}$X_2$\phantom{aaa}&
+			 \phantom{aaa}$X_3$\phantom{aaa}&\phantom{aaa}$X_4$\phantom{aaa}\\
 			\midrule
-		BN-NA (acc)&$63.09\%$&$	67.56	\%$&$60.85\%$&${	75.84	\%}$&$48.10\%$\\
-		CN-NA ($u_{65}$)& ${65.37\%}$&$67.71\%$&${66.67\%}$&$	70.33\%$&${56.76\%}$\\
+			BN-NA (acc)&$63.09\%$&$	67.56	\%$&$60.85\%$&${	75.84	
+			\%}$&$48.10\%$\\
+			CN-NA ($u_{65}$)& ${65.37\%}$&$67.71\%$&${66.67\%}$&$	
+			70.33\%$&${56.76\%}$\\
 			\bottomrule
@@
 
-In the AD case we also track the average number of asked questions.
-Results are in Fig.~\ref{fig:plots} (right).
-CN-AD (circles) is tested for different thresholds over the entropy (labels of the markers) against a version of BN-AD based on the joint entropy (triangles).
-Similar values are obtained by coping with marginal entropies.
-We also allow the BN-AD method to return multiple levels by maximizing the expected $u_{65}$ utility over any possible set of levels.
-This variant is called BN-AD' and the corresponding $u_{65}$ measure is reported  (squares).
+	In the AD case we also track the average number of asked questions. Results are in 
+	Fig.~\ref{fig:plots} (right). CN-AD (circles) is tested for different thresholds over the 
+	entropy (labels of the markers) against a version of BN-AD based on the joint entropy 
+	(triangles). Similar values are obtained by coping with marginal entropies. We also allow 
+	the BN-AD method to return multiple levels by maximizing the expected $u_{65}$ utility 
+	over any possible set of levels. This variant is called BN-AD' and the corresponding 
+	$u_{65}$ measure is reported  (squares).
 
@@
 		\begin{tikzpicture}
-\begin{axis}[width=4cm,height=3.5cm,ybar=0,bar width=7pt,ylabel={\small acc}, xlabel={Skills},xtick=data,ytick={0,25,50,75,100},ymin=0,ymax=100,yticklabels={0,.25,.50,.75,1},symbolic x coords={$X_1$,$X_2$,$X_3$,$X_4$}, y label style={at={(axis description cs:0.3,.5)},anchor=south},xtick align=inside, legend style={at={(1,1)},anchor=south east},legend style={draw=none}]
-\addplot[fill=black!10] coordinates {($X_1$,85.42)($X_2$,87.06)($X_3$,89.51)($X_4$,56.34)}; 
+			\begin{axis}[width=4cm,height=3.5cm,ybar=0,bar width=7pt,ylabel={\small acc}, 
+			xlabel={Skills},xtick=data,ytick={0,25,50,75,100},ymin=0,ymax=100,yticklabels={0,.25,.50,.75,1},symbolic
+			 x coords={$X_1$,$X_2$,$X_3$,$X_4$}, y label style={at={(axis description 
+			cs:0.3,.5)},anchor=south},xtick align=inside, legend 
+			style={at={(1,1)},anchor=south east},legend style={draw=none}]
+				\addplot[fill=black!10] coordinates 
+				{($X_1$,85.42)($X_2$,87.06)($X_3$,89.51)($X_4$,56.34)}; 
 				\addlegendentry{\tiny{determinate}} 
-\addplot[fill=black!70] coordinates {($X_1$,54.51)($X_2$,45.13)($X_3$,67.72)($X_4$,44.26)};
+				\addplot[fill=black!70] coordinates 
+				{($X_1$,54.51)($X_2$,45.13)($X_3$,67.72)($X_4$,44.26)};
 				\addlegendentry{\tiny{indeterminate}}
@@
 		\begin{tikzpicture}
-\begin{axis}[width=7.5cm,height=4cm,ylabel={\small acc/$u_{65}$},xlabel={Number of questions},xmin=35, xmax=100,ymin=50, ymax=70, xtick={40,50,60,70,80,90}, ytick={50,55,60,65},legend style={at={(1,0)},anchor=south east},ymajorgrids=true,xmajorgrids=true,  y label style={at={(axis description cs:0.13,.5)},anchor=south},legend style={draw=none}]
-\addplot[black,thick,mark=triangle,mark options={fill=black}, visualization depends on=\thisrow{alignment} \as \alignment, nodes near coords, point meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}]
+			\begin{axis}[width=7.5cm,height=4cm,ylabel={\small 
+			acc/$u_{65}$},xlabel={Number of questions},xmin=35, xmax=100,ymin=50, 
+			ymax=70, xtick={40,50,60,70,80,90}, ytick={50,55,60,65},legend 
+			style={at={(1,0)},anchor=south east},ymajorgrids=true,xmajorgrids=true,  y label 
+			style={at={(axis description cs:0.13,.5)},anchor=south},legend style={draw=none}]
+				\addplot[black,thick,mark=triangle,mark options={fill=black}, visualization 
+				depends on=\thisrow{alignment} \as \alignment, nodes near coords, point 
+				meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}] 
 				table [meta index=2 ] {
@@
 				\addlegendentry{\tiny{BN-AD}}
-\addplot[magenta,thick,mark=square,mark options={fill=black}, visualization depends on=\thisrow{alignment} \as \alignment, nodes near coords, point meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}]
+				\addplot[magenta,thick,mark=square,mark options={fill=black}, visualization 
+				depends on=\thisrow{alignment} \as \alignment, nodes near coords, point 
+				meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}] 
 				table [meta index=2 ] {
@@
 				nodes near coords, % Place nodes near each coordinate
-point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
+				point meta=explicit symbolic, % The meta data used in the nodes is not 
+				%explicitly provided and not numeric
 				every node near coord/.style={anchor=\alignment} ] table [meta index=2 ] {
@@
 
-As a comment, CNs seem to identify hard-to-evaluate students as those for which multiple levels are provided.
-In fact, the agreement between the BN and the traditional tests is larger when the CN test is determinate.
-As a consequence, the CN $u_{65}$ measure is, on average, larger than the BN accuracy.
-A limitation of the CN test is the large fraction of indeterminate evaluations.
-One can interpret this result as a lack of robustness of the BN model, as even small variations in the model specifications can result in different decisions.
-Results also show that, both BN-AD and CN-AD approaches reduce the number of questions asked without significantly affecting the accuracy.
-BN-AD performances are improved by the ``credal'' variant BN-AD'.
-The results becomes very similar to those of the CN-AD.
-Yet, the latter method appears to be a more principled and suitable approach for a direct modeling of qualitative expert knowledge.
-
-%does not require any, potentially questionable, imputation of the probabilistic ranges provided by the experts.
-
-%Yet, we regard theof BN-AD, we regard the CN approach as more principled and suitable for a direct modeling of qualitative expert knowledge.
+	As a comment, CNs seem to identify hard-to-evaluate students as those for which 
+	multiple levels are provided. In fact, the agreement between the BN and the traditional 
+	tests is larger when the CN test is determinate. As a consequence, the CN $u_{65}$ 
+	measure is, on average, larger than the BN accuracy. 
+	A limitation of the CN test is the large fraction of indeterminate evaluations. One can 
+	interpret this result as a lack of robustness of the BN model, as even small variations in 
+	the model specifications can result in different decisions. Results also show that, both 
+	BN-AD and CN-AD approaches reduce the number of questions asked without 
+	significantly affecting the accuracy. BN-AD performances are improved by the ``credal'' 
+	variant BN-AD'. The results becomes very similar to those of the CN-AD. Yet, the latter 
+	method appears to be a more principled and suitable approach for a direct modeling of 
+	qualitative expert knowledge.
+
+	%does not require any, potentially questionable, imputation of the probabilistic ranges 
+	%provided by the experts.
+
+	%Yet, we regard theof BN-AD, we regard the CN approach as more principled and 
+	%suitable for a direct modeling of qualitative expert knowledge.
 
 	%uch a difference disappear if the credal-like variant BN-AD' is considered.
-%However, the CN-AD procedure appears to be more effective, as the $u_{65}$ accuracy measure decreases more slowly than the accuracies of BN-AD procedures.  
-%Finally,comparing the two BN-AD approaches, one can see that the use of the local instead of the joint entropy does not compromise the effectiveness of the adaptive approach.
-
-%Different decision criteria for the assignment of the skill level, e.g., maximality or e-admissibility, should be considered.
-%As a consequence, although BNs achieve better performance when considering the discounted accuracy, CN tests should be preferred whenever the utility is better described by the U65 or U80 measures, that is, whenever being undecided between more level should be preferred than assigning one of them at random.
-%As the true level of the students is unknown, this measure should be regarded as the agreement between to different evaluation strategies. 
+	%However, the CN-AD procedure appears to be more effective, as the $u_{65}$ 
+	%accuracy measure decreases more slowly than the accuracies of BN-AD procedures.  
+	%Finally,comparing the two BN-AD approaches, one can see that the use of the local 
+	%instead of the joint entropy does not compromise the effectiveness of the adaptive 
+	%approach.
+
+	%Different decision criteria for the assignment of the skill level, e.g., maximality or 
+	%e-admissibility, should be considered.
+	%As a consequence, although BNs achieve better performance when considering the 
+	%discounted accuracy, CN tests should be preferred whenever the utility is better 
+	%described by the U65 or U80 measures, that is, whenever being undecided between 
+	%more level should be preferred than assigning one of them at random. 
+	%As the true level of the students is unknown, this measure should be regarded as the 
+	%agreement between to different evaluation strategies. 
 	%\begin{mdframed}[hidealllines=true,backgroundcolor=blue!20]
 	%\paragraph{Experimental results.} 
-%Tab.~\ref{tab:nonadaptive} shows in the non-adaptive case the relative agreement between the traditional evaluation method (TEM) and the two BN-based models (IBN and TBN), computed as the proportion of students to which the tests under comparison assign the same level, averaged over 10 runs of cross-validation.
-On average 15\% of the students are assigned to a different level with respect to the traditional method (although the difference is never more than one level).
-The reason is that the BN models account for the difficulty of the questions.
-E.g., a student with only 70\% of correct answers could be assigned the level B2 if he/she has answered correctly a large number of difficult questions which a student of lower level could not have guessed just by chance.
+	%Tab.~\ref{tab:nonadaptive} shows in the non-adaptive case the relative agreement 
+	%between the traditional evaluation method (TEM) and the two BN-based models (IBN 
+	%and TBN), computed as the proportion of students to which the tests under 
+	%comparison assign the same level, averaged over 10 runs of cross-validation. On 
+	%average 15\% of the students are assigned to a different level with respect to the 
+	%traditional method (although the difference is never more than one level). The reason 
+	%is 
+	%that the BN models account for the difficulty of the questions. E.g., a student with 
+	%only 
+	%70\% of correct answers could be assigned the level B2 if he/she has answered 
+	%correctly a large number of difficult questions which a student of lower level could 
+	%not 
+	%have guessed just by chance. 
 	%\end{mdframed}
@@
 	%Algorithm&\multicolumn{1}{l}{W\"ort.}&\multicolumn{1}{l}{Komm.}&\multicolumn{1}{l}{H\"oren}&\multicolumn{1}{l}{Lesen}&\multicolumn{1}{l}{Overall}\\
+	% 
 	%\midrule
@@
 	%\begin{mdframed}[hidealllines=true,backgroundcolor=blue!20]
-%In this view, we believe that our approach provides more reliable evaluations than the traditional one.
-Tab.~\ref{tab:halfsplit} shows the internal consistency of the three tests evaluated using the split-half methodology: the questions are randomly divided into two subset of equal size; the two half-tests thus obtained are used to generate two independent evaluations of the students; the correlation coefficient between the outputs of the two half-tests adjusted with the Spearman-Brown correction is retained as a measure of the test reliability.
-Results show that the reliability of both Bayesian approaches (IBN and TBN) is larger than that of the traditional method.
-TBN has the highest reliability, as it considers the correlation between different skills and thus all answers contribute to the determination of the level of a skill, even those referring to different skills.
-%Concerning the adaptive case, we have considered different thresholds for the entropy.
-The left plot in Fig.~\ref{fig:agreement} shows the relative agreement of the adaptive tests using IBN and TBN with the non-adaptive TBN, whereas the right plot shows the average number of questions asked to the students.
-Both models show a strong reduction in the number of questions as the threshold on the entropy increases.
-For instance, using the TBN model, the number of questions reduces of about 70\% passing from the non-adaptive test to an adaptive test with entropy threshold $\tilde{H}=0.5$.
-Yet, the test still provides the same evaluations as the non-adaptive one in more than 70\% of the cases.
-Such an accuracy loss might be problematic.
-However, even decreasing the entropy threshold to $\tilde{H}=0.19$, we can still save 20 question on average (to a maximum of 65 questions in the best case) at the price of a reduction of only 3\% in the accuracy.
-This shows that a significant number of questions provides very little information about the student level of knowledge.
-Our adaptive approach makes it possible to avoid wasting students' time asking uninformative questions.
+	%In this view, we believe that our approach provides more reliable evaluations than the 
+	%traditional one. Tab.~\ref{tab:halfsplit} shows the internal consistency of the three 
+	%tests evaluated using the split-half methodology: the questions are randomly divided 
+	%into two subset of equal size; the two half-tests thus obtained are used to generate 
+	%two independent evaluations of the students; the correlation coefficient between the 
+	%outputs of the two half-tests adjusted with the Spearman-Brown correction is 
+	%retained 
+	%as a measure of the test reliability. Results show that the reliability of both Bayesian 
+	%approaches (IBN and TBN) is larger than that of the traditional method. TBN has the 
+	%highest reliability, as it considers the correlation between different skills and thus all 
+	%answers contribute to the determination of the level of a skill, even those referring to 
+	%different skills. 
+	%Concerning the adaptive case, we have considered different thresholds for the 
+	%entropy. The left plot in Fig.~\ref{fig:agreement} shows the relative agreement of the 
+	%adaptive tests using IBN and TBN with the non-adaptive TBN, whereas the right plot 
+	%shows the average number of questions asked to the students. Both models show a 
+	%strong reduction in the number of questions as the threshold on the entropy 
+	%increases. 
+	%For instance, using the TBN model, the number of questions reduces of about 70\% 
+	%passing from the non-adaptive test to an adaptive test with entropy threshold 
+	%$\tilde{H}=0.5$. Yet, the test still provides the same evaluations as the non-adaptive 
+	%one in more than 70\% of the cases. Such an accuracy loss might be problematic. 
+	%However, even decreasing the entropy threshold to $\tilde{H}=0.19$, we can still save 
+	%20 question on average (to a maximum of 65 questions in the best case) at the price 
+	%of 
+	%a reduction of only 3\% in the accuracy. This shows that a significant number of 
+	%questions provides very little information about the student level of knowledge. Our 
+	%adaptive approach makes it possible to avoid wasting students' time asking 
+	%uninformative questions. 
 	%\end{mdframed}
@@
 	%\begin{tikzpicture}
-%\begin{axis}[title={Agreement},width=6cm, height=4cm,xlabel={Entropy Threshold $\tilde{H}$},xmin=0, xmax=0.5, ymin=0.7, ymax=1, xtick={0,.1,.2,.3,.4,.5}, ytick={.7,.8,.9,1}, legend pos=north east, ymajorgrids=true, xmajorgrids=true]
-%\addplot[color=black,mark=square] coordinates { (0.0625,0.99833) (0.125,0.99217) (0.1875,0.9685) (0.25,0.89583) (0.375,0.75183) (0.5,0.74517)};    
+	%\begin{axis}[title={Agreement},width=6cm, height=4cm,xlabel={Entropy Threshold 
+	%$\tilde{H}$},xmin=0, xmax=0.5, ymin=0.7, ymax=1, xtick={0,.1,.2,.3,.4,.5}, 
+	%ytick={.7,.8,.9,1}, legend pos=north east, ymajorgrids=true, xmajorgrids=true]
+	%\addplot[color=black,mark=square] coordinates { (0.0625,0.99833) (0.125,0.99217) 
+	%(0.1875,0.9685) (0.25,0.89583) (0.375,0.75183) (0.5,0.74517)};    
 	%\addlegendentry{TBN}
-%\addplot[color=black!60,mark=star] coordinates { (0.0625,0.94733)(0.125,0.946000)(0.1875,0.943333)(0.25,0.8965000)(0.375,0.744000)(0.5,0.724666)};
+	%\addplot[color=black!60,mark=star] coordinates { 
+	%(0.0625,0.94733)(0.125,0.946000)(0.1875,0.943333)(0.25,0.8965000)(0.375,0.744000)(0.5,0.724666)};
 	%\addlegendentry{IBN}
@@
 	%\begin{tikzpicture}
-%\begin{axis}[ title={Number of questions},width=6cm, height=4cm, xlabel={Entropy Threshold $\tilde{H}$}, xmin=0, xmax=0.5, ymin=0, ymax=100, xtick={0,.1,.2,.3,.4,.5}, ytick={0,20,40,60,80,100}, legend pos=north east, ymajorgrids=true, xmajorgrids=true]
-%\addplot[color=black!60,mark=star] coordinates { (0.0625,89.741) (0.125,87.229) (0.1875,81.309) (0.25,66.745) (0.375,32.5) (0.5,29.001)};    
+	%\begin{axis}[ title={Number of questions},width=6cm, height=4cm, xlabel={Entropy 
+	%Threshold $\tilde{H}$}, xmin=0, xmax=0.5, ymin=0, ymax=100, xtick={0,.1,.2,.3,.4,.5}, 
+	%ytick={0,20,40,60,80,100}, legend pos=north east, ymajorgrids=true, 
+	%xmajorgrids=true]
+	%\addplot[color=black!60,mark=star] coordinates { (0.0625,89.741) (0.125,87.229) 
+	%(0.1875,81.309) (0.25,66.745) (0.375,32.5) (0.5,29.001)};    
 	%\addlegendentry{IBN}
-%\addplot[color=black,mark=square] coordinates { (0.0625,88.553) (0.125,83.476) (0.1875,75.071) (0.25,58.484) (0.375,30.722) (0.5,29)};
+	%\addplot[color=black,mark=square] coordinates { (0.0625,88.553) (0.125,83.476) 
+	%(0.1875,75.071) (0.25,58.484) (0.375,30.722) (0.5,29)};
 	%\addlegendentry{TBN}
@@
 	%\end{tikzpicture}
-%\caption{Agreement between the adaptive methods and the non-adaptive TBN (left) and average number of questions asked by the adaptive methods (right)}\label{fig:agreement}
+	%\caption{Agreement between the adaptive methods and the non-adaptive TBN (left) 
+	%and average number of questions asked by the adaptive methods 
+	%(right)}\label{fig:agreement}
 	%\vspace{-.8cm}
 	%\end{figure}
-%As providing precise values for these probabilities can be very hard even for expert teachers, the subjective opinion about the likelihood of an event was described by using the verbal-numerical probability scales in Table \ref{tb:labels}.
-%The question and skill CPTs are given in tables \ref{tb:questionCPTs} and \ref{tb:skillCPTs}.
-%make the model specification complete, the CPTs of the skills, i.e., $\{ P(X_i|\mathrm{\Pi_{X_i}})\}_{i=1}^4$, and those of the questions, i.e., $\{ P(Y_j|B_{Y_j})\}_{j=1}^{95}$ should be quantified.
-%In previous work \cite{mangili2016a}, these parameters have been learned from the available data.
-Results have shown that the resulting model can achieve larger internal consistency than the traditional evaluation method in assessing the student level.
-Given this result, a data-driven approach is used here to provide \emph{ground truth} evaluations for each student.
-This approach, hereafter referred to as EM-BN, uses expectation maximization (EM) to learn the CPTs of the BN model in  figure \ref{fig:fourskills} and infer the students level in the four skills.
-%The focus of the paper, however, is to provide an approach to adaptive testing entirely based on expert elicitation. Therefore, 
-%As we are interested in adaptive testing entirely based on expert elicitation, teachers have been asked to elicit all CPTs in the model. 
-%Following \cite{zaffalon2012evaluating}, the $u_{65}$ descriptors slightly increases the discounted accuracy contribution (i.e., $1/L$ is the set of labels includes the correct one and zero otherwise) with a convex xxx.
-Note that this descriptors is knows.
-%The above-described model has been used to evaluate the skills of the 451 students in the dataset. 
+	%As providing precise values for these probabilities can be very hard even for expert 
+	%teachers, the subjective opinion about the likelihood of an event was described by 
+	%using the verbal-numerical probability scales in Table \ref{tb:labels}. 
+	%The question and skill CPTs are given in tables \ref{tb:questionCPTs} and 
+	%\ref{tb:skillCPTs}.
+	%make the model specification complete, the CPTs of the skills, i.e., $\{ 
+	%P(X_i|\mathrm{\Pi_{X_i}})\}_{i=1}^4$, and those of the questions, i.e., $\{ 
+	%P(Y_j|B_{Y_j})\}_{j=1}^{95}$ should be quantified.
+	%In previous work \cite{mangili2016a}, these parameters have been learned from the 
+	%available data. Results have shown that the resulting model can achieve larger internal 
+	%consistency than the traditional evaluation method in assessing the student level. 
+	%Given this result, a data-driven approach is used here to provide \emph{ground truth} 
+	%evaluations for each student. This approach, hereafter referred to as EM-BN, uses 
+	%expectation maximization (EM) to learn the CPTs of the BN model in  figure 
+	%\ref{fig:fourskills} and infer the students level in the four skills. 
+	%The focus of the paper, however, is to provide an approach to adaptive testing 
+	%entirely based on expert elicitation. Therefore, 
+	%As we are interested in adaptive testing entirely based on expert elicitation, teachers 
+	%have been asked to elicit all CPTs in the model. 
+	%Following \cite{zaffalon2012evaluating}, the $u_{65}$ descriptors slightly increases 
+	%the discounted accuracy contribution (i.e., $1/L$ is the set of labels includes the 
+	%correct one and zero otherwise) with a convex xxx. Note that this descriptors is 
+	%knows. 
+	%The above-described model has been used to evaluate the skills of the 451 students 
+	%in the dataset. 
 	%As a ground truth we take the result based on the percentage of correct answers.
-%Then, we have compared the effectiveness of the BN and CN-based adaptive approaches.
+	%Then, we have compared the effectiveness of the BN and CN-based adaptive 
+	%approaches.
 	%?? traditional method, come nel paper ITS, EM?? \todo{scegliere ground truth}. 
@@
 	%\begin{itemize}
-%\item discounted accuracy (disA), i.e., the average value of $\frac{I_{\mathcal{L}}(l)}{L}$, where $I$ is the indicator function and $l$ the true level.
-This can be regarded as the most unfavorable way (among the reasonable ones) to evaluate
+	%\item discounted accuracy (disA), i.e., the average value of 
+	%$\frac{I_{\mathcal{L}}(l)}{L}$, where $I$ is the indicator function and $l$ the true level. 
+	%This can be regarded as the most unfavorable way (among the reasonable ones) to 
+	%evaluate
 	%credal classifiers;
-%\item set accuracy (setAcc), i.e., the average value of $I_{\mathcal{L}(l)}$. This can be regarded as the performance measure most favorable to a credal classifier;
-%\item the utility-discounted accuracy U65 and U80 \cite{zaffalon2012evaluating}, i.e., the average value of a concave function $u\left(\frac{I_{\mathcal{L}}(l)}{L}\right)$ of the discounted utility.
-This measure assumes that being undecided between $k$ levels is better than choosing the correct level with probability $1/k$.
-This measure accounts for risk aversion, which increases with $u(0.5)$.
-We have $u(0.5)=0.65$ and $u(0.5)=0.8$ for, respectively the U65 and the U80 measures; \footnote{Notice that with $u(0.5)=0.5$ we obtain the discounted accuracy measure.}
-%\item the average number of times the credal test is determinate, that is, it returns a single level (DET);
-%\item the accuracy of the Bayesian test when the credal test is determinate (detA) and when it is indeterminate (indA).
-These indicators can show the capability of the credal test to identify the students which are more difficult to evaluate;
+	%\item set accuracy (setAcc), i.e., the average value of $I_{\mathcal{L}(l)}$. This can be 
+	%regarded as the performance measure most favorable to a credal classifier;
+	%\item the utility-discounted accuracy U65 and U80 \cite{zaffalon2012evaluating}, i.e., 
+	%the average value of a concave function $u\bigl(\frac{I_{\mathcal{L}}(l)}{L}\bigr)$ of 
+	%the 
+	%discounted utility. This measure assumes that being undecided between $k$ levels is 
+	%better than choosing the correct level with probability $1/k$. This measure accounts 
+	%for 
+	%risk aversion, which increases with $u(0.5)$. We have $u(0.5)=0.65$ and 
+	%$u(0.5)=0.8$ 
+	%for, respectively the U65 and the U80 measures; \footnote{Notice that with 
+	%$u(0.5)=0.5$ we obtain the discounted accuracy measure.}
+	%\item the average number of times the credal test is determinate, that is, it returns a 
+	%single level (DET);
+	%\item the accuracy of the Bayesian test when the credal test is determinate (detA) and 
+	%when it is indeterminate (indA). These indicators can show the capability of the credal 
+	%test to identify the students which are more difficult to evaluate;
 	%\item the average cardinality of $\mathcal{L}$ (Csize).
@@
 
-ISIPTA 2021 papers have to be prepared using \LaTeX.
-To start writing your paper, copy \texttt{isipta2021-paper\_template.tex} and replace author and content with your own.
-
-The ISIPTA 2021 paper style is based on the \textsf{jmlr} class with
-the \texttt{pmlr,twocolumn} class options.\footnotemark
-\footnotetext{%
-  You can find the \textsf{jmlr} documentation at \url{https://ctan.org/pkg/jmlr}.
-  The bundle you can download there also includes a sample file with more usage examples.
-  Version 1.21 and before are known not to work correctly and produce wrong margins.
-  Version 1.23 and after have been tested to work.
-  The necessary files from version 1.27 are included in the author kit.
-}
-This class already loads some commonly used packages, so please have a look at its documentation in case you want to load extra packages.
-Do not load packages that conflict with \textsf{jmlr}—you will get an error message—, as this would complicate creating the proceedings.
-
-We have added a style file, \textsf{isipta2021} that sets up some more style details and loads some packages.
-This includes font definitions, so do not load your own or change the font size or other style-related aspects.
-Also do not change the line width, margins, line spacing and other vertical whitespace between layout elements (so do not use \verb|\vspace|).
-
-You can load extra packages available in the big TeX distributions (Mik\TeX, \TeX{Live}, Mac\TeX) as long as your text compiles with PDF\LaTeX.
-Please avoid using obsolete commands, such as \verb|\rm|, and obsolete packages, such as \textsf{epsfig}.\footnote{See \url{https://ctan.org/pkg/l2tabu}.}
-\swap[ ]{in the header of your source file.}{But feel free to include your own macros}
-
-\section{Practical Guidelines}
-\subsection{Page Limits}
-\emph{Full papers} have a length of four to nine pages.
-This excludes the list of references and informational sections such as Acknowledgments.
-There is the option to provide supplementary materials, such as videos, pictures, code, data-sets, etc.
-However, these do not have to be considered by the reviewers, so do make sure the paper is self-contained without them.
-
-\emph{Short papers} have a length of three pages.
-Again, this excludes the list of references and informational sections such as Acknowledgments.
-However, no supplementary material is accepted in this case.
-
-Please be aware that these are the limits for the final versions of the papers.
-It is recommended that first submissions do not use all the allowed space, in order to leave some room to take into account reviewers suggestions.
-
-\subsection{Submission \& Filenames}
-Your ISIPTA 2021 paper must be submitted via the ISIPTA 2021 Easychair page: \url{https://easychair.org/conferences/?conf=isipta2021}
-
-For the submission deadlines, please check the conference website: \url{http://www.sipta.org/isipta21}.
-
-All the files you submit should follow the JMLR-required format: the surname of the first author, in lowercase, without spaces and accents, followed by \texttt{21} (for the publication year), and optional letter in case there are multiple submissions with the same first author surname, and then the extension.
-So if this were a submission, the source file must be named \texttt{alandvonvereweg21.tex} and the compiled one \texttt{alandvonvereweg21.pdf} or, in case of multiple submissions, \texttt{alandvonvereweg21a.tex} and \texttt{alandvonvereweg21a.pdf}.
-Supplementary materials gets a \texttt{-supp} affix to the name, so for this ‘submission’ a relevant dataset would, e.g., have to be named \texttt{alandvonvereweg21a-supp.csv}.
-
-For the initial submission, you will have to submit the pdf of your paper and separately, if present, all the supplementary materials in one zip file.
-
-If your paper has been accepted and you are preparing the version that will be published, download the copyright form from the conference web page.
-Print, fill, and sign the form.
-The name of the PDF scan should be the ID with the suffix \texttt{Permission} (for example, \texttt{alandvonvereweg21aPermission.pdf}).
-
-For the final submission, you should update the paper pdf and, if supplementary materials changed, the supplementary materials zip file.
-Additionally, you should create a zip file \texttt{alandvonvereweg21a.zip} with all the paper source files (\texttt{alandvonvereweg21a.tex}, \texttt{alandvonvereweg21a.bib}, etc.) and the permission pdf \texttt{alandvonvereweg21aPermission.pdf}.
-This zip file should then be uploaded on Easychair as well.
-
-\section{Sections}
-Section titles must be in title case at all levels.
-
-\subsection{Subsections}
-\subsubsection{Subsubsections}
-Avoid using subsubsections.
-In case you need to structure your subsections more finely than in paragraphs, have a look at the unnumbered inline sectioning styles below.
-
-\paragraph{‘Paragraphs’}
-‘Paragraphs’ are produced using \verb|\paragraph|.
-They can be used directly below sections or subsections.
-
-You can have more than one paragraph in a \LaTeX\ ‘paragraph’.
-
-\subparagraph{Subparagraphs}
-Subparagraphs are produced using \verb|\subparagraph|.
-
-\section{Cross-Referencing}
-Always use \verb|\label| and \verb|\ref|—or one of the commands described below—when cross-referencing.
-For example, the next section is Section~\ref{sec:math}.
-
-The \textsf{jmlr} class provides some convenient cross-referencing commands: \verb|\sectionref|, \verb|\equationref|, \verb|\tableref|, \verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|, \verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|, \verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|, \verb|\exampleref| and \verb|\appendixref|.
-The argument of these commands may either be a single label or a comma-separated list of labels.
-Examples: \sectionref{sec:math} or \sectionref{sec:intro,sec:math} or \sectionref{sec:intro,sec:math,sec:tables,sec:figures}.
-
-\section{Math}\label{sec:math}
-The \textsf{jmlr} class loads the \textsf{amsmath} package, so you can use any of the commands and environments defined there.\footnotemark
-\footnotetext{%
-  See the \textsf{amsmath} documentation at \url{https://ctan.org/pkg/amsmath} for further details.
-}
-Furthermore, the \textsf{isipta2021} style file loads the \textsf{mathtools} package, which extends \textsf{amsmath} with even more useful commands.\footnotetext{%
-  See the \textsf{mathtools} documentation at \url{https://ctan.org/pkg/mathtools} for further details.
-}
-
-Use the \textsf{amsmath} environments for displayed equations.
-So, specifically, use the \texttt{equation} environment instead of \verb|$$...$$| and the \texttt{align} environment instead of \texttt{eqnarray}.\footnote{For reasons why you shouldn't use the obsolete \texttt{eqnarray} environment, see Lars Madsen, \textit{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.}
-An \texttt{equation}:
-\begin{equation}\label{eq:example}
-  0 = 1 - 1
-\end{equation}
-Two \texttt{align}'ed equations:
-\begin{align*} % no numbers with starred version
-  1 + 2 &= 3,\\
-  1 - 2 &= -1.
-\end{align*}
-Equations can also be put inline, of course.
-For example, \equationref{eq:example}: \(0=1+1\). % $0=1+1$ also works
-
-The \textsf{amsmath} and \textsf{mathtools} packages provide a lot of nice functionality, such as many common math operators, such as \(\sin\), \(\max\), etc. and also commands for defining new ones.
-
-The following theorem-like environments are predefined by the \textsf{jmlr} class: \texttt{theorem}, \texttt{example}, \texttt{lemma}, \texttt{proposition}, \texttt{remark}, \texttt{corollary}, \texttt{definition}, \texttt{conjecture} and \texttt{axiom}.
-You can use the \texttt{proof} environment to display the proof if need be, as in \theoremref{thm:example}.
-\begin{theorem}[Example]\label{thm:example}
-  All elements of the powerset of \(\varnothing\) are equal.
-\end{theorem}
-\begin{proof}\textbf{of \theoremref{thm:example}.} % You can leave off the reference in the \textbf if the proof comes right after that what is to be proven
-  The powerset of \(\varnothing\) contains a unique element, \(\varnothing\).
-\end{proof}
-
-\section{Floats}\label{sec:floats}
-Floats, such as figures, tables and algorithms, are moving objects and are supposed to float to the nearest convenient location.
-Please do not force them to go in a particular place and do not
-put the figure or table in the middle of a paragraph.
-Floats are supposed to have a little extra space above and below them to make them stand out from the rest of the text.
-This extra spacing is put in automatically and shouldn't need modifying.
-
-\subsection{Figures}\label{sec:figures}
-Figures should go in the \texttt{figure} environment.
-Within this environment, use \verb|\floatconts| (defined by \textsf{jmlr}) to correctly position the caption and center the image.
-To see how this works, look at the definition of \figureref{fig:example}.
-Sub-figures can be created using \verb|\subfigure|, which is also defined by the \textsf{jmlr} class.
-Use \verb|\includegraphics| for external graphics files but omit the file extension.
-Supported formats are \textsf{pdf} (preferred for vector drawings and diagrams), \textsf{png} (preferred for screenshots), and \textsf{jpeg} (preferred for photographs).
-Do not use \verb|\epsfig| or \verb|\psfig|.
-If you want to scale the image, it's better to use a fraction of the line width rather than an explicit length.
-For example, see \figureref{fig:page}.
-
-\begin{figure}
- % The first argument is the label,
- % the caption goes in the second argument, and
- % the figure contents go in the third argument.
-\floatconts
-  {fig:example}
-  {\caption{Example Image}}
-  {
-    \subfigure[A page]{%
-      \label{fig:page}
-      \includegraphics[width=0.5\linewidth,page=1]{isipta2021-poster-abstract_template}
-    }
-    \quad
-    \subfigure[A coordinate system]{
-      \label{fig:coords}%
-      {
-        \begin{tikzpicture}[xscale=1.5]
-          \coordinate (origin);
-          \draw[->] (origin) -- +(1cm,0) node[below] {$x$};
-          \draw[->] (origin) -- +(0,1cm) node[left] {$y$};
-          \fill[gray] (45:1cm) circle[radius=.2cm];
-        \end{tikzpicture}
-      }
-    }
-  }
-\end{figure}
-
-Don't use \verb|\graphicspath|.
-If the images are contained in a subdirectory, specify this when you include the image, for example \verb|\includegraphics{figures/mypic}|.
-
-\subsection{Tables}\label{sec:tables}
-Tables should go in the \texttt{table} environment.
-Within this environment use \verb|\floatconts| (defined by \textsf{jmlr})
-to set the caption correctly and center the table contents.
-To see how this works, look at the definition of \tableref{tab:example}.
-Similarly to subfigures, subtables can be created using \verb|\subtable|, which is also defined by the \textsf{jmlr} class.
-
-\begin{table}[htbp]
- % The first argument is the label,
- % the caption goes in the second argument, and
- % the table contents go in the third argument.
-\floatconts{tab:example}%
-  {\caption{An example table with nice horizontal lines and without unnecessary vertical lines}}%
-  {
-    \begin{tabular}{rl}
-      \toprule % from booktabs package
-      \bfseries Dataset & \bfseries Result\\
-      \midrule % from booktabs package
-      Data1 & 0.12345\\
-      Data2 & 0.67890\\
-      Data3 & 0.54321\\
-      Data4 & 0.09876\\
-      \bottomrule % from booktabs package
-    \end{tabular}
-  }
-\end{table}
-
-\subsection{Algorithms}\label{sec:algorithms}
-
-Enumerated textual algorithms can be displayed using the \texttt{algorithm} environment; see the \textsf{jmlr} class documentation and sample file for a description.\footnotemark[1]
-Code can be displayed using the automatically loaded \texttt{algorithm2e} environment defined by the \textsf{algorithm2e} package.\footnote{See the \textsf{algorithm2e} documentation at \url{https://ctan.org/pkg/algorithm2e}.}
-
-\section{Citations and Bibliography}\label{sec:cite}
-The references must be managed using Bib\TeX.
-The \textsf{jmlr} class automatically loads \textsf{natbib} and the appropriate style file.
-So you have to use the commands provided by this package.\footnote{You can find the \textsf{natbib} documentation at \url{https://ctan.org/pkg/natbib}.}
-This template file has the citations defined in the accompanying BibTeX file \texttt{isipta2021-template.bib}.
-For a parenthetical citation use \verb|\citep|.
-For example: “Good introductions to the topic are available \citep{latexcompanion}.”
-For a textual citation use \verb|\citet|.
-For example: “\citet{einstein} discusses electrodynamics of moving bodies.”
-The citation style can be chosen using the \verb|\citestyle| command in the preamble.
-
-The bibliography is displayed using \verb|\bibliography|.
-
-\appendix
-
-\section{Boring Stuff}\label{apd:first}
-In case you wish to structure your paper using appendices, you can do so.
-However, they also count towards the page limit.
-
-\textbf{But, everything below this line does not count towards the page limit.}
-%% For papers, sections below this line do not count towards the page limit
-
-\acks{%
-Acknowledgments can go here.
-This includes acknowledgments for financial support as well as for support from other people.
-}
-
-\section*{Author Contributions}
-If you wish, you can mention which of the authors did what.
-Otherwise this section can be omitted.
-
-\section*{Competing Interests}
-In case any author has some competing interest it has to be mentioned here.
-Otherwise this section can be omitted.
-
-\bibliography{isipta2021-template}
-% should be alandvonvereweg21.bib if this were a submission
-
+	% ---- Bibliography ----
+	%
+	% BibTeX users should specify bibliography style 'splncs04'.
+	% References will then be sorted and formatted in the correct style.
+	%
+	% \bibliography{mybibliography}
+	%
+\bibliographystyle{splncs04}
+\bibliography{biblio}
 \end{document}

### 2021-04-18 paper.tex
First change

@@
 \documentclass[runningheads]{llncs}
-\usepackage{graphicx}
-\usepackage{xcolor} 
-\usepackage{amsmath} 
-\usepackage{amstext} 
-\usepackage{amssymb} 
-\usepackage{amsfonts} 
-\usepackage{mathptmx} 
-\usepackage[scaled=.90]{helvet} 
-\usepackage{courier} 
-\usepackage{textcomp} 
-\usepackage{hyperref} 
-\usepackage{array}
-\usepackage{varwidth}
-\usepackage[american]{babel}
-\usepackage{mathtools} % fixes and extends amsmath
-\mathtoolsset{mathic}
-\allowdisplaybreaks
-\usepackage{mathptmx}
-\usepackage{tabu}
-%\usepackage{breqn}
-\usepackage{algorithm,algorithmic,bm}
+\usepackage[]{algorithm2e}
+\usepackage[]{algorithmic}
+\usepackage{bm,hyperref,booktabs,tikz,pgf,pgfplots,amsmath}
+\usetikzlibrary{arrows,automata,circuits}
+%\pgfplotsset{compat=1.13}
+%\usepackage{pgfkeys}
+%\usepackage{graphicx}
+%xcolor} 
+%amsmath} 
+%amstext} 
+%amssymb} 
+%amsfonts} 
+%\usepackage{mathptmx} 
+%\usepackage[scaled=.90]{helvet} 
+%\usepackage{courier} 
+%\usepackage{textcomp} 
+%\usepackage{array}
+%\usepackage{varwidth}
+%\usepackage[american]{babel}
+%usepackage{mathtools} % fixes and extends amsmath
+%mathtoolsset{mathic}
+%\allowdisplaybreaks
+%\usepackage{mathptmx}
+%\usepackage{tabu}
+%%\usepackage{breqn}
+%\usepackage{algorithm,algorithmic,bm}
 % If you use the hyperref package, please uncomment the following line
 % to display URLs in blue roman font according to Springer's eBook style:
-\renewcommand\UrlFont{\color{blue}\rmfamily}
+%\renewcommand\UrlFont{\color{blue}\rmfamily}
 %% Suggested packages, as needed:
-\usepackage{booktabs} % commands to create good-looking tables
-\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
+%\usepackage{booktabs} % commands to create good-looking tables
+%\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
 %drawing custom shapes
-\usetikzlibrary{%
-	arrows,%
-	calc,%
-	fit,%
-	patterns,%
-	plotmarks,%
-	shapes.geometric,%
-	shapes.misc,%
-	shapes.symbols,%
-	shapes.arrows,%
-	shapes.callouts,%
+%\usetikzlibrary{%
+%	arrows,%
+%	calc,%
+%	fit,%
+%	patterns,%
+%	plotmarks,%
+%	shapes.geometric,%
+%	shapes.arrows,%
+%	shapes.callouts,%
 	% shapes.multipart,%
@@
 	% automata,%
-	backgrounds,%
-	chains,%
-	topaths,%
-	trees,%
-	petri,%
-	mindmap,%
-	matrix,%
-	% calendar,%
-	folding,%
-	fadings,%
-	through,%
-	positioning,%
-	scopes,%
-	decorations.fractals,%
-	decorations.shapes,%
-	decorations.text,%
-	decorations.pathmorphing,%
-	decorations.pathreplacing,%
-	decorations.footprints,%
-	decorations.markings,%
-	shadows}
-\usetikzlibrary{arrows,automata,circuits}
-\usepackage{pgfplots}
-\pgfplotsset{compat=1.13}
-\usepackage{pgfkeys}
+%	topaths,%
+%	trees,%
+%	matrix,%
+%	% calendar,%
+%	folding,%
+%	fadings,%
+%	positioning,%
+%	scopes,%
+%	decorations.fractals,%
+%	decorations.shapes,%
+%	decorations.text,%
+%	decorations.pathmorphing,%
+%	decorations.pathreplacing,%
+%	decorations.footprints,%
+%	decorations.markings,%
+%	shadows}
 %\usepackage{trace-pgfkeys}
 \begin{document}
-\title{Approximating Information-Theoretic Scores\\for Adaptive Tests}
+\title{Approximating Information-Theoretic Scores\\for Computer Adaptive Tests\\in Bayesian and Credal Networks}
 %%\thanks{Supported by organization x.}}
 %\titlerunning{Abbreviated paper title}
-\author{permutation of Alessandro Antonucci \and
-Francesca Mangili \and
-Claudio Bonesana\and
+\author{Alessandro Antonucci \and
+Francesca Mangili \and\\
+Claudio Bonesana \and
 Giorgia Adorni}
-\authorrunning{F. Author et al.}
-\institute{Dalle Molle Institute for Artificial Intelligence USI-SUPSI -- IDSIA \\
+%\authorrunning{F. Author et al.}
+\institute{Istituto Dalle Molle di Studi sull'Intelligenza Artificiale, Lugano, Switzerland\\
 \email{\{alessandro,francesca,claudio.bonesana,giorgia.adorni\}@idsia.ch}}
@@
 \begin{abstract}
-A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skill levels of the test taker.
+A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skills of the test taker.
 Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills.
 Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model.
-This might make inference considerably harded in the underlying model, this being especially the case for the information theoretic quantity generally used for these models.
-We present.
-
-with xxx. Interval valued quantification
-
-We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers.
+This might make inference considerably harder in the underlying model, this being especially the case for the information theoretic quantities generally used as a score to drive the adaptation process.
+Here we present an alternative score based on the mode of the posterior probabilities of the model.
+We show how this makes considerably simpler the evaluation of the score in the credal case.
+Numerical tests are promising, we show how the performance are similar in the Bayesian network case, while xxx.
+%considered. 
+%We propose an alternative 
+%We present.
+%with xxx. Interval valued quantification
+%We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers.
 Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge.
 The counterpart is a less straightforward identification of the
-information-theoretic measure controlling the question-selection and the test-stopping criteria.
+%information-theoretic measure controlling the question-selection and the test-stopping criteria.
 We elaborate on these issues and propose a sound and computationally feasible procedure.
-Validation against a Bayesian-network approach
-on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
-%\keywords{credal networks  \and adaptive test \and bayesian network.}
+Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
+%150-200 words - 12 pages
+\keywords{First keyword  \and Second keyword \and Another keyword.}
 \end{abstract}
+
 \section{Testing Algorithms}
@@
 
-\begin{algorithm}[htbp!]
-    \caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
+\begin{algorithm}[H]
+    \SetAlgoLined
+    \KwResult{Write here the result }
+    initialization\;
+    \While{While condition}{
+        instructions\;
+        \eIf{condition}{
+            instructions1\;
+            instructions2\;
+        }{
+            instructions3\;
+        }
+    }
+    \caption{How to write algorithms}
+\end{algorithm}
+
+\begin{algorithm}[htp]
     \begin{algorithmic}[1]
@@
     \end{algorithmic}\label{alg:ta}
+\caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
 \end{algorithm}
@@
 
-	\begin{algorithm}[htp!]
-		\caption{Single skill, precise model\\
-			a model (BN, skeleton) $M$ over the skills only
-			\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions 
-			$\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
-			the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
-			the student answer models $\{\tilde{P}(Q^j|S)\}$\\
-			an entropy threshold $h^*$,\\
-			a score function for questions $\gamma$
-			\label{alg:simple}}
-		\begin{algorithmic}[1]
-			\FOR {$i\gets\{1,\ldots,n\}$}
-			\STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
-			(M,\mathcal{Q},\emptyset,\emptyset)$
-			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
-			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(M',Q,\bm{e})$
-			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
-			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
-			\STATE{$q^* \gets \mathrm{sampling} \sim \tilde{P}(Q^*|s^i)$}
-			\STATE $M' \gets \mathrm{addChild}(M',Q,S,P(Q|S))$
-			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-			\STATE $h \gets H[P_{M'}(S|\bm{e})]$
-			\ENDWHILE
-			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P_{M'}(s|\bm{e})$
-			\ENDFOR
-			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
-		\end{algorithmic}
-	\end{algorithm}
+%	\begin{algorithm}[htp!]
+%		\caption{Single skill, precise model\\
+%			a model (BN, skeleton) $M$ over the skills only
+%			\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions 
+%			$\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
+%			the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
+%			the student answer models $\{\tilde{P}(Q^j|S)\}$\\
+%			an entropy threshold $h^*$,\\
+%			a score function for questions $\gamma$
+%			\label{alg:simple}}
+%		\begin{algorithmic}[1]
+%			\FOR {$i\gets\{1,\ldots,n\}$}
+%			\STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
+%			(M,\mathcal{Q},\emptyset,\emptyset)$
+%			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
+%			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(M',Q,\bm{e})$
+%			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
+%			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
+%			\STATE{$q^* \gets \mathrm{sampling} \sim \tilde{P}(Q^*|s^i)$}
+%			\STATE $M' \gets \mathrm{addChild}(M',Q,S,P(Q|S))$
+%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
+%			\STATE $h \gets H[P_{M'}(S|\bm{e})]$
+%			\ENDWHILE
+%			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P_{M'}(s|\bm{e})$
+%			\ENDFOR
+%			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
+%		\end{algorithmic}
+%	\end{algorithm}
 	Three possible scores:
@@
 
-	\begin{algorithm}[htp!]
-		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
-		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
-			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
-			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
-			an upper entropy threshold $\overline{h}^*$,\\
-			a score function for questions $\sigma$
-			\label{alg:simple2}}
-		\begin{algorithmic}[1]
-			\FOR {$i\gets\{1,\ldots,n\}$}
-			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
-			(\mathcal{Q},\emptyset,\emptyset)$
-			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
-			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
-			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
-			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
-			\STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
-			\STATE $\mathrm{addChild}(Q,S,P(Q|S))$
-			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-			\STATE $h \gets H[P(S|\bm{e})]$
-			\ENDWHILE
-			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
-			\ENDFOR
-			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
-		\end{algorithmic}
-	\end{algorithm}
+%	\begin{algorithm}[htp!]
+%		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
+%		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
+%			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
+%			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
+%			an upper entropy threshold $\overline{h}^*$,\\
+%			a score function for questions $\sigma$
+%			\label{alg:simple2}}
+%		\begin{algorithmic}[1]
+%			\FOR {$i\gets\{1,\ldots,n\}$}
+%			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
+%			(\mathcal{Q},\emptyset,\emptyset)$
+%			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
+%			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
+%			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
+%			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
+%			\STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
+%			\STATE $\mathrm{addChild}(Q,S,P(Q|S))$
+%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
+%			\STATE $h \gets H[P(S|\bm{e})]$
+%			\ENDWHILE
+%			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
+%			\ENDFOR
+%			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
+%		\end{algorithmic}
+%	\end{algorithm}
 	Three possible scores:
@@
 
-	\begin{algorithm}[htp!]
-		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
-		\begin{algorithmic}[1]
-			\FOR {$s\in\bm{S}$}
-			\WHILE{ $h > h^*$}
-			\STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
-			\STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
-			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-			\STATE $h \gets H[P(S|\bm{e}]$
-			\ENDWHILE
-			\ENDFOR
-			\STATE {\bf return} $\arg\max P(s|\bm{e})$
-		\end{algorithmic}
-	\end{algorithm}
+%	\begin{algorithm}[htp!]
+%		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
+%		\begin{algorithmic}[1]
+%			\FOR {$s\in\bm{S}$}
+%			\WHILE{ $h > h^*$}
+%			\STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
+%			\STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
+%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
+%			\STATE $h \gets H[P(S|\bm{e}]$
+%			\ENDWHILE
+%			\ENDFOR
+%			\STATE {\bf return} $\arg\max P(s|\bm{e})$
+%		\end{algorithmic}
+%	\end{algorithm}
 
@@
 	while $P(S=0|Q=1)$ by normalization. Accordingly:
-	\begin{multline}
-		\sigma_Q(p,\pi_0,\pi_1)=\\
-		h \circ f[\gamma/l(p)] \cdot t +
-		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
-		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
-		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
-	\end{multline}
+%	\begin{multline}
+%		\sigma_Q(p,\pi_0,\pi_1)=\\
+%		h \circ f[\gamma/l(p)] \cdot t +
+%		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
+%		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
+%		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
+%	\end{multline}
 	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
@@
 
-	\begin{multline}
-		\sigma_Q(p,\pi_0,\pi_1)=\\
-		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
-		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
-	\end{multline}
+%	\begin{multline}
+%		\sigma_Q(p,\pi_0,\pi_1)=\\
+%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
+%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
+%	\end{multline}
 
 	But, as $P(q_1)\geq 0$, then
-	\begin{multline}
-		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
-		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
-		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
-		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
-	\end{multline}
+%	\begin{multline}
+%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
+%		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
+%		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
+%		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
+%	\end{multline}
 
 	Similarly, as $1-P(q_1)\geq 0$, 
-	\begin{multline}
-		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
-		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
-	\end{multline}
+%	\begin{multline}
+%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
+%		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
+%	\end{multline}
 
@@
 
-	\begin{multline}
-		\sigma_Q(p,\pi_0,\pi_1)= \\
-		2 max\{\pi_1 p, \pi_0 (1-p)\}+
-		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
-	\end{multline}
+%	\begin{multline}
+%		\sigma_Q(p,\pi_0,\pi_1)= \\
+%		2 max\{\pi_1 p, \pi_0 (1-p)\}+
+%		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
+%	\end{multline}
 
@@
 	Let's use the following parametrization:
-	\begin{multline}\label{eq:minimization}
-		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
-		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
-		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
-	\end{multline}
+%	\begin{multline}\label{eq:minimization}
+%		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
+%		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
+%		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
+%		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
+%		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
+%	\end{multline}
 
@@
 
-	\begin{multline}
-		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
-		\begin{array}{ll}
-			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
-			~&\underline{x} \leq x\leq \overline{x}\\ 
-		\end{array}
-	\end{multline}
+%	\begin{multline}
+%		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
+%		\begin{array}{ll}
+%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
+%			~&\underline{x} \leq x\leq \overline{x}\\ 
+%		\end{array}
+%	\end{multline}
 	and 
-	\begin{multline}
-		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
-		\begin{array}{ll}
-			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
-			~&\underline{x} \leq x\leq \overline{x}\\ 
-		\end{array}
-	\end{multline}
+%	\begin{multline}
+%		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
+%		\begin{array}{ll}
+%			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
+%			~&\underline{x} \leq x\leq \overline{x}\\ 
+%		\end{array}
+%	\end{multline}
 
@@
 
-	\begin{multline}
-		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
-		\begin{array}{ll}
-			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
-			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
-			~&\underline{x} \leq x\leq \overline{x}\\ 
-		\end{array}
-	\end{multline}
+%	\begin{multline}
+%		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
+%		\begin{array}{ll}
+%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
+%			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
+%			~&\underline{x} \leq x\leq \overline{x}\\ 
+%		\end{array}
+%	\end{multline}
 	and so on. However, in this case, the number of optimizations to solve should be 
@@
 	\paragraph{*** Alessandro's reformulation ***}
-	\begin{equation}
-		\begin{split}
-			\text{min} \displaystyle \, \pi_1 \cdot p \\
-			\text{subject to} & \displaystyle \pi_1 p > \pi_0 (1-p)\\
-			&\displaystyle \underline{\pi}_0 \leq \pi_0 \leq \overline{\pi}_0 \\
-			&\displaystyle \underline{\pi}_1 \leq \pi_1 \leq \overline{\pi}_1 \\
-			&\displaystyle \underline{p} \leq p \leq \overline{p} \\
-		\end{split}
-	\end{equation}
+%	\begin{equation}
+%		\begin{split}
+%			\text{min} \displaystyle \, \pi_1 \cdot p \\
+%			\text{subject to} & \displaystyle \pi_1 p > \pi_0 (1-p)\\
+%			&\displaystyle \underline{\pi}_0 \leq \pi_0 \leq \overline{\pi}_0 \\
+%			&\displaystyle \underline{\pi}_1 \leq \pi_1 \leq \overline{\pi}_1 \\
+%%		\end{split}
+%	\end{equation}
 	with the new variable specification:
@@
 	the problem becomes:
-	\begin{equation}
-		\begin{split}
-			\text{min} \displaystyle \, x_1 \\
-			\text{subject to\phantom{xx}} & \displaystyle x_1 > x_4\\
-			&\displaystyle \underline{\pi}_0 \leq x_2+x_3 \leq \overline{\pi}_0 \\
-			&\displaystyle \underline{\pi}_1 \leq x_1+x_4 \leq \overline{\pi}_1 \\
-			&\displaystyle \underline{p} \leq x_1+x_3 \leq \overline{p} \\
-		\end{split}
-	\end{equation}
+%	\begin{equation}
+%		\begin{split}
+%			\text{min} \displaystyle \, x_1 \\
+%			\text{subject to\phantom{xx}} & \displaystyle x_1 > x_4\\
+%			&\displaystyle \underline{\pi}_0 \leq x_2+x_3 \leq \overline{\pi}_0 \\
+%			&\displaystyle \underline{\pi}_1 \leq x_1+x_4 \leq \overline{\pi}_1 \\
+%			&\displaystyle \underline{p} \leq x_1+x_3 \leq \overline{p} \\
+%		\end{split}
+%	\end{equation}
 
@@
 
-	\begin{figure*}[htp!]
-		\centering
-		\begin{tikzpicture}[auto,scale=.7]
-			\node[node distance=.cm,fill=black!10] (pick) 
-			{\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
-			\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) 
-			{\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
-			\node[right of=pick,node distance=3cm,fill=black!10] (ask) 
-			{\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
-			\node[right of=ask,node distance=3cm,fill=black!10] (collect) 
-			{\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
-			\node[below of=collect,node distance=1.4cm] (decide) 
-			{\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? 
-			}\end{varwidth}};
-			\node[ left of=decide, node distance=3cm,fill=black!10] (stop) 
-			{\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
-			\node[left of=stop, node distance=3cm,fill=black!10] (assign) 
-			{\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
-			\draw[] (decide) -- node {\tiny YES}(stop);
-			\draw[] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
-			\draw[dashed] (db) -- (pick);
-			\draw[] (pick) -- (ask);
-			\draw[] (ask) -- (collect);
-			\draw[] (collect) -- (decide);
-			\draw[] (decide) -- (stop);
-			\draw[] (stop) -- (assign);
-		\end{tikzpicture}
-		\caption{CAT procedure}
-		\label{fig:alg}
-		%\vspace{-1cm}
-	\end{figure*}
+%	\begin{figure*}[htp!]
+%		\centering
+%		\begin{tikzpicture}[auto,scale=.7]
+%			\node[node distance=.cm,fill=black!10] (pick) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
+%			\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
+%			\node[right of=pick,node distance=3cm,fill=black!10] (ask) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
+%			\node[right of=ask,node distance=3cm,fill=black!10] (collect) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
+%			\node[below of=collect,node distance=1.4cm] (decide) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? 
+%%			}\end{varwidth}};
+%			\node[ left of=decide, node distance=3cm,fill=black!10] (stop) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
+%			\node[left of=stop, node distance=3cm,fill=black!10] (assign) 
+%%			{\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
+%			\draw[] (decide) -- node {\tiny YES}(stop);
+%			\draw[] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
+%			\draw[dashed] (db) -- (pick);
+%			\draw[] (pick) -- (ask);
+%			\draw[] (ask) -- (collect);
+%			\draw[] (collect) -- (decide);
+%			\draw[] (decide) -- (stop);
+%			\draw[] (stop) -- (assign);
+%		\end{tikzpicture}
+%		\caption{CAT procedure}
+%		\label{fig:alg}
+%		%\vspace{-1cm}
+%	\end{figure*}
 
@@
 	%achieved for skill $X$ after the answers $\bm{y}$. 
-	Finally, to generalise Eq.~\eqref{eq:strongext} to CNs, we define the information gain 
+	Finally, to generalise Eq.~\ref{eq:strongext} to CNs, we define the information gain 
 	provided by a question $Y'$ for its background skill $X_{Y'}$ as 
@@
 	\ref{sec:credalCAT}.
+%\end{document}
 

### 2021-05-06 paper.tex

@@
 \end{abstract}
+
+\section{A Toy Example}
+As a first, demonstrative, example of our ideas consider a model characterized by a single (Boolean) Skill $S$ and a set of questions $\bm{Q}$ picked from a set of templates.
+Let us first focus on a Bayesian, i.e., precise, case.
+The prior specification $P(S)$ is achieve by a single parameter $p \in [0,1]$ such that $P(S=1)=p$.
+For a generic question $Q$, which is also assumed to be Boolean, a complete specification of the CPT $P(Q|S)$ is obtained by the two parameters $p_0,p_1\in [0,1]$ where $P(Q=1|S=0)=p_0$ and $P(Q=1|S=1)=p_1$.
+In other wrods $p_0$ denote the probability of providing a right answer to the question for a student who does not have the considered skill and $p_1$ for a student who have that skill.
+An obvious constraint is $p_1>p_0$, i.e., having the skill makes your probability of providing a right answer higher.
+The inequality should be strict, otherwise the two probabilities are equal, and this means that the answer is irrelevant for the skill.
+Although parameters $p_1$ and $p_0$ already give a complete parametrization, we perform the linear transformation
+$\lambda:=1-\frac{1}{2}(p_0+p_1)$ and $\delta=(p_1-p_0)$.
+The first quantity is the arithmetic average of giving a wrong answer and we might indent it as the \emph{level} of the question, this mining that the higher is $\lambda$ the more unlikely is to receive a correct answer is the students have the same probability of having and not having the skill.
+Regarding $\delta$ we might intend it as the (average) discriminative power of a question.
+Note that the inverse relations give $p_1=1-\lambda+\frac{\delta}{2}$
+and $p_0=1-\lambda-\frac{\delta}{2}$. Where constraint $p_1>p_0$ is just $\delta>0$ and any other value in $[0,1]$ for both parameters is valid.
+
+In our toy example, we consider nine possible templates, made of triads of templates with the same $\delta$ and same $\lambda$. The reference values $[0.4,0.5,0.6]$ are used.
 

### 2021-05-06 paper.tex
Better structure

@@
 \begin{document}
-\title{Approximating Information-Theoretic Scores\\for Computer Adaptive Tests\\in Bayesian and Credal Networks}
+\title{Information Theoretic Scores Approximation for Adaptive Tests in Bayesian and Credal Networks}
 %%\thanks{Supported by organization x.}}
@@
 \begin{abstract}
-A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skills of the test taker.
+A test is \emph{adaptive} when its sequence and number of questions is tuned on the basis of the estimated skills of the test taker.
 Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills.
-Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model.
-This might make inference considerably harder in the underlying model, this being especially the case for the information theoretic quantities generally used as a score to drive the adaptation process.
-Here we present an alternative score based on the mode of the posterior probabilities of the model.
-We show how this makes considerably simpler the evaluation of the score in the credal case.
-Numerical tests are promising, we show how the performance are similar in the Bayesian network case, while xxx.
-%considered. 
-%We propose an alternative 
-%We present.
-%with xxx. Interval valued quantification
-%We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers.
-Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge.
-The counterpart is a less straightforward identification of the
-%information-theoretic measure controlling the question-selection and the test-stopping criteria.
-We elaborate on these issues and propose a sound and computationally feasible procedure.
-Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
+Yet, a better elicitation of the question/skill uncertainty can be achieved by interval-valued probabilities.
+This transforms the model into a credal network, thus making the inferential complexity of the queries required to select the questions considerably harder.
+This is especially the case for the information theoretic quantities generally used as a score to drive the adaptation process.
+Here we present an alternative family of scores based on the mode of the posterior probabilities.
+We show how this makes considerably simpler the evaluation of the score in the credal case, without significantly affecting the quality of the adaptive process.
+Numerical tests involving synthetic and real-world data are used to support our thesis.
 %150-200 words - 12 pages
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Computer adaptive tests \and Information theory \and Credal networks \and Bayesian networks}
 \end{abstract}
 
-\section{A Toy Example}
-As a first, demonstrative, example of our ideas consider a model characterized by a single (Boolean) Skill $S$ and a set of questions $\bm{Q}$ picked from a set of templates.
-Let us first focus on a Bayesian, i.e., precise, case.
-The prior specification $P(S)$ is achieve by a single parameter $p \in [0,1]$ such that $P(S=1)=p$.
-For a generic question $Q$, which is also assumed to be Boolean, a complete specification of the CPT $P(Q|S)$ is obtained by the two parameters $p_0,p_1\in [0,1]$ where $P(Q=1|S=0)=p_0$ and $P(Q=1|S=1)=p_1$.
-In other wrods $p_0$ denote the probability of providing a right answer to the question for a student who does not have the considered skill and $p_1$ for a student who have that skill.
-An obvious constraint is $p_1>p_0$, i.e., having the skill makes your probability of providing a right answer higher.
-The inequality should be strict, otherwise the two probabilities are equal, and this means that the answer is irrelevant for the skill.
-Although parameters $p_1$ and $p_0$ already give a complete parametrization, we perform the linear transformation
-$\lambda:=1-\frac{1}{2}(p_0+p_1)$ and $\delta=(p_1-p_0)$.
-The first quantity is the arithmetic average of giving a wrong answer and we might indent it as the \emph{level} of the question, this mining that the higher is $\lambda$ the more unlikely is to receive a correct answer is the students have the same probability of having and not having the skill.
-Regarding $\delta$ we might intend it as the (average) discriminative power of a question.
-Note that the inverse relations give $p_1=1-\lambda+\frac{\delta}{2}$
-and $p_0=1-\lambda-\frac{\delta}{2}$. Where constraint $p_1>p_0$ is just $\delta>0$ and any other value in $[0,1]$ for both parameters is valid.
-
-In our toy example, we consider nine possible templates, made of triads of templates with the same $\delta$ and same $\lambda$. The reference values $[0.4,0.5,0.6]$ are used.
+\section{Introduction}
+A test or an exam can be naturally intended as a measurement process, with the questions acting as sensors measuring the skills of the test taker in a particular discipline.
+Such a measurement is typically imperfect with the skills acting as latent variables whose actual values cannot be revealed in a perfectly reliable why.
+The role of the questions, whose answers are regarded as manifest variables, is to reduce the uncertainty about the latent skills.
+Following this perspective, probabilistic modelling is an obvious framework to describe a test.
+Consider for instance the example in Figure X, where minimalistic Bayesian network is used to describe the probability of the test taker having or not having understood how to multiply numbers.
+In such a framework making the test \emph{adaptive}, i.e., picking a next question on the basis of the current knowledge level of the test takes is also very natural.
+The expected information gain for the available questions might be naturally used to select the question leading to the more informative results about the skill level of the student, this taking place before the answer to the question on the basis of the expectation about the answer of the question taker.
+
+An important issue when coping with such approaches is providing a realistic assessment for the probabilistic parameters associated with the modelling of the relations between the questions and the skills.
+Having to provide sharp numerical numbers for these probabilities might be critical: as the skill is typically a latent quantity complete data are not available for a statistical learning of the parameters and the elicitaion is typically demanded to experts (e.g., the teacher).
+Yet, it might be not obvious to express such a domain knowledge by single number and more robust eliicitation such as ranges of probability might add realism and robustness to the models.
+Under such a generalized setup, a Bayesian network approach would correspond to cope with a credal network instead.
+Yet, the higher computational complexity characterizing the inference in credal networks, might become a critical issue.
+This is especially the case when coping with information theoretic measures such a information gain, whose computation might lead to highly non-linear optimization tasks.
+The goal of this paper is to investigate the role of alternatives to information theoretic score in order to drive the question selection in adaptive tests.
+In particular we consider a family of scores based on the (expected) mode of the posterior distributions over the skill.
+We show that, when coping with credal networks, even these scores can be computed by reduction to xxx.
+
+The paper is organized as follows.
+A critical discussion about the existing work in this field is in Section \ref{sec:work}, while the necessary background material is reviewed in Section \ref{sec{background}}.
+The technical part of the paper is in Section X, while the experiments are in Section X.
+Conclusions and outlooks are in Section X.
+
+\section{Related Work}\label{sec:work}
+
+Apart from graphical models, adaptive algorithms have been proposed within a genetic optimization framework.
+
+The idea of using Bayesian network in grading environment is not new. xxx.
+
+As already noticed in the previous section, the latent nature of the student skills might hinder the direct statistical learning of the parameters of such models.
+This naturally led some authors to consider missing data modelling.
+In particular the work of xxxx Vomlel related to EM algorithm in Bayesian networks is a notable example of this kind of approaches.
+Some other authors considered even more extreme directions involving missingness even about the answers such as \cite{bachrach2012grade}.
+This is also related to the notion of monotonicity \cite{plajner2020monotonicity}.
+
+\section{Background}
+\subsection*{Basic Precise and Imprecise Probability Theory}
+We denote variables by Latin uppercase letters, lowercase for their generic values, and calligraphic ones for the set of their possible values.
+Thus $x \in \mathcal{X}$ is a possible value of $X$.
+Here only variable with a finite number of possible values is considered.\footnote{IRT is using continuous variables xxx}.
+A probability mass function over $X$ is denote as $P(X)$, while $P(x)$ is the probability assigned to state $x$.
+A joint PMF is similarly denotes as $P(X,Y)$.
+Conditional probabilities are obtained by xxx.
+Conditional independence.
+Expectations for a function $f$ of xxx.
+Entropy is denotes as $H(X)$.
+
+A credal set (CS) is a set of PMFs. $K(X)$ denote a CS over $X$, i.e., a set of PMFs over $X$.
+
+\subsection*{Bayesian and Credal Networks}
+Let $\mathcal{G}$ be a directed acyclig graph whose nodes are in one-to-one correspondence with a set of variables $\bm{X}$. A BN is just a xx A credal network is xxx.
 
@@
 
-\begin{algorithm}[H]
-    \SetAlgoLined
-    \KwResult{Write here the result }
-    initialization\;
-    \While{While condition}{
-        instructions\;
-        \eIf{condition}{
-            instructions1\;
-            instructions2\;
-        }{
-            instructions3\;
-        }
-    }
-    \caption{How to write algorithms}
-\end{algorithm}
+%\begin{algorithm}[H]
+%    \SetAlgoLined
+%    \KwResult{Write here the result }
+%    initialization\;
+%    \While{$\neg \tt{Stopping}(\bm{e})$}{
+%        instructions\;
+%        %\eIf{condition}{
+%        %    instructions1\;
+%        %    instructions2\;
+%        %}{
+%        %    instructions3\;
+%        %}
+%    }
+%    \caption{How to write algorithms}
+%\end{algorithm}
 
@@
 
-The typical goal of a TA is to achieve a reliable evaluation of the student $\sigma$.
+The typical goal of a TA is to achieve a reliable evaluation of the student $\sigma$ after the answers $\bm{e}$.
 As each answer is assumed to improve such quality, asking all the questions, no matter their order because of the exchangeability assumption, would be an obvious choice.
@@
 \section{Bayesian Adaptive Testing Algorithms}
+The general setup considered in Algorithm X can be specialized to the case of graphical models as in Section X.
+Let us assume that the knwoledge level of student $\sigma$ is described by a familty of skills $\bm{S}$, while the questions are similarly associated with a set of variables $\bm{Q}$.
+As a remark, note that we might coarsen the set of possible values $\mathcal{Q}$ each $Q\in \bm{Q}$ (e.g., a multiple choice question with three options might have a single right answer and two other answers that are not distinguishable from the evaluation point of view).
+Let us define a DAG over $\bm{S}$ and $\bm{Q}$, in particular, we assume each $Q\in\bm{Q}$ to be a leaf child of a subset of $\bm{S}$.
+This reflects the assumption xxx in the previous section.
+As a consequence of the irrelevance, we might remove unasked questions xxx.
+
+Regarding the stopping rule, besides the general criteria discussed in the previous section, a typical approach might consist in evaluating the entropy $H(\bm{S}|\bm{e}))$.
+
 In the setup of algorithm.
@@
 %	\end{equation}
+
+    \section{A Toy Example}
+    As a first, demonstrative, example of our ideas consider a model characterized by a single (Boolean) Skill $S$ and a set of questions $\bm{Q}$ picked from a set of templates.
+Let us first focus on a Bayesian, i.e., precise, case.
+The prior specification $P(S)$ is achieve by a single parameter $p \in [0,1]$ such that $P(S=1)=p$.
+For a generic question $Q$, which is also assumed to be Boolean, a complete specification of the CPT $P(Q|S)$ is obtained by the two parameters $p_0,p_1\in [0,1]$ where $P(Q=1|S=0)=p_0$ and $P(Q=1|S=1)=p_1$.
+In other wrods $p_0$ denote the probability of providing a right answer to the question for a student who does not have the considered skill and $p_1$ for a student who have that skill.
+An obvious constraint is $p_1>p_0$, i.e., having the skill makes your probability of providing a right answer higher.
+The inequality should be strict, otherwise the two probabilities are equal, and this means that the answer is irrelevant for the skill.
+Although parameters $p_1$ and $p_0$ already give a complete parametrization, we perform the linear transformation
+    $\lambda:=1-\frac{1}{2}(p_0+p_1)$ and $\delta=(p_1-p_0)$.
+The first quantity is the arithmetic average of giving a wrong answer and we might indent it as the \emph{level} of the question, this mining that the higher is $\lambda$ the more unlikely is to receive a correct answer is the students have the same probability of having and not having the skill.
+Regarding $\delta$ we might intend it as the (average) discriminative power of a question.
+    Note that the inverse relations give $p_1=1-\lambda+\frac{\delta}{2}$
+    and $p_0=1-\lambda-\frac{\delta}{2}$. Where constraint $p_1>p_0$ is just $\delta>0$ and any other value in $[0,1]$ for both parameters is valid.
+
+    In our toy example, we consider nine possible templates, made of triads of templates with the same $\delta$ and same $\lambda$. The reference values $[0.4,0.5,0.6]$ are used.
 
@@
 \bibliography{biblio}
-\end{document}
+\end{document}s

### 2021-05-12 paper.tex
More stable version

--- 2021-05-06 paper.tex
@@
 \documentclass[runningheads]{llncs}
-\usepackage[]{algorithm2e}
-\usepackage[]{algorithmic}
-\usepackage{bm,hyperref,booktabs,tikz,pgf,pgfplots,amsmath}
+\usepackage{algorithm,algorithmic,amsfonts,bm,hyperref,booktabs,tikz,pgf,pgfplots,amsmath,soul,subcaption,url,graphicx,amsmath,booktabs,booktabs,nicefrac,bm,colortbl,tikz,pgfplots,enumerate,xargs}
 \usetikzlibrary{arrows,automata,circuits}
-%\pgfplotsset{compat=1.13}
-%\usepackage{pgfkeys}
-%\usepackage{graphicx}
-%xcolor} 
-%amsmath} 
-%amstext} 
-%amssymb} 
-%amsfonts} 
-%\usepackage{mathptmx} 
-%\usepackage[scaled=.90]{helvet} 
-%\usepackage{courier} 
-%\usepackage{textcomp} 
-%\usepackage{array}
-%\usepackage{varwidth}
-%\usepackage[american]{babel}
-%usepackage{mathtools} % fixes and extends amsmath
-%mathtoolsset{mathic}
-%\allowdisplaybreaks
-%\usepackage{mathptmx}
-%\usepackage{tabu}
-%%\usepackage{breqn}
-%\usepackage{algorithm,algorithmic,bm}
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-%\renewcommand\UrlFont{\color{blue}\rmfamily}
-%% Suggested packages, as needed:
-%\usepackage{booktabs} % commands to create good-looking tables
-%\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
-%drawing custom shapes
-%\usetikzlibrary{%
-%	arrows,%
-%	calc,%
-%	fit,%
-%	patterns,%
-%	plotmarks,%
-%	shapes.geometric,%
-%	shapes.arrows,%
-%	shapes.callouts,%
-	% shapes.multipart,%
-	% shapes.gates.logic.US,%
-	% shapes.gates.logic.IEC,%
-	% er,%
-	% automata,%
-%	topaths,%
-%	trees,%
-%	matrix,%
-%	% calendar,%
-%	folding,%
-%	fadings,%
-%	positioning,%
-%	scopes,%
-%	decorations.fractals,%
-%	decorations.shapes,%
-%	decorations.text,%
-%	decorations.pathmorphing,%
-%	decorations.pathreplacing,%
-%	decorations.footprints,%
-%	decorations.markings,%
-%	shadows}
-%\usepackage{trace-pgfkeys}
+\captionsetup{compatibility=false}
+\usetikzlibrary{arrows,plotmarks,decorations.markings,trees,shapes}
+\tikzstyle{nodo}=[ellipse,draw=black!100,fill=black!30,line width=.7pt,minimum width=1.2cm,minimum height=.7cm]
+\tikzstyle{Qnodo}=[ellipse,draw=black!100,fill=black!10,line width=.7pt,minimum width=1.2cm,minimum height=.7cm]
+\tikzstyle{arco}=[draw=black!80,line width=.7pt, postaction={decorate}, decoration={markings,mark=at position 1.0 with {\arrow[ draw=black!80,line width=.7pt]{>}}}]
+\tikzstyle{decision} = [rectangle, draw, fill=black!100,text=white, text width=4.5em, text badly centered, node distance=3cm, minimum height=3em]
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, text width=5em, text centered, rounded corners, minimum height=3em]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm, minimum height=2em]
+\def\mystrut{\vphantom{hg}}
+\pgfplotsset{legend image with text/.style={
+legend image code/.code={%
+\node[anchor=center] at (0.3cm,0cm) {#1};}},}
+\pgfplotsset{compat=1.13}
 \begin{document}
-\title{Approximating Information-Theoretic Scores\\for Computer Adaptive Tests\\in Bayesian and Credal Networks}
-%%\thanks{Supported by organization x.}}
-%\titlerunning{Abbreviated paper title}
+\title{A New Score for Adaptive Tests\\in Bayesian and Credal Networks}
 \author{Alessandro Antonucci \and
@@
 Giorgia Adorni}
-%\authorrunning{F. Author et al.}
+%%\thanks{Supported by organization x.}}
+%\titlerunning{A New ScoreAbbreviated paper title}
+\authorrunning{Antonucci et al.}
 \institute{Istituto Dalle Molle di Studi sull'Intelligenza Artificiale, Lugano, Switzerland\\
@@
 \begin{abstract}
-A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skills of the test taker.
-Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills.
-Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model.
-This might make inference considerably harder in the underlying model, this being especially the case for the information theoretic quantities generally used as a score to drive the adaptation process.
-Here we present an alternative score based on the mode of the posterior probabilities of the model.
-We show how this makes considerably simpler the evaluation of the score in the credal case.
-Numerical tests are promising, we show how the performance are similar in the Bayesian network case, while xxx.
-%considered. 
-%We propose an alternative 
-%We present.
-%with xxx. Interval valued quantification
-%We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers.
-Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge.
-The counterpart is a less straightforward identification of the
-%information-theoretic measure controlling the question-selection and the test-stopping criteria.
-We elaborate on these issues and propose a sound and computationally feasible procedure.
-Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
-%150-200 words - 12 pages
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+A test is \emph{adaptive} when its sequence and number of questions is dynamically tuned on the basis of the estimated skills of the taker.
+Graphical models, such as Bayesian networks, are used for adaptive tests as they allow to model the uncertainty about the questions and the skills in an explainable fashion, especially when coping with multiple skills.
+A better elicitation of the uncertainty in the question/skills relations can be achieved by interval probabilities.
+This turns the model into a \emph{credal} network, thus making the inferential complexity of the queries required to select questions more demanding.
+This is especially the case for the information theoretic quantities used as \emph{scores} to drive the adaptive mechanism.
+We present an alternative family of scores, based on the mode of the posterior probabilities and hence easier to explain.
+This makes considerably simpler the evaluation in the credal case, without significantly affecting the quality of the adaptive process.
+Numerical tests on synthetic and real-world data are used to support this claim.
+%12 pages
+\keywords{Computer adaptive tests \and Information theory \and Credal networks \and Bayesian networks}
 \end{abstract}
-
-\section{A Toy Example}
+\section{Introduction}\label{sec:intro}
+A test or an exam can be naturally intended as a measurement process, with the questions acting as sensors measuring the skills of the test taker in a particular discipline.
+Such measurement is typically imperfect with the skills acting as latent variables whose actual values cannot be revealed in a perfectly reliable way.
+The role of the questions, whose answers are regarded instead as manifest variables, is to reduce the uncertainty about the latent skills.
+Following this perspective, probabilistic modelling is an obvious framework to describe tests.
+Consider for instance the example in Figure \ref{fig:minicat}, where a small Bayesian network is used to describe the probability of the test taker having understood how to multiply numbers.
+In such a framework making the test \emph{adaptive}, i.e., picking a next question on the basis of the current knowledge level of the test taker is also very natural.
+The expected information gain for the available questions might be naturally used to select the question leading to the more informative results about the skill level of the test taker.
+This might take place before the answer to the question on the basis of the expectations about the possible answers.
+
+A critical point when coping with such approaches is to provide a realistic assessment for the probabilistic parameters associated with the modelling of the relations between the questions and the skills.
+Having to provide sharp numerical values for these probabilities might be difficult.
+As the skill is typically a latent quantity, complete data are not available for a statistical learning of the parameters and the elicitation should therefore demanded to experts (e.g., a teacher).
+Yet, it might be not obvious to express such a domain knowledge by single numbers and a more robust elicitation, such as a probability interval, might add realism and robustness to the modelling process \cite{hajek2012rationality}.
+With such generalized assessments of the parameters a Bayesian network simply becomes a \emph{credal} network \cite{antonucci2010d}.
+Yet, the counterpart of such increased realism is the higher computational complexity characterizing the inference in credal networks \cite{maua14jair}.
+This is especially the case when coping with information theoretic measures such a information gain, whose computation might lead to complex non-linear optimization tasks \cite{mangili2017b}.
+The goal of this paper is to investigate the potential of alternatives to the information-theoretic scores driving the question selection in adaptive tests based on directed graphical models, no matter whether these are Bayesian or credal networks.
+In particular, we consider a family of scores based on the (expected) mode of the posterior distributions over the skills.
+We show that, when coping with credal networks, the computation of these scores can be reduced to the simpler optimization tasks involving multi-linear optimizations for which powerful approximation schemes are already available \cite{antonucci2013a}.
+Moreover, we show that these scores benefit of better explainability properties, thus allowing for a more transparent process in the question selection.
+
+\begin{figure}[htp!]
+\centering
+\begin{tikzpicture}[scale=1]
+\node[] ()  at (-5,0.5) {\tiny $P(S=1|Q=1)=0.5$};
+\node[] ()  at (-5,-2) {\tiny $P(S=1|Q=1)=0.5$};
+\node[] ()  at (-5,-3) {\tiny $P(S=1|Q=1)=0.5$};
+\node[] ()  at (3,0.5) {\tiny $P(S=1)=0.5$};
+\node[] ()  at (0,-3) {\tiny $2x3=?$ \quad $2x3=?$\quad  $2x3=?$};
+\node[] ()  at (0,-2) {\tiny $P(Q=1|S=1)=0.3$ \quad $0.4$\quad  $0.5$};
+\node[] ()  at (0,-2.5) {\tiny $P(Q=1|S=0)=0.3$ \quad  $0.4$ \quad  $0.5$};
+\node[nodo] (s)  at (0,0.5) {$S$};
+\node[Qnodo] (q1)  at (-2.,-1) {$Q_1$};
+\node[Qnodo] (q2)  at (0,-1) {$Q_2$};
+\node[Qnodo] (q3)  at (2,-1) {$Q_3$};
+\draw[arco] (s) -- (q1);
+\draw[arco] (s) -- (q2);
+\draw[arco] (s) -- (q3);
+\end{tikzpicture}
+\caption{Ad adaptive testing scheme to evaluate the multiplication (Boolean) skill $S$ by three (Boolean) questions. Probabilities are assessed by the Bayesian network on the right}
+    \label{fig:minicat}
+\end{figure}
+*** espandere figura ***
+\newpage 
+The paper is organized as follows.
+A critical discussion about the existing work in this area is in Section \ref{sec:work}.
+The necessary background material is reviewed in Section \ref{sec:background}.
+The adaptive testing concepts are introduced in Section \ref{sec:cat} and specialized to graphical models in \ref{sec:bncat}.
+The technical part of the paper is in Section \ref{sec:mode}, where the new scores are discussed and specialized to the credal case, while the experiments are in Section \ref{sec:exp}.
+Conclusions and outlooks are in Section \ref{sec:conc}.
+
+\section{Related Work}\label{sec:work}
+Modelling a test as a process involving latent variables is a classical approach since the proposal of the classical \emph{item response theory}, that has been widely used even to implement adaptive sequences \cite{xxx}.
+Despite its success related to the ease of implementation and inference, IRT might be inadequate when coping with multiple latent skill, especially when these are dependent.
+For such cases, interpretable graphical models such as Bayesian networks have been resulted more effective [x].
+The development of (computer) adaptive tests is a classical topic for AI \cite{xx}.
+Apart from graphical models, adaptive algorithms have been proposed within a genetic optimization framework.
+The idea of using Bayesian network in grading environment is not new.
+xxx.
+As already noticed in the previous section, the latent nature of the student skills might hinder the direct statistical learning of the parameters of such models.
+This naturally led some authors to consider missing data modelling.
+In particular the work of xxxx Vomlel related to EM algorithm in Bayesian networks is a notable example of this kind of approaches.
+Some other authors considered even more extreme directions involving missingness even about the answers such as \cite{bachrach2012grade}.
+This is also related to the notion of monotonicity \cite{plajner2020monotonicity}.
+The potential of these models in terms of explainability of the results has been emphasized in the work Work of Darwiche about same-probability problem.
+*** completare *** Bayesian networks (BNs) \cite{koller2009} have been used to model the knowledge driving such intelligent systems \cite{almond2015bayesian}.
+However, collecting large sets of reliable data in educational domains may be difficult and time consuming (e.g., a course with few students, or taught for the first time), and the quantification should be based on expert knowledge only.
+To elicit a Bayesian network, an expert might face questions like: ``\emph{which is the probability of a student with a particular knowledge level giving the right answer to a question?}''.
+Giving sharp probabilities for questions of this kind can be problematic for an expert, whose knowledge is mostly qualitative (e.g., ``\emph{a right answer is very unlikely}'').
+Fuzzy linguistic approaches represent a viable, non-numerical, way to address these issues \cite{badaracco2013fuzzy}.
+To stick within the probabilistic framework, verbal-numerical probability scales associated with sharp values \cite{renooij1999talking} or intervals \cite{walley1991statistical} have been also proposed.
+a generalization of BNs based on the imprecise probability theory \cite{walley1991statistical}, where local parameters are defined by set-valued probabilities.
+This simplifies the elicitation process and offers a more reliable handling of the related uncertainty.
+Moving from BNs to CNs implies two main issues: (i) numerical inferences will be interval-valued too, thus making debatable both the decision criterion \cite{troffaes} an the information measures \cite{klir1999uncertainty} to adopt; and (ii) inference tasks in CNs typically belongs to higher complexity classes than their Bayesian counterparts \cite{maua14jair}.
+Both these issues are addressed by defining a computationally feasible procedure based on CNs to be used for practical implementation of intelligent systems solely specified by expert knowledge.
+To the best of our knowledge this is the first attempt to perform e-testing with models of this kind.
+
+We focus on the application of CNs to \emph{computer adaptive testing} (CAT), i.e., an approach to e-testing that adjusts the sequence and the number of questions to the ability level of the test taker.
+CATs have the potential to make the test an individualised experience that challenges and does not discourage the test takers, as most of the questions are near their ability levels.
+Building upon \emph{item response theory} \cite{hambleton1985item}, the common background underpinning CATs, graphical modeling (such as BNs and CNs) offers a powerful language for describing complex multivariate dependencies between skills and rich tasks.
+Several researchers have exploited the potential of BNs both in adaptive and non-adaptive educational assessment \cite{vomlel2004building,plajner2015}.
+These authors focus on applications for which data are available to learn the model parameters.
+We regard this point as a serious limitation, possibly hindering CATs adoption by many teachers and instructors.
+The results are promising: CAT based on CNs is effective in reducing the number of questions while maintaining a high accuracy in the evaluation and the approximations introduced do not compromise the procedure's effectiveness.
+
+\section{Background on Bayesian and Credal Networks}\label{sec:background}
+We denote variables by Latin uppercase letters, while using lowercase for their generic values, and calligraphic for the set of their possible values.
+Thus, $x \in \mathcal{X}$ is a possible value of $X$.
+Here only variables with a finite number of possible values are considered.\footnote{Adaptive approaches such as IRT \cite{xx} adopt continuous latent variables.}
+
+\subsection{Bayesian Networks}
+A probability mass function over $X$ is denoted as $P(X)$, while $P(x)$ is the probability assigned to state $x$.
+Given a function $f$ of $X$, its expectation with respect to $P(X)$ is $\mathbb{E}_P(f):=\sum_{x\in\mathcal{X}} P(x) \cdot f(x)$.
+The expectation of $-\log_k[P(X)]$ is called \emph{entropy} and denoted also as $H_P(X)$.\footnote{To cope with zero probabilities, we set $0 \cdot \log_k 0 = 0$.} We assume $k:=|\mathcal{X}|$ to have the maximum of the entropy, achieved for uniform PMFs, equal to one.
+
+Given a joint PMF $P(X,Y)$, the marginal PMF $P(Y)$ is obtained by summing out the other variable, i.e., $P(y)=\sum_{x\in\mathcal{X}} P(x,y)$.
+Conditional PMFs such as $P(X|y)$ are similarly obtained by Bayes's rule, i.e., $P(x|y)=P(x,y)/P(y)$ provided that $P(y)>0$.
+Notation $P(X|Y):=\{P(X|y)\}_{y\in\mathcal{Y}}$ is used for such conditional probability table (CPT).
+The entropy of a conditional PMF is defined as in the unconditional case and denoted as $H_P(X|y)$.
+The expected entropy is a weighted average of conditional entropies, i.e., $H_P(X|Y):=\sum_{y\in\mathcal{Y}} H_P(X|y) P(y)$.
+If $P(x,y)=P(x) P(y)$ for each $x\in\mathcal{X}$ and $y\in\mathcal{Y}$, variables $X$ and $Y$ are stochastically independent.
+A conditional formulation can be also considered.
+
+We assume the set of variables $\bm{X}:=(X_1,\ldots,X_n)$ to be in one-to-one correspondence with a directed acyclic graph $\mathcal{G}$.
+For each $X\in\bm{X}$, the parents of $X$ are called predecessor of $X$ according to $\mathcal{G}$ and denoted as $\mathrm{Pa}_X$.
+The graph $\mathcal{G}$ together with the collection of CPTs $\{P(X|\mathrm{Pa}_X)\}_{X\in\bm{X}}$ provides a Bayesian network (BN) specification \cite{koller2009}.
+Under the Markov condition, that states that every variable is conditionally independent of its non-descendants non-parents given its parents, a BN compactly defines a joint PMF $P(\bm{X})$ that factorizes as $P(\bm{x})=\prod_{X\in\bm{X}} P(x|\mathrm{pa}_X)$.
+
+\subsection{Credal Sets and Credal Networks}
+A set of PMFs over $X$ is denoted as $K(X)$ and called \emph{credal set} (CS).
+Expectations based on CSs are the bounds of the PMF expectations with respect to the CS.
+Thus $\underline{E}_K[f]:=\inf_{P(X)\in K(X)} \mathbb{E}_P[f]$ and similarly for the supremum $\mathbb{E}_K$.
+Expectations of events are in particular caller lower and upper probabilities and denotes as $\underline{P}$ and $\overline{P}$.
+Notation $K(X|y)$ is used for a set of conditional CSs, while $K(X|Y):=\{K(X|y)\}_{y\in\mathcal{Y}}$ is a credal CPT (CCPT).
+
+Analogously to a BN, a credal network (CN) \cite{cozman2000}  is specified by graph $\mathcal{G}$ together with a family of CCPTs $\{K(X|\mathrm{Pa}_X)\}_{X\in\bm{X}}$.
+A CN defines a joint CS $K(\bm{X})$ obtained by the set of xxx.
+
+\section{Testing Algorithms}\label{sec:cat}
+A typical test aims at evaluating the knowledge level of a test taker $\sigma$ on the basis of her answers to a number of questions.
+Let $\bm{Q}$ denote a repository of questions available to the instructor.
+The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be defined in advance.
+We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the test taker, and to decide when the test stops.
+Algorithm \ref{alg:ta} depicts a general TA scheme, with $\bm{e}$ denoting the array of the answers collected from the test taker $\sigma$.
+
+\begin{algorithm}[htp!]
+\begin{algorithmic}[1]
+\STATE $\bm{e}\gets\emptyset$
+\WHILE{ {\bf not} $\tt{Stopping}(\bm{e})$}
+\STATE $Q^* \gets \tt{Pick}(\bm{Q},\bm{e})$
+\STATE $q^* \gets {\tt{Answer}}(Q^*,\sigma)$
+\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
+\STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
+\ENDWHILE
+\STATE {\bf return} $\tt{Evaluate}(\bm{e})$
+\end{algorithmic}
+\caption{General TA: given the profile $\sigma$ and repository $\bm{Q}$, an evaluation based on answers $\bm{e}$ is returned.\label{alg:ta}}
+\end{algorithm}
+
+Boolean function ${\tt Stopping}$ decides whether the test should end, this choice being possibly based on the previous answers in $\bm{e}$.
+Trivial stopping rules might be based on the number of questions asked to the test takes (${\tt Stopping}(\bm{e})=1$ if and only if $|\bm{e}|>n$) or on the number of correct answers provided that a maximum number of questions is not exceeded.
+Function ${\tt Pick}$ selects instead the question to be asked to the student from the repository $\bm{Q}$.
+A TA is called \emph{adaptive} when this function takes into account the previous answers $\bm{e}$.
+Trivial non-adaptive strategies might consist in randomly picking an element of $\bm{Q}$ or following a fixed order.
+Function ${\tt Answer}$ is simply collecting (or simulating) the answer of test taker $\sigma$ to a particular question $Q$.
+In our assumptions, this answer is not affected by the previous answers to other questions.\footnote{Generalized setups where the quality of the student answer is affected by the previous answers will be discussed at the end of the paper.
+This might include a \emph{fatigue} model negatively affecting the quality of the answers when many questions have been already answered as well as the presence of \emph{revealing} questions that might improve the quality of other answers.}
+
+Finally, ${\tt Evaluate}$ is a function returning the overall judgement of the test (e.g., a numerical grade or a pass/fail Boolean) on the basis of all the answers collected after the test termination.
+Trivial examples of such functions are the percentage of correct answers or a Boolean that is true when a sufficient number of correct answers has been provided.
+Note also that in our assumptions the TA is \emph{exchangeable}, i.e., the stopping rule, the question finder and the evaluation function are invariant with respect to permutations in $\bm{e}$.
+In other words, the same next question, the same evaluation and the same stopping decision is produced for any two students, who provided the same list of answers in two different orders.
+
+A typical TA is required to achieve a reliable evaluation of the student $\sigma$ after the answers $\bm{e}$.
+As each answer is individually assumed to improve such quality, asking all the questions, no matter in which  order because of the exchangeability assumption, is an obvious choice.
+Yet, this might be impractical (e.g., because of time limitations) or just provide an unnecessary burden to the test taker.
+The goal of a good TA is therefore to trade off the accuracy of the evaluation and the number of questions.\footnote{In some generalized setups, other elements such as a \emph{serendipity} in choice in order to avoid tedious sequences of questions might be also considered \cite{xx}.}
+
+\section{Adaptive Testing in Bayesian Networks}\label{sec:bncat}
+%Item response theory is a popular *** Something about IRT here ***.
+Most of these approaches are based an a unidimensional representation of the student knowledge level.
+Proposals to cope with multidimensional IRTs have been considered, but this results critical when coping with dependencies between them.
+For this reason probabilistic modelling can be considered.
+This is the topic of the next section.
+
+The general TA setup in Algorithm \ref{alg:ta} can be easily specialized to BNs as follows.
+First, we identify the profile $\sigma$ of the test saker with the actual states of a number of latent discrete variables, called \emph{skills}.
+Let $\bm{S}=\{S_i\}_{j=1}^n$ denote these skill variables, and $\bm{s}_\sigma$ the actual values associated with the test take.
+Skills are typically ordinal variables, whose states corresponds to increasing knowledge levels.
+Questions in $\bm{Q}$ are still described as manifest variables whose actual values are returned by the {\tt answer} function.
+This is achieved by a (possibly stochastic) function of the actual profile $\bm{s}_\sigma$.
+Thus reflect the taker perspective, while the teacher has clearly no access to $\bm{s}_\sigma$.
+As a remark, note that we might coarsen the set of possible values $\mathcal{Q}$ each $Q\in \bm{Q}$: for instance, a multiple choice question with three options might have a single right, the two other answers being indistinguishable from the evaluation point of view.\footnote{The case of \emph{abstention} to an answer and the consequent problem of modelling the incompleteness is a topic we do not consider here for the sake of conciseness.
+Yet, general approaches in the spirit of xxx could be naturally considered.}
+
+A joint PMF over the skills $\bm{S}$ and the questions $\bm{Q}$ is supposed to be available.
+In particular we assume this to correspond to a BN whose graph has the questions as leaf nodes.
+Thus, for each $Q\in\bm{Q}$, $Pa_Q \subseteq \bm{S}$ and we call $Pa_Q$ the \emph{scope} of question $Q$.
+Note that this assumption about the graph is simply reflecting a statement about the conditional independence between (the answer to) a question and all the other skills and questions given scope of the question.
+This basically means that the answers to other questions are not directly affecting the answer to a particular question, and this naturally follows from the exchangeability assumption.\footnote{Moving to other setups would not really be critical because of the property of observed nodes in Bayesian and credal networks, see for instance \cite{antonucci2009} or \cite{debock,bolt}.}
+
+In such a BN framework, ${\tt Stopping}(\bm{e})$ might be naturally based on an evaluation of the posterior PMF $P(\bm{S}|\bm{Q}=\bm{e})$, this being also the case for ${\tt Evaluate}$.
+Regarding the question selection, ${\tt Pick}$ might be similarly based on the (posterior) CPT $P(\bm{S}|Q,\bm{Q}=\bm{e})$, whose values for the different answers to $Q$ might be weighted by the marginal $P(Q|\bm{e})$.
+More specifically, entropies and conditional entropies\footnote{Information gain xxx} are considered by Algorithm \ref{alg:bnta}, while the evaluation is based on a conditional expectation for a given utility function.
+
+*** complete data or information by elicitation, otherwise EM ***
+
+\begin{algorithm}[htp!]
+\begin{algorithmic}[1]
+\STATE $\bm{e}=\emptyset$
+\WHILE{ {\bf not} $H(\bm{X}|\bm{e}) > H^*$}
+\STATE $Q^* \gets \arg\max_{Q \in \bm{Q}} H(\bm{S}|Q,\bm{Q}=\bm{e})$
+\STATE $q^* \gets {\tt{Answer}}(Q^*,\bm{s}_\sigma)$
+\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
+\STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
+\ENDWHILE
+\STATE {\bf return} $\mathbb{E}_{P(\bm{S}|\bm{e})}[f(\bm{S})]$
+\end{algorithmic}
+\caption{Information Theoretic TA in BN over the questions $\bm{Q}$ and the skills $\bm{S}$: given the student profile $\bm{s}_\sigma$, the algorithms returns an evaluation corresponding to the expectation of an evaluation function $f$ with respect to the posterio for the skills given the answers $\bm{e}$.\label{alg:bnta}}
+\end{algorithm}
+
+A CN version of Algorithm \ref{alg:bnta} could be equivalently considered.
+Moving to CN is almost the same, where bounds on the entropies to be considered instead.
+This makes especially critical the evaluation of the bounds of the entropy.
+As entropy is a convec function, upper entropy might be found, while the minimization has been proved to be NP-hard by Klir and fast techniques are only available for specific families of CSs.
+The optimization becomes even more challenging for expected entropies there are roughly mixtures with imprecise weights.
+Accordingly, in \cite{mangili2017b}, only special cases based on an inner approximation have been derived.
+
+\section{Coping with the Mode}\label{sec:mode}
+Following \cite{wilcox1973indices} we can regard the PMF entropy (and its conditional average) as used by Algorithm \ref{alg:bnta}, as a particular example of index of \emph{qualitative variation} (IQV).
+An IQV is just a normalized number that takes value zero for degenerate PMFs, one on uniform ones, being independent on the number of possible states (and samples in case of empirical models).
+The closer to uniform is the PMF the higher is the index and vice versa.
+In order to bypass the computational issues related to its application with CNs and the explainability limits in the general case, we want to consder alternative IQVs to replace entropy in Algorithm \ref{alg:bnta}.
+Wilkox's \emph{deviation from the mode} appears as a natural choice.
+For a given PMF $P(X)$, this corresponds to:
+\begin{equation}DFM_P:=\sum_{x\in\mathcal{X}} \frac{P(x) - \max_{x'\in\mathcal{X}} P(x')}{|\mathcal{X}|}\,.
+\end{equation}
+This might be identified with the \emph{modal} value of the PMF.
+It is a trivial exercise to check that this is a proper IQV, with the same qualitative behaviour of the entropy (e.g., see Figure X).
+From an explainability perspective, compared to entropy, the DFM has a more direct interpretation.
+From the point of view of computation, in both the marginal and the conditional case, both the entropy and the DFM can be trivially obtained for the probabilities of the singletons.
+The situation is different when coping with CSs.
+Entropy require optimization such as those discussed in the previous section, while DFM is simply based on the upper probabilities of the singletons $\{\overline{P}(x)\}_{x\in\mathcal{X}}$.
+
+Consider a PMF $P(X)$. Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$. Let $\mathcal{P}$
+denote the set of all PMFs with the same $p^*:=P(x^*)$. The most entropic PMF in 
+$\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq x^*$ where 
+$m:=|\mathcal{X}|$. While the least entropic is the one with a 
+$x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the other masses 
+equal to zero. These two bounds on the entropy are therefore:
+\begin{eqnarray}
+\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m \frac{1-p^*}{m-1}\,,\\
+\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m (1-p^*)\,.
+\end{eqnarray}
+This:
+\begin{equation}
+\overline{h}-\underline{h}=(1-p^*) \log_m (m-1)\,,
+\end{equation}
+The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as 
+soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being 
+zero for binary variables.
+
+For expected DFM, the situation is more complicated as outlined by the following result.
+
+\begin{theorem}
+Consider a CN with a single skill $S$ and a single question $Q$, that is a child of $S$.
+
+\begin{equation}
+\max_{\substack{P(S)\in K(S)\\P(Q|S)\in K(Q|S)}} \sum_{q\in\mathcal{Q}} \left[ \max_{s\in\mathcal{S}} P(s|q) \right] P(q)
+=\max_{\substack{P(S)\in K(S)\\P(Q|S)\in K(Q|S)}} \sum_q \left[ \max_{s\in\mathcal{S}} P(s)P(q|s) \right] 
+\end{equation}
+Let $\mathcal{S}:=\{s^1,\ldots,s^m\}$ and
+$\mathcal{Q}:=\{q^1,\ldots,q^k\}$.
+Let us make explicit the optimization variables of the task in Equation X as follows. 
+for each $i=1,\ldots,m$, $p_i:=P(S=s^i)$.
+For each $j=1,\ldots,k$, $\pi_{ji}:=P(q^j|s^i)$. Equation X rewrites as:
+\begin{equation}
+\max_{\substack{\{p_i\} \in K(S)\\ ss}} \sum_{j=1,\ldots,k} \max_{i=1,\ldots,m} p_i \pi_{ji} 
+\end{equation}
+We introduce the variables $v_{ij}:=p_i \pi_{ji}$.
+The normalization constraint $\sum_i p_i=1$ becomes $\sum_{ij} v_{ij}=1$, regarding the constraints on $K(S)$, $\underline{P}(s_i) \leq p_i \leq \overline{P}(s_i)$, the becomes:
+$$\underline{P} \pi_{ji} \leq v_{ij} \leq \overline{P} \pi$$
+The objective function can be rewritten as $\sum_{j=1}^q v_{ij}$
+to be considered for each xxx.
+The inner maximization can be achieved 
+\end{theorem}
+
+*** sistemare *** Three possible scores metter probability of true the variation ratio ($1-\max_q(P(q))$) or the M1 Gibb's index 	also known as coefficient of unalikeability and somehow related to the variance (it is 	the variance in the binary case): $M1 = 1-\sum_q P(q)^2$, or even the entropy, which is 	not so difficult to compute for $P(Q)$.
+They are all equivalent in the binary case, as they are all monotonic function of $\max_q(P(q))$ only.
+$\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|$
+*** distinguishing between templates and questions ***
+
+\section{Explainability and Parametrization}
 As a first, demonstrative, example of our ideas consider a model characterized by a single (Boolean) Skill $S$ and a set of questions $\bm{Q}$ picked from a set of templates.
@@
 and $p_0=1-\lambda-\frac{\delta}{2}$. Where constraint $p_1>p_0$ is just $\delta>0$ and any other value in $[0,1]$ for both parameters is valid.
-
 In our toy example, we consider nine possible templates, made of triads of templates with the same $\delta$ and same $\lambda$. The reference values $[0.4,0.5,0.6]$ are used.
 
-\section{Testing Algorithms}
-The typical goal of a test or exam is to evaluate the knowledge level of a student or examinee $\sigma$ on the basis of her answers to a number of questions or exercises.
-Let $\bm{Q}$ denote a repository of questions available to the instructor.
-The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be fixed.
-We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the student and able to decide when the test should stop.
-A standard TA pseudocode is in Algorithm \ref{alg:ta}, where $\bm{e}$ denotes the array of the answers collected from the student $\sigma$.
-
-\begin{algorithm}[H]
-    \SetAlgoLined
-    \KwResult{Write here the result }
-    initialization\;
-    \While{While condition}{
-        instructions\;
-        \eIf{condition}{
-            instructions1\;
-            instructions2\;
-        }{
-            instructions3\;
-        }
-    }
-    \caption{How to write algorithms}
-\end{algorithm}
-
-\begin{algorithm}[htp]
-    \begin{algorithmic}[1]
-    \STATE $\bm{e}=\emptyset$
-        \WHILE{ {\bf not} $\tt{Stopping}(\bm{e})$}
-        \STATE $Q^* \gets \tt{PickQuestion}(\bm{Q},\bm{e})$
-        \STATE $q^* \gets {\tt{Answer}}(Q^*,\sigma)$
-        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-        \STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
-        \ENDWHILE
-        \STATE {\bf return} $\tt{Evaluate}(\bm{e})$
-    \end{algorithmic}\label{alg:ta}
-\caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
-\end{algorithm}
-
-The Boolean function ${\tt Stopping}$ decides whether or not the test should end, this choice being possibly based on the previous answers as collected in $\bm{e}$.
-Trivial examples of such stopping rules might be based on the number of questions asked to the student (${\tt Stopping}(\bm{e})=1$ if and only if $|\bm{e}|>n$) or on the number of correct answers provided that a maximum number of questions is not exceeded.
-Function ${\tt PickQuestion}$ is instead in charge of deciding which question should be asked to the student from the repository $\bm{Q}$.
-A TA is called \emph{adaptive} when this function is based on the previous answers $\bm{e}$.
-Trivial non-adaptive strategies might consist in randomly picking an element of $\bm{Q}$ or following a fixed order.
-Function ${\tt Answer}$ is simply collecting (or simulating) the answer of the student $\sigma$ to a particular question $Q$.
-In our assumptions, this answer is not affected by the previous answers to other questions.\footnote{Generalized setups where the quality of the student answer is affected by the previous answers will be discussed at the end of the paper.
-This might include a \emph{fatigue} model negatively affecting the quality of the answers when many questions have been already answered as well as the presence of \emph{revealing} questions that might improve the quality of other answers.}
-
-Finally, the ${\tt Evaluate}$ function decides the overall judgement for the test (e.g., a numerical grade or a pass/fail Boolean) on the basis of all the answers collected after the test termination.
-Trivial examples of such function are the percentage of correct answers or a Boolean that is true when a sufficient percentage of correct answers has been provided.
-Note also that in our assumptions the TA is \emph{exchangeable}, i.e., the stopping rule, the question finder and the evaluation function are invariant with respect to permutations of $\bm{e}$.
-In other words, the would pick the same next question and the same evaluation for two students who provided the same list of answers in two different orders and similarly would decide to stop or not to stop in the same way.
-
-The typical goal of a TA is to achieve a reliable evaluation of the student $\sigma$.
-As each answer is assumed to improve such quality, asking all the questions, no matter their order because of the exchangeability assumption, would be an obvious choice.
-Yet, asking all the questions in the repository might be impractical (e.g., because of time limitations) in some cases or just provide an unnecessary burden to the students.
-The goal of a good TA is therefore to trade off the accuracy of the evaluation and the number of questions.\footnote{In some generalized setups, other elements such as the \emph{serendipity} to avoid boring sequences of questions might be also considered.}
-
-Item response theory is a popular *** Something about IRT here ***.
-Most of these approaches are based an a unidimensional representation of the student knowledge level.
-Proposals to cope with multidimensional IRTs have been considered, but this results critical when coping with dependencies between them.
-For this reason probabilistic modelling can be considered.
-This is the topic of the next section.
-
-\section{Bayesian Adaptive Testing Algorithms}
-In the setup of algorithm.
-
-Let us introduce the discussion by means of a simple example modelling the knowledge level of a student in a particular domain.
-In order to evaluate such level a number of questions can be asked to the student.
-We describe the knowledge level (or skill) of the student by means of a single variable $S$.
-We assume $S$ to be a discrete, ordinal, variable, whose $m$ states $\mathcal{S}:=(s^{(0)},\ldots,s^{(m-1)})$ can be intended as increasing knowledge levels in that domain.
-Regarding the questions, we initially describe them as Boolean variables, whose true state correspond to a correct answer to the question, while no distinctions between the possible wrong answers are considered.\footnote{Dedicated discussion about abstention.} Let $Q$ with $\mathcal{Q}:=(q,\overline{q})$ denote a generic question we ask to the student.
-A repository of $n$ questions $\bm{Q}$ is assumed to be available.
-A \emph{testing} algorithm is a procedure deciding which question and how many questions from $\bm{Q}$ should be asked to the student, on the basis of her previous answers.
-Algorithm X provides an abstract description of xxx.
-
-	%
-	%
-	\section{Brainstorming}
-
-	\subsection{Linear Programs for Credal Mode}
-
-	Given the Boolean question $Q$ and the Boolean skill $S$, we use the score:
-
-	\begin{equation}
-		\sigma_Q := \max_{P\in K} \bigl[ 
-		\max \{ P(S=0,Q=0) , P(S=1,Q=0) \}  + \max \{ P(S=0,Q=1),P(S=1,Q=1)\}
-		\bigr]
-	\end{equation}
-
-	\begin{theorem}
-		\begin{equation}
-			\max_{x}  \max \{ f(x) , g(x) \}  
-			=
-			\max \{ \max_{x'} f(x') , \max_{x''} g(x'') \} 
-		\end{equation}
-		Let 
-		$$y^{*}:=\max_x \max\{f(x),g(x)\}$$
-		$$y^{**}:= \max \{ \max_{x'} f(x') , \max_{x''} g(x'') \}$$
-		Say for instance that $y^{**}=max_x f(x)$ and let $x^{**}:=\arg\max_x f(x)$. Thus:
-		$$f(x^{**})\geq \max_{x'} g(x) \geq g(x^{**})$$
-
-		Let $x^{*}:= \arg\max_x \max\{f(x),g(x)\}$. 
-		It cannot be $y^{*}:=g(x^{*})$ as this would imply $g(x^{*}) \geq f(x^{*})$
-
-		%Assume ad absurdum $y^{*}\neq y^{**}$.
-
-		If $y^{*}:=f(x^{*})$ we should have $y^{*}=y^{**}$.
-		Vice versa,
-
-		or
-		%$y^{*}:=g(x^{*})$. In the first case 
-	\end{theorem}
-
-	\subsection*{Pseudocode}
-	Let us first specify the inputs:
-	\begin{itemize}
-		\item Let $\bm{S}:=(S_1,\ldots,S_N)$ denote the set of skills in the model. We 
-		describe a \emph{student} as a joint observation $\bm{s}$ of the skills.
-		\item Let $M$ denote the network \emph{skeleton}, i.e., the model over the skills only
-		\item A question $Q$ is a binary variables with states right and wrong
-		\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this 
-		skill
-		\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question 
-		associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
-		\item Let $n_q$ be the maximum number of questions we might ask for each skill
-	\end{itemize}
-	The algorithm works as follows.
-	\begin{enumerate}
-		\item For eachLet $\bm{S}:=(S_1,\ldots,S_N)$ denote the set of skills in the model
-		\item Let $M$ denote the network \emph{skeleton}, i.e., the model over the skills only
-		\item A question $Q$ is a binary variables with states right and wrong
-		\item Each question depends on a single skill only, let $\mathrm{Pa}(Q)$ denote this 
-		skill
-		\item Let $\tau(S)$ denote the number of \emph{templates} for the CPT of a question 
-		associated with $S$, $\{P(Q|S)\}_{t=1}^{\tau(S)}$ 
-		\item Let $n_q$ be the maximum number of questions we might ask for each skill
-	\end{enumerate}
-
-%	\begin{algorithm}[htp!]
-%		\caption{Single skill, precise model\\
-%			a model (BN, skeleton) $M$ over the skills only
-%			\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions 
-%			$\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
-%			the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
-%			the student answer models $\{\tilde{P}(Q^j|S)\}$\\
-%			an entropy threshold $h^*$,\\
-%			a score function for questions $\gamma$
-%			\label{alg:simple}}
-%		\begin{algorithmic}[1]
-%			\FOR {$i\gets\{1,\ldots,n\}$}
-%			\STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
-%			(M,\mathcal{Q},\emptyset,\emptyset)$
-%			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
-%			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(M',Q,\bm{e})$
-%			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
-%			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
-%			\STATE{$q^* \gets \mathrm{sampling} \sim \tilde{P}(Q^*|s^i)$}
-%			\STATE $M' \gets \mathrm{addChild}(M',Q,S,P(Q|S))$
-%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-%			\STATE $h \gets H[P_{M'}(S|\bm{e})]$
-%			\ENDWHILE
-%			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P_{M'}(s|\bm{e})$
-%			\ENDFOR
-%			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
-%		\end{algorithmic}
-%	\end{algorithm}
-	Three possible scores:
-	\begin{eqnarray}
-		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
-		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
-		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
-	\end{eqnarray}
-
-	\textcolor{red}{Maybe, instead of (3) I would use a known measure of qualitative 
-	variation (\url{https://en.wikipedia.org/wiki/Qualitative_variation}) which extend easily to 
-	non binary answers, e.g., the variation ratio ($1-\max_q(P(q))$) or the M1 Gibb's index 
-	also known as coefficient of unalikeability and somehow related to the variance (it is 
-	the variance in the binary case): $M1 = 1-\sum_q P(q)^2$, or even the entropy, which is 
-	not so difficult to compute for $P(Q)$. They are all equivalent in the binary case, as 
-	they are all monotonic function of $\max_q(P(q))$ only. }
-
-%	\begin{algorithm}[htp!]
-%		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
-%		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
-%			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
-%			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
-%			an upper entropy threshold $\overline{h}^*$,\\
-%			a score function for questions $\sigma$
-%			\label{alg:simple2}}
-%		\begin{algorithmic}[1]
-%			\FOR {$i\gets\{1,\ldots,n\}$}
-%			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
-%			(\mathcal{Q},\emptyset,\emptyset)$
-%			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
-%			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
-%			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
-%			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
-%			\STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
-%			\STATE $\mathrm{addChild}(Q,S,P(Q|S))$
-%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-%			\STATE $h \gets H[P(S|\bm{e})]$
-%			\ENDWHILE
-%			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
-%			\ENDFOR
-%			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
-%		\end{algorithmic}
-%	\end{algorithm}
-	Three possible scores:
-	\begin{eqnarray}
-		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
-		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
-		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
-	\end{eqnarray}
-
-%	\begin{algorithm}[htp!]
-%		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
-%		\begin{algorithmic}[1]
-%			\FOR {$s\in\bm{S}$}
-%			\WHILE{ $h > h^*$}
-%			\STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
-%			\STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
-%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
-%			\STATE $h \gets H[P(S|\bm{e}]$
-%			\ENDWHILE
-%			\ENDFOR
-%			\STATE {\bf return} $\arg\max P(s|\bm{e})$
-%		\end{algorithmic}
-%	\end{algorithm}
-
-	\subsection*{Formulae}
-	Let us define the functions, all defined for $x\in [0,1]$, apart from $f$ defines for each 
-	$x\geq 0$:
-	\begin{eqnarray}
-		f(x)&:=& \frac{1}{1+x},\,,\\
-		h(x)&:=&-x \cdot \log_2 x - (1-x)  \cdot \log_2 (1-x)\,,\\
-		l(x)&:=&\frac{x}{1-x}\,,\\
-		m(x)&:=&2 \max\{x,1-x\}\,,\\
-		i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
-		\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
-	\end{eqnarray}
-
-	Derivatives:
-	\begin{eqnarray}
-		f'(x)&:=& -\frac{1}{(1+x)^2},\,,\\
-		h'(x)&:=&\log_2 \frac{1-x}{x}\,\\
-		G(x) &:=& h \circ f(x)\,\\
-		G'(x) &:=& h[f(x)] f'(x)=-\frac{\log_2\frac{1-f(x)}{f(x)}}{(1+x)^2}\,\\
-		G'(x) &:=& -\frac{\log_2 x}{(1+x)^2}\,\\
-		l(x)&:=&\frac{x}{1-x}\,,\\
-		m(x)&:=&2 \max\{x,1-x\}\,,\\
-		i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
-		\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
-	\end{eqnarray}
-
-	A few remarks. Function $f$ is a monotonically decreasing function with values in 
-	$[0,1]$. Function $h(x)$ corresponds to the entropy of a mass function over a Boolean 
-	variable with a probability equal to $x$. On the extreme points of its domain, we take 
-	the limit value, i.e., zero. The function is unimodal and achieve its maximum on  
-	$x=\frac{1}{2}$. Function $l$ is the popular \emph{logit} function, it is monotonically 
-	increasing function of $x$ and $l(1-x)=l(x)^-1$. Function $m(x)$ is $x$ for $x\geq 
-	\frac{1}{2}$ and $1-x$ otherwise. 
-	Exactly as $h$, functions $m$ and $\tilde{i}_\epsilon$, for each $\epsilon>0$, have the 
-	same (zero) value for $x=0$ and $x=1$, being all unimodal with maximum in 
-	$x=\frac{1}{2}$.
-	Finally, the popular Gumbel's trick implies:
-	\begin{equation}
-		\lim_{\epsilon \to 0} i_\epsilon(x)= 
-		\lim_{\epsilon \to 0} \tilde{i}_\epsilon(x)
-		= m(x)\,.
-	\end{equation}
-	\subsection*{Another Formula}
-	Consider a PMF $P(X)$. Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$. Let $\mathcal{P}$ 
-	denote the set of all PMFs with the same $p^*:=P(x^*)$. The most entropic PMF in 
-	$\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq x^*$ where 
-	$m:=|\mathcal{X}|$. While the least entropic is the one with a 
-	$x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the other masses 
-	equal to zero. These two bounds on the entropy are therefore:
-	\begin{eqnarray}
-		\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m \frac{1-p^*}{m-1}\,,\\
-		\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m (1-p^*)\,.
-	\end{eqnarray}
-	This:
-	\begin{equation}
-		\overline{h}-\underline{h}=(1-p^*) \log_m (m-1)\,,
-	\end{equation}
-	The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as 
-	soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being 
-	zero for binary variables.
-
-	\subsection*{Toy Example}
-	Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean 
-	question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is 
-	specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified 
-	instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The 
-	informativeness score we assign two the question is
-	\begin{equation}
-		\sigma_Q = H[S|Q]:=H[S|q_0]P(q_0)+H[S|q_1]P(q_1)\,.
-	\end{equation}
-	We have
-	\begin{equation}
-		P(q_1)=\pi_1 p + \pi_0 (1-p)
-	\end{equation}
-	while $P(q_0)=1-P(q_1)$ and also
-	\begin{equation}
-		P(s_1|q_1)=\frac{\pi_1 p}{\pi_1 p + \pi_0 (1-p)}=\frac{1}{1+\frac{\pi_0(1-p)}{\pi_1 p}}
-	\end{equation}
-	and
-	\begin{equation}
-		P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ 
-		(1-p)(1-\pi_0)}{p (1-\pi_1)}} 
-	\end{equation}
-	while $P(S=0|Q=1)$ by normalization. Accordingly:
-%	\begin{multline}
-%		\sigma_Q(p,\pi_0,\pi_1)=\\
-%		h \circ f[\gamma/l(p)] \cdot t +
-%		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
-%		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
-%		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
-%	\end{multline}
-	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
-	p + \pi_0 (1-p)$.
-
-	{\color{blue}{In other words:
-			$\sigma_Q(p,\pi_0,\pi_1):= G(\frac{1-p}{p} \frac{1-\pi_0}{1-\pi_1}) (1-p) + 
-			G(\frac{1-p}{p} \frac{\pi_0}{\pi_1}) p$}}
-
-	An alternative score might be achieved by replacing $h$ with $m$, i.e.,
-	\begin{equation}
-		\sigma_Q' := 
-		m \circ f[\gamma/l(p)] \cdot t +
-		m \circ f[\gamma'/l(p)] \cdot (1-t)\,
-	\end{equation}
-	As $f$ is monotone, we can commute $m$ and $f$ *** explain ***, i.e.,
-	\begin{equation}
-		\sigma_Q' := 
-		f \circ m[\gamma/l(p)] \cdot t +
-		f \circ m[\gamma'/l(p)] \cdot (1-t)\,
-	\end{equation}
-	with, as $\gamma>0$. $f \circ m[\gamma/l(p)] = f[\gamma m(l(p))]$
-	We can similarly define another score $\sigma_Q''$ based on $\tilde{i}_\epsilon$.
-	\subsection*{Explicit maximization}
-	$$H[S|Q]\simeq \sigma_Q' = \sum_q P(s^*(q)|q) P(q)$$
-	where $s^*(q):=\arg\max_s P(s|q)$. 
-	$$\sigma_Q'= \sum_q P(s^*(q),q) = \sum_q P(s^*(q) P(q|s^*(q))$$
-	Note that, if $s^*(q)$ is the same for each $q$, the score just corresponds to $P(s^*)$. 
-	In other words, the score is flat is each answer gives the same most likely skill level *** 
-	reasonable ***. Let us move to an imprecise setting and intend the $s^*$ state as
-	$s^*(q):=\arg\max_s \overline{P}(s|q)$. The objective function is a linear combination of 
-	$P(s*(q)$ whose coefficient can be optimized independently. Overall, this corresponds 
-	to a linear programming task.
-	$$\max_s \overline{P}(s,q) = \max_s \max_P P(s) P(q|s) = \max_s \overline{P}(s) 
-	\overline{P}(q|s)$$
-
-	\subsection*{Francesca's comments}
-
-	Comment1: This sentence is not clear to me:  "as $\gamma>0$. $f \circ m[\gamma/l(p)] 
-	= f[\gamma m(l(p))]$".\\
-	Comment2: How shall we use the Gumbel's trick
-
-	Comment 3: Below I obtain something that looks different to me, but maybe it is 
-	equivalent.
-
-	\begin{equation}
-		P(s_1|q_1)=\frac{\pi_1 p}{P(q_1)}
-	\end{equation}
-
-%	\begin{multline}
-%		\sigma_Q(p,\pi_0,\pi_1)=\\
-%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
-%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
-%	\end{multline}
-
-	But, as $P(q_1)\geq 0$, then
-%	\begin{multline}
-%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
-%		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
-%		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
-%		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
-%	\end{multline}
-
-	Similarly, as $1-P(q_1)\geq 0$, 
-%	\begin{multline}
-%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
-%		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
-%	\end{multline}
-
-	so that,
-
-%	\begin{multline}
-%		\sigma_Q(p,\pi_0,\pi_1)= \\
-%		2 max\{\pi_1 p, \pi_0 (1-p)\}+
-%		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
-%	\end{multline}
-
-	Comment 4: The optimisation in the credal setting shouldn't be the following one?
-
-	$$\max_P [\max_s P(s,q=0)+\max_s P(s,q=1)]$$
-
-	$\P(s,q=0)$ and $P(s,q=1)$ are both functions of $p, \pi_0,$ and $\pi_1$ so I do not 
-	think we can split the optimization
-
-	$$\max_P \max_s P(s,q=0)+\max_P\max_s P(s,q=1)$$
-
-	However, it could be a reasonable approximation. Then, we can switch the optimization 
-	over $P$ and $s$ because they are both max, and obtain: 
-	$$\max_s \overline{P}(s)\overline{P}(q=0|s)+\max_s  \overline{P}(s)\overline{P}(q=1|s)$$.
-
-	If instead we are looking for the minimum over P, we cannot switch the optimization 
-	over $P$ and $s$:
-	$$\min_P \max_s P(s,q) \neq \max_s \min_P P(s,q)$$.
-
-	However I think we can split the optimization into 4 quadratic optimizations.
-	Let's use the following parametrization:
-%	\begin{multline}\label{eq:minimization}
-%		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
-%		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-%		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
-%		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-%		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
-%	\end{multline}
-
-	Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It 
-	can be written as
-	$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
-	where
-
-%	\begin{multline}
-%		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
-%		\begin{array}{ll}
-%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
-%			~&\underline{x} \leq x\leq \overline{x}\\ 
-%		\end{array}
-%	\end{multline}
-	and 
-%	\begin{multline}
-%		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
-%		\begin{array}{ll}
-%			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
-%			~&\underline{x} \leq x\leq \overline{x}\\ 
-%		\end{array}
-%	\end{multline}
-
-	where the constraint $x = (\pi_0, \pi_1 ,p)$.
-
-	In general, let $N_s$ be the number of skill levels and $N_q$ the number of possible 
-	answers, then the number of quadratic optimizations to solve should be equal to 
-	$N_s\cdot N_q$.
-
-	In this two dimensional example, we might not need the approximation above as the 
-	minimization in \ref{eq:minimization} can be written as $\min_{i=1:4}(\tilde{P}_1)$, where
-
-%	\begin{multline}
-%		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
-%		\begin{array}{ll}
-%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
-%			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
-%			~&\underline{x} \leq x\leq \overline{x}\\ 
-%		\end{array}
-%	\end{multline}
-	and so on. However, in this case, the number of optimizations to solve should be 
-	$N_s^{N_q}$, that is, it grows exponentially with  $N_q$.
-
-	\paragraph{*** Alessandro's reformulation ***}
-%	\begin{equation}
-%		\begin{split}
-%			\text{min} \displaystyle \, \pi_1 \cdot p \\
-%			\text{subject to} & \displaystyle \pi_1 p > \pi_0 (1-p)\\
-%			&\displaystyle \underline{\pi}_0 \leq \pi_0 \leq \overline{\pi}_0 \\
-%			&\displaystyle \underline{\pi}_1 \leq \pi_1 \leq \overline{\pi}_1 \\
-%%		\end{split}
-%	\end{equation}
-	with the new variable specification:
-	\begin{eqnarray}
-		x_1&:=&\pi_1 \cdot p \,,\\
-		x_2&:=&\pi_0 \cdot p \,,\\
-		x_3&:=&(1-\pi_1) \cdot p \,,\\
-		x_4&:=& \pi_0 \cdot (1-p)\,.\\
-	\end{eqnarray}
-	the problem becomes:
-%	\begin{equation}
-%		\begin{split}
-%			\text{min} \displaystyle \, x_1 \\
-%			\text{subject to\phantom{xx}} & \displaystyle x_1 > x_4\\
-%			&\displaystyle \underline{\pi}_0 \leq x_2+x_3 \leq \overline{\pi}_0 \\
-%			&\displaystyle \underline{\pi}_1 \leq x_1+x_4 \leq \overline{\pi}_1 \\
-%			&\displaystyle \underline{p} \leq x_1+x_3 \leq \overline{p} \\
-%		\end{split}
-%	\end{equation}
-
-	\section{Introduction}\label{sec:intro}
-	The use of communication and information technologies in education is actually 
-	growing. Both online (e.g., MOOCs) and classroom courses are urgently asking for 
-	more flexible and sophisticated e-learning and e-testing tools 
-	\cite{pollard2001exploring}. AI-based approaches such as intelligent tutoring systems, 
-	adapting the interaction with the student on the basis of his/her knowledge and/or 
-	psychological profile, represent an important direction to improve the quality of the 
-	(e-)learning experience \cite{burns2014intelligent}.
-
-	Bayesian networks (BNs) \cite{koller2009} have been used to model the knowledge 
-	driving such intelligent systems \cite{almond2015bayesian}. However, collecting large 
-	sets of reliable data in educational domains may be difficult and time consuming (e.g., a 
-	course with few students, or taught for the first time), and the quantification should be 
-	based on expert knowledge only. To elicit a Bayesian network, an expert might face 
-	questions like: ``\emph{which is the probability of a student with a particular 
-	knowledge level giving the right answer to a question?}''. Giving sharp probabilities for 
-	questions of this kind can be problematic for an expert, whose knowledge is mostly 
-	qualitative (e.g., ``\emph{a right answer is very unlikely}''). Fuzzy linguistic approaches 
-	represent a viable, non-numerical, way to address these issues 
-	\cite{badaracco2013fuzzy}. To stick within the probabilistic framework, 
-	verbal-numerical probability scales associated with sharp values 
-	\cite{renooij1999talking} or intervals \cite{walley1991statistical} have been also 
-	proposed.
-
-	In this paper we show how to conjugate an interval-valued probabilistic elicitation of 
-	expert knowledge with the BN framework. This means to cope with a \emph{credal 
-	network} (CN) \cite{novapiatti}, a generalization of BNs based on the imprecise 
-	probability theory \cite{walley1991statistical}, where local parameters are defined by 
-	set-valued probabilities. This simplifies the elicitation process and offers a more reliable 
-	handling of the related uncertainty. Moving from BNs to CNs implies two main issues: 
-	(i) numerical inferences will be interval-valued too, thus making debatable both the 
-	decision criterion \cite{troffaes} an the information measures \cite{klir1999uncertainty} 
-	to adopt; and (ii) inference tasks in CNs typically belongs to higher complexity classes 
-	than their Bayesian counterparts \cite{maua14jair}. Both these issues are addressed by 
-	defining a computationally feasible procedure based on CNs to be used for practical 
-	implementation of intelligent systems solely specified by expert knowledge. To the best 
-	of our knowledge this is the first attempt to perform e-testing with models of this kind.
-
-	We focus on the application of CNs to \emph{computer adaptive testing} (CAT), i.e., an 
-	approach to e-testing that adjusts the sequence and the number of questions to the 
-	ability level of the test taker. CATs have the potential to make the test an individualised 
-	experience that challenges and does not discourage the test takers, as most of the 
-	questions are near their ability levels. Building upon \emph{item response theory} 
-	\cite{hambleton1985item}, the common background underpinning CATs, graphical 
-	modeling (such as BNs and CNs) offers a powerful language for describing complex 
-	multivariate dependencies between skills and rich tasks. Several researchers have 
-	exploited the potential of BNs both in adaptive and non-adaptive educational 
-	assessment \cite{vomlel2004building,plajner2015}. These authors focus on applications 
-	for which data are available to learn the model parameters. We regard this point as a 
-	serious limitation, possibly hindering CATs adoption by many teachers and instructors.
-
-	We start from a CAT procedure based on BNs that uses \emph{entropy} as the 
-	information-theoretic measure driving the question selection and the stopping criteria 
-	(Sect.~\ref{sec:bayesianCAT}). Our goal is to improve  this procedure by using CNs to 
-	better describe the pervasive uncertainty characterizing the model. A direct extension 
-	of the Bayesian framework to CNs would require the computation of bounds for the 
-	conditional entropy with respect to the CN specification. This corresponds to a 
-	non-linear non-convex optimization task. We therefore propose a number of 
-	simplifying assumptions to overcome this problem at the price of accepting 
-	sub-optimal question selection schemes (Sect.~\ref{sec:credalCAT}). The approach is 
-	tested on a real-world benchmark about German language proficiency assessment 
-	(Sect.~\ref{sec:conc}). The results are promising: CAT based on CNs is effective in 
-	reducing the number of questions while maintaining a high accuracy in the evaluation 
-	and the approximations introduced do not compromise the procedure's effectiveness.
-
-	\section{Bayesian CAT}
-
-	\paragraph{Skills modeling.} We describe the knowledge level of a student as a 
-	collection of categorical variables, say $\bm{X}:=(X_1,\ldots,X_n)$, called \emph{skills}. 
-	A joint \emph{probability mass function} (PMF) $P(\bm{X})$ describes the uncertainty 
-	about the actual values of the skills. A compact specification of such multivariate model 
-	can be achieved by a BN \cite{koller2009}. This corresponds to: (i) a directed acyclic 
-	graph whose nodes are in one-to-one correspondence with the variables of $\bm{X}$; 
-	and (ii), for each $X_i\in\bm{X}$, 
-	a collection of conditional PMFs $P(X_i|\mathrm{\pi}_{X_i})$, one for each value 
-	$\pi_{X_i}$ of the joint variable $\mathrm{\Pi}_{X_i}$ denoting the \emph{parents} (i.e., 
-	the immediate predecessors) of $X_i$. The \emph{Markov condition} for BNs assumes 
-	every variable conditionally independent of its non-descendants non-parents given the 
-	parents. Accordingly, the joint PMF associated with a BN is such that $P(\bm{x}):= 
-	\prod_{i=1}^n P(x_i|\pi_{X_i})$, for each $\bm{x}$, where the values of $x_i$ and 
-	$\pi_{X_i}$ are those consistent with $\bm{x}$.
-
-	\paragraph{Questions modeling.} The above joint probabilistic model describes the 
-	uncertainty about the skills of a student prior to his/her answers to the questions. To 
-	evaluate the student we formulate a number of \emph{questions}, described as a 
-	collection of variables $\bm{Y}:=(Y_1,\ldots,Y_m)$. We assume these variables to be 
-	Boolean, with the true value corresponding to the correct answer.\footnote{Extension 
-	to non Boolean answers is trivial as all answers $Y_i$ are \emph{manifest} variables, 
-	and, thus, $Y_i$ can be always regarded as a binary variable with the two values 
-	denoting the observed answer $y_i$ and its negation \cite{antonucci2009}.} We call 
-	\emph{background} of a question the set of skills ``required'' to answer it. This can be 
-	regarded as a conditional independence statement: given the background skills, the 
-	answer to the question is independent of the other skills and of the other questions. 
-	Following the Markov condition, this can be modeled by representing each question as 
-	a leaf node whose parents are the background skills. Such augmented graph requires 
-	the quantification, for each $Y_j\in\bm{Y}$, of a conditional PMF 
-	$P(Y_j|\mathrm{\pi}_{Y_j})$ for each value $\mathrm{\pi}_{Y_j}$ of the background skills 
-	$\mathrm{\Pi}_{Y_j}$. This procedure defines a BN over the skills and the questions, 
-	and hence a joint PMF $P(\bm{X},\bm{Y})$.
-
-	\paragraph{Non-adaptive testing.} Let $\bm{Y}=\bm{y}$ denote a student's answers 
-	to the test. In the above considered framework, the posterior knowledge about the 
-	skills is modeled by the joint PMF $P(\bm{X}|\bm{y})$. By running standard BN updating 
-	algorithms, the most probable level $\tilde{x}_i$ of skill $X_i$ can be therefore 
-	evaluated  as $\tilde{x}_i:= \arg\max_{x_i} P(x_i|\bm{y})$, for each $X_i\in\bm{X}$. This 
-	reflects a non-adaptive, probabilistic approach to student evaluation.
-
-	\paragraph{Adaptive testing.} To add adaptiveness to the above approach, every 
-	question should be chosen on the basis of the previous answers. As the goal is to 
-	gather information about the student skills, we evaluate the expected 
-	\emph{information gain} (IG, i.e., the change in information entropy) associated with 
-	each possible new question, and pick the one maximizing this measure. The entropy of 
-	a BN over $\bm{X}$ can be computed as $H(\bm{X}):=\sum_{i=1}^n 
-	H(X_i|\mathrm{\Pi_{X_i}})$ \cite{koller2009}, where 
-	$H(X_i|\mathrm{\Pi_{X_i}}):=\sum_{\pi_{X_i}} H(X_i|\pi_{X_i}) P(\pi_{X_i})$ is the 
-	\emph{conditional entropy} for $X$ given its parents and $H(X_i|\pi_{X_i})$ is the 
-	entropy of the conditional PMF $P(X_i|\pi_{X_i})$.\footnote{To have entropy levels 
-	between zero and one, we define the entropy of the PMF $P(X)$ as $H(X):=-\sum_x 
-	P(x) \log_b P(x)$, with $b$ number of states of $X$.} Let $\bm{Y}=\bm{y}$ denote the 
-	answers to the questions already asked and $\bm{Y}'$ the set from which the next 
-	question should be picked. If the answer to every question $Y'\in\bm{Y}'$ would be 
-	known, and denoted by $y'$, the question $\tilde{Y}' \in \bf{\mathbf{Y}'}$ to choose 
-	would be the one leading to the largest IG. Yet, as the decision has to be made before 
-	the student's answer, conditional entropy should be considered instead, i.e.,
-	\begin{equation}
-		\tilde{Y}' := \arg \max_{Y'\in \bm{Y}'} 
-		\bigl[H(\bm{X}|\bm{y})-H(\bm{X}|Y',\bm{y})\bigr]\,. 
-		\label{eq:expent}
-	\end{equation}
-
-%	\begin{figure*}[htp!]
-%		\centering
-%		\begin{tikzpicture}[auto,scale=.7]
-%			\node[node distance=.cm,fill=black!10] (pick) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
-%			\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
-%			\node[right of=pick,node distance=3cm,fill=black!10] (ask) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
-%			\node[right of=ask,node distance=3cm,fill=black!10] (collect) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
-%			\node[below of=collect,node distance=1.4cm] (decide) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? 
-%%			}\end{varwidth}};
-%			\node[ left of=decide, node distance=3cm,fill=black!10] (stop) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
-%			\node[left of=stop, node distance=3cm,fill=black!10] (assign) 
-%%			{\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
-%			\draw[] (decide) -- node {\tiny YES}(stop);
-%			\draw[] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
-%			\draw[dashed] (db) -- (pick);
-%			\draw[] (pick) -- (ask);
-%			\draw[] (ask) -- (collect);
-%			\draw[] (collect) -- (decide);
-%			\draw[] (decide) -- (stop);
-%			\draw[] (stop) -- (assign);
-%		\end{tikzpicture}
-%		\caption{CAT procedure}
-%		\label{fig:alg}
-%		%\vspace{-1cm}
-%	\end{figure*}
-
-CATs should also decide when to stop asking questions. Again, entropy can be used as 
-a measure to decide when the current evaluation is sufficiently informative, i.e., we stop 
-the test if the skills entropy given the answers is below some threshold $\tilde{H}$. The 
-overall approach is depicted in Fig.~\ref{fig:alg}.
-
-	\section{Credal CAT}
-
-	\paragraph{Credal sets and credal networks.} A set of PMFs over $X_i$ is called here 
-	\emph{credal set} (CS) and denoted as $K(X_i)$. We always remove the inner points 
-	(i.e., those corresponding to convex combinations of the others) of a CS. CNs 
-	\cite{cozman2000} are generalized BNs whose local PMFs are replaced by CSs.  The BN 
-	defined in the previous section over the skills $\bm{X}$ and the questions $\bm{Y}$ 
-	becomes a CN if we replace with CSs the skill-to-skill and skill-to-question conditional 
-	PMFs. A joint CS $K(\bm{X},\bm{Y})$ is consequently obtained as the collection of all 
-	the joint PMFs induced by BNs whose parameters take their values from the 
-	corresponding CSs, i.e., 
-	\begin{equation}\label{eq:strongext}
-		K(\bm{X},\bm{Y}):=\bigl\{ P(\bm{X},\bm{Y}) \bigl| 
-		\substack{
-			P(\bm{x},\bm{y}):=\prod_{i=1}^n P(x_i|\pi_{X_i}) \cdot \prod_{j=1}^m P(y_j|\pi_{Y_j}), 
-			\\P(X_i|\pi_{X_i}) \in K(X_i|\pi_{X_i}) ,\, P(Y_j|\pi_{Y_j}) \in K(Y_j|\pi_{Y_j})}
-		\bigr.
-		\bigr\}\,,
-	\end{equation}
-	where the values of $x_i$, $\pi_{X_i}$, $y_j$, $\pi_{Y_j}$ are those consistent with 
-	$\bm{x}$ and $\bm{y}$.
-
-	\paragraph{Expert knowledge modeling.} For a reliable expert knowledge modeling, 
-	we use CSs induced by \emph{probability intervals}. Qualitative judgments about the 
-	probability of a state are converted in interval constraints such as $l\leq P(x) \leq u$, 
-	with the interval $[l,u]$ capturing the expert knowledge behind the judgment in a more 
-	reliable way than a sharp assessment. The CS consistent with these constraints is 
-	eventually obtained by standard polyhedral algorithms. Verbal to interval-numeric 
-	scales such as that Tab.~\ref{tb:labels} are used. For instance, if for the probability of 
-	the true state of the Boolean variable $Y$ the expert judgment is ``very likely'', the 
-	corresponding linear constraint is $.2 \leq P(Y=\textrm{true}) \leq .4$.% and we obtain a 
-	%CS $K(Y)$ with the PMFs $P_1(Y)=[.2,.8]$ and $P_2(Y)=[.4,.6]$ as non-inner points.
-
-	\paragraph{Non-adaptive testing.} Given the answers $\bm{y}$ to the questions 
-	$\bm{Y}$, we evaluate the student as in the previous section by updating the marginal 
-	probabilities of each skill. With CNs, these posterior values are set-valued and their 
-	characterization can be provided by lower and upper bounds, say 
-	$\underline{P}(X_i|\bm{y})$ and $\overline{P}(X_i|\bm{y})$ for each $X_i\in\bm{X}$. CN 
-	updating algorithms can eventually compute these bounds. The task displays higher 
-	complexity than in the case of BNs (e.g., exact inference in non-binary 
-	singly-connected CNs is NP-hard \cite{maua14jair}), but approximate techniques can be 
-	considered when exact inference is unfeasible \cite{antonucci2014e}.
-
-	To compare the posterior intervals and decide the actual level of the student we might 
-	adopt the (conservative) \emph{interval dominance} criterion \cite{troffaes}, which 
-	rejects a level if its upper probability is smaller than the lower probability of some other 
-	level. Overlaps between intervals might therefore induce a situation of 
-	\emph{indecision} between two or more levels. This is a so-called \emph{credal} 
-	classification of the student level \cite{zaffalon2012evaluating}, and it represents the 
-	fact that students answers are somehow contradictory or not informative enough to 
-	provide a sharp decision. Interval dominance can return unnecessarily imprecise results. 
-	\emph{Maximality} is a more refined criterion that rejects the levels which are less 
-	probable than another level for all the elements of the CS \cite{walley1991statistical}. 
-	Maximality  can be reduced to multiple updating tasks on auxiliary binary leaf nodes 
-	defined for each pair of states \cite{antonucci2014e}.
-
-	\paragraph{Adaptive testing.}
-	To achieve CAT with CNs using entropy as measure of informativeness for PMFs, as in 
-	the BN approach of Sect. \ref{sec:bayesianCAT}, computation of entropies should be 
-	extended to CSs. This topic has been the subject of much discussion 
-	\cite{klir1999uncertainty}. A cautious approach \cite{abellan2003maximum} consists in 
-	taking the upper entropy $\overline{H}(\bm{X})$, i.e., the entropy of the most entropic 
-	PMF in the convex closure $\overline{K}(\bm{X})$ of  $K(\bm{X})$. 
-	In our framework, we should, then, look for maximum values of conditional entropies, 
-	such as $\overline{H}(X_i|Y',\bm{y})$ or $\overline{H}(X_i|\Pi_{X_i})$, as conditional 
-	entropies are required to compute both: (i) the joint (unconditional) entropy 
-	$H(\bm{X})$ (and its posterior values); and (ii) the conditional entropies  involved in 
-	the  question selection in Eq.~\eqref{eq:expent}.
-	By definition a conditional entropy is a convex combination (whose weights are the 
-	elements of a marginal PMF) of convex functions (the entropies). The objective 
-	function might, then, be non-convex, as the weights are also optimization 
-	variables.\footnote{E.g., if $f(x)$ and $g(x)$ are convex functions of $x$, $h(x,y):= y 
-	f(x) + (1-y) g(x)$ is not convex even for $0 \leq y \leq 1$.}
-
-	Then, to bypass this non-convex optimization task, we compute (i) by separately 
-	considering the entropies of each skill $X_i\in\bm{X}$. This is analogous to the marginal 
-	approach commonly considered in multi-label classification to minimize Hamming losses 
-	\cite{antonucci2016c}. The issue (ii) is more challenging. We consider the following 
-	upper approximation of $\overline{H}(X_i|Y',\bm{y})$:
-	\begin{equation}
-		\overline{\overline{H}}(X_i|Y',\bm{y})=
-		\max_{P(y'|\bm{y})\in
-			\{\underline{P}(y'|\bm{y}),\overline{P}(y'|\bm{y})\}}
-		\sum_{y' \in \{\textrm{true},\textrm{false}\}}
-		\overline{H}(X_i|\bm{y},y') P(y'|\bm{y})\,,
-	\end{equation}
-	where the bounds of $P(y'|\bm{y})$ are obtained by standard CN updating algorithms.
-	The problem thus reduces to the computation of upper entropies as
-	\begin{equation}\label{eq:entropy}
-		\overline{H}(X_i|\bm{y}) := \sup_{P(X_i|\bm{y}) \in \overline{K}(X_i|\bm{y})} 
-		H(X_i|\bm{y})\,,
-	\end{equation}
-	where  $\overline{K}(X_i|\bm{y})$ is the posterior CS after conditioning on the observed 
-	answers $\bm{y}$.  If $\overline{K}(X_i|\bm{y})$ has a finite number of non-inner 
-	points, this is a linearly-constrained convex optimization whose solution typically 
-	corresponds to either the uniform PMF or a non-inner point on the frontier of 
-	$\overline{K}(X_i|\bm{y})$. A numerical solution can be easily found by a simple iterative 
-	approach in the special case of CS specified by probability intervals 
-	\cite{abellan2003maximum}. We have therefore computed the posterior lower and 
-	upper bounds of $P(X_i|\bm{y})$, and then maximized the entropy with respect to 
-	those bounds. % as in Eq.~\eqref{eq:entropy}. 
-	The procedure induces an outer approximation of $\overline{K}(X_i|\bm{y})$, and hence 
-	the upper approximation  of the maximum entropy 
-	$\overline{\overline{H}}(X|\bm{y})\geq\overline{H}(X|\bm{y})$. 
-	%With a small notation abuse such approximate value is also denoted as 
-	%$\overline{H}(X|\bm{y})$ and is regarded here as a measure of the informativeness 
-	%level 
-	%achieved for skill $X$ after the answers $\bm{y}$. 
-	Finally, to generalise Eq.~\ref{eq:strongext} to CNs, we define the information gain 
-	provided by a question $Y'$ for its background skill $X_{Y'}$ as 
-	$\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y})$ and 
-	select the question $\tilde{Y}'$ leading to the maximum information gain, i.e.,
-	\begin{equation}\label{eq:credalentropy}
-		\tilde{Y}' := \arg \max_{Y'\in\bm{Y}'} 
-		\bigl[
-		\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y}) 
-		\bigr]
-		\,.
-	\end{equation}
-	For the stopping criterion, as we do not consider the joint entropy over the skills, we 
-	separately require each $\overline{\overline{H}}(X_i|\bm{y})$ to be smaller than a 
-	threshold $\tilde{H}$. To be consistent with this choice, we remove from the set of 
-	questions to be selected, those whose background skills already satisfy this condition.
-
-	Note that the use of an outer approximation of the upper entropy affects only the 
-	question selection process (eventually making it sub-optimal), whereas it has no effect 
-	on the student evaluation given a set of answers.
-
-	\section{Application}
-	Before the academic year begins, the students of the University of Applied Sciences 
-	and Arts of Southern Switzerland (SUPSI) are asked to take an online German language 
-	placement test with 95 questions. In years 2015 and 2016, the answers of 451 students 
-	to all the questions have been collected. This benchmark is used to simulate CATs 
-	based on BNs and CNs as described in Sects.~\ref{sec:bayesianCAT} and 
-	\ref{sec:credalCAT}.
-%\end{document}
+\section{Experiments}\label{sec:exp}
+In this section we validate.
+\subsection{Single-Skill Experiments on Synthetic Data}
+For a very first validation of our approach, we consider a simple setup made of a single skill $S$ and nine different templates for the questions.
+The values in the two parameters are xxx in Table X.
+In the Bayesian case we set $P(S=1)=.5$.
+The credal model is obtained by a simple contamination with xxx.
+Two questions for each one of the nine templates are xxx.
+As stopping rule a threshold on the entropy is set.
+
+\begin{figure}[htp!]
+\centering
+\input{acc.tex}
+\hspace{0.9cm}
+\caption{Aggregated cumulative costs and bounds.}
+\label{fig:sx2}
+\end{figure}
+
+\begin{figure}[htp!]
+\centering
+\input{brier.tex}
+\caption{Aggregated cumulative costs and bounds.}
+\label{fig:sx}
+\end{figure}
+
+\subsection{Multi-Skill Experiments on Real Data}
+For a validation on real data, we consider data xxx.
+Before the academic year begins, the students of the University of Applied Sciences and Arts of Southern Switzerland (SUPSI) are asked to take an online German language placement test with 95 questions.
+In years 2015 and 2016, the answers of 451 students to all the questions have been collected.
 
@@
 Four skills are assessed: \textit{W\"ortschatz} ($X_1$, vocabulary), 
-	\textit{Kommunikation} ($X_2$, communication), \textit{H\"oren} ($X_3$, listening), and 
-	\textit{Lesen} ($X_4$, reading). For each skill the student is assigned to a knowledge 
+\textit{Kommunikation} ($X_2$, communication), \textit{H\"oren} ($X_3$, listening), and \textit{Lesen} ($X_4$, reading). For each skill the student is assigned to a knowledge 
 	level compliant with EU 
@@
 
-	%Different decision criteria for the assignment of the skill level, e.g., maximality or 
-	%e-admissibility, should be considered.
-	%As a consequence, although BNs achieve better performance when considering the 
-	%discounted accuracy, CN tests should be preferred whenever the utility is better 
-	%described by the U65 or U80 measures, that is, whenever being undecided between 
-	%more level should be preferred than assigning one of them at random. 
-	%As the true level of the students is unknown, this measure should be regarded as the 
-	%agreement between to different evaluation strategies. 
-	%\begin{mdframed}[hidealllines=true,backgroundcolor=blue!20]
-	%\paragraph{Experimental results.} 
-	%Tab.~\ref{tab:nonadaptive} shows in the non-adaptive case the relative agreement 
-	%between the traditional evaluation method (TEM) and the two BN-based models (IBN 
-	%and TBN), computed as the proportion of students to which the tests under 
-	%comparison assign the same level, averaged over 10 runs of cross-validation. On 
-	%average 15\% of the students are assigned to a different level with respect to the 
-	%traditional method (although the difference is never more than one level). The reason 
-	%is 
-	%that the BN models account for the difficulty of the questions. E.g., a student with 
-	%only 
-	%70\% of correct answers could be assigned the level B2 if he/she has answered 
-	%correctly a large number of difficult questions which a student of lower level could 
-	%not 
-	%have guessed just by chance. 
-	%\end{mdframed}
-	%
-	%\begin{table}[htp!]
-	%%\renewcommand{\arraystretch}{1.1}
-	%\centering
-	%\begin{tabular}{@{}p{2.5cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}@{}}\toprule
-	%Algorithm&\multicolumn{1}{l}{W\"ort.}&\multicolumn{1}{l}{Komm.}&\multicolumn{1}{l}{H\"oren}&\multicolumn{1}{l}{Lesen}&\multicolumn{1}{l}{Overall}\\
-	% 
-	%\midrule
-	%TEM vs IBN&.80 &.87 &.89 &.85 &.85 \\
-	%TEM vs TBN&.79 &.87 &.88 &.83 &.84 \\
-	%IBN vs TBN&.98 &.95 &.94 &.92 &.95 \\
-	%\bottomrule
-	%\end{tabular}
-	%\caption{Relative agreement between models}\label{tab:nonadaptive}
-	%\vspace{-0.cm}
-	%\end{table}
-	%\begin{table}[htp!]
-	%%\renewcommand{\arraystretch}{1.1}
-	%\centering
-	%\begin{tabular}{@{}p{2.5cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}@{}}\toprule
-	%Algorithm&\multicolumn{1}{l}{W\"ort.}&\multicolumn{1}{l}{Komm.}&\multicolumn{1}{l}{H\"oren}&\multicolumn{1}{l}{Lesen}&\multicolumn{1}{l}{Overall}\\
-	% 
-	%\midrule
-	%TEM& .28 &	.82 &	.88 &	.79 &	.84 \\
-	%IBN& .71 &	.89 &	.83 &	.87 &	.90 \\
-	%TBN& .79 &	.91 &	.87 &	.89 &	.92 \\
-	%\bottomrule
-	%\end{tabular}
-	%\caption{Split-half reliability}
-	%\label{tab:halfsplit}
-	%\vspace{-0.8cm}
-	%\end{table}
-	%\begin{mdframed}[hidealllines=true,backgroundcolor=blue!20]
-	%In this view, we believe that our approach provides more reliable evaluations than the 
-	%traditional one. Tab.~\ref{tab:halfsplit} shows the internal consistency of the three 
-	%tests evaluated using the split-half methodology: the questions are randomly divided 
-	%into two subset of equal size; the two half-tests thus obtained are used to generate 
-	%two independent evaluations of the students; the correlation coefficient between the 
-	%outputs of the two half-tests adjusted with the Spearman-Brown correction is 
-	%retained 
-	%as a measure of the test reliability. Results show that the reliability of both Bayesian 
-	%approaches (IBN and TBN) is larger than that of the traditional method. TBN has the 
-	%highest reliability, as it considers the correlation between different skills and thus all 
-	%answers contribute to the determination of the level of a skill, even those referring to 
-	%different skills. 
-	%Concerning the adaptive case, we have considered different thresholds for the 
-	%entropy. The left plot in Fig.~\ref{fig:agreement} shows the relative agreement of the 
-	%adaptive tests using IBN and TBN with the non-adaptive TBN, whereas the right plot 
-	%shows the average number of questions asked to the students. Both models show a 
-	%strong reduction in the number of questions as the threshold on the entropy 
-	%increases. 
-	%For instance, using the TBN model, the number of questions reduces of about 70\% 
-	%passing from the non-adaptive test to an adaptive test with entropy threshold 
-	%$\tilde{H}=0.5$. Yet, the test still provides the same evaluations as the non-adaptive 
-	%one in more than 70\% of the cases. Such an accuracy loss might be problematic. 
-	%However, even decreasing the entropy threshold to $\tilde{H}=0.19$, we can still save 
-	%20 question on average (to a maximum of 65 questions in the best case) at the price 
-	%of 
-	%a reduction of only 3\% in the accuracy. This shows that a significant number of 
-	%questions provides very little information about the student level of knowledge. Our 
-	%adaptive approach makes it possible to avoid wasting students' time asking 
-	%uninformative questions. 
-	%\end{mdframed}
-	%\begin{figure}[htp!]
-	%\centering
-	%\begin{tikzpicture}
-	%\begin{axis}[title={Agreement},width=6cm, height=4cm,xlabel={Entropy Threshold 
-	%$\tilde{H}$},xmin=0, xmax=0.5, ymin=0.7, ymax=1, xtick={0,.1,.2,.3,.4,.5}, 
-	%ytick={.7,.8,.9,1}, legend pos=north east, ymajorgrids=true, xmajorgrids=true]
-	%\addplot[color=black,mark=square] coordinates { (0.0625,0.99833) (0.125,0.99217) 
-	%(0.1875,0.9685) (0.25,0.89583) (0.375,0.75183) (0.5,0.74517)};    
-	%\addlegendentry{TBN}
-	%\addplot[color=black!60,mark=star] coordinates { 
-	%(0.0625,0.94733)(0.125,0.946000)(0.1875,0.943333)(0.25,0.8965000)(0.375,0.744000)(0.5,0.724666)};
-	%\addlegendentry{IBN}
-	%\end{axis}
-	%\end{tikzpicture}
-	%\begin{tikzpicture}
-	%\begin{axis}[ title={Number of questions},width=6cm, height=4cm, xlabel={Entropy 
-	%Threshold $\tilde{H}$}, xmin=0, xmax=0.5, ymin=0, ymax=100, xtick={0,.1,.2,.3,.4,.5}, 
-	%ytick={0,20,40,60,80,100}, legend pos=north east, ymajorgrids=true, 
-	%xmajorgrids=true]
-	%\addplot[color=black!60,mark=star] coordinates { (0.0625,89.741) (0.125,87.229) 
-	%(0.1875,81.309) (0.25,66.745) (0.375,32.5) (0.5,29.001)};    
-	%\addlegendentry{IBN}
-	%\addplot[color=black,mark=square] coordinates { (0.0625,88.553) (0.125,83.476) 
-	%(0.1875,75.071) (0.25,58.484) (0.375,30.722) (0.5,29)};
-	%\addlegendentry{TBN}
-	%\end{axis}
-	%\end{tikzpicture}
-	%\caption{Agreement between the adaptive methods and the non-adaptive TBN (left) 
-	%and average number of questions asked by the adaptive methods 
-	%(right)}\label{fig:agreement}
-	%\vspace{-.8cm}
-	%\end{figure}
-	%As providing precise values for these probabilities can be very hard even for expert 
-	%teachers, the subjective opinion about the likelihood of an event was described by 
-	%using the verbal-numerical probability scales in Table \ref{tb:labels}. 
-	%The question and skill CPTs are given in tables \ref{tb:questionCPTs} and 
-	%\ref{tb:skillCPTs}.
-	%make the model specification complete, the CPTs of the skills, i.e., $\{ 
-	%P(X_i|\mathrm{\Pi_{X_i}})\}_{i=1}^4$, and those of the questions, i.e., $\{ 
-	%P(Y_j|B_{Y_j})\}_{j=1}^{95}$ should be quantified.
-	%In previous work \cite{mangili2016a}, these parameters have been learned from the 
-	%available data. Results have shown that the resulting model can achieve larger internal 
-	%consistency than the traditional evaluation method in assessing the student level. 
-	%Given this result, a data-driven approach is used here to provide \emph{ground truth} 
-	%evaluations for each student. This approach, hereafter referred to as EM-BN, uses 
-	%expectation maximization (EM) to learn the CPTs of the BN model in  figure 
-	%\ref{fig:fourskills} and infer the students level in the four skills. 
-	%The focus of the paper, however, is to provide an approach to adaptive testing 
-	%entirely based on expert elicitation. Therefore, 
-	%As we are interested in adaptive testing entirely based on expert elicitation, teachers 
-	%have been asked to elicit all CPTs in the model. 
-	%Following \cite{zaffalon2012evaluating}, the $u_{65}$ descriptors slightly increases 
-	%the discounted accuracy contribution (i.e., $1/L$ is the set of labels includes the 
-	%correct one and zero otherwise) with a convex xxx. Note that this descriptors is 
-	%knows. 
-	%The above-described model has been used to evaluate the skills of the 451 students 
-	%in the dataset. 
-	%As a ground truth we take the result based on the percentage of correct answers.
-	%Then, we have compared the effectiveness of the BN and CN-based adaptive 
-	%approaches.
-	%?? traditional method, come nel paper ITS, EM?? \todo{scegliere ground truth}. 
-	% we adopt the following performance descriptors:
-	%\begin{itemize}
-	%\item discounted accuracy (disA), i.e., the average value of 
-	%$\frac{I_{\mathcal{L}}(l)}{L}$, where $I$ is the indicator function and $l$ the true level. 
-	%This can be regarded as the most unfavorable way (among the reasonable ones) to 
-	%evaluate
-	%credal classifiers;
-	%\item set accuracy (setAcc), i.e., the average value of $I_{\mathcal{L}(l)}$. This can be 
-	%regarded as the performance measure most favorable to a credal classifier;
-	%\item the utility-discounted accuracy U65 and U80 \cite{zaffalon2012evaluating}, i.e., 
-	%the average value of a concave function $u\bigl(\frac{I_{\mathcal{L}}(l)}{L}\bigr)$ of 
-	%the 
-	%discounted utility. This measure assumes that being undecided between $k$ levels is 
-	%better than choosing the correct level with probability $1/k$. This measure accounts 
-	%for 
-	%risk aversion, which increases with $u(0.5)$. We have $u(0.5)=0.65$ and 
-	%$u(0.5)=0.8$ 
-	%for, respectively the U65 and the U80 measures; \footnote{Notice that with 
-	%$u(0.5)=0.5$ we obtain the discounted accuracy measure.}
-	%\item the average number of times the credal test is determinate, that is, it returns a 
-	%single level (DET);
-	%\item the accuracy of the Bayesian test when the credal test is determinate (detA) and 
-	%when it is indeterminate (indA). These indicators can show the capability of the credal 
-	%test to identify the students which are more difficult to evaluate;
-	%\item the average cardinality of $\mathcal{L}$ (Csize).
-	%\end{itemize}
-
-	% ---- Bibliography ----
-	%
-	% BibTeX users should specify bibliography style 'splncs04'.
-	% References will then be sorted and formatted in the correct style.
-	%
-	% \bibliography{mybibliography}
-	%
+\section{Outlooks and Conclusions}\label{sec:conc}
+A new approach to the xxx.
+
+%\footnote{Extension to non Boolean answers is trivial as all answers $Y_i$ are \emph{manifest} variables, and, thus, $Y_i$ can be always regarded as a binary variable with the two values denoting the observed answer $y_i$ and its negation \cite{antonucci2009}.}
+%We call \emph{background} of a question the set of skills ``required'' to answer it.
+This can be regarded as a conditional independence statement: given the background skills, the answer to the question is independent of the other skills and of the other questions.
+
+%\paragraph{Expert knowledge modeling.} For a reliable expert knowledge modeling, we use CSs induced by \emph{probability intervals}.
+Qualitative judgments about the probability of a state are converted in interval constraints such as $l\leq P(x) \leq u$, with the interval $[l,u]$ capturing the expert knowledge behind the judgment in a more reliable way than a sharp assessment.
+The CS consistent with these constraints is eventually obtained by standard polyhedral algorithms.
+Verbal to interval-numeric scales such as that Tab.~\ref{tb:labels} are used.
+For instance, if for the probability of the true state of the Boolean variable $Y$ the expert judgment is ``very likely'', the 	corresponding linear constraint is $.2 \leq P(Y=\textrm{true}) \leq .4$.
+
+%The task displays higher complexity than in the case of BNs (e.g., exact inference in non-binary singly-connected CNs is NP-hard \cite{maua14jair}), but approximate techniques can be considered when exact inference is unfeasible \cite{antonucci2014e}.
+
+%To compare the posterior intervals and decide the actual level of the student we might adopt the (conservative) \emph{interval dominance} criterion \cite{troffaes}, which rejects a level if its upper probability is smaller than the lower probability of some other level.
+Overlaps between intervals might therefore induce a situation of \emph{indecision} between two or more levels.
+This is a so-called \emph{credal} classification of the student level \cite{zaffalon2012evaluating}, and it represents the fact that students answers are somehow contradictory or not informative enough to provide a sharp decision.
+
+%This topic has been the subject of much discussion \cite{klir1999uncertainty}.
+A cautious approach \cite{abellan2003maximum} consists in taking the upper entropy $\overline{H}(\bm{X})$, i.e., the entropy of the most entropic PMF in the convex closure $\overline{K}(\bm{X})$ of  $K(\bm{X})$.
+In our framework, we should, then, look for maximum values of conditional entropies, such as $\overline{H}(X_i|Y',\bm{y})$ or $\overline{H}(X_i|\Pi_{X_i})$, as conditional  entropies are required to compute both: (i) the joint (unconditional) entropy $H(\bm{X})$ (and its posterior values); and (ii) the conditional entropies  involved in the  question selection in Eq.~\eqref{eq:expent}.By definition a conditional entropy is a convex combination (whose weights are the elements of a marginal PMF) of convex functions (the entropies).
+The objective function might, then, be non-convex, as the weights are also optimization variables.
+
+		Comment 4: The optimisation in the credal setting shouldn't be the following one?
+
+	$$\max_P [\max_s P(s,q=0)+\max_s P(s,q=1)]$$
+
+	$\P(s,q=0)$ and $P(s,q=1)$ are both functions of $p, \pi_0,$ and $\pi_1$ so I do not 
+	think we can split the optimization
+
+	$$\max_P \max_s P(s,q=0)+\max_P\max_s P(s,q=1)$$
+
+	However, it could be a reasonable approximation. Then, we can switch the optimization 
+	over $P$ and $s$ because they are both max, and obtain: 
+	$$\max_s \overline{P}(s)\overline{P}(q=0|s)+\max_s  \overline{P}(s)\overline{P}(q=1|s)$$.
+
+	If instead we are looking for the minimum over P, we cannot switch the optimization 
+	over $P$ and $s$:
+	$$\min_P \max_s P(s,q) \neq \max_s \min_P P(s,q)$$.
+
+	However I think we can split the optimization into 4 quadratic optimizations.
+	Let's use the following parametrization:
+%	\begin{multline}\label{eq:minimization}
+%		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
+%		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
+%		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
+%		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
+%		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
+%	\end{multline}
+
+	Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It 
+	can be written as
+	$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
+	where
+
+%	\begin{multline}
+%		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
+%		\begin{array}{ll}
+%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
+%			~&\underline{x} \leq x\leq \overline{x}\\ 
+%		\end{array}
+%	\end{multline}
+	and 
+%	\begin{multline}
+%		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
+%		\begin{array}{ll}
+%			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
+%			~&\underline{x} \leq x\leq \overline{x}\\ 
+%		\end{array}
+%	\end{multline}
+
+	where the constraint $x = (\pi_0, \pi_1 ,p)$.
+
+	In general, let $N_s$ be the number of skill levels and $N_q$ the number of possible 
+	answers, then the number of quadratic optimizations to solve should be equal to 
+	$N_s\cdot N_q$.
+
+	In this two dimensional example, we might not need the approximation above as the 
+	minimization in \ref{eq:minimization} can be written as $\min_{i=1:4}(\tilde{P}_1)$, where
+
+%	\begin{multline}
+%		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
+%		\begin{array}{ll}
+%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
+%			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
+%			~&\underline{x} \leq x\leq \overline{x}\\ 
+%		\end{array}
+%	\end{multline}
+	and so on. However, in this case, the number of optimizations to solve should be 
+	$N_s^{N_q}$, that is, it grows exponentially with  $N_q$.
+
+	Then, to bypass this non-convex optimization task, we compute (i) by separately considering the entropies of each skill $X_i\in\bm{X}$.
+This is analogous to the marginal approach commonly considered in multi-label classification to minimize Hamming losses
+	\cite{antonucci2016c}. The issue (ii) is more challenging. We consider the following 
+	upper approximation of $\overline{H}(X_i|Y',\bm{y})$:
+	\begin{equation}
+		\overline{\overline{H}}(X_i|Y',\bm{y})=
+		\max_{P(y'|\bm{y})\in
+			\{\underline{P}(y'|\bm{y}),\overline{P}(y'|\bm{y})\}}
+		\sum_{y' \in \{\textrm{true},\textrm{false}\}}
+		\overline{H}(X_i|\bm{y},y') P(y'|\bm{y})\,,
+	\end{equation}
+	where the bounds of $P(y'|\bm{y})$ are obtained by standard CN updating algorithms.
+	The problem thus reduces to the computation of upper entropies as
+	\begin{equation}\label{eq:entropy}
+		\overline{H}(X_i|\bm{y}) := \sup_{P(X_i|\bm{y}) \in \overline{K}(X_i|\bm{y})} 
+		H(X_i|\bm{y})\,,
+	\end{equation}
+	where  $\overline{K}(X_i|\bm{y})$ is the posterior CS after conditioning on the observed 
+	answers $\bm{y}$.  If $\overline{K}(X_i|\bm{y})$ has a finite number of non-inner 
+	points, this is a linearly-constrained convex optimization whose solution typically 
+	corresponds to either the uniform PMF or a non-inner point on the frontier of 
+	$\overline{K}(X_i|\bm{y})$. A numerical solution can be easily found by a simple iterative 
+	approach in the special case of CS specified by probability intervals 
+	\cite{abellan2003maximum}. We have therefore computed the posterior lower and 
+	upper bounds of $P(X_i|\bm{y})$, and then maximized the entropy with respect to 
+	those bounds. % as in Eq.~\eqref{eq:entropy}. 
+	The procedure induces an outer approximation of $\overline{K}(X_i|\bm{y})$, and hence 
+	the upper approximation  of the maximum entropy 
+	$\overline{\overline{H}}(X|\bm{y})\geq\overline{H}(X|\bm{y})$. 
+	%With a small notation abuse such approximate value is also denoted as 
+	%$\overline{H}(X|\bm{y})$ and is regarded here as a measure of the informativeness 
+	%level 
+	%achieved for skill $X$ after the answers $\bm{y}$. 
+	Finally, to generalise Eq.~\ref{eq:strongext} to CNs, we define the information gain 
+	provided by a question $Y'$ for its background skill $X_{Y'}$ as 
+	$\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y})$ and 
+	select the question $\tilde{Y}'$ leading to the maximum information gain, i.e.,
+	\begin{equation}\label{eq:credalentropy}
+		\tilde{Y}' := \arg \max_{Y'\in\bm{Y}'} 
+		\bigl[
+		\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y}) 
+		\bigr]
+		\,.
+	\end{equation}
+	For the stopping criterion, as we do not consider the joint entropy over the skills, we 
+	separately require each $\overline{\overline{H}}(X_i|\bm{y})$ to be smaller than a 
+	threshold $\tilde{H}$. To be consistent with this choice, we remove from the set of 
+	questions to be selected, those whose background skills already satisfy this condition.
+
+	Note that the use of an outer approximation of the upper entropy affects only the 
+	question selection process (eventually making it sub-optimal), whereas it has no effect 
+	on the student evaluation given a set of answers.
+
+		\begin{theorem}
+		\begin{equation}
+			\max_{x}  \max \{ f(x) , g(x) \}  
+			=
+			\max \{ \max_{x'} f(x') , \max_{x''} g(x'') \} 
+		\end{equation}
+		Let 
+		$$y^{*}:=\max_x \max\{f(x),g(x)\}$$
+		$$y^{**}:= \max \{ \max_{x'} f(x') , \max_{x''} g(x'') \}$$
+		Say for instance that $y^{**}=max_x f(x)$ and let $x^{**}:=\arg\max_x f(x)$. Thus:
+		$$f(x^{**})\geq \max_{x'} g(x) \geq g(x^{**})$$
+
+		Let $x^{*}:= \arg\max_x \max\{f(x),g(x)\}$. 
+		It cannot be $y^{*}:=g(x^{*})$ as this would imply $g(x^{*}) \geq f(x^{*})$
+
+		%Assume ad absurdum $y^{*}\neq y^{**}$.
+
+		If $y^{*}:=f(x^{*})$ we should have $y^{*}=y^{**}$.
+		Vice versa,
+
+		or
+		%$y^{*}:=g(x^{*})$. In the first case 
+	\end{theorem}
+
 \bibliographystyle{splncs04}
@@
 \end{document}
+
+\subsection*{Toy Example}
+	Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean 
+	question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is 
+	specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified 
+	instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The 
+	informativeness score we assign two the question is
+	\begin{equation}
+		\sigma_Q = H[S|Q]:=H[S|q_0]P(q_0)+H[S|q_1]P(q_1)\,.
+	\end{equation}
+	We have
+	\begin{equation}
+		P(q_1)=\pi_1 p + \pi_0 (1-p)
+	\end{equation}
+	while $P(q_0)=1-P(q_1)$ and also
+	\begin{equation}
+		P(s_1|q_1)=\frac{\pi_1 p}{\pi_1 p + \pi_0 (1-p)}=\frac{1}{1+\frac{\pi_0(1-p)}{\pi_1 p}}
+	\end{equation}
+	and
+	\begin{equation}
+		P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ 
+		(1-p)(1-\pi_0)}{p (1-\pi_1)}} 
+	\end{equation}
+	while $P(S=0|Q=1)$ by normalization. Accordingly:
+%	\begin{multline}
+%		\sigma_Q(p,\pi_0,\pi_1)=\\
+%		h \circ f[\gamma/l(p)] \cdot t +
+%		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
+%		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
+%		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
+%	\end{multline}
+	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
+	p + \pi_0 (1-p)$.
+
+	{\color{blue}{In other words:
+			$\sigma_Q(p,\pi_0,\pi_1):= G(\frac{1-p}{p} \frac{1-\pi_0}{1-\pi_1}) (1-p) + 
+			G(\frac{1-p}{p} \frac{\pi_0}{\pi_1}) p$}}
+
+	An alternative score might be achieved by replacing $h$ with $m$, i.e.,
+	\begin{equation}
+		\sigma_Q' := 
+		m \circ f[\gamma/l(p)] \cdot t +
+		m \circ f[\gamma'/l(p)] \cdot (1-t)\,
+	\end{equation}
+	As $f$ is monotone, we can commute $m$ and $f$ *** explain ***, i.e.,
+	\begin{equation}
+		\sigma_Q' := 
+		f \circ m[\gamma/l(p)] \cdot t +
+		f \circ m[\gamma'/l(p)] \cdot (1-t)\,
+	\end{equation}
+	with, as $\gamma>0$. $f \circ m[\gamma/l(p)] = f[\gamma m(l(p))]$
+	We can similarly define another score $\sigma_Q''$ based on $\tilde{i}_\epsilon$.
+	\subsection*{Explicit maximization}
+	$$H[S|Q]\simeq \sigma_Q' = \sum_q P(s^*(q)|q) P(q)$$
+	where $s^*(q):=\arg\max_s P(s|q)$. 
+	$$\sigma_Q'= \sum_q P(s^*(q),q) = \sum_q P(s^*(q) P(q|s^*(q))$$
+	Note that, if $s^*(q)$ is the same for each $q$, the score just corresponds to $P(s^*)$. 
+	In other words, the score is flat is each answer gives the same most likely skill level *** 
+	reasonable ***. Let us move to an imprecise setting and intend the $s^*$ state as
+	$s^*(q):=\arg\max_s \overline{P}(s|q)$. The objective function is a linear combination of 
+	$P(s*(q)$ whose coefficient can be optimized independently. Overall, this corresponds 
+	to a linear programming task.
+	$$\max_s \overline{P}(s,q) = \max_s \max_P P(s) P(q|s) = \max_s \overline{P}(s) 
+	\overline{P}(q|s)$$
+
+	\subsection*{Francesca's comments}
+
+	Comment1: This sentence is not clear to me:  "as $\gamma>0$. $f \circ m[\gamma/l(p)] 
+	= f[\gamma m(l(p))]$".\\
+	Comment2: How shall we use the Gumbel's trick
+
+	Comment 3: Below I obtain something that looks different to me, but maybe it is 
+	equivalent.
+
+	\begin{equation}
+		P(s_1|q_1)=\frac{\pi_1 p}{P(q_1)}
+	\end{equation}
+
+%	\begin{multline}
+%		\sigma_Q(p,\pi_0,\pi_1)=\\
+%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
+%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
+%	\end{multline}
+
+	But, as $P(q_1)\geq 0$, then
+%	\begin{multline}
+%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
+%		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
+%		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
+%		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
+%	\end{multline}
+
+	Similarly, as $1-P(q_1)\geq 0$, 
+%	\begin{multline}
+%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
+%		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
+%	\end{multline}
+
+	so that,
+
+%	\begin{multline}
+%		\sigma_Q(p,\pi_0,\pi_1)= \\
+%		2 max\{\pi_1 p, \pi_0 (1-p)\}+
+%		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
+%	\end{multline}
+
+	\subsection*{Formulae}
+	Let us define the functions, all defined for $x\in [0,1]$, apart from $f$ defines for each 
+	$x\geq 0$:
+	\begin{eqnarray}
+		f(x)&:=& \frac{1}{1+x},\,,\\
+		h(x)&:=&-x \cdot \log_2 x - (1-x)  \cdot \log_2 (1-x)\,,\\
+		l(x)&:=&\frac{x}{1-x}\,,\\
+		m(x)&:=&2 \max\{x,1-x\}\,,\\
+		i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
+		\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
+	\end{eqnarray}
+
+	Derivatives:
+	\begin{eqnarray}
+		f'(x)&:=& -\frac{1}{(1+x)^2},\,,\\
+		h'(x)&:=&\log_2 \frac{1-x}{x}\,\\
+		G(x) &:=& h \circ f(x)\,\\
+		G'(x) &:=& h[f(x)] f'(x)=-\frac{\log_2\frac{1-f(x)}{f(x)}}{(1+x)^2}\,\\
+		G'(x) &:=& -\frac{\log_2 x}{(1+x)^2}\,\\
+		l(x)&:=&\frac{x}{1-x}\,,\\
+		m(x)&:=&2 \max\{x,1-x\}\,,\\
+		i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
+		\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
+	\end{eqnarray}
+
+A few remarks. Function $f$ is a monotonically decreasing function with values in 
+$[0,1]$. Function $h(x)$ corresponds to the entropy of a mass function over a Boolean 
+	variable with a probability equal to $x$. On the extreme points of its domain, we take 
+	the limit value, i.e., zero. The function is unimodal and achieve its maximum on  
+	$x=\frac{1}{2}$. Function $l$ is the popular \emph{logit} function, it is monotonically 
+	increasing function of $x$ and $l(1-x)=l(x)^-1$. Function $m(x)$ is $x$ for $x\geq 
+	\frac{1}{2}$ and $1-x$ otherwise. 
+	Exactly as $h$, functions $m$ and $\tilde{i}_\epsilon$, for each $\epsilon>0$, have the 
+	same (zero) value for $x=0$ and $x=1$, being all unimodal with maximum in 
+	$x=\frac{1}{2}$.
+	Finally, the popular Gumbel's trick implies:
+	\begin{equation}
+		\lim_{\epsilon \to 0} i_\epsilon(x)= 
+		\lim_{\epsilon \to 0} \tilde{i}_\epsilon(x)
+		= m(x)\,.
+	\end{equation}

### 2021-05-12 cat.py
Add files via upload
Data analysis script

@@ -1,0 +1,194 @@
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import style
+import matplotlib.patches as mpatches
+from tikzplotlib import save as tikz_save
+
+#directory = os.listdir(".")
+#for filename in directory:
+#	print(filename)
+n_students = 1024
+n_questions = 18
+
+profiles_csv = 'Minimalistic1x2x9.profiles.csv'
+profiles = pd.read_csv(profiles_csv,names=['pr'])
+
+head_c = ['s','skill','q','t','sc','a','l0','l1','u0','u1']
+head_b = ['s','skill','q','t','sc','a','p0','p1']
+
+c_mode_csv = 'Minimalistic1x2x9.progress.credal-adaptive-mode.eps01.csv'
+c_ent_csv = 'Minimalistic1x2x9.progress.credal-adaptive-entropy.eps01.csv'
+c_mode2_csv = 'Minimalistic1x2x9.progress.credal-adaptive-mode.csv'
+c_ent2_csv = 'Minimalistic1x2x9.progress.credal-adaptive-entropy.csv'
+b_ran_csv = 'Minimalistic1x2x9.progress.bayesian-non-adaptive.csv'
+b_mode_csv = 'Minimalistic1x2x9.progress.bayesian-adaptive-mode.csv'
+b_ent_csv = 'Minimalistic1x2x9.progress.bayesian-adaptive-entropy.csv'
+b_pr_csv = 'Minimalistic1x2x9.progress.bayesian-adaptive-pright.csv'
+c_pr_csv = 'Minimalistic1x2x9.progress.credal-adaptive-pright.csv'
+
+c_mode = pd.read_csv(c_mode_csv,names=head_c)
+c_ent = pd.read_csv(c_ent_csv,names=head_c)
+c_mode2 = pd.read_csv(c_mode2_csv,names=head_c)
+c_ent2 = pd.read_csv(c_ent2_csv,names=head_c)
+c_pr = pd.read_csv(c_pr_csv,names=head_c)
+b_ran = pd.read_csv(b_ran_csv,names=head_b)
+b_mode = pd.read_csv(b_mode_csv,names=head_b)
+b_ent = pd.read_csv(b_ent_csv,names=head_b)
+b_pr = pd.read_csv(b_pr_csv,names=head_b)
+
+nn1 = np.zeros(n_questions+1)
[…]

### 2021-05-16 paper.tex

@@
 \documentclass[runningheads]{llncs}
-\usepackage{algorithm,algorithmic,amsfonts,bm,hyperref,booktabs,tikz,pgf,pgfplots,amsmath,soul,subcaption,url,graphicx,amsmath,booktabs,booktabs,nicefrac,bm,colortbl,tikz,pgfplots,enumerate,xargs}
+\usepackage{algorithm,algorithmic,amsfonts,bm,booktabs,tikz,pgf,pgfplots,amsmath,soul,url,graphicx,amsmath,booktabs,booktabs,nicefrac,bm,colortbl,tikz,pgfplots,enumerate,xargs,optidef}
 \usetikzlibrary{arrows,automata,circuits}
-\captionsetup{compatibility=false}
+%\captionsetup{compatibility=false}
 \usetikzlibrary{arrows,plotmarks,decorations.markings,trees,shapes}
@@
 \begin{document}
-\title{A New Score for Adaptive Tests\\in Bayesian and Credal Networks}
+\title{A New Score for Adaptive Tests\\ in Bayesian and Credal Networks}
 \author{Alessandro Antonucci \and
-Francesca Mangili \and\\
+Francesca Mangili \and \\
 Claudio Bonesana \and
@@
 \authorrunning{Antonucci et al.}
-\institute{Istituto Dalle Molle di Studi sull'Intelligenza Artificiale, Lugano, Switzerland\\
+\institute{Istituto Dalle Molle di Studi sull'Intelligenza Artificiale, Lugano, Switzerland
 \email{\{alessandro,francesca,claudio.bonesana,giorgia.adorni\}@idsia.ch}}
@@
 A better elicitation of the uncertainty in the question/skills relations can be achieved by interval probabilities.
-This turns the model into a \emph{credal} network, thus making the inferential complexity of the queries required to select questions more demanding.
+This turns the model into a \emph{credal} network, thus making more challenging the inferential complexity of the queries required to select questions.
 This is especially the case for the information theoretic quantities used as \emph{scores} to drive the adaptive mechanism.
-We present an alternative family of scores, based on the mode of the posterior probabilities and hence easier to explain.
+We present an alternative family of scores, based on the mode of the posterior probabilities, and hence easier to explain.
 This makes considerably simpler the evaluation in the credal case, without significantly affecting the quality of the adaptive process.
 Numerical tests on synthetic and real-world data are used to support this claim.
-%12 pages
-\keywords{Computer adaptive tests \and Information theory \and Credal networks \and Bayesian networks}
+\keywords{computer adaptive tests \and information theory \and credal networks \and Bayesian networks \and index of qualitative variation}
 \end{abstract}
@@
 A test or an exam can be naturally intended as a measurement process, with the questions acting as sensors measuring the skills of the test taker in a particular discipline.
-Such measurement is typically imperfect with the skills acting as latent variables whose actual values cannot be revealed in a perfectly reliable way.
+Such measurement is typically imperfect with the skills modelled as latent variables whose actual values cannot be revealed in a perfectly reliable way.
 The role of the questions, whose answers are regarded instead as manifest variables, is to reduce the uncertainty about the latent skills.
-Following this perspective, probabilistic modelling is an obvious framework to describe tests.
-Consider for instance the example in Figure \ref{fig:minicat}, where a small Bayesian network is used to describe the probability of the test taker having understood how to multiply numbers.
-In such a framework making the test \emph{adaptive}, i.e., picking a next question on the basis of the current knowledge level of the test taker is also very natural.
-The expected information gain for the available questions might be naturally used to select the question leading to the more informative results about the skill level of the test taker.
-This might take place before the answer to the question on the basis of the expectations about the possible answers.
+Following this perspective, probabilistic models are an obvious framework to describe tests.
+Consider for instance the example in Figure \ref{fig:minicat}, where a Bayesian network evaluates the probability that the test taker knows how to multiply integers.
+In such framework making the test \emph{adaptive}, i.e., picking a next question on the basis of the current knowledge level of the test taker is also very natural.
+The information gain for the available questions might be used to select the question leading to the more informative results (e.g., according to Table \ref{tab:minicat}, $Q_1$ is more informative than $Q_2$ no matter what the answer is).
+This might also be done before the answer on the basis of expectations over the possible alternatives.
 
@@
 Having to provide sharp numerical values for these probabilities might be difficult.
-As the skill is typically a latent quantity, complete data are not available for a statistical learning of the parameters and the elicitation should therefore demanded to experts (e.g., a teacher).
-Yet, it might be not obvious to express such a domain knowledge by single numbers and a more robust elicitation, such as a probability interval, might add realism and robustness to the modelling process \cite{hajek2012rationality}.
+As the skill is a latent quantity, complete data are not available for a statistical learning and a direct elicitation should be typically demanded to experts (e.g., a teacher).
+Yet, it might be not obvious to express such a domain knowledge by single numbers and a more robust elicitation, such as a probability interval (e.g., $P(Q_1=1|S_1=1)\in[0.85,0.95]$), might add realism and robustness to the modelling process \cite{hajek2012rationality}.
 With such generalized assessments of the parameters a Bayesian network simply becomes a \emph{credal} network \cite{antonucci2010d}.
-Yet, the counterpart of such increased realism is the higher computational complexity characterizing the inference in credal networks \cite{maua14jair}.
-This is especially the case when coping with information theoretic measures such a information gain, whose computation might lead to complex non-linear optimization tasks \cite{mangili2017b}.
+The counterpart of such increased realism is the higher computational complexity characterizing inference in credal networks \cite{maua14jair}.
+This is an issue especially when coping with information theoretic measures such an information gain, whose computation in credal networks might lead to complex non-linear optimization tasks \cite{mangili2017b}.
 The goal of this paper is to investigate the potential of alternatives to the information-theoretic scores driving the question selection in adaptive tests based on directed graphical models, no matter whether these are Bayesian or credal networks.
@@
 \begin{tikzpicture}[scale=1]
-\node[] ()  at (-5,0.5) {\tiny $P(S=1|Q=1)=0.5$};
-\node[] ()  at (-5,-2) {\tiny $P(S=1|Q=1)=0.5$};
-\node[] ()  at (-5,-3) {\tiny $P(S=1|Q=1)=0.5$};
-\node[] ()  at (3,0.5) {\tiny $P(S=1)=0.5$};
-\node[] ()  at (0,-3) {\tiny $2x3=?$ \quad $2x3=?$\quad  $2x3=?$};
-\node[] ()  at (0,-2) {\tiny $P(Q=1|S=1)=0.3$ \quad $0.4$\quad  $0.5$};
-\node[] ()  at (0,-2.5) {\tiny $P(Q=1|S=0)=0.3$ \quad  $0.4$ \quad  $0.5$};
-\node[nodo] (s)  at (0,0.5) {$S$};
-\node[Qnodo] (q1)  at (-2.,-1) {$Q_1$};
-\node[Qnodo] (q2)  at (0,-1) {$Q_2$};
-\node[Qnodo] (q3)  at (2,-1) {$Q_3$};
+%\node[] ()  at (4,0.5) {\tiny $P(S=1)=0.5$};
+\node[] ()  at (5.5,0.5) {$P(Q_1=1|S=1)=0.9$};
+\node[] ()  at (5.5,0.) {$P(Q_1=1|S=0)=0.3$};
+\node[] ()  at (5.5,-0.5) {$P(Q_2=1|S=1)=0.6$};
+\node[] ()  at (5.5,-1.) {$P(Q_2=1|S=0)=0.4$};
+\node[nodo] (s)  at (0,0.5) {Knows multiplication ($S$)};
+\node[Qnodo] (q1)  at (-2.,-1) {$10\times 5?$ ($Q_1$)};
+\node[Qnodo] (q2)  at (+2,-1) {$13\times 14?$($Q_2$)};
 \draw[arco] (s) -- (q1);
 \draw[arco] (s) -- (q2);
-\draw[arco] (s) -- (q3);
 \end{tikzpicture}
-\caption{Ad adaptive testing scheme to evaluate the multiplication (Boolean) skill $S$ by three (Boolean) questions. Probabilities are assessed by the Bayesian network on the right}
+\caption{A Bayesian network over Boolean variables modelling a simple test to evaluate integer multiplication skill with two questions.}
 \label{fig:minicat}
 \end{figure}
-*** espandere figura ***
-\newpage 
+\begin{table}[htbp!]
+\centering
+\caption{Posterior probabilities of the skill after one or two questions in the test based on the Bayesian network in Figure \ref{fig:minicat}.
+A uniform prior over the skill is considered.
+Probabilities are regarded as grades and sorted from the lowest one.
+Bounds to a perturbation $\epsilon=\pm 0.05$ of all the model input parameters are also reported.}
+\begin{tabular}{@{}ccrrr@{}}
+\toprule
+$Q_1$&$Q_2$&$P(S=1|q_1,q_2)$&
+$\underline{P}(S=1|q_1,q_2)$&
+$\overline{P}(S=1|q_1,q_2)$
+\\
+\midrule
+$0$&$0$&$0.087$&$0.028$&$0.187$\\
+$0$&$-$&$0.125$&$0.052$&$0.220$\\
+$0$&$1$&$0.176$&$0.092$&$0.256$\\
+$-$&$0$&$0.400$&$0.306$&$0.506$\\
+$-$&$1$&$0.600$&$0.599$&$0.603$\\
+$1$&$0$&$0.667$&$0.626$&$0.708$\\
+$1$&$-$&$0.750$&$0.748$&$0.757$\\
+$1$&$1$&$0.818$& $0.784$ &$0.852$\\
+\bottomrule
+\end{tabular}
+\label{tab:minicat}
+\end{table}
 The paper is organized as follows.
@@
 \section{Related Work}\label{sec:work}
-Modelling a test as a process involving latent variables is a classical approach since the proposal of the classical \emph{item response theory}, that has been widely used even to implement adaptive sequences \cite{xxx}.
+Modelling a test as a process relating latent and manifest variables since the classical \emph{item response theory}, that has been widely used even to implement adaptive sequences \cite{embretson2013item}.
 Despite its success related to the ease of implementation and inference, IRT might be inadequate when coping with multiple latent skill, especially when these are dependent.
-For such cases, interpretable graphical models such as Bayesian networks have been resulted more effective [x].
-The development of (computer) adaptive tests is a classical topic for AI \cite{xx}.
-Apart from graphical models, adaptive algorithms have been proposed within a genetic optimization framework.
-The idea of using Bayesian network in grading environment is not new.
-xxx.
-As already noticed in the previous section, the latent nature of the student skills might hinder the direct statistical learning of the parameters of such models.
-This naturally led some authors to consider missing data modelling.
-In particular the work of xxxx Vomlel related to EM algorithm in Bayesian networks is a notable example of this kind of approaches.
-Some other authors considered even more extreme directions involving missingness even about the answers such as \cite{bachrach2012grade}.
-This is also related to the notion of monotonicity \cite{plajner2020monotonicity}.
-The potential of these models in terms of explainability of the results has been emphasized in the work Work of Darwiche about same-probability problem.
-*** completare *** Bayesian networks (BNs) \cite{koller2009} have been used to model the knowledge driving such intelligent systems \cite{almond2015bayesian}.
-However, collecting large sets of reliable data in educational domains may be difficult and time consuming (e.g., a course with few students, or taught for the first time), and the quantification should be based on expert knowledge only.
-To elicit a Bayesian network, an expert might face questions like: ``\emph{which is the probability of a student with a particular knowledge level giving the right answer to a question?}''.
-Giving sharp probabilities for questions of this kind can be problematic for an expert, whose knowledge is mostly qualitative (e.g., ``\emph{a right answer is very unlikely}'').
-Fuzzy linguistic approaches represent a viable, non-numerical, way to address these issues \cite{badaracco2013fuzzy}.
-To stick within the probabilistic framework, verbal-numerical probability scales associated with sharp values \cite{renooij1999talking} or intervals \cite{walley1991statistical} have been also proposed.
-a generalization of BNs based on the imprecise probability theory \cite{walley1991statistical}, where local parameters are defined by set-valued probabilities.
-This simplifies the elicitation process and offers a more reliable handling of the related uncertainty.
-Moving from BNs to CNs implies two main issues: (i) numerical inferences will be interval-valued too, thus making debatable both the decision criterion \cite{troffaes} an the information measures \cite{klir1999uncertainty} to adopt; and (ii) inference tasks in CNs typically belongs to higher complexity classes than their Bayesian counterparts \cite{maua14jair}.
-Both these issues are addressed by defining a computationally feasible procedure based on CNs to be used for practical implementation of intelligent systems solely specified by expert knowledge.
-To the best of our knowledge this is the first attempt to perform e-testing with models of this kind.
-
-We focus on the application of CNs to \emph{computer adaptive testing} (CAT), i.e., an approach to e-testing that adjusts the sequence and the number of questions to the ability level of the test taker.
-CATs have the potential to make the test an individualised experience that challenges and does not discourage the test takers, as most of the questions are near their ability levels.
-Building upon \emph{item response theory} \cite{hambleton1985item}, the common background underpinning CATs, graphical modeling (such as BNs and CNs) offers a powerful language for describing complex multivariate dependencies between skills and rich tasks.
-Several researchers have exploited the potential of BNs both in adaptive and non-adaptive educational assessment \cite{vomlel2004building,plajner2015}.
-These authors focus on applications for which data are available to learn the model parameters.
-We regard this point as a serious limitation, possibly hindering CATs adoption by many teachers and instructors.
-The results are promising: CAT based on CNs is effective in reducing the number of questions while maintaining a high accuracy in the evaluation and the approximations introduced do not compromise the procedure's effectiveness.
+This led researchers towards the area of probabilistic graphical models as tools to implement IRT in more complex setups \cite{mislevy1997graphical}.
+Eventually, Bayesian networks have been identified as a natural framework to models tests, even behind the IRT framework \cite{vomlel2004bayesian}, this being especially the case for adaptive models \cite{vomlel2004building} and coached solving \cite{conati1997line}.
+In order to cope with latent skills, some authors explored the application of EM-like approaches to these models \cite{plajner2020monotonicity}, this also involving the extreme situation of no ground truth information about the answers \cite{bachrach2012grade}.
+As an alternative approach to the same issue, some authors considered relaxations of the Bayesian formalism, such as fuzzy models \cite{badaracco2013fuzzy} and imprecise probabilities \cite{mangili2017b}.
+This latter direction is the same direction we consider, but trying to overcome the computational limitations of that approach when coping with information-theoretic scores.
+Compared to the approach in \cite{chen2015computer}, that is focused in the Bayesian case only, we are interested in measures that could easily extended to the imprecise probability framework, this not being the case of the same-decision problem considered in that work.
 
@@
 Thus, $x \in \mathcal{X}$ is a possible value of $X$.
-Here only variables with a finite number of possible values are considered.\footnote{Adaptive approaches such as IRT \cite{xx} adopt continuous latent variables.}
+Here we only consider discrete variables.\footnote{IRT uses instead with continuous skills.
+Yet, when coping probabilistic models, having discrete skill does no prevent evaluations to range over a continuous domain.
+E.g., see Table \ref{tab:minicat}, where the grade corresponds to a (continuous) probability.}
 
 \subsection{Bayesian Networks}
-A probability mass function over $X$ is denoted as $P(X)$, while $P(x)$ is the probability assigned to state $x$.
-Given a function $f$ of $X$, its expectation with respect to $P(X)$ is $\mathbb{E}_P(f):=\sum_{x\in\mathcal{X}} P(x) \cdot f(x)$.
-The expectation of $-\log_k[P(X)]$ is called \emph{entropy} and denoted also as $H_P(X)$.\footnote{To cope with zero probabilities, we set $0 \cdot \log_k 0 = 0$.} We assume $k:=|\mathcal{X}|$ to have the maximum of the entropy, achieved for uniform PMFs, equal to one.
+A probability mass function (PMF) over $V$ is denoted as $P(V)$, while $P(v)$ is the probability assigned to state $v$.
+Given a function $f$ of $V$, its expectation with respect to $P(V)$ is $\mathbb{E}_P(f):=\sum_{v\in\mathcal{V}} P(v) \cdot f(v)$.
+The expectation of $-\log_b[P(V)]$ is called \emph{entropy} and denoted also as $H(X)$.\footnote{We set $0 \cdot \log_b 0 = 0$ to cope with zero probabilities.} We set $b:=|\mathcal{V}|$ to have the maximum of the entropy, achieved for uniform PMFs, equal to one.
 
-Given a joint PMF $P(X,Y)$, the marginal PMF $P(Y)$ is obtained by summing out the other variable, i.e., $P(y)=\sum_{x\in\mathcal{X}} P(x,y)$.
-Conditional PMFs such as $P(X|y)$ are similarly obtained by Bayes's rule, i.e., $P(x|y)=P(x,y)/P(y)$ provided that $P(y)>0$.
-Notation $P(X|Y):=\{P(X|y)\}_{y\in\mathcal{Y}}$ is used for such conditional probability table (CPT).
-The entropy of a conditional PMF is defined as in the unconditional case and denoted as $H_P(X|y)$.
-The expected entropy is a weighted average of conditional entropies, i.e., $H_P(X|Y):=\sum_{y\in\mathcal{Y}} H_P(X|y) P(y)$.
-If $P(x,y)=P(x) P(y)$ for each $x\in\mathcal{X}$ and $y\in\mathcal{Y}$, variables $X$ and $Y$ are stochastically independent.
-A conditional formulation can be also considered.
+Given joint PMF $P(U,V)$, the marginal PMF $P(V)$ is obtained by summing out the other variable, i.e., $P(v)=\sum_{u\in\mathcal{U}} P(u,v)$.
+Conditional PMFs such as $P(U|v)$ are similarly obtained by Bayes's rule, i.e., $P(u|v)=P(u,v)/P(v)$ provided that $P(v)>0$.
+Notation $P(U|V):=\{P(U|v)\}_{v\in\mathcal{V}}$ is used for such conditional probability table (CPT).
+The entropy of a conditional PMF is defined as in the unconditional case and denoted as $H(U|v)$.
+The conditional entropy is a weighted average of entropies of the conditional PMFs, i.e., $H(U|V):=\sum_{v\in\mathcal{V}} H(U|v) P(v)$.
+If $P(u,v)=P(u) P(v)$ for each $u\in\mathcal{U}$ and $v\in\mathcal{V}$, variables $U$ and $V$ are independent.
+Conditional formulations are also considered.
 
-We assume the set of variables $\bm{X}:=(X_1,\ldots,X_n)$ to be in one-to-one correspondence with a directed acyclic graph $\mathcal{G}$.
-For each $X\in\bm{X}$, the parents of $X$ are called predecessor of $X$ according to $\mathcal{G}$ and denoted as $\mathrm{Pa}_X$.
-The graph $\mathcal{G}$ together with the collection of CPTs $\{P(X|\mathrm{Pa}_X)\}_{X\in\bm{X}}$ provides a Bayesian network (BN) specification \cite{koller2009}.
-Under the Markov condition, that states that every variable is conditionally independent of its non-descendants non-parents given its parents, a BN compactly defines a joint PMF $P(\bm{X})$ that factorizes as $P(\bm{x})=\prod_{X\in\bm{X}} P(x|\mathrm{pa}_X)$.
+We assume the set of variables $\bm{V}:=(V_1,\ldots,V_r)$ to be in one-to-one correspondence with a directed acyclic graph $\mathcal{G}$.
+For each $V\in\bm{V}$, the parents of $V$, i.e., the predecessors of $V$ in  $\mathcal{G}$, are denoted as $\mathrm{Pa}_V$.
+Graph $\mathcal{G}$ together with the collection of CPTs $\{P(V|\mathrm{Pa}_V)\}_{V\in\bm{V}}$ provides a Bayesian network (BN) specification \cite{koller2009}.
+Under the Markov condition, that states that every variable is conditionally independent of its non-descendants non-parents given its parents, a BN compactly defines a joint PMF $P(\bm{V})$ that factorizes as $P(\bm{v})=\prod_{V\in\bm{V}} P(v|\mathrm{pa}_V)$.
+Inference intended as the computation of the posterior PMF of a single (queried) variables given some evidence about other variables is in general NP-hard, but exact and approximate schemes are available (see \cite{koller2009} for details).
 
 \subsection{Credal Sets and Credal Networks}
-A set of PMFs over $X$ is denoted as $K(X)$ and called \emph{credal set} (CS).
+A set of PMFs over $V$ is denoted as $K(V)$ and called \emph{credal set} (CS).
 Expectations based on CSs are the bounds of the PMF expectations with respect to the CS.
-Thus $\underline{E}_K[f]:=\inf_{P(X)\in K(X)} \mathbb{E}_P[f]$ and similarly for the supremum $\mathbb{E}_K$.
-Expectations of events are in particular caller lower and upper probabilities and denotes as $\underline{P}$ and $\overline{P}$.
-Notation $K(X|y)$ is used for a set of conditional CSs, while $K(X|Y):=\{K(X|y)\}_{y\in\mathcal{Y}}$ is a credal CPT (CCPT).
+Thus $\underline{\mathbb{E}}[f]:=\inf_{P(V)\in K(V)} \mathbb{E}[f]$ and similarly for the supremum $\overline{\mathbb{E}}$.
+Expectations of events are in particular caller lower and upper probabilities and denoted as $\underline{P}$ and $\overline{P}$.
+Notation $K(U|v)$ is used for a set of conditional CSs, while $K(U|V):=\{K(U|v)\}_{v\in\mathcal{V}}$ is a credal CPT (CCPT).
 
-Analogously to a BN, a credal network (CN) \cite{cozman2000}  is specified by graph $\mathcal{G}$ together with a family of CCPTs $\{K(X|\mathrm{Pa}_X)\}_{X\in\bm{X}}$.
-A CN defines a joint CS $K(\bm{X})$ obtained by the set of xxx.
+Analogously to a BN, a credal network (CN) is specified by graph $\mathcal{G}$ together with a family of CCPTs $\{K(V|\mathrm{Pa}_V)\}_{V\in\bm{V}}$ \cite{cozman2000}.
+A CN defines a joint CS $K(\bm{V})$ corresponding to all the joint PMFs induced by BNs whose CPTs are consistent with the CN CCPTs.
+For CNs, we intend inference as the computation of the lower and upper posterior probabilities.
+The task generalizes BN inference being therefore NP-hard, see  \cite{maua2014jair} for a deeper characterization.
 
@@
 Let $\bm{Q}$ denote a repository of questions available to the instructor.
-The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be defined in advance.
+The order and the number of questions picked from $\bm{Q}$ to be asked to $\sigma$ might not be defined in advance.
 We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the test taker, and to decide when the test stops.
-Algorithm \ref{alg:ta} depicts a general TA scheme, with $\bm{e}$ denoting the array of the answers collected from the test taker $\sigma$.
+Algorithm \ref{alg:ta} depicts a general TA scheme, with $\bm{e}$ denoting the array of the answers collected from test taker $\sigma$.
 
@@
 In our assumptions, this answer is not affected by the previous answers to other questions.\footnote{Generalized setups where the quality of the student answer is affected by the previous answers will be discussed at the end of the paper.
-This might include a \emph{fatigue} model negatively affecting the quality of the answers when many questions have been already answered as well as the presence of \emph{revealing} questions that might improve the quality of other answers.}
+This might include a \emph{fatigue} model negatively affecting the quality of the answers when many questions have been already answered as well as the presence of \emph{revealing} questions that might improve the quality of other answers \cite{laitusis2007examination}.}
 
@@
 Trivial examples of such functions are the percentage of correct answers or a Boolean that is true when a sufficient number of correct answers has been provided.
-Note also that in our assumptions the TA is \emph{exchangeable}, i.e., the stopping rule, the question finder and the evaluation function are invariant with respect to permutations in $\bm{e}$.
+Note also that in our assumptions the TA is \emph{exchangeable}, i.e., the stopping rule, the question finder and the evaluation function are invariant with respect to permutations in $\bm{e}$ \cite{sawatzky2016accuracy}.
 In other words, the same next question, the same evaluation and the same stopping decision is produced for any two students, who provided the same list of answers in two different orders.
@@
 Yet, this might be impractical (e.g., because of time limitations) or just provide an unnecessary burden to the test taker.
-The goal of a good TA is therefore to trade off the accuracy of the evaluation and the number of questions.\footnote{In some generalized setups, other elements such as a \emph{serendipity} in choice in order to avoid tedious sequences of questions might be also considered \cite{xx}.}
+The goal of a good TA is therefore to trade off the accuracy of the evaluation and the number of questions.\footnote{In some generalized setups, other elements such as a \emph{serendipity} in choice in order to avoid tedious sequences of questions might be also considered \cite{badran2019adaptive}.}
 
-\section{Adaptive Testing in Bayesian Networks}\label{sec:bncat}
-%Item response theory is a popular *** Something about IRT here ***.
-Most of these approaches are based an a unidimensional representation of the student knowledge level.
-Proposals to cope with multidimensional IRTs have been considered, but this results critical when coping with dependencies between them.
-For this reason probabilistic modelling can be considered.
-This is the topic of the next section.
-
+\section{Adaptive Testing in Bayesian and Credal Networks}\label{sec:bncat}
 The general TA setup in Algorithm \ref{alg:ta} can be easily specialized to BNs as follows.
-First, we identify the profile $\sigma$ of the test saker with the actual states of a number of latent discrete variables, called \emph{skills}.
+First, we identify the profile $\sigma$ of the test taker with the actual states of a number of latent discrete variables, called \emph{skills}.
 Let $\bm{S}=\{S_i\}_{j=1}^n$ denote these skill variables, and $\bm{s}_\sigma$ the actual values associated with the test take.
@@
 Note that this assumption about the graph is simply reflecting a statement about the conditional independence between (the answer to) a question and all the other skills and questions given scope of the question.
-This basically means that the answers to other questions are not directly affecting the answer to a particular question, and this naturally follows from the exchangeability assumption.\footnote{Moving to other setups would not really be critical because of the property of observed nodes in Bayesian and credal networks, see for instance \cite{antonucci2009} or \cite{debock,bolt}.}
+This basically means that the answers to other questions are not directly affecting the answer to a particular question, and this naturally follows from the exchangeability assumption.\footnote{Moving to other setups would not really be critical because of the property of observed nodes in Bayesian and credal networks, see for instance \cite{antonucci2009,bolt}.}
+
+As the available data are typically incomplete because of the latent nature of the skills, dedicated learning strategies, such as various form of constrained EM should be considered to train a BN from data.
+We refer the reader to the various contributions of Plajner and Vomlel in this field (e.g., \cite{plajner2020monotonicity}) for a complete discussion of that approach.
+Here we assume the BN quantification already available.
 
@@
 Regarding the question selection, ${\tt Pick}$ might be similarly based on the (posterior) CPT $P(\bm{S}|Q,\bm{Q}=\bm{e})$, whose values for the different answers to $Q$ might be weighted by the marginal $P(Q|\bm{e})$.
-More specifically, entropies and conditional entropies\footnote{Information gain xxx} are considered by Algorithm \ref{alg:bnta}, while the evaluation is based on a conditional expectation for a given utility function.
-
-*** complete data or information by elicitation, otherwise EM ***
+More specifically, entropies and conditional entropies are considered by Algorithm \ref{alg:bnta}, while the evaluation is based on a conditional expectation for a given utility function.
 
@@
 \end{algorithmic}
-\caption{Information Theoretic TA in BN over the questions $\bm{Q}$ and the skills $\bm{S}$: given the student profile $\bm{s}_\sigma$, the algorithms returns an evaluation corresponding to the expectation of an evaluation function $f$ with respect to the posterio for the skills given the answers $\bm{e}$.\label{alg:bnta}}
+\caption{Information Theoretic TA in BN over the questions $\bm{Q}$ and the skills $\bm{S}$: given the student profile $\bm{s}_\sigma$, the algorithms returns an evaluation corresponding to the expectation of an evaluation function $f$ with respect to the posterior for the skills given the answers $\bm{e}$.\label{alg:bnta}}
 \end{algorithm}
 
-A CN version of Algorithm \ref{alg:bnta} could be equivalently considered.
-Moving to CN is almost the same, where bounds on the entropies to be considered instead.
-This makes especially critical the evaluation of the bounds of the entropy.
-As entropy is a convec function, upper entropy might be found, while the minimization has been proved to be NP-hard by Klir and fast techniques are only available for specific families of CSs.
-The optimization becomes even more challenging for expected entropies there are roughly mixtures with imprecise weights.
-Accordingly, in \cite{mangili2017b}, only special cases based on an inner approximation have been derived.
+When no data can be used for the training, elicitation techniques should be considered instead.
+As already discussed CNs might offer a better formalism to capture domain knowledge, especially by providing interval-valued probabilities instead of sharp values.
+If this is the case, a CN version of Algorithm \ref{alg:bnta} can be equivalently considered.
+Moving to CN is almost the same, provided that bounds on the entropies are considered instead.
+Yet, the price of such increased realism in the elicitation is the higher complexity characterizing inferences based on CNs.
+The work in \cite{mangili2017b} offers a critical discussion of those issues, that are only partially addressed by heuristic techniques used to approximate such bounds.
+In the next section we conside an alternative approach to cope with CNs and adaptive TAs based on different scores used to select the questions.
 
 \section{Coping with the Mode}\label{sec:mode}
-Following \cite{wilcox1973indices} we can regard the PMF entropy (and its conditional average) as used by Algorithm \ref{alg:bnta}, as a particular example of index of \emph{qualitative variation} (IQV).
+Following \cite{wilcox1973indices} we can regard the PMF entropy (and its conditional version) used by Algorithm \ref{alg:bnta} as an example of index of \emph{qualitative variation} (IQV).
 An IQV is just a normalized number that takes value zero for degenerate PMFs, one on uniform ones, being independent on the number of possible states (and samples in case of empirical models).
-The closer to uniform is the PMF the higher is the index and vice versa.
-In order to bypass the computational issues related to its application with CNs and the explainability limits in the general case, we want to consder alternative IQVs to replace entropy in Algorithm \ref{alg:bnta}.
-Wilkox's \emph{deviation from the mode} appears as a natural choice.
+The closer to uniform is the PMF, the higher is the index and vice versa.
+
+In order to bypass the computational issues related to its application with CNs and the explainability limits in the general case, here we consder alternative IQVs to replace entropy in Algorithm \ref{alg:bnta}.
+Wilkox's \emph{deviation from the mode} (DM) appears as a natural choice.
 For a given PMF $P(X)$, this corresponds to:
-\begin{equation}DFM_P:=\sum_{x\in\mathcal{X}} \frac{P(x) - \max_{x'\in\mathcal{X}} P(x')}{|\mathcal{X}|}\,.
+\begin{equation}
+M(X):=1-\sum_{x\in\mathcal{X}} \frac{\max_{x'\in\mathcal{X}} P(x') - P(x)}{|\mathcal{X}|-1}\,.
 \end{equation}
-This might be identified with the \emph{modal} value of the PMF.
-It is a trivial exercise to check that this is a proper IQV, with the same qualitative behaviour of the entropy (e.g., see Figure X).
-From an explainability perspective, compared to entropy, the DFM has a more direct interpretation.
-From the point of view of computation, in both the marginal and the conditional case, both the entropy and the DFM can be trivially obtained for the probabilities of the singletons.
-The situation is different when coping with CSs.
-Entropy require optimization such as those discussed in the previous section, while DFM is simply based on the upper probabilities of the singletons $\{\overline{P}(x)\}_{x\in\mathcal{X}}$.
+It is a trivial exercise to check that this is a proper IQV, with the same unimodal behaviour of the entropy.
+Concerning explainability, being a linear function of the modal probability, the numerical value of the DM offers a more transparent interpretation than the entropy.
+From a computational point of view, for both marginal and unconditional PMFs, both the entropy and DM can be directly obtained from the probabilities of the singletons.
 
-Consider a PMF $P(X)$. Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$. Let $\mathcal{P}$
-denote the set of all PMFs with the same $p^*:=P(x^*)$. The most entropic PMF in 
-$\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq x^*$ where 
-$m:=|\mathcal{X}|$. While the least entropic is the one with a 
-$x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the other masses 
-equal to zero. These two bounds on the entropy are therefore:
-\begin{eqnarray}
-\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m \frac{1-p^*}{m-1}\,,\\
-\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m (1-p^*)\,.
-\end{eqnarray}
-This:
+The situation is different when computing the bounds of these quantities with respect to a CS.
+The bounds of $M(X)$ are obtained from the upper and lower probabilities of the singletons by simple algebra, i.e,
 \begin{equation}
-\overline{h}-\underline{h}=(1-p^*) \log_m (m-1)\,,
+\overline{M}(X):=
+\max_{P(X)\in K(X)} M(X):=\frac{|\mathcal{X}|-\max_{x'\in\mathcal{X}} \overline{P}(x')}{|\mathcal{X}|-1}\,.
 \end{equation}
-The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as 
-soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being 
-zero for binary variables.
+and analogously with the upper probabilities for $\overline{M}(X)$.
+Maximizing entropy requires instead a non-trivial, but convex, optimization.
+See for instance \cite{abellan2003maximum} for an iterative procedure to find such maximum when coping with CSs defined by probability intervals.
+The situation is even more critical for the minimization, that has been proved to be NP-hard in \cite{xiang2006estimating}.
 
-For expected DFM, the situation is more complicated as outlined by the following result.
+The optimization becomes even more challenging for conditional entropies there are roughly mixtures with imprecise weights.
+Accordingly, in \cite{mangili2017b}, only inner approximation for the upper bound have been derived.
+The situation is different for conditional DMs.
+Let us discuss this case in a simplified setup that will be later extended.
 
-\begin{theorem}
-Consider a CN with a single skill $S$ and a single question $Q$, that is a child of $S$.
+\begin{theorem}\label{th:dm}
+Under the setup of Section \ref{sec:bncat}, consider a CN with a single skill $S$ and a single question $Q$, that is a child of $S$.
+Let $K(S)$ and $K(Q|S)$ be the CCPTs of such CN.
+Let also $\mathcal{Q}=\{q^1,\ldots,q^n\}$ and $\mathcal{S}=\{s^1,\ldots,s^n\}$.
+The upper conditional DM, i.e.,
+\begin{equation}\label{eq:upperM}
+\overline{M}(S|Q):=\max_{\substack{P(S)\in K(S)\\P(Q|S)\in K(Q|S)}} \sum_{i=1,\ldots,n} \left[ \max_{j=1,\ldots,m} P(s_j|q_i) \right] P(q_i)\,,
+\end{equation}
+is such that:
+\begin{equation}\label{eq:upperM2}
+\overline{M}(S|Q):=\max_{\substack{\hat{j}_i=1,\ldots,m\\i=1,\ldots,n}} \Omega(\hat{j}_1,\ldots,\hat{j}_n)
+%\overline{M}(S|Q):=\max_{\substack{i=1,\ldots,n\\j=1,\ldots,m}} \omega_{ij}
+\end{equation}
+where $\Omega(\hat{j}_1,\ldots,\hat{j}_n)$ is the solution of the following linear programming task:
 
+\begin{alignat}{3}
+\max && \sum_j x_{ij}&&&\nonumber\\
+\text{s.t.}\qquad&&\sum_{ij} x_{ij}&=1&& \label{c1}\\
+&&x_{ij}&\geq 0&&\qquad \forall i,j \label{c2}\\
+&&\sum_{i} x_{ij}&\geq \underline{P}(s_j)&&\qquad \forall j \label{c4}\\
+&&\sum_{i} x_{ij}&\leq \underline{P}(s_j)&&\qquad \forall j \label{c5}\\
+&&\underline{P}(q_i|s_j) \sum_{i} x_{ij}&\leq x_{ij}&&\qquad \forall i,j \label{c6}\\
+&&\overline{P}(q_i|s_j) \sum_{i} x_{ij}&\geq x_{ij}&&\qquad \forall i,j
+\label{c7}\\
+&&x_{i\hat{j}_i}&\geq x_{ij}&&\qquad \forall i,j \label{c3}
+\end{alignat}
+where the bounds on the sums over the indexes and on the universal quantifiers.
+are omitted for the sake of brevity, 
+\begin{proof}
+Equation \eqref{eq:upperM} rewrites as:
+\begin{equation}\label{eq:firstopt}
+\overline{M}(S|Q)
+=\max_{\substack{P(S)\in K(S)\\P(Q|S)\in K(Q|S)}} \sum_{i=1}^n \left[ \max_{j=1,\ldots,m} P(s_j)P(q_i|s_j) \right]\,.
+\end{equation}
+Let us define the variables of such constrained optimization task as:
 \begin{equation}
-\max_{\substack{P(S)\in K(S)\\P(Q|S)\in K(Q|S)}} \sum_{q\in\mathcal{Q}} \left[ \max_{s\in\mathcal{S}} P(s|q) \right] P(q)
-=\max_{\substack{P(S)\in K(S)\\P(Q|S)\in K(Q|S)}} \sum_q \left[ \max_{s\in\mathcal{S}} P(s)P(q|s) \right] 
+x_{ij}:=P(s_j)P(q_i|s_j)\,.
 \end{equation}
-Let $\mathcal{S}:=\{s^1,\ldots,s^m\}$ and
-$\mathcal{Q}:=\{q^1,\ldots,q^k\}$.
-Let us make explicit the optimization variables of the task in Equation X as follows. 
-for each $i=1,\ldots,m$, $p_i:=P(S=s^i)$.
-For each $j=1,\ldots,k$, $\pi_{ji}:=P(q^j|s^i)$. Equation X rewrites as:
+for each $i=1,\ldots,n$ and $j=1,\ldots,m$.
+Let us show how the CCPT constraints can be easily reformulated with respect to such new variables by simply noticing that $x_{ij}=P(s_j,q_i)$, and hence $P(s_i)=\sum_i x_{ij}$ and $P(q_j|s_i)=x_{ij}/(\sum_{k} x_{kj})$.
+Consequently, the interval constraints on $P(S)$ corresponds to the linear constraints in Equations \eqref{c4} and \eqref{c5}.
+Similarly, for $P(Q|S)$, we obtain:
+\begin{equation}\label{eq:fract}
+\underline{P}(q_i|s_j) \leq \frac{x_{ij}}{\sum_k x_{kj}} \leq \overline{P}(q_i|s_j)\,,
+\end{equation}
+that easily gives the linear constraints in Equations \eqref{c6} and \eqref{c7}.
+Finally the non-negativity of the probabilities corresponds to Equation \eqref{c2}, while Equation \eqref{c1} gives the normalization of $P(S)$, while the normalization of $P(Q|S)$ is automatically satisfied.
+
+Equation \eqref{eq:firstopt} rewrites therefore as:
+\begin{equation}\label{eq:lastopt}
+\overline{M}(S|Q)
+=\max_{ \{v_{ij}\}_{ij} \in \Gamma} \sum_{i} \max_{j} x_{ij} \,,
+\end{equation}
+where $\Gamma$ denotes the linear constraints in Equations \eqref{c1}-\eqref{c7}. If we set:
 \begin{equation}
-\max_{\substack{\{p_i\} \in K(S)\\ ss}} \sum_{j=1,\ldots,k} \max_{i=1,\ldots,m} p_i \pi_{ji} 
+\hat{j}_i:= \arg \max x_{ij}\,,
 \end{equation}
-We introduce the variables $v_{ij}:=p_i \pi_{ji}$.
-The normalization constraint $\sum_i p_i=1$ becomes $\sum_{ij} v_{ij}=1$, regarding the constraints on $K(S)$, $\underline{P}(s_i) \leq p_i \leq \overline{P}(s_i)$, the becomes:
-$$\underline{P} \pi_{ji} \leq v_{ij} \leq \overline{P} \pi$$
-The objective function can be rewritten as $\sum_{j=1}^q v_{ij}$
-to be considered for each xxx.
-The inner maximization can be achieved 
+Equation \eqref{eq:lastopt} rewrites as:
+\begin{equation}\label{eq:lastopt2}
+\overline{M}(S|Q)
+=\max_{ \{v_{ij}\}_{ij} \in \Gamma'} \sum_{i} x_{i\hat{j}_i} \,,
+\end{equation}
+where $\Gamma'$ are the constraints in $\Gamma$ with the additional (linear) constraints in Equation \eqref{c3}.
+
+Yet, the optimization in the right-hand side of Equation \eqref{eq:lastopt2} is not a linear pragramming task, as the values of the indexes $\hat{j}_i$ cannot be decided in advance being potentially different for different assigments of the optimization variables consistent with the constraints in $\Gamma$.
+Yet, we might address such optimization as a brute-force task with respect to all the possible assignation of the optimal indexes $\hat{j}_i$.
+This is exactly what is done by Equation \eqref{eq:upperM2} where all the $m^n$ possible assignations are considered.
+This proves the thesis.
+\qed
+\end{proof}
 \end{theorem}
 
-*** sistemare *** Three possible scores metter probability of true the variation ratio ($1-\max_q(P(q))$) or the M1 Gibb's index 	also known as coefficient of unalikeability and somehow related to the variance (it is 	the variance in the binary case): $M1 = 1-\sum_q P(q)^2$, or even the entropy, which is 	not so difficult to compute for $P(Q)$.
-They are all equivalent in the binary case, as they are all monotonic function of $\max_q(P(q))$ only.
-$\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|$
-*** distinguishing between templates and questions ***
+An analogous result with the linear programming tasks minimizing the same objective functions with exactly the same constraints allows to compute $\underline{M}(S|Q)$. 
+The overall complexity is clearly $O(m^n)$ with $n:=|\mathcal{Q}|$.
+This means linear complexity for any test where only the difference between a wrong and a right answer is considered from an elicitation perspective.
+Extending the result to the case of multiple answers is trivial by means of the results in \cite{antonucci2009}, that allows to merge multiple observed children of a single node into a single one.
+Finally, the case of multiple skills might be similarly considered by using the marginal bounds of probabilities for the single skills in Equations \eqref{c4} and \eqref{c5}.
 
-\section{Explainability and Parametrization}
-As a first, demonstrative, example of our ideas consider a model characterized by a single (Boolean) Skill $S$ and a set of questions $\bm{Q}$ picked from a set of templates.
-Let us first focus on a Bayesian, i.e., precise, case.
-The prior specification $P(S)$ is achieve by a single parameter $p \in [0,1]$ such that $P(S=1)=p$.
-For a generic question $Q$, which is also assumed to be Boolean, a complete specification of the CPT $P(Q|S)$ is obtained by the two parameters $p_0,p_1\in [0,1]$ where $P(Q=1|S=0)=p_0$ and $P(Q=1|S=1)=p_1$.
-In other wrods $p_0$ denote the probability of providing a right answer to the question for a student who does not have the considered skill and $p_1$ for a student who have that skill.
-An obvious constraint is $p_1>p_0$, i.e., having the skill makes your probability of providing a right answer higher.
-The inequality should be strict, otherwise the two probabilities are equal, and this means that the answer is irrelevant for the skill.
-Although parameters $p_1$ and $p_0$ already give a complete parametrization, we perform the linear transformation
-$\lambda:=1-\frac{1}{2}(p_0+p_1)$ and $\delta=(p_1-p_0)$.
+\section{Experiments}\label{sec:exp}
+In this section we validate the ideas outlined in the previous section in order to check whether or not the DM can be used as a sensible alternative to information-theoretic scores such as the entropy in practical TAs.
+In the BN context, this is simply achieved by computing the necessary updated probabilities, while Theorem \ref{th:dm} is used instead for CNs.
+
+\subsection{Single-Skill Experiments on Synthetic Data}
+For a very first validation of our approach, we consider a simple setup made of a single skill $S$ and a repository with 18 Boolean questions based on nine different parametrizations (two questions for parametrization).
+In the BN, the CPT of a question can be parametrized by two numbers.
+E.g., in the example in Figure \ref{fig:minicat}, we used the probabilities of correctly answering the question given that the skill is present or not, i.e., $P(Q=1|S=1)$ and $P(Q=1|S=0)$.
+A more interpretable parametrization can be obtained as follows:
+\begin{eqnarray}
+\delta &:=& 1-\frac{1}{2}[P(Q=1|S=1)+P(Q=1|S=0)]\,,\\
+\kappa &:=& P(Q=1|S=1)-P(Q=1|S=0)\,.
+\end{eqnarray}
+Note that $P(Q=1|S=1)>P(Q=1|S=0)$ is an obvious rationality constraint for questions, otherwise having the skill would make less likely to answer properly to a question.
+Both parameters are therefore non-negative.
+Parameter $\delta$, corresponding to the (arithmetic) average of the probability for a wrong answer over the different skill values, can be regarded as a normalized index of the question \emph{difficulty}.
+E.g., in Figure \ref{fig:minicat}, $Q_1$ ($\delta=0.4$) is less difficult than $Q_2$ ($\delta=0.5$).
+Parameter $\kappa$ can be instead regarded as a descriptor of the difference of the conditional PMFs associated with the different skill values.
+In the most extreme case $\kappa=1$, the CPT $P(Q|S)$ is diagonal implementing an identity mapping between the skill and the question.
+We therefore regard $\kappa$ as a indicator of the discriminative power of the question.
+In our tests, for the BN quantifications, we consider the nine possible parametrizations corresponding to $(\delta,\gamma) \in [0.4,0.5,0.6]^2$.
+For $P(S)$ we use instead a uniform quantification.
+For the CN approach we perturb all the BN parameters with $\epsilon=\pm 0.05$, thus obtaining a CN quantification.
+A group of 1024 simulated students, half of them having $S=0$ and half with $S=1$ is used for simulations.
+The student answers are sampled from the CPT of the asked question on the basis of the student profile.
+Figure X depicts the accuracy of the BN and CN approaches based on both the entropy and the DM scores, while the Brier score is instead depicted on the left.
+As baseline, we use the results obtained by randomly picking the questions.
+As expexted the adaptive aproaches outperform the non-adaptive random approach and, notably, the differences between the two scores seems to be minimal.
+A closer view can be achieve by considering the Brier score, with the xxx.
+
+%$\lambda:=1-\frac{1}{2}(p_0+p_1)$ and $\delta=(p_1-p_0)$.
 The first quantity is the arithmetic average of giving a wrong answer and we might indent it as the \emph{level} of the question, this mining that the higher is $\lambda$ the more unlikely is to receive a correct answer is the students have the same probability of having and not having the skill.
 Regarding $\delta$ we might intend it as the (average) discriminative power of a question.
-Note that the inverse relations give $p_1=1-\lambda+\frac{\delta}{2}$
-and $p_0=1-\lambda-\frac{\delta}{2}$. Where constraint $p_1>p_0$ is just $\delta>0$ and any other value in $[0,1]$ for both parameters is valid.
-In our toy example, we consider nine possible templates, made of triads of templates with the same $\delta$ and same $\lambda$. The reference values $[0.4,0.5,0.6]$ are used.
+%Note that the inverse relations give $p_1=1-\lambda+\frac{\delta}{2}$
+%and $p_0=1-\lambda-\frac{\delta}{2}$. Where constraint $p_1>p_0$ is just $\delta>0$ and any other value in $[0,1]$ for both parameters is valid.
 
-\section{Experiments}\label{sec:exp}
-In this section we validate.
-\subsection{Single-Skill Experiments on Synthetic Data}
-For a very first validation of our approach, we consider a simple setup made of a single skill $S$ and nine different templates for the questions.
-The values in the two parameters are xxx in Table X.
+%The values in the two parameters are xxx in Table X.
 In the Bayesian case we set $P(S=1)=.5$.
@@
 As stopping rule a threshold on the entropy is set.
+%This result allows to apply DM to adaptive TA with both BNs
+%*** distinguishing between templates and questions ***
+
+%This makes especially critical the evaluation of the bounds of the entropy.
+As entropy is a convec function, upper entropy might be found, while the minimization has been proved to be NP-hard by Klir and fast techniques are only available for specific families of CSs.
+The optimization becomes even more challenging for expected entropies there are roughly mixtures with imprecise weights.
+Accordingly, in \cite{mangili2017b}, only special cases based on an inner approximation have been derived.
+%for each $i,j$. Note that in this case normalization is automatically satisfied and this linear fractional constraint can be 
+%\begin{equation}\label{eq:boundsPS}
+%\underline{P}(s_j) \leq \sum_i x_{ij} \leq \overline{P}(s_j)\,, 
+%\end{equation}
+%for each $j$. Normalization of $P(S)$ is therefore:
+%\begin{equation}\label{eq:normal}
+%\sum_{ij} x_{ij} = 1\,.
+%\end{equation}
+%Regarding the constraints on $P(Q|S)$: for each $i,j$.
+Note that in this case normalization is automatically satisfied and this linear fractional constraint can be easily translated into a linear one.
+Finally, the non-negativity of $P(q_i)$ and $P(s_j|q_i)$ corresponds to the non-negativity of $v_{ij}$.
+%:boundsPS} and \eqref{eq:normal} together with the linearized version of Equation \eqref{eq:fract} and the non-negativity.
+
+%As a first, demonstrative, example of our ideas consider a model characterized by a single (Boolean) Skill $S$ and a set of questions $\bm{Q}$ picked from a set of templates.
+Let us first focus on a Bayesian, i.e., precise, case.
+The prior specification $P(S)$ is achieve by a single parameter $p \in [0,1]$ such that $P(S=1)=p$.
+For a generic question $Q$, which is also assumed to be Boolean, a complete specification of the CPT $P(Q|S)$ is obtained by the two parameters $p_0,p_1\in [0,1]$ where $P(Q=1|S=0)=p_0$ and $P(Q=1|S=1)=p_1$.
+%Consider a PMF $P(X)$. Let $x^*:=\arg\max_{x\in\mathcal{X}} P(x)$. Let %$\mathcal{P}$
+%denote the set of all PMFs with the same $p^*:=P(x^*)$. The most entropic %PMF in 
+%$\mathcal{P}$ is the one with  $P(x)=\frac{1-p^*}{m-1}$ for each $x\neq %x^*$ where 
+%$m:=|\mathcal{X}|$. While the least entropic is the one with a 
+%$x'\in\mathcal{X}\setminus\{x^*\}$ such that $P(x')=1-p^*$ and all the %other masses 
+%equal to zero. These two bounds on the entropy are therefore:
+%\begin{eqnarray}
+%\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m \frac{1-p^*}{m-1}\,,\\
+%\overline{h}&:=& -p^* \log_m p^* - (1-p^*) \log_m (1-p^*)\,.
+%\end{eqnarray}
+%This:
+%\begin{equation}
+%\overline{h}-\underline{h}=(1-p^*) \log_m (m-1)\,,
+%\end{equation}
+%The maximum gap between the entropies of the PMFs in $\mathcal{P}$ decreases as 
+%soon as $p^*$ increases and as soon as the number of states of $X$ decreases, being 
+%zero for binary variables.
 
@@
 \input{acc.tex}
-\hspace{0.9cm}
-\caption{Aggregated cumulative costs and bounds.}
-\label{fig:sx2}
+\input{brier.tex}
+\caption{Aggregated Accuracy (left) and Brier score (right) for a single-skill TA}
+\label{fig:mono}
 \end{figure}
+\subsection{Multi-Skill Experiments on Real Data}
+For a validation on real data, we consider data about online German language placement (see also \cite{mangili2017b}).
+Four different Boolean skills associated with different abilities (vocabulary, communication, listening and reading) are considered and modeled by a chain-shaped graph, for which BN and CN quantification are already available.
+Experiments have been achieved by means of the CREMA library for credal networks \cite{huber2020a}.\footnote{github.com/IDSIA/crema} The Java code used for the modelling and the simulations is available together with the Python scripts used to analyze the results.\footnote{github.com/IDSIA/adaptive-tests}.
+Results are depicted with the same spirit of those in Section X in Figure xxx.
+Notably, even with multiple skills, we obtain similar results xxx.
 
@@
 \centering
+\input{acc.tex}
 \input{brier.tex}
-\caption{Aggregated cumulative costs and bounds.}
-\label{fig:sx}
+\caption{Aggregated Accuracy (left) and Brier score (right) for a multi-skill TA}
+\label{fig:multi}
 \end{figure}
 
-\subsection{Multi-Skill Experiments on Real Data}
-For a validation on real data, we consider data xxx.
-Before the academic year begins, the students of the University of Applied Sciences and Arts of Southern Switzerland (SUPSI) are asked to take an online German language placement test with 95 questions.
-In years 2015 and 2016, the answers of 451 students to all the questions have been collected.
-
-\paragraph{Model elicitation.}
-Four skills are assessed: \textit{W\"ortschatz} ($X_1$, vocabulary), 
-\textit{Kommunikation} ($X_2$, communication), \textit{H\"oren} ($X_3$, listening), and \textit{Lesen} ($X_4$, reading). For each skill the student is assigned to a knowledge 
-	level compliant with EU 
-	guidelines.\footnote{\url{http://www.coe.int/t/dg4/linguistic/Source/Framework_EN.pdf}.}
-	Levels A1, A2, B1, and B2 are considered, and skills are therefore modeled as 
-	quaternary variables.
-	Teachers associate each question with a single skill, which is set as the unique 
-	background skill of the question. The number of questions associated with 
-	$X_1$/$X_2$/$X_3$/$X_4$ is 26/24/30/15. The current evaluation method assigns 
-	levels by setting thresholds on the percentage $\gamma$ of correct answers on each 
-	skill (A1 if  $\gamma < 35\%$, A2 up to $55\%$, B1 up to $75\%$).\footnote{These data 
-	as well as the software used for the simulations are freely available at 
-	\url{http://ipg.idsia.ch/software.php?id=138}.}
-
-	We first elicit from the teachers the structure of the BN/CN graph over the skills. The 
-	result is a chain, which is augmented by leaf nodes modeling the questions, each 
-	having its background skill as single parent. Overall, a tree-shaped topology as in 
-	Fig.~\ref{fig:fourskills} is obtained. This makes exact inference in the BN fast, while in 
-	the CN a variable elimination might be slow (a minute for query in our setup). A faster 
-	approximate CN algorithm is therefore used \cite{antonucci2014e}.
-
-	\begin{figure}[htp!]
-		\centering
-		\begin{tikzpicture}%[scale=.8]
-			\node[]  at (-0.25,0)  (w)  {$X_1$};
-			\node[]  at (3,0) 		 (k)   {$X_2$};
-			\node[]  at (6.5,0) 	(h)   {$X_3$};
-			\node[]  at (9.25,0)   (l)    {$X_4$};
-			\draw[] (w) -- (k);
-			\draw[] (k) -- (h);
-			\draw[] (h) -- (l);
-			\node[]  at (-0.25,-1)(f1) {$Y_1$};
-			\node[]  at (1.5,-1) 	 (f2) {$Y_2$};
-			\node[]  at (3,-1) 	 (f3) {$Y_3$};
-			\node[]  at (4.5,-1) 	(f4) {$Y_4$};
-			\node[]  at (6.5,-1)	(f5) {$Y_5$};
-			\node[]  at (8.5,-1)   (f6) {$Y_6$};
-			\node[]  at (10,-1)  	(f7)  {$Y_7$};
-			\draw[] (w) -- (f1);
-			\draw[] (k) -- (f2);
-			\draw[] (k) -- (f3);
-			\draw[] (k) -- (f4);
-			\draw[] (h) -- (f5);
-			\draw[] (l) -- (f6);
-			\draw[] (l) -- (f7);
-		\end{tikzpicture}
-		\caption{A directed graph for CAT\label{fig:fourskills}.}
-	\end{figure}
-	\vspace{-5mm}
-
-	Teachers report their knowledge about the unconditional states of $X_1$ and the 
-	conditional states of $X_i$ given $X_{i-1}$, for $i=2,3,4$, as qualitative judgments (top 
-	of Tab.~\ref{tb:CPTs}). 
-	To simplify the elicitation, the probabilities $P(X_i|X_{i-1})$ are given the same verbal 
-	judgment for all $i=2,3,4$. A more detailed model could provide more accurate 
-	evaluations but it would be very hard for the domain expert to elicit it in a reliable way. 
-	Also, questions are divided by the teachers in three groups, corresponding to different 
-	difficulty levels. Questions in the same group are quantified in the same way, 
-	irrespective of their background skill, giving the judgments reported in the bottom part 
-	of Tab.~\ref{tb:CPTs}.
-
-	{\small \begin{table*}[htp!] 
-			\renewcommand{\arraystretch}{1.2}
-			\centering
-			{%\footnotesize
-				\begin{tabular}{@{}lc@{}}
-					\toprule
-					$X_1$&$P(X_1)$\\
-					\midrule
-					A1&\emph{improbable}\\
-					A2&\emph{uncertain}\\
-					B1&\emph{uncertain}\\
-					B2&\emph{improbable}\\
-					\bottomrule
-				\end{tabular}
-				\quad
-				\begin{tabular}{@{}lcccc@{}}
-					\toprule	
-					$P(X_i|X_{i-1})$&\phantom{.}$X_{i-1}=\mathrm{A1}$\phantom{.}&\phantom{.}$X_{i-1}=\mathrm{A2}$\phantom{.}&\phantom{.}$X_{i-1}=\mathrm{B1}$\phantom{.}&\phantom{.}$X_{i-1}=\mathrm{B2}$\phantom{.}\\
-					\midrule
-					$X_i$=A1&\emph{fifty-fifty}&\emph{uncertain}&\emph{improbable}&\emph{impossible}\\
-					$X_i$=A2&\emph{uncertain}&\emph{fifty-fifty}&\emph{uncertain}&\emph{improbable}\\
-					$X_i$=B1&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}&\emph{uncertain}\\
-					$X_i$=B2&\emph{impossible}&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}\\
-					\bottomrule
-			\end{tabular}}
-			\vskip 2mm
-			\begin{tabular}{@{}lcccc@{}}\toprule
-				$P(Y=T|X)$\phantom{aa}&\phantom{a}$X=\mathrm{A1}$\phantom{a}&\phantom{a}$X=\mathrm{A2}$\phantom{a}&\phantom{a}$X=\mathrm{B1}$\phantom{a}&\phantom{a}$X=\mathrm{B2}$\phantom{a}\\
-				\midrule
-				Easy&\emph{uncertain}&\emph{fifty-fifty}&\emph{expected}&\emph{probable}\\
-				Medium&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}& 
-				\emph{expected}\\
-				Difficult&\emph{impossible}&\emph{improbable}&\emph{uncertain}& 
-				\emph{fifty-fifty}\\
-				\bottomrule
-			\end{tabular}
-			\vskip 2mm
-			\caption{Expert judgements.}\label{tb:CPTs}
-	\end{table*}}
-	%\vspace{-10mm}
-	For the CN, those judgements are translated in interval constraints for the 
-	corresponding events on the basis of the verbal-numerical scale in Tab.~\ref{tb:labels}. 
-	Different probability intervals are considered for skills and questions as they refer to 
-	events of different type. For instance, when the expert considers ``\emph{impossible}'' 
-	for an A1 level student to know the answer to a difficult question, the student is 
-	assigned a probability between .175 and .2 of answering correctly, as the questions 
-	offer only four choices plus the option of giving no answer. 
-	Notice that, by doing so, we are not anymore assuming that all questions in the same 
-	difficulty group share exactly the same conditional PMFs (as done by the BN model), as 
-	PMFs of different questions can vary independently in the given intervals. This seems a 
-	more sensible assumption than that of the precise model.
-	For the BN, the PMFs corresponding to the centers of mass of the CSs defining the CN 
-	are used. Numerical inferences in the BN are consequently included in the intervals 
-	computed with the CN.
-
-	{\small
-		\begin{table*}[htp!] 
-			\renewcommand{\arraystretch}{1.2}
-			\centering
-			\begin{tabular}{@{}lcccccc@{}}
-				\toprule
-				Judgement&\emph{impossible}&\emph{improbable}&\emph{uncertain}&\emph{fifty-fifty}&\emph{expected}&\emph{probable}\\
-				\midrule
-				Skills&$1$-$10\%$&$10$-$20\%$&$20$-$40\%$&$30$-$50\%$&-&-\\
-				Questions&$17.5$-$20\%$&$22.5$-$25\%$&$30$-$35\%$&$60$-$65\%$&$75$-$80\%$&
-				 $95$-$97.5\%$\\
-				\bottomrule
-			\end{tabular}
-			\caption{A verbal-numerical scale for probability-intervals 
-			elicitation.}\label{tb:labels}
-	\end{table*}}
-
-	\paragraph{Experimental results.} 
-	%Acronyms BN-NA, CN-NA, BN-AD, CN-AD denote 
-	BN and CN methods in their non-adaptive (NA) and adaptive (AD) versions are 
-	considered. \emph{Accuracy}, i.e., the proportion of students to whom the test assigns 
-	the same level of the current evaluation method, describes BN performances. This 
-	measure cannot be used for the set-valued outputs of CN methods. In this case the 
-	$u_{65}$ measure can provide a comparison with the accuracy 
-	\cite{zaffalon2012evaluating}. If $\mathcal{L}$ is the set of levels assigned by the CN 
-	on a skill and $L$ its cardinality, a \emph{discounted} accuracy gives $1/L$ if 
-	$\mathcal{L}$ includes the true level and zero otherwise. The $u_{65}$ is a concave 
-	reinforcement of this score based on risk-adverse arguments. Its underlying 
-	assumption is that acknowledging the indecision between more levels has larger utility 
-	than randomly choosing one of them (e.g., the teacher could set up further 
-	assessments in the undecided cases). Tab.~\ref{tb:nonAdaptiveResults} shows the NA 
-	comparison. In Fig.~\ref{fig:plots} (left), the BN-NA accuracy is separately evaluated on 
-	the determinate (light bars) and indeterminate (dark bars) instances, i.e. those for 
-	which, respectively, a single level or multiple levels are returned by the CN model. On 
-	average, CN-NA returns single levels in $37.25\%$ of the cases and, if this is not the 
-	case, an average of $2.36$ levels ($3.22$ with interval dominance) are returned.
-
-	\begin{table*}[htp!]
-		\centering
-		\begin{tabular}{@{}lccccc@{}}\toprule
-			Algorithm&\phantom{aa}Average\phantom{aa}&\phantom{aaa}$X_1$\phantom{aaa}&\phantom{aaa}$X_2$\phantom{aaa}&
-			 \phantom{aaa}$X_3$\phantom{aaa}&\phantom{aaa}$X_4$\phantom{aaa}\\
-			\midrule
-			BN-NA (acc)&$63.09\%$&$	67.56	\%$&$60.85\%$&${	75.84	
-			\%}$&$48.10\%$\\
-			CN-NA ($u_{65}$)& ${65.37\%}$&$67.71\%$&${66.67\%}$&$	
-			70.33\%$&${56.76\%}$\\
-			\bottomrule
-		\end{tabular}
-		\caption{Non-adaptive tests results.}\label{tb:nonAdaptiveResults}
-	\end{table*}
-
-	In the AD case we also track the average number of asked questions. Results are in 
-	Fig.~\ref{fig:plots} (right). CN-AD (circles) is tested for different thresholds over the 
-	entropy (labels of the markers) against a version of BN-AD based on the joint entropy 
-	(triangles). Similar values are obtained by coping with marginal entropies. We also allow 
-	the BN-AD method to return multiple levels by maximizing the expected $u_{65}$ utility 
-	over any possible set of levels. This variant is called BN-AD' and the corresponding 
-	$u_{65}$ measure is reported  (squares).
-
-	\begin{figure}[htp!]
-		\centering
-		\begin{tikzpicture}
-			\begin{axis}[width=4cm,height=3.5cm,ybar=0,bar width=7pt,ylabel={\small acc}, 
-			xlabel={Skills},xtick=data,ytick={0,25,50,75,100},ymin=0,ymax=100,yticklabels={0,.25,.50,.75,1},symbolic
-			 x coords={$X_1$,$X_2$,$X_3$,$X_4$}, y label style={at={(axis description 
-			cs:0.3,.5)},anchor=south},xtick align=inside, legend 
-			style={at={(1,1)},anchor=south east},legend style={draw=none}]
-				\addplot[fill=black!10] coordinates 
-				{($X_1$,85.42)($X_2$,87.06)($X_3$,89.51)($X_4$,56.34)}; 
-				\addlegendentry{\tiny{determinate}} 
-				\addplot[fill=black!70] coordinates 
-				{($X_1$,54.51)($X_2$,45.13)($X_3$,67.72)($X_4$,44.26)};
-				\addlegendentry{\tiny{indeterminate}}
-			\end{axis}
-		\end{tikzpicture}
-		\begin{tikzpicture}
-			\begin{axis}[width=7.5cm,height=4cm,ylabel={\small 
-			acc/$u_{65}$},xlabel={Number of questions},xmin=35, xmax=100,ymin=50, 
-			ymax=70, xtick={40,50,60,70,80,90}, ytick={50,55,60,65},legend 
-			style={at={(1,0)},anchor=south east},ymajorgrids=true,xmajorgrids=true,  y label 
-			style={at={(axis description cs:0.13,.5)},anchor=south},legend style={draw=none}]
-				\addplot[black,thick,mark=triangle,mark options={fill=black}, visualization 
-				depends on=\thisrow{alignment} \as \alignment, nodes near coords, point 
-				meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}] 
-				table [meta index=2 ] {
-					x y label alignment
-					40.36	51.51 .7 0
-					49.84	55.43 .65 -20
-					58.34	57.49 .6 80
-					66.50 59.45 .55 80
-					79.43	62.75 .45 80
-					89.04	63.14 .3 80
-					95  63.09     0  160
-				};
-				\addlegendentry{\tiny{BN-AD}}
-				\addplot[magenta,thick,mark=square,mark options={fill=black}, visualization 
-				depends on=\thisrow{alignment} \as \alignment, nodes near coords, point 
-				meta=explicit symbolic,  every node near coord/.style={anchor=\alignment}] 
-				table [meta index=2 ] {
-					x y label alignment
-					40.36	59.9 .7 -20
-					49.84	61.00 .65 -40
-					58.34	60.86 .6 50
-					66.50 60.34 .55 -30
-					79.43	64.90 .45 -80
-					89.04	66.3 .3 -80
-					95  66.22     0  -160
-				};
-				\addlegendentry{\tiny{BN-AD'}}
-				\addplot[dashed,blue,thick,mark=o,mark options={solid,fill=white},
-				visualization depends on=\thisrow{alignment} \as \alignment,
-				nodes near coords, % Place nodes near each coordinate
-				point meta=explicit symbolic, % The meta data used in the nodes is not 
-				%explicitly provided and not numeric
-				every node near coord/.style={anchor=\alignment} ] table [meta index=2 ] {
-					x       y   label  alignment
-					42.45 58.27  .95   20
-					56.96 62.37  .925   -80
-					66.87 63.49   .9   -80
-					83.75 62.83  .8    -110
-					95   65.37   0  160
-				};
-				\addlegendentry{\tiny{CN-AD}}
-			\end{axis}
-		\end{tikzpicture}
-		\caption{Non-adaptive (left) and adaptive (right) tests performance.}\label{fig:plots}
-	\end{figure}
-
-	As a comment, CNs seem to identify hard-to-evaluate students as those for which 
-	multiple levels are provided. In fact, the agreement between the BN and the traditional 
-	tests is larger when the CN test is determinate. As a consequence, the CN $u_{65}$ 
-	measure is, on average, larger than the BN accuracy. 
-	A limitation of the CN test is the large fraction of indeterminate evaluations. One can 
-	interpret this result as a lack of robustness of the BN model, as even small variations in 
-	the model specifications can result in different decisions. Results also show that, both 
-	BN-AD and CN-AD approaches reduce the number of questions asked without 
-	significantly affecting the accuracy. BN-AD performances are improved by the ``credal'' 
-	variant BN-AD'. The results becomes very similar to those of the CN-AD. Yet, the latter 
-	method appears to be a more principled and suitable approach for a direct modeling of 
-	qualitative expert knowledge.
-
-	%does not require any, potentially questionable, imputation of the probabilistic ranges 
-	%provided by the experts.
-
-	%Yet, we regard theof BN-AD, we regard the CN approach as more principled and 
-	%suitable for a direct modeling of qualitative expert knowledge.
-
-	%uch a difference disappear if the credal-like variant BN-AD' is considered.
-	%However, the CN-AD procedure appears to be more effective, as the $u_{65}$ 
-	%accuracy measure decreases more slowly than the accuracies of BN-AD procedures.  
-	%Finally,comparing the two BN-AD approaches, one can see that the use of the local 
-	%instead of the joint entropy does not compromise the effectiveness of the adaptive 
-	%approach.
-
 \section{Outlooks and Conclusions}\label{sec:conc}
-A new approach to the xxx.
-
-%\footnote{Extension to non Boolean answers is trivial as all answers $Y_i$ are \emph{manifest} variables, and, thus, $Y_i$ can be always regarded as a binary variable with the two values denoting the observed answer $y_i$ and its negation \cite{antonucci2009}.}
-%We call \emph{background} of a question the set of skills ``required'' to answer it.
-This can be regarded as a conditional independence statement: given the background skills, the answer to the question is independent of the other skills and of the other questions.
-
-%\paragraph{Expert knowledge modeling.} For a reliable expert knowledge modeling, we use CSs induced by \emph{probability intervals}.
-Qualitative judgments about the probability of a state are converted in interval constraints such as $l\leq P(x) \leq u$, with the interval $[l,u]$ capturing the expert knowledge behind the judgment in a more reliable way than a sharp assessment.
-The CS consistent with these constraints is eventually obtained by standard polyhedral algorithms.
-Verbal to interval-numeric scales such as that Tab.~\ref{tb:labels} are used.
-For instance, if for the probability of the true state of the Boolean variable $Y$ the expert judgment is ``very likely'', the 	corresponding linear constraint is $.2 \leq P(Y=\textrm{true}) \leq .4$.
-
-%The task displays higher complexity than in the case of BNs (e.g., exact inference in non-binary singly-connected CNs is NP-hard \cite{maua14jair}), but approximate techniques can be considered when exact inference is unfeasible \cite{antonucci2014e}.
-
-%To compare the posterior intervals and decide the actual level of the student we might adopt the (conservative) \emph{interval dominance} criterion \cite{troffaes}, which rejects a level if its upper probability is smaller than the lower probability of some other level.
-Overlaps between intervals might therefore induce a situation of \emph{indecision} between two or more levels.
-This is a so-called \emph{credal} classification of the student level \cite{zaffalon2012evaluating}, and it represents the fact that students answers are somehow contradictory or not informative enough to provide a sharp decision.
-
-%This topic has been the subject of much discussion \cite{klir1999uncertainty}.
-A cautious approach \cite{abellan2003maximum} consists in taking the upper entropy $\overline{H}(\bm{X})$, i.e., the entropy of the most entropic PMF in the convex closure $\overline{K}(\bm{X})$ of  $K(\bm{X})$.
-In our framework, we should, then, look for maximum values of conditional entropies, such as $\overline{H}(X_i|Y',\bm{y})$ or $\overline{H}(X_i|\Pi_{X_i})$, as conditional  entropies are required to compute both: (i) the joint (unconditional) entropy $H(\bm{X})$ (and its posterior values); and (ii) the conditional entropies  involved in the  question selection in Eq.~\eqref{eq:expent}.By definition a conditional entropy is a convex combination (whose weights are the elements of a marginal PMF) of convex functions (the entropies).
-The objective function might, then, be non-convex, as the weights are also optimization variables.
-
-		Comment 4: The optimisation in the credal setting shouldn't be the following one?
-
-	$$\max_P [\max_s P(s,q=0)+\max_s P(s,q=1)]$$
-
-	$\P(s,q=0)$ and $P(s,q=1)$ are both functions of $p, \pi_0,$ and $\pi_1$ so I do not 
-	think we can split the optimization
-
-	$$\max_P \max_s P(s,q=0)+\max_P\max_s P(s,q=1)$$
-
-	However, it could be a reasonable approximation. Then, we can switch the optimization 
-	over $P$ and $s$ because they are both max, and obtain: 
-	$$\max_s \overline{P}(s)\overline{P}(q=0|s)+\max_s  \overline{P}(s)\overline{P}(q=1|s)$$.
-
-	If instead we are looking for the minimum over P, we cannot switch the optimization 
-	over $P$ and $s$:
-	$$\min_P \max_s P(s,q) \neq \max_s \min_P P(s,q)$$.
-
-	However I think we can split the optimization into 4 quadratic optimizations.
-	Let's use the following parametrization:
-%	\begin{multline}\label{eq:minimization}
-%		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
-%		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-%		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
-%		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
-%		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
-%	\end{multline}
-
-	Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It 
-	can be written as
-	$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
-	where
-
-%	\begin{multline}
-%		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
-%		\begin{array}{ll}
-%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
-%			~&\underline{x} \leq x\leq \overline{x}\\ 
-%		\end{array}
-%	\end{multline}
-	and 
-%	\begin{multline}
-%		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
-%		\begin{array}{ll}
-%			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
-%			~&\underline{x} \leq x\leq \overline{x}\\ 
-%		\end{array}
-%	\end{multline}
-
-	where the constraint $x = (\pi_0, \pi_1 ,p)$.
-
-	In general, let $N_s$ be the number of skill levels and $N_q$ the number of possible 
-	answers, then the number of quadratic optimizations to solve should be equal to 
-	$N_s\cdot N_q$.
-
-	In this two dimensional example, we might not need the approximation above as the 
-	minimization in \ref{eq:minimization} can be written as $\min_{i=1:4}(\tilde{P}_1)$, where
-
-%	\begin{multline}
-%		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
-%		\begin{array}{ll}
-%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
-%			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
-%			~&\underline{x} \leq x\leq \overline{x}\\ 
-%		\end{array}
-%	\end{multline}
-	and so on. However, in this case, the number of optimizations to solve should be 
-	$N_s^{N_q}$, that is, it grows exponentially with  $N_q$.
-
-	Then, to bypass this non-convex optimization task, we compute (i) by separately considering the entropies of each skill $X_i\in\bm{X}$.
-This is analogous to the marginal approach commonly considered in multi-label classification to minimize Hamming losses
-	\cite{antonucci2016c}. The issue (ii) is more challenging. We consider the following 
-	upper approximation of $\overline{H}(X_i|Y',\bm{y})$:
-	\begin{equation}
-		\overline{\overline{H}}(X_i|Y',\bm{y})=
-		\max_{P(y'|\bm{y})\in
-			\{\underline{P}(y'|\bm{y}),\overline{P}(y'|\bm{y})\}}
-		\sum_{y' \in \{\textrm{true},\textrm{false}\}}
-		\overline{H}(X_i|\bm{y},y') P(y'|\bm{y})\,,
-	\end{equation}
-	where the bounds of $P(y'|\bm{y})$ are obtained by standard CN updating algorithms.
-	The problem thus reduces to the computation of upper entropies as
-	\begin{equation}\label{eq:entropy}
-		\overline{H}(X_i|\bm{y}) := \sup_{P(X_i|\bm{y}) \in \overline{K}(X_i|\bm{y})} 
-		H(X_i|\bm{y})\,,
-	\end{equation}
-	where  $\overline{K}(X_i|\bm{y})$ is the posterior CS after conditioning on the observed 
-	answers $\bm{y}$.  If $\overline{K}(X_i|\bm{y})$ has a finite number of non-inner 
-	points, this is a linearly-constrained convex optimization whose solution typically 
-	corresponds to either the uniform PMF or a non-inner point on the frontier of 
-	$\overline{K}(X_i|\bm{y})$. A numerical solution can be easily found by a simple iterative 
-	approach in the special case of CS specified by probability intervals 
-	\cite{abellan2003maximum}. We have therefore computed the posterior lower and 
-	upper bounds of $P(X_i|\bm{y})$, and then maximized the entropy with respect to 
-	those bounds. % as in Eq.~\eqref{eq:entropy}. 
-	The procedure induces an outer approximation of $\overline{K}(X_i|\bm{y})$, and hence 
-	the upper approximation  of the maximum entropy 
-	$\overline{\overline{H}}(X|\bm{y})\geq\overline{H}(X|\bm{y})$. 
-	%With a small notation abuse such approximate value is also denoted as 
-	%$\overline{H}(X|\bm{y})$ and is regarded here as a measure of the informativeness 
-	%level 
-	%achieved for skill $X$ after the answers $\bm{y}$. 
-	Finally, to generalise Eq.~\ref{eq:strongext} to CNs, we define the information gain 
-	provided by a question $Y'$ for its background skill $X_{Y'}$ as 
-	$\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y})$ and 
-	select the question $\tilde{Y}'$ leading to the maximum information gain, i.e.,
-	\begin{equation}\label{eq:credalentropy}
-		\tilde{Y}' := \arg \max_{Y'\in\bm{Y}'} 
-		\bigl[
-		\overline{\overline{H}}(X_{Y'}|\bm{y})-\overline{\overline{H}}(X_{Y'}|Y',\bm{y}) 
-		\bigr]
-		\,.
-	\end{equation}
-	For the stopping criterion, as we do not consider the joint entropy over the skills, we 
-	separately require each $\overline{\overline{H}}(X_i|\bm{y})$ to be smaller than a 
-	threshold $\tilde{H}$. To be consistent with this choice, we remove from the set of 
-	questions to be selected, those whose background skills already satisfy this condition.
-
-	Note that the use of an outer approximation of the upper entropy affects only the 
-	question selection process (eventually making it sub-optimal), whereas it has no effect 
-	on the student evaluation given a set of answers.
-
-		\begin{theorem}
-		\begin{equation}
-			\max_{x}  \max \{ f(x) , g(x) \}  
-			=
-			\max \{ \max_{x'} f(x') , \max_{x''} g(x'') \} 
-		\end{equation}
-		Let 
-		$$y^{*}:=\max_x \max\{f(x),g(x)\}$$
-		$$y^{**}:= \max \{ \max_{x'} f(x') , \max_{x''} g(x'') \}$$
-		Say for instance that $y^{**}=max_x f(x)$ and let $x^{**}:=\arg\max_x f(x)$. Thus:
-		$$f(x^{**})\geq \max_{x'} g(x) \geq g(x^{**})$$
-
-		Let $x^{*}:= \arg\max_x \max\{f(x),g(x)\}$. 
-		It cannot be $y^{*}:=g(x^{*})$ as this would imply $g(x^{*}) \geq f(x^{*})$
-
-		%Assume ad absurdum $y^{*}\neq y^{**}$.
-
-		If $y^{*}:=f(x^{*})$ we should have $y^{*}=y^{**}$.
-		Vice versa,
-
-		or
-		%$y^{*}:=g(x^{*})$. In the first case 
-	\end{theorem}
-
+A new score for adaptive testing in Bayesian and credal networks has been proposed.
 \bibliographystyle{splncs04}
@@
 \end{document}
-
-\subsection*{Toy Example}
-	Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean 
-	question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is 
-	specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified 
-	instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The 
-	informativeness score we assign two the question is
-	\begin{equation}
-		\sigma_Q = H[S|Q]:=H[S|q_0]P(q_0)+H[S|q_1]P(q_1)\,.
-	\end{equation}
-	We have
-	\begin{equation}
-		P(q_1)=\pi_1 p + \pi_0 (1-p)
-	\end{equation}
-	while $P(q_0)=1-P(q_1)$ and also
-	\begin{equation}
-		P(s_1|q_1)=\frac{\pi_1 p}{\pi_1 p + \pi_0 (1-p)}=\frac{1}{1+\frac{\pi_0(1-p)}{\pi_1 p}}
-	\end{equation}
-	and
-	\begin{equation}
-		P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ 
-		(1-p)(1-\pi_0)}{p (1-\pi_1)}} 
-	\end{equation}
-	while $P(S=0|Q=1)$ by normalization. Accordingly:
-%	\begin{multline}
-%		\sigma_Q(p,\pi_0,\pi_1)=\\
-%		h \circ f[\gamma/l(p)] \cdot t +
-%		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
-%		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
-%		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
-%	\end{multline}
-	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
-	p + \pi_0 (1-p)$.
-
-	{\color{blue}{In other words:
-			$\sigma_Q(p,\pi_0,\pi_1):= G(\frac{1-p}{p} \frac{1-\pi_0}{1-\pi_1}) (1-p) + 
-			G(\frac{1-p}{p} \frac{\pi_0}{\pi_1}) p$}}
-
-	An alternative score might be achieved by replacing $h$ with $m$, i.e.,
-	\begin{equation}
-		\sigma_Q' := 
-		m \circ f[\gamma/l(p)] \cdot t +
-		m \circ f[\gamma'/l(p)] \cdot (1-t)\,
-	\end{equation}
-	As $f$ is monotone, we can commute $m$ and $f$ *** explain ***, i.e.,
-	\begin{equation}
-		\sigma_Q' := 
-		f \circ m[\gamma/l(p)] \cdot t +
-		f \circ m[\gamma'/l(p)] \cdot (1-t)\,
-	\end{equation}
-	with, as $\gamma>0$. $f \circ m[\gamma/l(p)] = f[\gamma m(l(p))]$
-	We can similarly define another score $\sigma_Q''$ based on $\tilde{i}_\epsilon$.
-	\subsection*{Explicit maximization}
-	$$H[S|Q]\simeq \sigma_Q' = \sum_q P(s^*(q)|q) P(q)$$
-	where $s^*(q):=\arg\max_s P(s|q)$. 
-	$$\sigma_Q'= \sum_q P(s^*(q),q) = \sum_q P(s^*(q) P(q|s^*(q))$$
-	Note that, if $s^*(q)$ is the same for each $q$, the score just corresponds to $P(s^*)$. 
-	In other words, the score is flat is each answer gives the same most likely skill level *** 
-	reasonable ***. Let us move to an imprecise setting and intend the $s^*$ state as
-	$s^*(q):=\arg\max_s \overline{P}(s|q)$. The objective function is a linear combination of 
-	$P(s*(q)$ whose coefficient can be optimized independently. Overall, this corresponds 
-	to a linear programming task.
-	$$\max_s \overline{P}(s,q) = \max_s \max_P P(s) P(q|s) = \max_s \overline{P}(s) 
-	\overline{P}(q|s)$$
-
-	\subsection*{Francesca's comments}
-
-	Comment1: This sentence is not clear to me:  "as $\gamma>0$. $f \circ m[\gamma/l(p)] 
-	= f[\gamma m(l(p))]$".\\
-	Comment2: How shall we use the Gumbel's trick
-
-	Comment 3: Below I obtain something that looks different to me, but maybe it is 
-	equivalent.
-
-	\begin{equation}
-		P(s_1|q_1)=\frac{\pi_1 p}{P(q_1)}
-	\end{equation}
-
-%	\begin{multline}
-%		\sigma_Q(p,\pi_0,\pi_1)=\\
-%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
-%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
-%	\end{multline}
-
-	But, as $P(q_1)\geq 0$, then
-%	\begin{multline}
-%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
-%		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
-%		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
-%		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
-%	\end{multline}
-
-	Similarly, as $1-P(q_1)\geq 0$, 
-%	\begin{multline}
-%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
-%		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
-%	\end{multline}
-
-	so that,
-
-%	\begin{multline}
-%		\sigma_Q(p,\pi_0,\pi_1)= \\
-%		2 max\{\pi_1 p, \pi_0 (1-p)\}+
-%		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
-%	\end{multline}
-
-	\subsection*{Formulae}
-	Let us define the functions, all defined for $x\in [0,1]$, apart from $f$ defines for each 
-	$x\geq 0$:
-	\begin{eqnarray}
-		f(x)&:=& \frac{1}{1+x},\,,\\
-		h(x)&:=&-x \cdot \log_2 x - (1-x)  \cdot \log_2 (1-x)\,,\\
-		l(x)&:=&\frac{x}{1-x}\,,\\
-		m(x)&:=&2 \max\{x,1-x\}\,,\\
-		i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
-		\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
-	\end{eqnarray}
-
-	Derivatives:
-	\begin{eqnarray}
-		f'(x)&:=& -\frac{1}{(1+x)^2},\,,\\
-		h'(x)&:=&\log_2 \frac{1-x}{x}\,\\
-		G(x) &:=& h \circ f(x)\,\\
-		G'(x) &:=& h[f(x)] f'(x)=-\frac{\log_2\frac{1-f(x)}{f(x)}}{(1+x)^2}\,\\
-		G'(x) &:=& -\frac{\log_2 x}{(1+x)^2}\,\\
-		l(x)&:=&\frac{x}{1-x}\,,\\
-		m(x)&:=&2 \max\{x,1-x\}\,,\\
-		i_\epsilon(x)&:=&\epsilon\log(e^{\frac{2x}{\epsilon}}+e^{\frac{2(1-x)}{\epsilon}})\,,\\
-		\tilde{i}_\epsilon(x)&:=&\frac{i_\epsilon(x)-i_\epsilon(0)}{i_\epsilon(\frac{1}{2})-i_\epsilon(0)}\,.
-	\end{eqnarray}
-
-A few remarks. Function $f$ is a monotonically decreasing function with values in 
-$[0,1]$. Function $h(x)$ corresponds to the entropy of a mass function over a Boolean 
-	variable with a probability equal to $x$. On the extreme points of its domain, we take 
-	the limit value, i.e., zero. The function is unimodal and achieve its maximum on  
-	$x=\frac{1}{2}$. Function $l$ is the popular \emph{logit} function, it is monotonically 
-	increasing function of $x$ and $l(1-x)=l(x)^-1$. Function $m(x)$ is $x$ for $x\geq 
-	\frac{1}{2}$ and $1-x$ otherwise. 
-	Exactly as $h$, functions $m$ and $\tilde{i}_\epsilon$, for each $\epsilon>0$, have the 
-	same (zero) value for $x=0$ and $x=1$, being all unimodal with maximum in 
-	$x=\frac{1}{2}$.
-	Finally, the popular Gumbel's trick implies:
-	\begin{equation}
-		\lim_{\epsilon \to 0} i_\epsilon(x)= 
-		\lim_{\epsilon \to 0} \tilde{i}_\epsilon(x)
-		= m(x)\,.
-	\end{equation}

### 2021-05-16 Results_1Skill/cat.py
Results 1Skill

@@ -1,0 +1,194 @@
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import style
+import matplotlib.patches as mpatches
+from tikzplotlib import save as tikz_save
+
+#directory = os.listdir(".")
+#for filename in directory:
+#	print(filename)
+n_students = 1024
+n_questions = 18
+
+profiles_csv = 'Minimalistic1x2x9.profiles.csv'
+profiles = pd.read_csv(profiles_csv,names=['pr'])
+
+head_c = ['s','skill','q','t','sc','a','l0','l1','u0','u1']
+head_b = ['s','skill','q','t','sc','a','p0','p1']
+
+c_mode_csv = 'Minimalistic1x2x9.progress.credal-adaptive-mode.eps01.csv'
+c_ent_csv = 'Minimalistic1x2x9.progress.credal-adaptive-entropy.eps01.csv'
+c_mode2_csv = 'Minimalistic1x2x9.progress.credal-adaptive-mode.csv'
+c_ent2_csv = 'Minimalistic1x2x9.progress.credal-adaptive-entropy.csv'
+b_ran_csv = 'Minimalistic1x2x9.progress.bayesian-non-adaptive.csv'
+b_mode_csv = 'Minimalistic1x2x9.progress.bayesian-adaptive-mode.csv'
+b_ent_csv = 'Minimalistic1x2x9.progress.bayesian-adaptive-entropy.csv'
+b_pr_csv = 'Minimalistic1x2x9.progress.bayesian-adaptive-pright.csv'
+c_pr_csv = 'Minimalistic1x2x9.progress.credal-adaptive-pright.csv'
+
+c_mode = pd.read_csv(c_mode_csv,names=head_c)
+c_ent = pd.read_csv(c_ent_csv,names=head_c)
+c_mode2 = pd.read_csv(c_mode2_csv,names=head_c)
+c_ent2 = pd.read_csv(c_ent2_csv,names=head_c)
+c_pr = pd.read_csv(c_pr_csv,names=head_c)
+b_ran = pd.read_csv(b_ran_csv,names=head_b)
+b_mode = pd.read_csv(b_mode_csv,names=head_b)
+b_ent = pd.read_csv(b_ent_csv,names=head_b)
+b_pr = pd.read_csv(b_pr_csv,names=head_b)
+
+nn1 = np.zeros(n_questions+1)
[…]
